% introduce new LaTeX macros only used within Quill documentation files,
% such that if the files are removed, so are the LaTeX macros
\newcommand{\QuillMacroNI}[1]{\texttt{#1}}      % Quill file macro, NO index
\newcommand{\QuillMacro}[1]{\texttt{#1}  \index{Quill source code contrib configuration macro!\texttt{#1}}}  % Quill file macro and index
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:Quill}Quill}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{Quill contrib|(}
\index{HTCondor daemon, source code contrib!condor\_quill@\Condor{quill}}
\index{condor\_quill source code contrib daemon}
\index{HTCondor daemon, source code contrib!condor\_dbmsd@\Condor{dbmsd}}
\index{condor\_dbmsd source code contrib daemon}
Quill is an optional component of HTCondor that maintains a mirror 
of HTCondor operational data
in a relational database.  The \Condor{quill} daemon updates
the data in the relation database, and the \Condor{dbmsd} daemon
maintains the database itself.

As of HTCondor version 7.5.5,
Quill is distributed only with the source code.
It is not included in the builds of HTCondor provided by UW,
but it is available as a feature that can be enabled by those who compile
HTCondor from the source code.
Find the code within the \File{condor\_contrib} directory, 
in the directories \File{condor\_tt} and \File{condor\_dbmsd}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:Quill-Installation}Installation and Configuration}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Quill uses the \Prog{PostgreSQL} database management system.
Quill uses the \Prog{PostgreSQL} server as its back end
and client library, 
\Prog{libpq} to talk to the server.
We \Bold{strongly recommend} the use of version 
8.2 or later due to its integrated facilities of certain key 
database maintenance tasks, and stronger security features.

Obtain \Prog{PostgreSQL} from

\URL{http://www.postgresql.org/ftp/source/}

Installation instructions are detailed in:
\URL{http://www.postgresql.org/docs/8.2/static/installation.html}

Configure \Prog{PostgreSQL} after installation:

\begin{enumerate}

\item Initialize the database with the \Prog{PostgreSQL} command 
\verb@initdb@.

\item Configure to accept TCP/IP connections.
For \Prog{PostgreSQL} version 8,
use the \Code{listen\_addresses} variable in 
\File{postgresql.conf} file as a guide.
For example,
\Code{listen\_addresses = '*'}
means listen on any IP interface.

\item Configure automatic vacuuming.
Ensure that these variables with these defaults are
commented in and/or set properly in the 
\File{postgresql.conf} configuration file:
\begin{verbatim}
# Turn on/off automatic vacuuming
autovacuum = on

# time between autovacuum runs, in secs
autovacuum_naptime = 60

# min # of tuple updates before vacuum
autovacuum_vacuum_threshold = 1000

# min # of tuple updates before analyze
autovacuum_analyze_threshold = 500

# fraction of rel size before vacuum
autovacuum_vacuum_scale_factor = 0.4 

# fraction of rel size before analyze
autovacuum_analyze_scale_factor = 0.2

# default vacuum cost delay for 
   # autovac, -1 means use 
   # vacuum_cost_delay
autovacuum_vacuum_cost_delay = -1  

# default vacuum cost limit for 
   # autovac, -1 means use
   # vacuum_cost_limit
autovacuum_vacuum_cost_limit = -1   
\end{verbatim}


\item Configure \Prog{PostgreSQL} to accept TCP/IP connections from 
specific hosts.
Modify the \File{pg\_hba.conf} file 
(which usually resides in the \Prog{PostgreSQL} server's data directory).
Access is required by the \Condor{quill} daemon,
as well as the database users
\Username{quillreader} and \Username{quillwriter}.
For example, to give
database users \Username{quillreader} and \Username{quillwriter}
password-enabled access to all databases on current machine from any
machine in the 128.105.0.0/16 subnet, add the following:

\begin{tabular}{llllll}
host&all&quillreader&128.105.0.0&255.255.0.0&md5\\
host&all&quillwriter&128.105.0.0&255.255.0.0&md5
\end{tabular}

Note that in addition to the database specified by
the configuration variable \QuillMacroNI{QUILL\_DB\_NAME},
the \Condor{quill} daemon also needs access to the database
"template1".
In order to create the database in the first place, 
the \Condor{quill} daemon needs to connect to the database.

\item Start the \Prog{PostgreSQL} server service. See the
installation instructions for the appropriate method to start the service at
\URL{http://www.postgresql.org/docs/8.2/static/installation.html}

\item The \Condor{quill} and \Condor{dbmsd} daemons and client tools connect
to the database as users \Username{quillreader} and 
\Username{quillwriter}.
These are database users, not operating system users.
The two types of users are quite different from each other.
If these database users do not exist,
add them using the 
\Prog{createuser} command supplied with the installation.
Assign them with appropriate passwords;
these passwords will be used by the Quill tools to connect
to the database in a secure way.
User \Username{quillreader} should not be allowed to create
more databases nor create more users.
User \Username{quillwriter} should
not be allowed to create more users,
however it should be allowed to create more databases.
The following commands create the two users
with the appropriate permissions,
and be ready to enter the corresponding passwords when prompted.

\footnotesize
\begin{verbatim}
/path/to/postgreSQL/bin/directory/createuser quillreader \
	--no-createdb --no-createrole --pwprompt

/path/to/postgreSQL/bin/directory/createuser quillwriter \
	--createdb --no-createrole --pwprompt
\end{verbatim}
\normalsize

Answer ``no'' to the question about the ability for role creation.

\item Create a database for Quill to store data in
with the \verb@createdb@ command. 
Create this database with the \Username{quillwriter} user as the owner.
A sample command to do this is
\footnotesize
\begin{verbatim}
createdb -O quillwriter quill
\end{verbatim}
\normalsize
\verb@quill@ is the database name to use with the \QuillMacroNI{QUILL\_DB\_NAME}
configuration variable.

\item The \Condor{quill} and \Condor{dbmsd} daemons need read and write access
to the database.
They connect as user \Username{quillwriter},
which has owner privileges to the database.
Since this gives all access to the \Username{quillwriter} user,
its password cannot be stored in a public place 
(such as in a ClassAd).
For this reason, the \Username{quillwriter} password is stored
in a file named \File{.pgpass} in the HTCondor spool directory.
Appropriate protections on this file guarantee secure access to the database.
This file must be created and protected by the site administrator;
if this file does not exist as and where expected, the \Condor{quill}
and \Condor{dbmsd} daemons log an error and exit.
The \File{.pgpass} file contains a single line that
has fields separated by colons and is properly terminated by
an operating system specific newline character (Unix) or CRLF (Windows).
The first field may be either the machine name and fully qualified domain,
or it may be a dotted quad IP address.
This is followed by four fields containing:
the TCP port number, 
the name of the database,
the "quillwriter" user name,
and the password.
The form used in the first field must exactly match the value set for 
the configuration variable \QuillMacro{QUILL\_DB\_IP\_ADDR}.
HTCondor uses a string comparison between the two, and it does not resolve the
host names to compare IP addresses.
Example:
\footnotesize
\begin{verbatim}
machinename.cs.wisc.edu:5432:quill:quillwriter:password
\end{verbatim}
\normalsize

\end{enumerate}

After the \Prog{PostgreSQL} database is initialized and running, 
the Quill schema
must be loaded into it.  First, load the plsql programming language
into the server:

\begin{verbatim}
createlang plpgsql [databasename]
\end{verbatim}

Then, load the Quill schema from the sql files in the \File{sql} subdirectory
of the HTCondor release directory:

\begin{verbatim}
psql [databasename] [username] < common_createddl.sql
psql [databasename] [username] < pgsql_createddl.sql
\end{verbatim}
where \verb@[username]@ will be \verb@quillwriter@.


After \Prog{PostgreSQL} is configured and running, HTCondor must also be
configured to use Quill, since by default Quill is configured to be off.

\begin{description}
\item Add the file \File{.pgpass} to the 
  \QuillMacroNI{VALID\_SPOOL\_FILES} variable, since \Condor{preen} must
  be told not to delete this file.
  This step may not be necessary, depending on which version of HTCondor 
  you are upgrading from. 
 
\item Set up configuration variables that are specific to the installation,
and check that the \QuillMacroNI{HISTORY} variable is set.
\footnotesize
\begin{verbatim}
HISTORY                 = $(SPOOL)/history
QUILL_ENABLED           = TRUE
QUILL_USE_SQL_LOG       = FALSE
QUILL_NAME              = some-unique-quill-name.cs.wisc.edu
QUILL_DB_USER           = quillwriter
QUILL_DB_NAME           = database-for-some-unique-quill-name
QUILL_DB_IP_ADDR        = databaseIPaddress:port
# the following parameter's units is in seconds
QUILL_POLLING_PERIOD    = 10
QUILL_HISTORY_DURATION 	= 30
QUILL_MANAGE_VACUUM     = FALSE
QUILL_IS_REMOTELY_QUERYABLE = TRUE
QUILL_DB_QUERY_PASSWORD =  password-for-database-user-quillreader
QUILL_ADDRESS_FILE      = $(LOG)/.quill_address
QUILL_DB_TYPE           = PGSQL
# The Purge and Reindex intervals are in seconds
DATABASE_PURGE_INTERVAL	= 86400
DATABASE_REINDEX_INTERVAL = 86400
# The History durations are all in days 
QUILL_RESOURCE_HISTORY_DURATION  = 7
QUILL_RUN_HISTORY_DURATION = 7
QUILL_JOB_HISTORY_DURATION = 3650
#The DB Size limit is in gigabytes
QUILL_DBSIZE_LIMIT      = 20
QUILL_MAINTAIN_DB_CONN  = TRUE
SCHEDD_SQLLOG           = $(LOG)/schedd_sql.log
SCHEDD_DAEMON_AD_FILE   = $(LOG)/.schedd_classad

\end{verbatim}
\normalsize

\end{description}

The default HTCondor configuration file should already contain definitions
for \QuillMacroNI{QUILL} and \QuillMacroNI{QUILL\_LOG}.  
When upgrading from a previous version that did not have Quill to
a new one that does, define these two configuration variables.

Only one machine should run the \Condor{dbmsd} daemon.  
On this machine, add it to the \QuillMacroNI{DAEMON\_LIST} configuration variable.
All Quill-enabled machines should also run the \Condor{quill} daemon.
The machine running the \Condor{dbmsd} daemon can also 
run a \Condor{quill} daemon.  An example \QuillMacroNI{DAEMON\_LIST}
for a machine running both daemons,
and acting as both a submit machine and a central manager might 
look like the following:

\footnotesize
\begin{verbatim}
DAEMON_LIST  = MASTER, SCHEDD, COLLECTOR, NEGOTIATOR, DBMSD, QUILL
\end{verbatim}
\normalsize

The \Condor{dbmsd} daemon will need configuration file entries
common to all daemons.
If not already in the configuration file, add the following entries:

\begin{verbatim}
DBMSD = $(SBIN)/condor_dbmsd
DBMSD_ARGS = -f
DBMSD_LOG = $(LOG)/DbmsdLog
MAX_DBMSD_LOG = 10000000
\end{verbatim}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\label{sec:Quill-Config}Configuration Variables}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\index{configuration of source code contrib!Quill configuration variables}
These macros affect the Quill database
management and interface to its representation of the job queue.

\begin{description}
\label{param:Quill}
\item[\QuillMacro{QUILL}]
  The full path name to the \Condor{quill} daemon.

\label{param:QuillArgs}
\item[\QuillMacro{QUILL\_ARGS}]
  Arguments to be passed to the \Condor{quill} daemon upon its invocation.

\label{param:QuillLog}
\item[\QuillMacro{QUILL\_LOG}]
  Path to the Quill daemon's log file.

\label{param:QuillEnabled}
\item[\QuillMacro{QUILL\_ENABLED}]
  A boolean variable that defaults to \Expr{False}.
  When \Expr{True}, Quill functionality is enabled.
  When \Expr{False}, the Quill daemon writes a message to its log and exits.
  The \Condor{q} and \Condor{history} tools then do not use Quill.

\label{param:QuillName}
\item[\QuillMacro{QUILL\_NAME}]
  A string that uniquely identifies an instance of the \Condor{quill}
  daemon, as there may be more than \Condor{quill} daemon per pool.
  The string must not be the same as for any \Condor{schedd} daemon.

  See the description of \QuillMacroNI{MASTER\_NAME} in
  section~\ref{param:MasterName} on page~\pageref{param:MasterName}
  for defaults and composition of valid HTCondor daemon names.

\label{param:QuillUseSQLLog}
\item[\QuillMacro{QUILL\_USE\_SQL\_LOG}]
  In order for Quill to store historical job information or resource
  information, the HTCondor daemons must write information to the SQL logfile.
  By default, this is set to \Expr{False}, and the only information Quill
  stores in the database is the current job queue.
  This can be set on a per daemon basis. For example, to store information
  about historical jobs, but not store execute resource information, set
  \QuillMacroNI{QUILL\_USE\_SQL\_LOG} to \Expr{False} and set
  \QuillMacroNI{SCHEDD.\_QUILL\_USE\_SQL\_LOG} to \Expr{True}.

\label{param:QuillDBName}
\item[\QuillMacro{QUILL\_DB\_NAME}]
  A string that identifies a database within a database server.

\label{param:QuillDBUser}
\item[\QuillMacro{QUILL\_DB\_USER}] 
  A string that identifies the \Prog{PostgreSQL} user that Quill 
  will connect as to the database.
  We recommend \Username{quillwriter} for this setting. 
  There is no default setting for \QuillMacroNI{QUILL\_DB\_USER}, 
  so it must be specified in the configuration file. 

\label{param:QuillDBType}
\item[\QuillMacro{QUILL\_DB\_TYPE}]
  A string that distinguishes between database system types.
  Defaults to the only database system currently defined,
  \verb@"PGSQL"@.

\label{param:QuillDBIPAddr}
\item[\QuillMacro{QUILL\_DB\_IP\_ADDR}]
  The host address of the database server. It can be either an IP address
  or an IP address.
  It must match exactly what is used in the \File{.pgpass} file.
  More than one Quill server can talk to the same database
  server.  This can be accomplished by letting all the 
  \QuillMacroNI{QUILL\_DB\_IP\_ADDR} values point to the same database server.

\label{param:QuillPollingPeriod}
\item[\QuillMacro{QUILL\_POLLING\_PERIOD}]
  The frequency, in number of seconds, at which the Quill daemon
  polls the file \File{job\_queue.log} for updates.
  New information in the log file is sent to the database.
  The default value is 10.
  Since Quill works by periodically sniffing the log file for updates and 
  then sending those updates to the database, 
  this variable controls the trade off between the currency of query results 
  and Quill's load on the system, which is usually negligible.

\label{param:QuillNotRespondingTimeout}
\item[\QuillMacro{QUILL\_NOT\_RESPONDING\_TIMEOUT}]
  The length of time, in seconds, before the \Condor{master}
  may decide that the \Condor{quill} daemon is hung due to 
  a lack of communication,
  potentially causing  the \Condor{master} to kill and
  restart the \Condor{quill} daemon.
  When the \Condor{quill} daemon is processing a very long log file, it 
  may not be able to communicate with the master. 
  The default is 3600 seconds, or one hour. It may be
  advisable to increase this to several hours. 

\label{param:QuillMaintainDBConn}
\item[\QuillMacro{QUILL\_MAINTAIN\_DB\_CONN}]
  A boolean variable that defaults to \Expr{True}.
  When \Expr{True}, the \Condor{quill} daemon
  maintains an open connection the database server,
  which speeds up updates to the database.
  As each open connection consumes resources at the database server,
  we recommend a setting of \Expr{False} for large pools.

\label{param:QuillDatabasePurgeInterval}
\item[\QuillMacro{DATABASE\_PURGE\_INTERVAL}] 
  The interval, in seconds, between scans of the database to identify and
  delete records that are beyond their history durations. 
  The default value is 86400, or one day.

\label{param:QuillJobHistoryDuration}
\item[\QuillMacro{QUILL\_JOB\_HISTORY\_DURATION}]
  The number of days after entry into the database that a job will
  remain in the database.
  After \QuillMacroNI{QUILL\_JOB\_HISTORY\_DURATION} days, the job is deleted.
  The job history is the final ClassAd, and contains all information 
  necessary for \Condor{history} to succeed.
  The default is 3650, or about 10 years. 

\label{param:QuillRunHistoryDuration}
\item[\QuillMacro{QUILL\_RUN\_HISTORY\_DURATION}]
  The number of days after entry into the database that extra information 
  about the job will remain in the database.
  After \QuillMacroNI{QUILL\_RUN\_HISTORY\_DURATION} days, the records are deleted.
  This data includes matches made for the job, file transfers the job 
  performed, and user log events.
  The default is 7 days, or one week. 

\label{param:QuillResourceHistoryDuration}
\item[\QuillMacro{QUILL\_RESOURCE\_HISTORY\_DURATION}]
  The number of days after entry into the database that a resource record will
  remain in the database.
  After \QuillMacroNI{QUILL\_RESOURCE\_HISTORY\_DURATION} days, the record is 
  deleted.
  The resource history data includes the ClassAd of a compute slot,
  submitter ClassAds, and daemon ClassAds.
  The default is 7 days, or one week. 

\label{param:QuillDBSizeLimit}
\item[\QuillMacro{QUILL\_DBSIZE\_LIMIT}]
  At intervals of time set by \QuillMacroNI{DATABASE\_PURGE\_INTERVAL},
  the \Condor{quill} daemon estimates the size of the database. 
  If the size of the database exceeds the limit set by this variable, 
  the \Condor{quill} daemon will e-mail the administrator a warning. 
  This size is given in Gbytes, and defaults to 20. 

\label{param:QuillManageVacuum}
\item[\QuillMacro{QUILL\_MANAGE\_VACUUM}]
  A boolean value that defaults to \Expr{False}.
  When \Expr{True}, the \Condor{quill} daemon takes on 
  the maintenance task of vacuuming the database.
  As of \Prog{PostgreSQL} version 8.1, the database
  can perform this task automatically; 
  therefore, having the \Condor{quill} daemon vacuum is not necessary.
  A value of \Expr{True} causes warnings to be written to the log file.

\label{param:QuillShouldReindex}
\item[\QuillMacro{QUILL\_SHOULD\_REINDEX}]
  A boolean value that defaults to \Expr{True}.
  When \Expr{True}, the \Condor{quill} daemon will re-index the database
  tables when the history file is purged of old data. So, if Quill is
  configured to never delete history data, the tables are never re-indexed.

\label{param:QuillDatabaseReindexInterval}
\item[\QuillMacro{DATABASE\_REINDEX\_INTERVAL}] 
  Because \Prog{PostgreSQL} does not aggressively maintain the index 
  structures for deleted tuples, it can lead to bloated index structures.
  This variable is the interval, in seconds, 
  between re-index commands on the database.
  The default value is 86400, or one day.
  This is only used when the \QuillMacroNI{QUILL\_DB\_TYPE} is set to
  \verb@"PGSQL"@.

\label{param:QuillIsRemotelyQueryable}
\item[\QuillMacro{QUILL\_IS\_REMOTELY\_QUERYABLE}]
  A boolean value that defaults to \Expr{True}.
  Thanks to \Prog{PostgreSQL},
  one can now remotely query both the job queue and the history tables. 
  This variable controls whether this remote querying 
  feature should be enabled.  
  Note that even if \Expr{False}, one can still query the job queue 
  at the remote \Condor{schedd} daemon.

\label{param:QuillDBQueryPassword}
\item[\QuillMacro{QUILL\_DB\_QUERY\_PASSWORD}]
  Defines the password string needed by \Condor{q} to gain read
  access for remotely querying the Quill database.
  In order for the query tools to connect to a database, 
  they need to provide the password that is assigned to the 
  database user \Username{quillreader}. 
  This variable is then advertised by the \Condor{quill} daemon
  to the \Condor{collector}.  
  This facility enables remote querying: remote \Condor{q} query tools first 
  ask the \Condor{collector} for
  the password associated with a particular Quill database, 
  and then query that database.  
  Users who do not have access to the \Condor{collector} 
  cannot view the password, and as such cannot query the database.

\label{param:QuillAddressFile}
\item[\QuillMacro{QUILL\_ADDRESS\_FILE}]
  When defined, it specifies the path and file name of a local file
  that contains the IP address and port number of the Quill daemon.
  By using the file, tools executed on the local machine do not need
  to query the central manager in order to find the \Condor{quill} daemon.

\label{param:DBMSD} 
\item[\QuillMacro{DBMSD}]
  The full path name to the \Condor{dbmsd} daemon.
  The default location is \File{\$(SBIN)/condor\_dbmsd}.

\label{param:DBMSDArgs}
\item[\QuillMacro{DBMSD\_ARGS}]
  Arguments to be passed to the \Condor{dbmsd} daemon upon its invocation.
  The default arguments are \verb@-f@.

\label{param:DBMSDLog}
\item[\QuillMacro{DBMSD\_LOG}]
  Path to the \Condor{dbmsd} daemon's log file.
  The default log location is \File{\$(LOG)/DbmsdLog}.

\label{param:DBMSDNotRespondingTimeout}
\item[\QuillMacro{DBMSD\_NOT\_RESPONDING\_TIMEOUT}]
  The length of time, in seconds, before the \Condor{master}
  may decide that the \Condor{dbmsd} is hung due to a lack of communication,
  potentially causing  the \Condor{master} to kill and
  restart the \Condor{dbmsd} daemon.
  When the \Condor{dbmsd} is purging or re-indexing a very large database, 
  it may not be able to communicate with the master. 
  The default is 3600 seconds, or one hour. 
  It may be advisable to increase this to several hours. 

\end{description}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:Quill-Example}Four Usage Examples}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{enumerate}
\item Query a remote Quill daemon on \File{regular.cs.wisc.edu}
for all the jobs in the queue
\begin{verbatim}
	condor_q -name quill@regular.cs.wisc.edu
	condor_q -name schedd@regular.cs.wisc.edu

\end{verbatim}
There are two ways to get to a Quill daemon: directly using its name as 
specified in the \QuillMacroNI{QUILL\_NAME} configuration variable, or indirectly
by querying the \Condor{schedd} daemon using its name.
In the latter case, \Condor{q} will detect 
if that \Condor{schedd} daemon is being serviced by a database, and if so, directly query it.
In both cases, the IP address and port of the database server hosting the data of 
this particular remote Quill daemon can be figured out by the \QuillMacroNI{QUILL\_DB\_IP\_ADDR} 
and \QuillMacroNI{QUILL\_DB\_NAME} variables specified in the \QuillMacroNI{QUILL\_AD}
sent by the quill daemon to the collector and in the \QuillMacroNI{SCHEDD\_AD} sent by
the \Condor{schedd} daemon.  

\item Query a remote Quill daemon on \File{regular.cs.wisc.edu} for all historical 
jobs belonging to owner einstein.
\begin{verbatim}
	condor_history -name quill@regular.cs.wisc.edu einstein
\end{verbatim}

\item Query the local Quill daemon for the average time spent in the queue 
for all non-completed jobs. 
\begin{verbatim}
	condor_q -avgqueuetime 
\end{verbatim}
The average queue time is defined as the average of
\Expr{(currenttime - jobsubmissiontime)} over all jobs which are neither
completed \Expr{(JobStatus == 4)} or removed \Expr{(JobStatus == 3)}.

\item Query the local Quill daemon for all historical jobs completed since 
Apr 1, 2005 at 13h 00m.
\begin{verbatim}
	condor_history -completedsince '04/01/2005 13:00'
\end{verbatim}
It fetches all jobs
which got into the 'Completed' state on or after the
specified time stamp.  It use the \Prog{PostgreSQL} date/time
syntax rules, as it encompasses most format options.  See
\URL{http://www.postgresql.org/docs/8.2/static/datatype-datetime.html}
for the various time stamp formats.

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:Quill-Security}Quill and Security}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

There are several layers of security in Quill, some provided by HTCondor and
others provided by the database.  First, all accesses to the database
are password-protected.

\begin{enumerate}
\item The query tools, \Condor{q} and
\Condor{history} connect to the database as user \Username{quillreader}.
The password for this user can vary from one database to another and
as such, each Quill daemon advertises this password to the collector.
The query tools then obtain this password from the collector and
connect successfully to the database.  Access to the database by the
\Username{quillreader} user is read-only, as this is sufficient for the
query tools.  The \Condor{quill} daemon ensures this protected access using the sql
GRANT command when it first creates the tables in the database.  Note that
access to the \Username{quillreader} password itself can be blocked by
blocking access to the collector, a feature already supported in HTCondor.

\item The \Condor{quill} and \Condor{dbmsd} daemons, on the other hand,
need read and write access to the database.
As such, they connect as user \Username{quillwriter},
who has owner privileges to the database.  Since this gives all
access to the \Username{quillwriter} user, this password cannot
be stored in a public place (such as the collector).  For this
reason, the \Username{quillwriter} password is stored in a file called
\File{.pgpass} in the HTCondor spool directory.
Appropriate protections on this file guarantee secure access to the database.
This file must be created and protected by the site administrator;
if this file does not exist as and where expected, the \Condor{quill}
daemon logs an error and exits.

\item The \Attr{IsRemotelyQueryable} attribute in the Quill ClassAd advertised
by the Quill daemon to the collector can be used by site administrators
to disallow the database from being read by all remote HTCondor query tools.

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:Quill-Schema}Quill and Its RDBMS Schema}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{contrib/quill-schema.tex}

\index{Quill contrib|)}
