%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:Absent-Ads}Absent ClassAds}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{pool management!absent ClassAds}
\index{absent ClassAd}
\index{ClassAd!absent ClassAd}

By default, HTCondor assumes that resources are transient: 
the \Condor{collector}
will discard ClassAds older than \Macro{CLASSAD\_LIFETIME} seconds.
Its default configuration value is 15 minutes, 
and as such, the default value for \Macro{UPDATE\_INTERVAL} will 
pass three times before HTCondor forgets about a resource.
In some pools, especially those with dedicated resources, 
this approach may make it unnecessarily difficult to determine 
what the composition of the pool ought to be, 
in the sense of knowing which machines would be in the pool,
if HTCondor were properly functioning on all of them.

This assumption of transient machines can be modified by 
the use of absent ClassAds.  
When a machine ClassAd would otherwise expire, 
the \Condor{collector} evaluates the configuration variable
\Macro{ABSENT\_REQUIREMENTS} against the machine ClassAd.
If \Expr{True}, 
the machine ClassAd will be saved in a persistent manner and 
be marked as absent;
this causes the machine to appear in the output of 
\Expr{condor\_status -absent}.
When the machine returns to the pool, 
its first update to the \Condor{collector} will 
invalidate the absent machine ClassAd.

Absent ClassAds, like offline ClassAds, 
are stored to disk to ensure that they are remembered,
even across \Condor{collector} crashes.
The configuration variable \Macro{COLLECTOR\_PERSISTENT\_AD\_LOG}
defines the file in which the ClassAds are stored,
and replaces the no longer used variable \MacroNI{OFFLINE\_LOG}.
Absent ClassAds are retained on disk as maintained by 
the \Condor{collector} for a length of time in seconds defined by the
configuration variable \Macro{ABSENT\_EXPIRE\_ADS\_AFTER}.
A value of 0 for this variable means that the ClassAds are never discarded,
and the default value is thirty days.

Absent ClassAds are only returned by the \Condor{collector} and displayed
when the \Opt{-absent} option to \Condor{status} is specified,
or when the absent machine ClassAd attribute is mentioned on 
the \Condor{status} command line.  
This renders absent ClassAds invisible to the rest of 
the HTCondor infrastructure.

A daemon may inform the \Condor{collector} that the daemon's
ClassAd should not expire, but should be removed right away;
the daemon asks for its ClassAd to be invalidated.
It may be useful to place an invalidated ClassAd in the absent state,
instead of having it removed as an invalidated ClassAd.
An example of a ClassAd that could benefit from being absent
is a system with an uninterruptible power supply that shuts
down cleanly but unexpectedly as a result of a power outage.
To cause all invalidated ClassAds to become absent instead of invalidated, 
set \Macro{EXPIRE\_INVALIDATED\_ADS} to \Expr{True}.
Invalidated ClassAds will instead be treated as if they expired, 
including when evaluating \MacroNI{ABSENT\_REQUIREMENTS}.
