%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:GCB}Generic Connection Brokering (GCB)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{GCB (Generic Connection Brokering)}

Generic Connection Brokering, or GCB, is a system for managing network
connections across private network and firewall boundaries.
Starting with Condor version 6.7.13,
Condor's Linux releases are linked with GCB,
and can use GCB functionality to run jobs
(either directly or via flocking)
on pools that span public and private networks.

While GCB provides numerous advantages over restricting Condor to use
a range of ports which are then opened on the firewall (see
section~\ref{sec:Ports-Firewalls} on
page~\pageref{sec:Ports-Firewalls}),
GCB is also a very complicated system, with major
implications for Condor's networking and security functionality.
Therefore, sites must carefully weigh the 
advantages and disadvantages
of attempting
to configure and use GCB before making a decision.

Advantages:
\begin{itemize}

\item Better connectivity. GCB works with pools that have multiple
  private networks (even multiple private networks that use the same
  IP addresses (for example, 192.168.2.*).
  GCB also works with sites that use network address translation
  (NAT). 

\item More secure. Administrators never need to allow inbound
  connections through the firewall.
  With GCB, only outbound connections from behind the firewall must be
  allowed (which is a standard firewall configuration).
  It is possible to trade decreased performance for better security, and
  configure the firewall to only allow outbound connections to a
  single public IP address.

\item Does not require \Login{root} access to any machines.
  All parts of a GCB system can be run as an unprivileged user, and in
  the common case, no changes to the firewall configuration are
  required.

\end{itemize}

Disadvantages:
\begin{itemize}

\item The GCB broker 
  (section~\ref{sec:GCB-Broker-Intro} describes the broker)
  node(s) is a potential failure point to the pool.
  Any private nodes that want to communicate outside their own network
  must be represented by a GCB broker.
  This machine must be highly reliable, since if the broker is ever
  down, all inbound communication with the private nodes is
  impossible.
  Furthermore, no other Condor services should be run on a GCB broker
  (for example, the Condor pool's central manager).
  While it is possible to do so, it is not recommended.
  In general, no other services should be run on the machine at all,
  and the host should be dedicated to the task of serving as a GCB
  broker.

\item All Condor nodes behind a given firewall share a single IP
  address (the public IP address of their GCB broker).
  All Condor daemons using a GCB broker will advertise themselves with
  this single IP address, and in some cases, connections to/from those
  daemons will actually originate at the broker.
  This has implications for Condor's host/IP based security,
  and the general level of confusion for users and
  administrators of the pool.
  Debugging problems will be more difficult, as any log messages which 
  only print the IP address (not the name and/or port) will become ambiguous.
  Even log or error messages that include the port will not necessarily
  be helpful, as it is difficult to correlate ports on the broker
  with the corresponding private nodes.
  
\item Can not function with Kerberos authentication.
  Kerberos tickets include the IP address of the machine where they
  were created.
  However, when Condor daemons are using GCB, they use a different IP
  address, and therefore, any attempt to authenticate
  using Kerberos will fail, as Kerberos will consider this a (poor)
  attempt to fool it into using an invalid host principle.

\item Scalability and performance degradation: 
  \begin{itemize}
  \item Connections are more expensive to establish.
  \item In some cases, connections must be forwarded through a proxy
    server on the GCB broker.
  \item Each network port on each private node must correspond to a
    unique port on the broker host, so there is a fixed limit to how
    many private nodes a given broker can service (which is a function
    of the number of ports each private node requires and the total
    number of available ports on the broker).
  \item Each private node must maintain an open TCP connection to its
    GCB broker.  GCB will attempt to recover in the case of the socket
    being closed, but this means the broker must have at least as many
    sockets open as there are private nodes.
  \end{itemize}

\item It is more complex to configure and debug.

\end{itemize}

Given the increased complexity, use of GCB requires a careful
read of this entire manual section, followed by a thorough
installation.
%% Derek's use of non-subtle advice:
%% Please do not skim the information in this section, attempt to quickly
%% install GCB, and then ask for help when things go wrong.

Details of GCB and how it works can be found at the GCB
homepage:

\URL{http://www.cs.wisc.edu/\~{}sschang/firewall/gcb}

This information is useful for understanding the technical
details of how GCB works, and the various parts of the system.
While some of the information is partly out of date (especially the
discussion of how to configure GCB) most of the sections are perfectly
accurate and worth reading.
Ignore the section on ``GCBnize'', which describes
how to get a given application to use GCB, as 
the Linux port of all Condor daemons and tools have already 
been converted to use GCB.



The rest of this section gives the details for configuring a
Condor pool to use GCB.
It is divided into the following topics:

\begin{itemize}
\item Introduction to the GCB broker
\item Configuring the GCB broker
\item Spawning a GCB broker (with a \Condor{master} or using \Prog{initd})
\item How to configure Condor machines to use GCB
\item Configuring the GCB routing table
\item Implications for Condor's host/IP security settings
\item Implications for other Condor configuration settings
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\label{sec:GCB-Broker-Intro}Introduction to the GCB Broker}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\index{GCB (Generic Connection Brokering)!broker}
\index{GCB (Generic Connection Brokering)!inagent}
At the heart of GCB is a logical entity known as a \Term{broker} or
\Term{inagent}.
In reality, the entity is made up of daemon
processes running on
the same machine comprised of the \Prog{gcb\_broker} and a set of
\Prog{gcb\_relay\_server} processes, each one spawned by the
\Prog{gcb\_broker}.

Every private network using GCB
must have at least one broker to arrange connections.
%Every private network in a given network topology trying to use GCB
%must have at least one corresponding broker to arrange connections for it.
The broker must be installed on a machine that nodes in both the
public and the private (firewalled) network can directly talk to.
The broker need not be able to initiate connections to the
private nodes.  
It can take advantage of the case where it can
initiate connections to the private nodes, and that will improve
performance. 
The broker is generally installed on a 
machine with multiple network interfaces
(on the network boundary) or just outside
of a network that allows outbound connections.
If the private network contains many hosts, sites can configure
multiple GCB brokers, and partition the private nodes so that different
subsets of the nodes use different brokers.

For a more thorough explanation of what a GCB broker is, check out:
\URL{http://www.cs.wisc.edu/\~{}sschang/firewall/gcb/mechanism.htm}

A GCB broker should generally be installed on a dedicated machine.
These are machines that are not running other Condor daemons or services.
If running any other Condor service 
(for example, the central manager of the pool)
on the same machine as the GCB broker,
all other machines attempting
to use this Condor service
(for example, to connect to the \Condor{collector} or \Condor{negotiator})
will incur additional connection costs and latency.
It is possible that future versions of GCB and Condor will be able to
overcome these limitations, but for now, we recommend that a broker
is run on a dedicated machine with no other Condor daemons (except
perhaps a single \Condor{master} used to spawn the \Prog{gcb\_broker}
daemon, as described below).

In principle, a GCB broker is a network element that functions almost
like a router.
It allows certain connections through the firewall by redirecting
connections or forwarding connections.
In general, it is not a good idea to run a lot of other services on
the network elements, especially not services like Condor which can
spawn arbitrary jobs.
Furthermore, the GCB broker relies on listening to many network
ports.
If other applications are running on the same host as the broker,
problems exist
where the broker does not have enough network
ports available to forward all the connections that might be required
of it.
Also, all nodes inside a private network rely on the GCB broker for
all incoming communication.
For performance reasons, avoid forcing the GCB broker to
contend with other processes for system resources, such that it is always
available to handle communication requests.
There is nothing in GCB or Condor requiring
the broker to run on a separate machine, 
but it is the recommended configuration.

\index{GCB broker!ports 65432 and 65430}
The \Prog{gcb\_broker} daemon listens on two hard-coded,
fixed ports (65432 and 65430).
A future version of Condor and GCB will remove this limitation.
However, for now, to run a \Prog{gcb\_broker} on a
given host, ensure that ports 65432 and 65430 are not already
in use. 

If \Login{root} access on a machine where a GCB 
broker is planned, one good option is to have \Prog{initd} configured to
spawn (and re-spawn) the \Prog{gcb\_broker} binary (which is located in
the \Release{libexec} directory).
This way, the \Prog{gcb\_broker} will be automatically restarted on
reboots, or in the event that the broker itself crashes or is killed.
Without \Login{root} access, use a \Condor{master} to
manage the \Prog{gcb\_broker} binary. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\label{sec:GCB-Broker-Config}
Configuring the GCB broker}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\index{GCB broker!configuration}
Since the \Prog{gcb\_broker} and \Prog{gcb\_relay\_server} are not
Condor daemons, they do not read the Condor configuration
files.
Therefore, they must be configured by other means, namely the
environment and through the use of command-line arguments.

There is one required command-line argument for the \Prog{gcb\_broker}.
This argument defines the public IP address this broker will use to
represent itself and any private network nodes that are configured to
use this broker.
This information is defined with \Opt{-i xxx.xxx.xxx.xxx} on the
command-line when the \Prog{gcb\_broker} is executed.
If the broker is being setup outside the private network, it is likely
that the machine will only have one IP address, which is clearly the
one to use.
However, if the broker is being run on a machine on the
network boundary (a multi-homed machine with interfaces into both the
private and public networks), be sure to use the IP address of the
interface on the public network.

Additionally, specify environment variables to control
how the \Prog{gcb\_broker} (and the \Prog{gcb\_relay\_server}
processes it spawns) will behave.
Some of these settings can also be specified as command-line
arguments to the \Prog{gcb\_broker}.
All of them have reasonable defaults if not defined.

\begin{itemize}

\item General daemon behavior

\begin{description}

\item The environment variable \Env{GCB\_RELAY\_SERVER} \label{Env:GCB-relay-server}
  defines the full path to the \File{gcb\_relay\_server} binary
  the broker should use.
  The command-line override for this is \Opt{-r /full/path/to/relayserver}.
  If not set either on the command-line or in the environment,
  the \Prog{gcb\_broker} process will search for a program named
  \File{gcb\_relay\_server} in the same directory where the
  \File{gcb\_broker} binary is located, and attempt to use that one.

\item The environment variable \Env{GCB\_ACTIVE\_TO\_CLIENT}
  \label{Env:GCB-active-to-client}
  is a boolean that defines whether the GCB broker can directly talk to servers
  running inside the network that it manages
  The value must be \verb@yes@ or \verb@no@, case sensitive.
  \Env{GCB\_ACTIVE\_TO\_CLIENT} should be set to \verb@yes@ only if
  this GCB broker is running on a network boundary and can connect to
  both the private and public nodes.
  If the broker is running in the public network, it should be left
  undefined or set to \verb@no@.

\end{description}

\item Log file locations

\begin{description}

\item The environment variable \Env{GCB\_LOG\_DIR} \label{Env:GCB-log-dir}
  defines a directory to use for all GCB-related log files.
  If defined, and the per-daemon log file settings (described
  below) are not defined, the broker will write to
  \verb@$GCB_LOG_DIR/BrokerLog@ and the relay server will write to
  \verb@$GCB_LOG_DIR/RelayServerLog.<pid>@

\item The environment variable \Env{GCB\_BROKER\_LOG} \label{Env:GCB-broker-log}
  defines the full path for the GCB broker's log file.
  The command-line override is \Opt{-l /full/path/to/log/file}.
  This definition overrides \Env{GCB\_LOG\_DIR}.

\item The environment variable \Env{GCB\_RELAY\_SERVER\_LOG}
  \label{Env:GCB-relay-server-log}
  defines the full path to the GCB relay server's log file.
  Each relay server writes its own log file, so the actual filename
  will be: \verb@$GCB_RELAY_SERVER_LOG.<pid>@ where \verb@<pid>@ is
  replaced with the process id of the corresponding
  \Prog{gcb\_relay\_server}.
  When defined, this setting overrides \Env{GCB\_LOG\_DIR}.

\end{description}

\item Verbose logging 

\begin{description}

\item The environment variable \Env{GCB\_DEBUG\_LEVEL} 
  \label{Env:GCB-DEBUG-LEVEL}
  controls how verbose all the GCB daemon's log files should be.
  Can be either \verb@fulldebug@ (more verbose) or \verb@basic@.
  This defines logging behavior for all GCB daemons, unless
  the following daemon-specific settings are defined.

\item The environment variable \Env{GCB\_BROKER\_DEBUG}
  \label{Env:GCB-BROKER-DEBUG}
  controls verbose logging specifically for the GCB broker.
  The command-line override for this is \Opt{-d level}.
  Overrides \Env{GCB\_DEBUG\_LEVEL}. 

\item The environment variable \Env{GCB\_RELAY\_SERVER\_DEBUG} 
  \label{Env:GCB-RELAY-SERVER-DEBUG}
  controls verbose logging specifically for the GCB relay server.  
  Overrides \Env{GCB\_DEBUG\_LEVEL}. 

\end{description}

\item Maximum log file size

\begin{description}

\item The environment variable \Env{GCB\_MAX\_LOG} \label{Env:GCB-MAX-LOG}
  defines the maximum size in bytes of all GCB log files.
  When the log file reaches this size, the content of the file will be
  moved to \File{filename.old}, and a new log is started.
  This defines logging behavior for all GCB daemons, unless
  the following daemon-specific settings are used.

\item The environment variable \Env{GCB\_BROKER\_MAX\_LOG} \label{Env:GCB-BROKER-MAX-LOG}
  defines the maximum size in bytes of the GCB broker log file.

\item The environment variable \Env{GCB\_RELAY\_SERVER\_MAX\_LOG} 
  \label{Env:GCB-RELAY-SERVER-MAX-LOG}
  defines the maximum size in bytes of the GCB relay server log file.

\end{description}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\label{sec:GCB-broker-spawn}
Spawning the GCB Broker}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\index{GCB broker!how to spawn the broker}
There are two ways to spawn the GCB broker:

\begin{itemize}
\item Use a \Condor{master}.

To spawn the GCB broker with a \Condor{master}, here are 
the recommended \File{condor\_config} settings that will work:

\footnotesize
\begin{verbatim}
# Specify that you only want the master and the broker running
DAEMON_LIST = MASTER, GCB_BROKER

# Define the path to the broker binary for the master to spawn
GCB_BROKER = $(RELEASE_DIR)/libexec/gcb_broker

# Define the path to the release_server binary for the broker to use 
GCB_RELAY = $(RELEASE_DIR)/libexec/gcb_relay_server

# Setup the gcb_broker's environment.  We use a macro to build up the
# environment we want in pieces, and then finally define
# GCB_BROKER_ENVIRONMENT, the setting that condor_master uses.

# Initialize an empty macro
GCB_BROKER_ENV =

# (recommended) Provide the full path to the gcb_relay_server
GCB_BROKER_ENV = $(GCB_BROKER_ENV);GCB_RELAY_SERVER=$(GCB_RELAY)

# (recommended) Tell GCB to write all log files into the Condor log
# directory (the directory used by the condor_master itself)
GCB_BROKER_ENV = $(GCB_BROKER_ENV);GCB_LOG_DIR=$(LOG)
# Or, you can specify a log file separately for each GCB daemon:
#GCB_BROKER_ENV = $(GCB_BROKER_ENV);GCB_BROKER_LOG=$(LOG)/GCB_Broker_Log
#GCB_BROKER_ENV = $(GCB_BROKER_ENV);GCB_RELAY_SERVER_LOG=$(LOG)/GCB_RS_Log

# (optional -- only set if true) Tell the GCB broker that it can
# directly connect to machines in the private network which it is
# handling communication for.  This should only be enabled if the GCB
# broker is running directly on a network boundary and can open direct
# connections to the private nodes.
#GCB_BROKER_ENV = $(GCB_BROKER_ENV);GCB_ACTIVE_TO_CLIENT=yes

# (optional) turn on verbose logging for all of GCB
#GCB_BROKER_ENV = $(GCB_BROKER_ENV);GCB_DEBUG_LEVEL=fulldebug
# Or, you can turn this on separately for each GCB daemon:
#GCB_BROKER_ENV = $(GCB_BROKER_ENV);GCB_BROKER_DEBUG=fulldebug
#GCB_BROKER_ENV = $(GCB_BROKER_ENV);GCB_RELAY_SERVER_DEBUG=fulldebug

# (optional) specify the maximum log file size (in bytes)
#GCB_BROKER_ENV = $(GCB_BROKER_ENV);GCB_MAX_LOG=640000
# Or, you can define this separately for each GCB daemon:
#GCB_BROKER_ENV = $(GCB_BROKER_ENV);GCB_BROKER_MAX_LOG=640000
#GCB_BROKER_ENV = $(GCB_BROKER_ENV);GCB_RELAY_SERVER_MAX_LOG=640000

# Finally, set the value the condor_master really uses
GCB_BROKER_ENVIRONMENT = $(GCB_BROKER_ENV)

# If your Condor installation on this host already has a public
# interface as the default (either because it is the first interface
# listed in this machine's host entry, or because you've already
# defined NETWORK_INTERFACE), you can just use Condor's special macro
# that holds the IP address for this.
GCB_BROKER_IP = $(ip_address)
# Otherwise, you could define it yourself with your real public IP:
# GCB_BROKER_IP = 123.123.123.123

# (required) define the command-line arguments for the broker 
GCB_BROKER_ARGS = -i $(GCB_BROKER_IP)
\end{verbatim}
\normalsize

Once those settings are in place, either spawn or restart the
\Condor{master} and the \Prog{gcb\_broker} should be started.
Ensure the broker is running by reading the log file
specified with \Env{GCB\_BROKER\_LOG}, or in
\File{\MacroUNI{LOG}/BrokerLog} if using the default.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\subsubsection{\label{sec:GCB-initd-spawn}
%%Using \Prog{initd} to spawn the GCB broker}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\item Use \Prog{initd}.

The system's \Prog{initd} may be used to manage the
\Prog{gcb\_broker} without running the \Condor{master} on the broker
node, but this requires \Login{root} access.
Generally, this involves adding a line to the \File{/etc/inittab}
file.
Some sites use other means to manage and generate the
\File{/etc/inittab}, such as \Prog{cfengine} or other system configuration
management tools, so check with the local system administrator
to be sure.
An example line might be something like:

\footnotesize
\begin{verbatim}
GB:23:respawn:/path/to/gcb_broker -i 123.123.123.123 -r /path/to/relay_server
\end{verbatim}
\normalsize

It may be easier to wrap the \Prog{gcb\_broker} binary
in a shell script, in order to change the command-line arguments (and
set environment variables) without having to edit \File{/etc/inittab}
all the time.
This will be similar to:

\footnotesize
\begin{verbatim}
GB:23:respawn:/opt/condor-6.7.13/libexec/gcb_broker.sh
\end{verbatim}
\normalsize

Then, create the wrapper, as similar to: 

\footnotesize
\begin{verbatim}
#!/bin/sh

libexec=/opt/condor-6.7.13/libexec
ip=123.123.123.123
relay=$libexec/gcb_relay_server

exec $libexec/gcb_broker -i $ip -r $relay
\end{verbatim}
\normalsize

You will probably also want to set some environment variables to tell
the GCB daemons where to write their log files (\Env{GCB\_LOG\_DIR}),
and possibly some of the other variables described above.

Either way, after updating the \File{/etc/inittab}, send
the \Prog{initd} process (always PID 1) a \verb@SIGHUP@ signal, and it
will re-read the \File{inittab} and spawn the \Prog{gcb\_broker}.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\label{sec:GCB-condor-config}
Configuring Condor nodes to be GCB clients}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\index{GCB (Generic Connection Brokering)!Condor client configuration}
In general, before configuring a node in a Condor pool to use GCB,
the GCB broker node(s) for the pool must be set up and running.
Set up, configure, and spawn the broker first.

To enable the use of GCB on a given Condor host, set the following
Condor configuration variables:

\footnotesize
\begin{verbatim}
# Tell Condor to use a network remapping service (currently only GCB
# is supported, but in the future, there might be other options)
NET_REMAP_ENABLE = true
NET_REMAP_SERVICE = GCB
\end{verbatim}
\normalsize

Only GCB clients within a private network need to define the following
variable, which specifies the IP address of the broker serving this
network.
Note that this IP address must be the same as the IP address
that was specified on the
broker's command-line with the \Opt{-i} option.

\footnotesize
\begin{verbatim}
# Public IP address (in standard dot notation) of the GCB broker
# serving this private node.
NET_REMAP_INAGENT = xxx.xxx.xxx.xxx
\end{verbatim}
\normalsize

Obviously, because the \MacroNI{NET\_REMAP\_INAGENT} setting is only
valid on private nodes, it should not be defined in a global
Condor configuration file (\File{condor\_config}).
Furthermore, with a large number of hosts in a given private
network, if multiple brokers are to be run to alleviate
scalability issues, each subset of the private nodes that uses a
specific broker will need a different value for this variable.

Finally, if setting up  the recommended (but optional) GCB routing table, 
tell Condor daemons where to find their table.
Define the following variable:

\footnotesize
\begin{verbatim}
# The full path to the routing table used by GCB
NET_REMAP_ROUTE = /full/path/to/GCB-routing-table
\end{verbatim}
\normalsize

Setting \MacroNI{NET\_REMAP\_ENABLE} causes the
\Macro{BIND\_ALL\_INTERFACES} variable to be automatically set.
More information about this setting can be found in
section~\ref{sec:Using-BindAllInterfaces} on
page~\pageref{sec:Using-BindAllInterfaces}.
It would not hurt to place the following in the
configuration file near the other GCB-related settings,
just to remember it:

\footnotesize
\begin{verbatim}
# Tell Condor to bind to all network interfaces, instead of a single
# interface.
BIND_ALL_INTERFACES = true
\end{verbatim}
\normalsize

Once a GCB broker is set up and running to manage connections for a
each private network, and the Condor installation for all the nodes in
either private and public networks are configured to enable GCB,
restart the Condor daemons, and all of the different machines
should be able to communicate with each other.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\label{sec:GCB-routing-table}Configuring the GCB
  routing table} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\index{GCB (Generic Connection Brokering)!GCB routing table configuration}
By default, a GCB-enabled application will always attempt to directly
connect to a given IP/port pair.
In the case of a private nodes being represented by a GCB broker, the
IP/port will be a proxy socket on the broker node, not the real
address at each private node.
When the GCB broker receives a direct connection to one of its proxy 
sockets, it notifies the corresponding private node, which
establishes a new connection to the broker.
The broker then forwards packets between these two sockets,
establishing a communication pathway into the private node.
This allows clients which are not linked with the GCB libraries to communicate
with private nodes using a GCB broker.

This mechanism is expensive
in terms of latency (time between messages) and total bandwidth
(how much data can be moved in a given time period),
as well as expensive in terms of the broker's
system resources such as network I/O, processor time, and memory.
This expensive mechanism is 
unnecessary in the case of
GCB-aware clients trying to connect to private nodes that can directly
communicate with the public host.
The alternative is to contact the GCB broker's command interface (the
fixed port where the broker is listening for GCB management commands),
and use
a GCB-specific protocol to request a connection to the given IP/port.
In this case, the GCB broker will notify the private node to directly
connect to the public client (technically, to a new socket created by
the GCB client library linked in with the client's application), and a
direct socket between the two is established, removing the need for
packet forwarding between the proxy sockets at the GCB broker.

On the other hand, in cases where a direct connection from the client
to a given server is possible
(for example, two GCB-aware clients in the same
public network attempting to communicate with each other),
it is
expensive and unnecessary to attempt to contact a GCB broker, and the
client should connect directly.

To allow a GCB-enabled client to know if it should make a direct
connection (which might involve packet forwarding through proxy
sockets), or if it should use the GCB protocol to communicate with the
broker's command port and arrange a direct socket,
GCB provides a \Term{routing table}.
Using this table, an administrator can define what IP addresses should
be considered private nodes where the GCB connection protocol will be
used, and what nodes are public, where a direct connection (without
incurring the latency of contacting the GCB broker, only to find out
there is no information about the given IP/port) should be made
immediately. 

If the attempt to contact the GCB broker for a given IP/port fails, or
if the desired port is not being managed by the broker, the GCB client
library making the connection will fall back and attempt a direct
connection.
Therefore, configuring a GCB routing table is not required for
communication to work within a GCB-enabled environment.
However, the GCB routing table can significantly improve performance
for communication with private nodes being represented by a GCB
broker. 

One confusing aspect of GCB is that all of the nodes on a private
network believe that their own IP address is the address of their GCB
broker.
Due to this, all the Condor daemons on a private network advertise
themselves with the same IP address (though the broker will map the
different ports to different nodes within the private network).
Therefore, a given node in the public network needs to be told that if
it is contacting this IP address, it should know that the IP address is really
a GCB broker representing a node in the private network, so that 
the public network node
can contact the broker to arrange a single socket from the private
node to the public one, instead of relying on forwarding packets
between proxy sockets at the broker.
Any other addresses, such as other public IP addresses, can be
contacted directly, without going through a GCB broker.
Similarly, other nodes within the same private network will still be
advertising their address with their GCB broker's public IP address.
So, nodes within the same private network also have to know that the
public IP address of the broker is really a GCB broker, yet all other public
IP addresses are valid for direct communication.

In general, all connections can be made directly, except to a host
represented by a GCB broker.
Furthermore, the default behavior of the GCB client library is to make
a direct connection.
The routing table is a (somewhat complicated) way to tell a
given GCB installation what GCB brokers it might have to communicate
with, and that it should directly communicate with anything else.
In practice, the routing table should have a single entry for
each GCB broker in the system.
Future versions of GCB will be able to make use of more complicated
routing behavior, which is why the full routing table infrastructure
described below is implemented, even if the current version of GCB is
not taking advantage of all of it.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\Bold{Format of the GCB routing table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{GCB (Generic Connection Brokering)!GCB routing table syntax and examples}

The routing table is a plain ASCII text file.
Each line of the file contains one rule.
Each rule consists of a \Term{target} and a \Term{method}.
The target specifies destination IP address(es) to match, and the method
defines what mechanism must be used to connect to the given target.
The target must be a valid IP address string in the standard
dotted notation, followed by a slash character (\verb@/@),
as well as an integer \Term{mask}.
The mask specifies how many bits of the destination IP address
and target IP address must match.
The method must be one of the strings 
\begin{verbatim}
    GCB
    direct
\end{verbatim}
GCB stops searching the table as soon as it finds a matching rule,
therefore place more specific rules
(rules with a larger value for the mask and without wildcards)
before generic rules
(rules with wildcards or smaller mask values).
The default when no rule is matched is to use direct communication.
Some examples and the corresponding routing tables may help clarify
this syntax.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\Bold{Simple GCB routing table example (1 private, 1 public)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Consider an example with
a private network that has a set of nodes whose IP
addresses are \verb@192.168.2.*@.
Other nodes are in a public network 
whose IP addresses are \verb@123.123.123.*@.
A GCB broker for the 192
network is running on IP address \verb@123.123.123.123@.
In this case, the routing table for both the public and private nodes
should be:

\begin{verbatim}
123.123.123.123/32 GCB
\end{verbatim}

This rule states that for IP addresses where all 32 bits exactly match
the address \verb@123.123.123.123@, first communicate with the GCB broker.

Since the default is to directly connect when no rule in the routing
table matches a given target IP, this single rule is all that is
required.
However, to illustrate how the routing table syntax works, the
following routing table is equivalent:

\begin{verbatim}
123.123.123.123/32 GCB
*/0 direct
\end{verbatim}

Any attempt to connect to \verb@123.123.123.123@ uses GCB,
as it is the first rule in the file.
All other IP addresses
will connect directly.
This table explicitly defines GCB's default behavior.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\Bold{More complex GCB routing table example (2 private, 1 public)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

As a more complicated case, consider a single Condor pool that
spans one public network and two private networks.
The two separate private networks each have machines
with private addresses like \verb@192.168.2.*@.
Identify one of these private networks as \verb@A@, and the other one
as \verb@B@. 
The public network has nodes with IP addresses like
\verb@123.123.123.*@.
Assume that the GCB broker for nodes in the \verb@A@ network 
has IP address
\verb@123.123.123.65@,
and the GCB broker for the nodes in the \verb@B@ network
has IP address
\verb@123.123.123.66@.
All of the nodes need to be able to talk to each other.
In this case, nodes in private network \verb@A@ advertise
themselves as \verb@123.123.123.65@, so any node, regardless of being
in A, B, or the public network, must treat that IP address as a GCB broker.
Similarly, nodes in private network \verb@B@ advertise 
themselves as \verb@123.123.123.66@, so any node, regardless of being
in A, B, or the public network, must treat that IP address as a GCB broker.
All other connections from any node can be made directly.
Therefore, here is the appropriate routing table for all nodes:

\begin{verbatim}
123.123.123.65/32 GCB
123.123.123.66/32 GCB
\end{verbatim}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\label{sec:GCB-host-security-implications}Implications
of GCB on Condor's Host/IP-based Security Configuration} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\index{GCB (Generic Connection Brokering)!security implications}
When a message is received at a Condor daemon's command socket,
Condor authenticates based on the IP
address of the incoming socket.
For more information about this host-based security in Condor, see
section~\ref{sec:Host-Security} on page~\pageref{sec:Host-Security}.
Because of the way GCB changes the IP addresses that are used and
advertised by GCB-enabled clients, and since all nodes being
represented by a GCB broker are represented by different ports on the
broker node (a process known as \Term{address leasing}), using GCB has
implications for this process.

Depending on the communication pathway used by a GCB-enabled Condor
client (either a tool or another Condor daemon) to connect to a given
Condor server daemon, and where in the network each side of the
connection resides, the IP address of the resulting socket actually
used will be very different.
In the case of a private client (that is, a client behind a firewall,
which may or may not be using NAT and a fully private, non-routable IP
address) attempting to connect to a server, there are three
possibilities: 

\begin{itemize}

  \item For a direct connection to another node within the private network,
  the server will see the private IP address of the client.

  \item For a direct outbound connection to a public node: if NAT is being
  used, the server will see the IP address of the NAT server for the private
  network.
  If there is no NAT, and the firewall is blocking connections in
  only one direction, but not re-writing IP addresses, the server will see
  the client's real IP address.

  \item For a connection to a host in a different private network that must
  be relayed through the GCB broker, the server will see the IP
  address of the GCB broker representing the server.
  This is an instance of the private server case, as
  described below.

\end{itemize}

Therefore, any public server that wants to allow a command from a
specific client must have any or all of the various IP addresses
mentioned above within the appropriate \MacroNI{HOSTALLOW} settings.  In
practice, that means opening up the \MacroNI{HOSTALLOW} settings to
include not just the actual IP addresses of each node, but also the IP
address of the various GCB brokers in use, and potentially, the public
IP address of the NAT host for each private network.

However, given that all private nodes which are represented by a
given GCB broker could potentially make connections to any other
host using the GCB broker's IP address (whenever proxy socket
forwarding is being used), if a single private node is being granted
a certain level of permission within the Condor pool,
all of the private nodes
using the same GCB broker will have the same level of permission.
This is particularly important in the consideration of granting
\Macro{HOSTALLOW\_ADMINISTRATOR} or \Macro{HOSTALLOW\_CONFIG}
privileges to a private node represented by a GCB broker.

In the case of a public client attempting to connect to a private
server, there are only two possible cases:

\begin{itemize}

  \item the GCB broker can arrange a direct socket from the private server.
  The private server will see the real public IP address of the client.

  \item the GCB broker must forward packets from a proxy socket.
  This may happen because
  of a non-GCB aware public client,
  a misconfigured or missing GCB routing table,
  or a client in a different private network.
  The private server will see the IP address of its own GCB broker.
  In the case where the GCB broker runs on a node on the network
  boundary, the private server will see the GCB broker's private IP
  address (even if the GCB broker is also listening on the public
  interface and the leased addresses it provides use the public IP
  addresses). 
  If the GCB broker is running entirely in the public network and cannot
  directly connect to the private nodes, the private server will see
  the remote connection as coming from the broker's public IP
  address.

\end{itemize}

This second case is particularly troubling.
Since there are legitimate circumstances where a private server would
need to use a forwarded proxy socket from its GCB broker, in general,
the server should allow requests originating from its GCB broker.
But, precisely because of the proxy forwarding, that implies that
\emph{any} client
that can connect to the GCB broker would be allowed into the
private server
(if IP-based authorization was the only defense).

The final host-based security setting that requires special mention is
\Macro{HOSTALLOW\_NEGOTIATOR}.
If the \Condor{negotiator} for the pool is running on a private node
being represented by a GCB broker, there must be
modifications to the default value.
For the purposes of Condor's host-based security, the
\Condor{negotiator} acts as a client when communicating with each 
\Condor{schedd} in the pool which has idle jobs that need to be
matched with available resources.
Therefore, all the possible cases of a private client attempting to
connect to a given server apply to a private \Condor{negotiator}.
In practice, that means adding the public IP address of the broker, the real
private IP address of the negotiator host, and possibly the 
public IP address of
the NAT host for this private network to the
\MacroNI{HOSTALLOW\_NEGOTIATOR} setting.
Unfortunately, this implies that \emph{any} host behind the
same NAT host or using
the same GCB broker will be authorized as if it was the
\Condor{negotiator}. 

Future versions of GCB and Condor will hopefully add some form of
authentication and authorization to the GCB broker itself, to help
alleviate these problems.
Until then, sites using GCB are encouraged to use GSI strong
authentication (since Kerberos also depends on IP addresses and is
therefore incompatible with GCB) to rely on an authorization system
that is not affected by address leasing.
This is especially true for sites that (foolishly) choose to run their
central manager on a private node.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\label{sec:GCB-config-implications}Implications of
GCB for Other Condor Configuration} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Using GCB and address leasing has implications for Condor
configuration settings outside of the Host/IP-based security
settings.
Each is described. 

\begin{description}

% i'm intentionally using \Macro, not \MacroNI for each of these,
% since they should show up in the index...

\item[\Macro{COLLECTOR\_HOST}]
  If the \Condor{collector} for the pool is running on a private node
  being represented by a GCB broker, \MacroNI{COLLECTOR\_HOST}
  must be set to the host name or IP address of the GCB broker machine,
  \emph{not} the real host name/IP address of the private node
  where the daemons are actually running.
  When the \Condor{collector} on the private node attempts to
  \Syscall{bind} to its command port (9618 by default), it will
  request port 9618 on the GCB broker node, instead.
  The port is not a worry, but the host name or IP address 
  is a worry.
  When public nodes want to communicate with the \Condor{collector},
  they must go through the GCB broker.
  In theory, other nodes inside the same private network could be told
  to directly use the private IP address of the \Condor{collector} host,
  but that is
  unnecessary, and would probably lead to other confusion and
  configuration problems.

  However, because the \Condor{collector} is listening on a fixed
  port, and that single port is reserved on the GCB broker node, no
  two private nodes using the same broker can attempt to use the same
  port for their \Condor{collector}.
  Therefore, any site that is attempting to set up multiple pools
  within the same private network is strongly encouraged to set up
  separate GCB brokers for each pool.
  Otherwise, one or both of the pools must use a
  non-standard port for the \Condor{collector}, which adds yet more
  complication to an already complicated situation. 

\item[\Macro{CKPT\_SERVER\_HOST}]
  Much like the case for \MacroNI{COLLECTOR\_HOST} described above,
  a checkpoint server on a private node will have to lease a port on
  the GCB broker node.
  However, the checkpoint server also uses a fixed port, and unlike
  the \Condor{collector}, there is no way to configure an alternate
  value.
  Therefore, only a single checkpoint server can be run behind a given
  GCB broker.
  The same solution works: if multiple checkpoint servers are required,
  multiple
  GCB brokers are deployed and configured.
  Furthermore, the host name of the GCB broker should be used as the
  value for \MacroNI{CKPT\_SERVER\_HOST}, not the real IP address or host name
  of the private node where the \Condor{ckpt\_server} is running.

\item[\Macro{SEC\_DEFAULT\_AUTHENTICATION\_METHODS}]
  \verb@KERBEROS@ may not be used for authentication
  on a GCB-enabled pool.
  The IP addresses used in various
  circumstances will not be the real IP addresses of the machines.
  Since Kerberos stores the IP address of each host as part of the
  Kerberos ticket, authentication will fail on a GCB-enabled
  pool.

\end{description}

Due to the complications and security limitations that arise from
running a central manager on a private node represented by GCB (both
regarding the \MacroNI{COLLECTOR\_HOST} and
\MacroNI{HOSTALLOW\_NEGOTIATOR}), we
recommend that sites avoid locating a central manager on a private
host whenever possible.

