%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:HTCBluegeneP}
	Configuring Condor for HTC on the Blue Gene/P} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The Blue Gene/P (BG/P) machine provides a high throughput computing
(HTC) model which reconciles traditional cluster interface semantics
with a massively parallel computing system. Condor takes advantage of
this model by providing a wrapping layer for the BG/P HTC model similar
to the notion of a``glidin factory''. At this time, the PowerPC binaries
for the SLES 9 distribution of Condor is the necessary port in order to
utilize this feature.

The mechanism of Condor's interface to the BG/P is a new long-lived
daemon, under the \Condor{master}, called the \Condor{startd\_factory}
and a set of scripts invoked by said daemon to effect the BG/P partition
changes with the BG/P HTC API.  The \Condor{startd\_factory} daemon's role
is to periodically determine if there is more work in the participating
\Condor{schedd}s than HTC resources available from the BG/P and if so
boot and back (wrap the booted BG/P partition by a \Condor{startd})
more partitions of the types needed by the jobs in the \Condor{schedd}.
The partitions must have been previously generated at the correct size
by the administrator of the BG/P prior to Condor utilizing them.

Backed resources present with a slot per CPU matching the total number
of compute nodes in the block. Each slot ad is born with attributes
(described below) that only allow the jobs of the particular HTC flavor
(SMP, DUAL, VN) to execute on the slot and which also describes the slot
to the \Condor{startd\_factory}. This policy is implemented via custom
classad attributes in the slot and job ad.

Backed, but unused, partitions are released via a daemon termination
timeout in the \Condor{startd} when its slots have not been utilized after
a configurable amount of time.

\subsubsection{\Condor{startd\_factory Daemon Configuration}}

# These attributes describe the daemon similarly to other daemons in Condor
# Just put STARTD_FACTORY into DAEMON_LIST to start the service.
STARTD_FACTORY = $(SBIN)/condor_startd_factory
STARTD_FACTORY_ARGS = -f
STARTD_FACTORY_LOG = $(LOG)/StartdFactoryLog
# MAX_STARTD_FACTORY_LOG = 10000000

# The list of pregenerated partitions on the BG/P which may be booted and
# backed by the condor_startd_factory daemon according to the workload.
STARTD_FACTORY_BGP_PARTITION_LIST = R00-M00-N0, R00-M00-N1, ...

# This says how often to determine the workload and adjust the partitions to
# match it. It is an integer in seconds and defaults to 4200 seconds (7 minutes)
# if not specified.
# STARTD_FACTORY_ADJUSTMENT_INTERVAL = 4200

# This will scrape all schedds cared about and provide a summary of the
# work loads available.
STARTD_FACTORY_SCRIPT_QUERY_WORK_LOADS = $(LIBEXEC)/bgp_query_work_loads

# if any are already partitions created, what are they and what state
# are they in?
STARTD_FACTORY_SCRIPT_AVAILABLE_PARTITIONS = $(LIBEXEC)/bgp_available_partitions

# Boot/free a known partition
STARTD_FACTORY_SCRIPT_BOOT_PARTITION = $(LIBEXEC)/bgp_boot_partition
STARTD_FACTORY_SCRIPT_SHUTDOWN_PARTITION = $(LIBEXEC)/bgp_shutdown_partition

# create a startd which will back a partition with a known kind
STARTD_FACTORY_SCRIPT_BACK_PARTITION = $(LIBEXEC)/bgp_back_partition

There are two unused config file entries that may be supported in a future
version of Condor.

# This will create/destroy a parition on the BlueGene
STARTD_FACTORY_SCRIPT_GENERATE_PARTITION = $(LIBEXEC)/bgp_generate_partition
STARTD_FACTORY_SCRIPT_DESTROY_PARTITION =  $(LIBEXEC)/bgp_destroy_partition

\subsubsection{Script Descriptions}

Here we describe exactly what all of these scripts do at a high level
and what inputs and outputs they expect as to interface with the
\Condor{startd\_factory} daemon. 

STARTD_FACTORY_SCRIPT_QUERY_WORK_LOADS
	This blocking script queries the collector to find all
	\Condor{schedd}s in the Condor pool, then queries each
	\Condor{schedd} to find jobs with the BGP_BLOCK_TYPE attribute
	paired with the current job status--idle or running.

	Script command line arguments:
		None
	Script input:
		Nothing
	Script output:
		A set of classads written to stdout representing the
		work from each \Condor{schedd}. Each ad is separated
		by the the characters --- occuring on a single line,
		which must also terminate the set of classads.

		The required attributes in the classads are:
			WorkloadName 
				The name of the source of the work, in this case the name of
				a schedd. The value must be a string.

			SMPIdle
			SMPRunning
				How many SMP jobs in the workload are idle/running.

			DUALIdle
			DUALRunning
				How many DUAL jobs in the workload are idle/running.

			VNIdle
			VNRunning
				How many VN jobs in the workload are idle/running.
	
	Example output of script:

		WorkloadName = "psilord\@cs.wisc.edu"
		SMPIdle = 100
		SMPRunning = 0
		DUALIdle = 0
		DUALRunning = 0
		VNIdle = 0
		VNRunning = 0
		---
		WorkloadName = "gthain\@cs.wisc.edu"
		SMPIdle = 1024
		SMPRunning = 0
		DUALIdle = 0
		DUALRunning = 0
		VNIdle = 256
		VNRunning = 0
		---

STARTD_FACTORY_SCRIPT_AVAILABLE_PARTITIONS
	This blocking script inspects the BG/P machine and the Condor
	pool itself and, for each partition id, figures out the state
	of the partition id (generated only, booted, or backed)

	Script command line arguments:
		--partition-ids-info <one or more partition ids>
	
	Script input:
		None
	
	Script output:
		A set of classads delimited by the characters --- occuring
		on a line by itself, which must also terminate the set
		of classads. The classads describe in what state each
		partition exists. An example of each kind of state is
		presented in the example output. Depending upon the state
		of the partition, the required classad attributes change.

		Attributes in emitted classad:

		Partition
			Always required.
			A string which is the name of the partition id.

		State
			Always required
			A string, either 
			"INVALID", "NOT_GENERATED", "GENERATED", "BOOTED", or "BACKED".

		Size
			Required only of the partition is GENERATED, BOOTED, or BACKED.
			An integer detailing the number of compute nodes.

		Kind
			Present only if the partition is BOOTED, or BACKED.
			A string, either "SMP", "DUAL", or "VN".

		Backer
			Present only if the partition is BACKED.
			A string which is the Name attribute of the startd backing
			the resource.

	Example script output:

		Partition = "R00-M0-N00"
		State = "BACKED"
		Size = 64
		Kind = "DUAL"
		Backer = "R00-M0-N00\@fqdn.com"
		---
		Partition = "R00-M0-N01"
		State = "BOOTED"
		Size = 64
		Kind = "DUAL"
		---
		Partition = "R00-M0-N02"
		State = "GENERATED"
		Size = 64
		---
		Partition = "R00-M0-N03"
		State = "NOT_GENERATED"
		---
		Partition = "XXXXX"
		State = "INVALID"
		---

STARTD_FACTORY_SCRIPT_BOOT_PARTITION
	This blocking script takes a partition id and an HTC type and
	boots the partition on the BG/P with the required type. The type
	may be SMP, DUAL, or VN. This script may only boot a single partition
	at a time.

	Script command line arguments:
		--boot <partitionid> --type <type>
	
	Script input:
		None

	Script output:
		If the booting of the partition goes well, then "OK"
		on a single line should be the output. Otherwise, lines
		of descriptive output may be emitted ending with "NOT_OK"
		on a single line after the text.

STARTD_FACTORY_SCRIPT_SHUTDOWN_PARTITION
	This blocking script is responsible for taking a partition id
	which has already been booted and shutting it down. If the
	partition is also backed, then this script should stop the
	\Condor{startd} associated with the partition as well. When this
	script finishes, the parition is only in the generated state.

	Script command line arguments:
		--partition-id <partitionid>
	
	Script input:
		None:
	
	Script output:
		If the booting of the partition goes well, then "OK"
		on a single line should be the output. Otherwise, lines
		of descriptive output may be emitted ending with "NOT_OK"
		on a single line after the text.
		
STARTD_FACTORY_SCRIPT_BACK_PARTITION
	This blocking script takes a partition, size, and type, and
	starts a \Condor{startd} (doing all the work necessary, including
	creating a specific confguration file and appropriate LOCAL_DIR)
	which presents the same number of slots of the correct HTC type
	as there are compute nodes in the partition.

	Script command line arguments:
		--partition-id <partitionid> --size <size> --type [SMP | DUAL | VN]
	
	Script input:
		None:
	
	Script output:
		If the backing of the partition goes well, then "OK"
		on a single line should be the output. Otherwise, lines
		of descriptive output may be emitted ending with "NOT_OK"
		on a single line after the text.

\subsubsection{\Condor(startd} Presentation}

In the current implementation of STARTD_FACTORY_SCRIPT_BACK_PARTITION,
each backing startd's LOCAL directory appears in a directory
named /tmp/startd.<pid> where <pid> is the pid of the
STARTD_FACTORY_SCRIPT_BACK_PARTITION process. A dynamic config file
is constructed for the startd as well which defines some config
file attributes that describe the backed partition. At this time, the
/tmp/startd.<pid> directory and files are leaked in the file system--we
will address this known problem in a future release of Condor.

The attributes added/specified into the \Condor{startd}'s ad are:

\begin{verbatim}
STARTD_NAME = partition name
PARTITION_NAME = partition name
BGP_BLOCK_SIZE = block size
BGP_BLOCK_TYPE = SMP | DUAL | VN
\end{verbatim}

The \Condor{startd} will report to the collector, as in a glide-in
scenario, running jobs which match the BGP_CLOCK_TYPE. When all of the
slots managed by a \Condor{startd} are continuously unclaimed/idle for at
least STARTD_NOCLAIM_SHUTDOWN seconds (currently defaulting to 5 minutes),
the startd self-terminates.

\subsubsection{BG/P HTC Jobs in the Queue}

Attributes in the job ad:
BGP_BLOCK_TYPE = SMP | DUAL | VN

The job types available with the BG/P HTC model are SMP, DUAL, and VN.
Respectively, they mean a job that may be single threaded, dual threaded,
or quad threaded. From the perspective of the user of these resources,
each job ad destined for the BG/P resource must contain an attribute
called \Macro{BGP\_BLOCK\_TYPE} which have the string values "SMP" or
"DUAL" or "VN".

This attribute can be added to the submit file as in this example:

\begin{verbatim}
+BGP_BLOCK_TYPE = SMP
\end{verbatim}

\subsubsection{BG/P HTC Partition Scheduling}

For the initial implementation of this feature, the
\Condor{startd\_factory} uses a very simple, but hardcoded, algorithm
for scheduling the generated partitions.

0. Query the state of all available partitions with
STARTD_FACTORY_SCRIPT_AVAILABLE_PARTITIONS. This allows the
\Condor{startd\_factory} to know of a partitions is generated, or booted
to a specific htc type, or backed. The \Condor{startd\_factory} keeps
track of certain state changes of the partitions to ensure they are in
the correct state at the time they are expected to be.

1. Query all participating schedds (those who report to the collector)
with STARTD_FACTORY_SCRIPT_QUERY_WORK_LOADS to see what kinds, how many,
and in what states any submitted HTC jobs exist. The important states
at this time are not present, idle, and running.

2. If there are more idle jobs of any particular BGP_BLOCK_TYPE than there
are unclaimed slots of that type, then follow this algorithm:

	START_ALGORITHM

	SCHED_SMP:
		If the SMP idle count is greater than available SMP slots, then
			If there exists a BOOTED/SMP partition, then
				back it with a startd
				goto SCHED_DUAL
			else if there exists a generated partition, then
				boot it as an SMP HTC type
				goto SCHED_SMP
	
	SCHED_DUAL:
		If the DUAL idle count is greater than available DUAL slots, then
			If there exists a BOOTED/DUAL partition, then
				back it with a startd
				goto SCHED_VN
			else if there exists a generated partition, then
				boot it as an DUAL HTC type
				goto SCHED_DUAL

	SCHED_VN:
		If the VN idle count is greater than available VN slots, then
			If there exists a BOOTED/VN partition, then
				back it with a startd
				goto EVICT_UNEEDED:
			else if there exists a generated partition, then
				boot it as an DUAL VN type
				goto SCHED_VN
				
	EVICT_UNEEDED:
		If any partitions are booted and not backed after the scheduling
		algorithm above finishes. We've overcommited the partitions so
		for each of these partitions, shut them down.

	END_ALGORITHM



