%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:Resource-Limits}Limiting Resource Usage with a User Job Wrapper} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{resource limits}
\index{limits!on resource usage}

An administrator can strictly limit the usage of system resources
by jobs for any job that may be wrapped using
the script defined by the configuration variable
\Macro{USER\_JOB\_WRAPPER}.
These are jobs within universes that are controlled by the
\Condor{starter} daemon, and they include 
the \SubmitCmd{vanilla}, \SubmitCmd{standard}, \SubmitCmd{java},
\SubmitCmd{local}, and \SubmitCmd{parallel} universes.

The job's ClassAd is written by the \Condor{starter} daemon.
It will need to contain attributes that the script defined by
\MacroNI{USER\_JOB\_WRAPPER} can use to implement 
platform specific resource limiting actions.
Examples of resources that may be referred to for limiting purposes
are RAM, swap space, file descriptors, stack size, and core file size. 

An initial sample of a \MacroNI{USER\_JOB\_WRAPPER} script is provided
in the installation at
\File{\$(LIBEXEC)/condor\_limits\_wrapper.sh}.
Here is the contents of that file:

\footnotesize
\begin{verbatim}
#!/bin/sh
# Copyright 2008 Red Hat, Inc.
#
# Licensed under the Apache License, Version 2.0 (the "License");
# you may not use this file except in compliance with the License.
# You may obtain a copy of the License at
#
#     http://www.apache.org/licenses/LICENSE-2.0
#
# Unless required by applicable law or agreed to in writing, software
# distributed under the License is distributed on an "AS IS" BASIS,
# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
# See the License for the specific language governing permissions and
# limitations under the License.

if [[ $_CONDOR_MACHINE_AD != "" ]]; then
   mem_limit=$((`egrep '^Memory' $_CONDOR_MACHINE_AD | cut -d ' ' -f 3` * 1024))
#   block_size=$((`stat -f -c %s .` / 1024))
#   disk_limit=$((`egrep '^Disk' $_CONDOR_MACHINE_AD | cut -d ' ' -f 3` / $block_size))
   disk_limit=`egrep '^Disk' $_CONDOR_MACHINE_AD | cut -d ' ' -f 3`
   vm_limit=`egrep '^VirtualMemory' $_CONDOR_MACHINE_AD | cut -d ' ' -f 3`

   ulimit -d $mem_limit
   if [[ $? != 0 ]] || [[ $mem_limit = "" ]]; then
      echo "Failed to set Memory Resource Limit" > $_CONDOR_WRAPPER_ERROR_FILE
      exit 1
   fi
   ulimit -f $disk_limit
   if [[ $? != 0 ]] || [[ $disk_limit = "" ]]; then
      echo "Failed to set Disk Resource Limit" > $_CONDOR_WRAPPER_ERROR_FILE
      exit 1
   fi
   ulimit -v $vm_limit
   if [[ $? != 0 ]] || [[ $vm_limit = "" ]]; then
      echo "Failed to set Virtual Memory Resource Limit" > $_CONDOR_WRAPPER_ERROR_FILE
      exit 1
   fi
fi

exec "$@"
error=$?
echo "Failed to exec($error): $@" > $_CONDOR_WRAPPER_ERROR_FILE
exit 1
\end{verbatim}
\normalsize

If used in an unmodified form,
this script sets the job's limits on a per slot basis for
memory, disk, and virtual memory usage,
with the limits defined by the values in the machine ClassAd.
This example file will need to be modified and merged for use with a
preexisting \MacroNI{USER\_JOB\_WRAPPER} script.

If additional functionality is added to the script,
an administrator is likely to use the \MacroNI{USER\_JOB\_WRAPPER} script
in conjunction with \Macro{SUBMIT\_EXPRS} to force the job ClassAd
to contain attributes that the \MacroNI{USER\_JOB\_WRAPPER} script
expects to have defined.

The following variables are set in the environment of the
the \MacroNI{USER\_JOB\_WRAPPER} script by the \Condor{starter}
daemon, when the \MacroNI{USER\_JOB\_WRAPPER} is defined.
\begin{description}
\item[\Env{\_CONDOR\_MACHINE\_AD}
\index{environment variables!\_CONDOR\_MACHINE\_AD}]
  The full path and file name of the file containing the machine ClassAd.
\item[\Env{\_CONDOR\_JOB\_AD}
\index{environment variables!\_CONDOR\_JOB\_AD}]
  The full path and file name of the file containing the job ClassAd.
\item[\Env{\_CONDOR\_WRAPPER\_ERROR\_FILE}
\index{environment variables!\_CONDOR\_WRAPPER\_ERROR\_FILE}]
  The full path and file name of the file that the \MacroNI{USER\_JOB\_WRAPPER}
  script should create, if there is an error.
  The text in this file will be included in any HTCondor failure messages. 
\end{description}
