%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:Quill}Quill}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{Quill|(}
\index{Condor daemon!condor\_quill@\Condor{quill}}
\index{daemon!condor\_quill@\Condor{quill}}
\index{condor\_quill daemon}
\index{Condor daemon!condor\_dbmsd@\Condor{dbmsd}}
\index{daemon!condor\_dbmsd@\Condor{dbmsd}}
\index{condor\_dbmsd daemon}
Quill is an optional component of Condor that maintains a mirror 
of Condor operational data
in a relational database.  The \Condor{quill} daemon updates
the data in the relation database, and the \Condor{dbmsd} daemon
maintains the database itself.

As of Condor version 7.5.5,
Quill is distributed only with the source code.
It is not included in the builds of Condor provided by UW,
but it is available as a feature that can be enabled by those who compile
Condor from the source code.
Find the code within the \File{condor\_contrib} directory, 
in the directories \File{condor\_tt} and \File{condor\_dbmsd}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:Quill-Installation}Installation and Configuration}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Quill uses the \Prog{PostgreSQL} database management system.
Quill uses the \Prog{PostgreSQL} server as its back end
and client library, 
\Prog{libpq} to talk to the server.
We \Bold{strongly recommend} the use of version 
8.2 or later due to its integrated facilities of certain key 
database maintenance tasks, and stronger security features.

Obtain \Prog{PostgreSQL} from

\URL{http://www.postgresql.org/ftp/source/}

Installation instructions are detailed in:
\URL{http://www.postgresql.org/docs/8.2/static/installation.html}

Configure \Prog{PostgreSQL} after installation:

\begin{enumerate}

\item Initialize the database with the \Prog{PostgreSQL} command 
\verb@initdb@.

\item Configure to accept TCP/IP connections.
For \Prog{PostgreSQL} version 8,
use the \Code{listen\_addresses} variable in 
\File{postgresql.conf} file as a guide.
For example,
\Code{listen\_addresses = '*'}
means listen on any IP interface.

\item Configure automatic vacuuming.
Ensure that these variables with these defaults are
commented in and/or set properly in the 
\File{postgresql.conf} configuration file:
\begin{verbatim}
# Turn on/off automatic vacuuming
autovacuum = on

# time between autovacuum runs, in secs
autovacuum_naptime = 60

# min # of tuple updates before vacuum
autovacuum_vacuum_threshold = 1000

# min # of tuple updates before analyze
autovacuum_analyze_threshold = 500

# fraction of rel size before vacuum
autovacuum_vacuum_scale_factor = 0.4 

# fraction of rel size before analyze
autovacuum_analyze_scale_factor = 0.2

# default vacuum cost delay for 
   # autovac, -1 means use 
   # vacuum_cost_delay
autovacuum_vacuum_cost_delay = -1  

# default vacuum cost limit for 
   # autovac, -1 means use
   # vacuum_cost_limit
autovacuum_vacuum_cost_limit = -1   
\end{verbatim}


\item Configure \Prog{PostgreSQL} to accept TCP/IP connections from 
specific hosts.
Modify the \File{pg\_hba.conf} file 
(which usually resides in the \Prog{PostgreSQL} server's data directory).
Access is required by the \Condor{quill} daemon,
as well as the database users
\Username{quillreader} and \Username{quillwriter}.
For example, to give
database users \Username{quillreader} and \Username{quillwriter}
password-enabled access to all databases on current machine from any
machine in the 128.105.0.0/16 subnet, add the following:

\begin{tabular}{llllll}
host&all&quillreader&128.105.0.0&255.255.0.0&md5\\
host&all&quillwriter&128.105.0.0&255.255.0.0&md5
\end{tabular}

Note that in addition to the database specified by
the configuration variable \MacroNI{QUILL\_DB\_NAME},
the \Condor{quill} daemon also needs access to the database
"template1".
In order to create the database in the first place, 
the \Condor{quill} daemon needs to connect to the database.

\item Start the \Prog{PostgreSQL} server service. See the
installation instructions for the appropriate method to start the service at
\URL{http://www.postgresql.org/docs/8.2/static/installation.html}

\item The \Condor{quill} and \Condor{dbmsd} daemons and client tools connect
to the database as users \Username{quillreader} and 
\Username{quillwriter}.
These are database users, not operating system users.
The two types of users are quite different from each other.
If these database users do not exist,
add them using the 
\Prog{createuser} command supplied with the installation.
Assign them with appropriate passwords;
these passwords will be used by the Quill tools to connect
to the database in a secure way.
User \Username{quillreader} should not be allowed to create
more databases nor create more users.
User \Username{quillwriter} should
not be allowed to create more users,
however it should be allowed to create more databases.
The following commands create the two users
with the appropriate permissions,
and be ready to enter the corresponding passwords when prompted.

\footnotesize
\begin{verbatim}
/path/to/postgreSQL/bin/directory/createuser quillreader \
	--no-createdb --no-createrole --pwprompt

/path/to/postgreSQL/bin/directory/createuser quillwriter \
	--createdb --no-createrole --pwprompt
\end{verbatim}
\normalsize

Answer ``no'' to the question about the ability for role creation.

\item Create a database for Quill to store data in
with the \verb@createdb@ command. 
Create this database with the \Username{quillwriter} user as the owner.
A sample command to do this is
\footnotesize
\begin{verbatim}
createdb -O quillwriter quill
\end{verbatim}
\normalsize
\verb@quill@ is the database name to use with the \MacroNI{QUILL\_DB\_NAME}
configuration variable.

\item The \Condor{quill} and \Condor{dbmsd} daemons need read and write access
to the database.
They connect as user \Username{quillwriter},
which has owner privileges to the database.
Since this gives all access to the \Username{quillwriter} user,
its password cannot be stored in a public place 
(such as in a ClassAd).
For this reason, the \Username{quillwriter} password is stored
in a file named \File{.pgpass} in the Condor spool directory.
Appropriate protections on this file guarantee secure access to the database.
This file must be created and protected by the site administrator;
if this file does not exist as and where expected, the \Condor{quill}
and \Condor{dbmsd} daemons log an error and exit.
The \File{.pgpass} file contains a single line that
has fields separated by colons and is properly terminated by
an operating system specific newline character (Unix) or CRLF (Windows).
The first field may be either the machine name and fully qualified domain,
or it may be a dotted quad IP address.
This is followed by four fields containing:
the TCP port number, 
the name of the database,
the "quillwriter" user name,
and the password.
The form used in the first field must exactly match the value set for 
the configuration variable \Macro{QUILL\_DB\_IP\_ADDR}.
Condor uses a string comparison between the two, and it does not resolve the
host names to compare IP addresses.
Example:
\footnotesize
\begin{verbatim}
machinename.cs.wisc.edu:5432:quill:quillwriter:password
\end{verbatim}
\normalsize

\end{enumerate}

After the \Prog{PostgreSQL} database is initialized and running, 
the Quill schema
must be loaded into it.  First, load the plsql programming language
into the server:

\begin{verbatim}
createlang plpgsql [databasename]
\end{verbatim}

Then, load the Quill schema from the sql files in the \File{sql} subdirectory
of the Condor release directory:

\begin{verbatim}
psql [databasename] [username] < common_createddl.sql
psql [databasename] [username] < pgsql_createddl.sql
\end{verbatim}
where \verb@[username]@ will be \verb@quillwriter@.


After \Prog{PostgreSQL} is configured and running, Condor must also be
configured to use Quill, since by default Quill is configured to be off.

\begin{description}
\item Add the file \File{.pgpass} to the 
  \MacroNI{VALID\_SPOOL\_FILES} variable, since \Condor{preen} must
  be told not to delete this file.
  This step may not be necessary, depending on which version of Condor 
  you are upgrading from. 
 
\item Set up configuration variables that are specific to the installation,
and check that the \MacroNI{HISTORY} variable is set.
\footnotesize
\begin{verbatim}
HISTORY                 = $(SPOOL)/history
QUILL_ENABLED           = TRUE
QUILL_USE_SQL_LOG       = FALSE
QUILL_NAME              = some-unique-quill-name.cs.wisc.edu
QUILL_DB_USER           = quillwriter
QUILL_DB_NAME           = database-for-some-unique-quill-name
QUILL_DB_IP_ADDR        = databaseIPaddress:port
# the following parameter's units is in seconds
QUILL_POLLING_PERIOD    = 10
QUILL_HISTORY_DURATION 	= 30
QUILL_MANAGE_VACUUM     = FALSE
QUILL_IS_REMOTELY_QUERYABLE = TRUE
QUILL_DB_QUERY_PASSWORD =  password-for-database-user-quillreader
QUILL_ADDRESS_FILE      = $(LOG)/.quill_address
QUILL_DB_TYPE           = PGSQL
# The Purge and Reindex intervals are in seconds
DATABASE_PURGE_INTERVAL	= 86400
DATABASE_REINDEX_INTERVAL = 86400
# The History durations are all in days 
QUILL_RESOURCE_HISTORY_DURATION  = 7
QUILL_RUN_HISTORY_DURATION = 7
QUILL_JOB_HISTORY_DURATION = 3650
#The DB Size limit is in gigabytes
QUILL_DBSIZE_LIMIT      = 20
QUILL_MAINTAIN_DB_CONN  = TRUE
SCHEDD_SQLLOG           = $(LOG)/schedd_sql.log
SCHEDD_DAEMON_AD_FILE   = $(LOG)/.schedd_classad

\end{verbatim}
\normalsize

\end{description}

The default Condor configuration file should already contain definitions
for \MacroNI{QUILL} and \MacroNI{QUILL\_LOG}.  
When upgrading from a previous version that did not have Quill to
a new one that does, define these two configuration variables.

Only one machine should run the \Condor{dbmsd} daemon.  
On this machine, add it to the \MacroNI{DAEMON\_LIST} configuration variable.
All Quill-enabled machines should also run the \Condor{quill} daemon.
The machine running the \Condor{dbmsd} daemon can also 
run a \Condor{quill} daemon.  An example \MacroNI{DAEMON\_LIST}
for a machine running both daemons,
and acting as both a submit machine and a central manager might 
look like the following:

\footnotesize
\begin{verbatim}
DAEMON_LIST  = MASTER, SCHEDD, COLLECTOR, NEGOTIATOR, DBMSD, QUILL
\end{verbatim}
\normalsize

The \Condor{dbmsd} daemon will need configuration file entries
common to all daemons.
If not already in the configuration file, add the following entries:

\begin{verbatim}
DBMSD = $(SBIN)/condor_dbmsd
DBMSD_ARGS = -f
DBMSD_LOG = $(LOG)/DbmsdLog
MAX_DBMSD_LOG = 10000000
\end{verbatim}

Descriptions of these and other configuration variables are in
section~\ref{sec:Quill-Config-File-Entries}.
Here are further brief details:

\begin{description}

\item[\Macro{QUILL\_DB\_NAME} and \Macro{QUILL\_DB\_IP\_ADDR}]
These two variables are used to determine the location of the database
server that this Quill would talk to, and the name of the database that
it creates.  More than one Quill server can talk to the same database
server.  This can be accomplished by letting all the 
\MacroNI{QUILL\_DB\_IP\_ADDR} values point to the same database server.

\item[\Macro{QUILL\_DB\_USER}] 
This is the \Prog{PostgreSQL} user that Quill will connect as to the database.
We recommend \Username{quillwriter} for this setting. 
There is no default setting for \MacroNI{QUILL\_DB\_USER}, so it must
be specified in the configuration file. 

\item[\Macro{QUILL\_NAME}]
Each \Condor{quill} daemon in the pool has to be uniquely named.

\item[\Macro{QUILL\_POLLING\_PERIOD}]
This controls the frequency with which Quill polls the
\File{job\_queue.log} file.  By default, it is 10 seconds.  Since Quill
works by periodically sniffing the log file for updates and then sending
those updates to the database, this variable controls the trade off between
the currency of query results and Quill's load on the system, which
is usually negligible.

\item[ \Macro{QUILL\_RESOURCE\_HISTORY\_DURATION}, 
		\Macro{QUILL\_RUN\_HISTORY\_DURATION}, and
		\Macro{QUILL\_JOB\_HISTORY\_DURATION}]
These three variables control the deletion of historical information from the
database. 
\MacroNI{QUILL\_RESOURCE\_HISTORY\_DURATION} is the number of days
historical information about the state of a resource will be kept in the 
database. 
The default for resource history is 7 days.
An example of a resource is the ClassAd for a compute slot.
\MacroNI{QUILL\_RUN\_HISTORY\_DURATION} is the number of days
after completion that auxiliary information about a  given job will stay in 
the database.  
This includes user log events, file transfers performed by the job, the matches
that were made for a job, et cetera. 
The default for run history is 7 days.
\MacroNI{QUILL\_JOB\_HISTORY\_DURATION} is the number of days
after completion that a given job will stay in the database.  
A more precise definition is the number of days since the history ad got 
into the history database; those two might be different,
if a job is completed but stays in the queue for a while.
The default for job history is 3,650 days (about 10 years.)

\item[\Macro{DATABASE\_PURGE\_INTERVAL}]
As scanning the entire database for old jobs can be expensive,
the other variable \MacroNI{DATABASE\_PURGE\_INTERVAL}
is the number of seconds between two successive scans.  
\MacroNI{DATABASE\_PURGE\_INTERVAL} is set to 86400 seconds, or one day.

\item[\Macro{DATABASE\_REINDEX\_INTERVAL}]
\Prog{PostgreSQL} does not aggressively maintain the index structures for
deleted tuples. This can lead to bloated index structures.
Quill can periodically reindex the database, which is controlled by the
variable \MacroNI{DATABASE\_REINDEX\_INTERVAL}.
\MacroNI{DATABASE\_PURGE\_INTERVAL} is set to 86400 seconds, or one day.

\item[\Macro{QUILL\_DBSIZE\_LIMIT}]
Quill can estimate the size of the database, and send email to the Condor
administrator if the database size exceeds this threshold. 
The estimate is checked after every \MacroNI{DATABASE\_PURGE\_INTERVAL}.
The limit is given as gigabytes, and the default is 20.

\item[\Macro{QUILL\_MAINTAIN\_DB\_CONN}]
Quill can maintain an open connection the database server, which speeds up
updates to the database. 
However, each open connection consumes resources at the database server.
The default is TRUE, but for large pools we recommend setting this 
FALSE.

\item[\Macro{QUILL\_MANAGE\_VACUUM}]
Set to \Expr{False} by default, this variable determines whether Quill is to 
perform vacuuming tasks on its tables or not. Vacuuming is a maintenance 
task that needs to be performed on tables in \Prog{PostgreSQL}. The 
frequency with which a table is vacuumed typically depends on the number 
of updates (inserts/deletes) performed on the table. Fortunately, with 
\Prog{PostgreSQL} version 8.1, vacuuming tasks can be configured to be 
performed automatically by the database server. We recommend that users 
upgrade to 8.1 and use the integrated vacuuming facilities of the database 
server, instead of having Quill do them. If the user does prefer having 
Quill perform those vacuuming tasks, it can be achieved by setting this 
variable to Expr{True}. However, it cannot be overstated that Quill's vacuuming 
policy is quite rudimentary as compared to the integrated facilities 
of the database server, and under high update workloads, can prove to 
be a bottleneck on the Quill daemon. As such, setting this variable to 
Expr{True} results in some warning messages in the log file regarding this 
issue.

\item[\Macro{QUILL\_IS\_REMOTELY\_QUERYABLE}]
Thanks to 
\Prog{PostgreSQL},
one can now remotely query both the job queue and the
history tables. This variable controls whether this remote querying 
feature should be enabled.  By default it is \Expr{True}.  Note that even if 
this is \Expr{False}, one can still query the job queue 
at the remote \Condor{schedd} daemon.
This variable only controls whether the database tables are remotely queryable.

\item[\Macro{QUILL\_DB\_QUERY\_PASSWORD}]
In order for the query tools to connect to a database, they need to provide
the password that is assigned to the database user \Username{quillreader}. 
This variable is then advertised by the \Condor{quill} daemon
to the \Condor{collector}.  
This facility enables remote querying: remote \Condor{q} query tools first 
ask the \Condor{collector} for
the password associated with a particular Quill database, 
and then query that database.  Users who do not have access to the 
\Condor{collector} 
cannot view the password, and as such cannot query the database.  Again, this 
password only provides read access to the database.

\item[\Macro{QUILL\_ADDRESS\_FILE}]
When Quill starts up, it can place its address (IP and port)
into a file.  This way, tools running on the local machine do not
need to query the central manager to find Quill.  This 
feature can be turned off by commenting out the variable.

\end{description}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:Quill-Example}Four Usage Examples}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{enumerate}
\item Query a remote Quill daemon on \File{regular.cs.wisc.edu}
for all the jobs in the queue
\begin{verbatim}
	condor_q -name quill@regular.cs.wisc.edu
	condor_q -name schedd@regular.cs.wisc.edu

\end{verbatim}
There are two ways to get to a Quill daemon: directly using its name as 
specified in the \MacroNI{QUILL\_NAME} configuration variable, or indirectly
by querying the \Condor{schedd} daemon using its name.
In the latter case, \Condor{q} will detect 
if that \Condor{schedd} daemon is being serviced by a database, and if so, directly query it.
In both cases, the IP address and port of the database server hosting the data of 
this particular remote Quill daemon can be figured out by the \MacroNI{QUILL\_DB\_IP\_ADDR} 
and \MacroNI{QUILL\_DB\_NAME} variables specified in the \MacroNI{QUILL\_AD}
sent by the quill daemon to the collector and in the \MacroNI{SCHEDD\_AD} sent by
the \Condor{schedd} daemon.  

\item Query a remote Quill daemon on \File{regular.cs.wisc.edu} for all historical 
jobs belonging to owner einstein.
\begin{verbatim}
	condor_history -name quill@regular.cs.wisc.edu einstein
\end{verbatim}

\item Query the local Quill daemon for the average time spent in the queue 
for all non-completed jobs. 
\begin{verbatim}
	condor_q -avgqueuetime 
\end{verbatim}
The average queue time is defined as the average of
\Expr{(currenttime - jobsubmissiontime)} over all jobs which are neither
completed \Expr{(JobStatus == 4)} or removed \Expr{(JobStatus == 3)}.

\item Query the local Quill daemon for all historical jobs completed since 
Apr 1, 2005 at 13h 00m.
\begin{verbatim}
	condor_history -completedsince '04/01/2005 13:00'
\end{verbatim}
It fetches all jobs
which got into the 'Completed' state on or after the
specified time stamp.  It use the \Prog{PostgreSQL} date/time
syntax rules, as it encompasses most format options.  See
\URL{http://www.postgresql.org/docs/8.2/static/datatype-datetime.html}
for the various time stamp formats.

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:Quill-Security}Quill and Security}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

There are several layers of security in Quill, some provided by Condor and
others provided by the database.  First, all accesses to the database
are password-protected.

\begin{enumerate}
\item The query tools, \Condor{q} and
\Condor{history} connect to the database as user \Username{quillreader}.
The password for this user can vary from one database to another and
as such, each Quill daemon advertises this password to the collector.
The query tools then obtain this password from the collector and
connect successfully to the database.  Access to the database by the
\Username{quillreader} user is read-only, as this is sufficient for the
query tools.  The \Condor{quill} daemon ensures this protected access using the sql
GRANT command when it first creates the tables in the database.  Note that
access to the \Username{quillreader} password itself can be blocked by
blocking access to the collector, a feature already supported in Condor.

\item The \Condor{quill} and \Condor{dbmsd} daemons, on the other hand,
need read and write access to the database.
As such, they connect as user \Username{quillwriter},
who has owner privileges to the database.  Since this gives all
access to the \Username{quillwriter} user, this password cannot
be stored in a public place (such as the collector).  For this
reason, the \Username{quillwriter} password is stored in a file called
\File{.pgpass} in the Condor spool directory.
Appropriate protections on this file guarantee secure access to the database.
This file must be created and protected by the site administrator;
if this file does not exist as and where expected, the \Condor{quill}
daemon logs an error and exits.

\item The \Attr{IsRemotelyQueryable} attribute in the Quill ClassAd advertised
by the Quill daemon to the collector can be used by site administrators
to disallow the database from being read by all remote Condor query tools.

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:Quill-Schema}Quill and Its RDBMS Schema}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{admin-man/quill-schema.tex}
