\begin{description}

\item[\Macro{VIRTUAL\_MACHINES\_CONNECTED\_TO\_CONSOLE}] 
\label{param:VirtualMachinesConnectedToConsole}
  This should be an integer which indicates how many of the virtual
  machines the startd is representing should be "connected" to the
  console (in other words, notice when there's console activity).
  This defaults to all virtual machines (N in a machine with N CPUs).
  This must be an integer ("N" isn't a valid setting, that's just used
  to represent the default).

\item[\Macro{VIRTUAL\_MACHINES\_CONNECTED\_TO\_KEYBOARD}]
\label{param:VirtualMachinesConnectedToKeyboard}
  This should be an integer which indicates how many of the virtual
  machines the startd is representing should be "connected" to the
  keyboard (for remote tty activity, as well as console activity).
  Defaults to 1.

\item[\Macro{DISCONNECTED\_KEYBOARD\_IDLE\_BOOST}]
\label{param:DisconnectedKeyboardIdleBoost}
  If there are virtual machines not connected to either the keyboard
  or the console, the corresponding idle time reported will be the
  time since the startd was spawned, plus the value of this parameter.
  It defaults to 1200 seconds (20 minutes). 
  We do this because if the virtual machine is configured not to care
  about keyboard activity, we want it to be available to Condor jobs
  as soon as the startd starts up, instead of having to wait for 15
  minutes or more (which is the default time a machine must be idle
  before Condor will start a job).
  If you don't want this boost, just set the value to 0.  
  If you change your START expression to require more than 15 minutes
  before a job starts, but you still want jobs to start right away on
  some of your SMP nodes, just increase this parameter.

\end{description}
