%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:batch}The batch Grid Type (for PBS, LSF, and SGE) }
\label{sec:PBS}
\label{sec:LSF}
\label{sec:SGE}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{batch grid type}

The \SubmitCmd{batch} grid type is used to submit to a local PBS, LSF, or SGE
system using the \SubmitCmd{grid} universe and the
\SubmitCmd{grid\_resource} command by placing a variant of the following
into the submit description file.
\begin{verbatim}
grid_resource = batch pbs
\end{verbatim}

The second argument on the right hand side will be one of
\Expr{pbs}, \Expr{lsf}, or \Expr{sge}.

Any of these batch grid types requires two variables to be set in the HTCondor
configuration file.
\Macro{BATCH\_GAHP} is the path to the GAHP server binary that is to be
used to submit one of these batch jobs.
\Macro{GLITE\_LOCATION} is the path to the directory containing the GAHP's
configuration file and auxiliary binaries.
In the HTCondor distribution, these files are located in 
\File{\MacroUNI{LIB}/glite}.
The batch GAHP's configuration file is in
\File{\MacroUNI{GLITE\_LOCATION}/etc/batch\_gahp.config}.
The batch GAHP's auxiliary binaries
are to be in the directory \File{\MacroUNI{GLITE\_LOCATION}/bin}.
The HTCondor configuration file appears

\footnotesize
\begin{verbatim}
GLITE_LOCATION = $(LIB)/glite
BATCH_GAHP     = $(GLITE_LOCATION)/bin/batch_gahp
\end{verbatim}
\normalsize

The batch GAHP's configuration file has variables that must be
modified to tell it where to find 
\begin{description}
\item[PBS] on the local system.
  \Expr{pbs\_binpath} is the directory that contains the PBS binaries.
  \Expr{pbs\_spoolpath} is the PBS spool directory.
\item[LSF] on the local system.
  \Expr{lsf\_binpath} is the directory that contains the LSF binaries.
  \Expr{lsf\_confpath} is the location of the LSF configuration file.
\end{description}

%------------------

\index{PBS (Portable Batch System)}
\index{grid computing!submitting jobs to PBS}
The popular PBS (Portable Batch System) can be found at
\URL{http://www.pbsworks.com/},
and Torque is at
(\URL{http://www.adaptivecomputing.com/products/open-source/torque/}).

As an alternative to the submission details given above,
HTCondor jobs may be submitted to a local PBS system
using the \SubmitCmd{grid} universe and the
\SubmitCmd{grid\_resource} command by placing the following
into the submit description file.
\begin{verbatim}
grid_resource = pbs
\end{verbatim}

%------------------


\index{LSF}
\index{grid computing!submitting jobs to Platform LSF}

HTCondor jobs may be submitted to the Platform LSF batch system.
Find the Platform product from the page
\URL{http://www.platform.com/Products/}
for more information about Platform LSF.

As an alternative to the submission details given above,
HTCondor jobs may be submitted to a local Platform LSF system
using the \SubmitCmd{grid} universe and the
\SubmitCmd{grid\_resource} command  by placing the following
into the submit description file.
\begin{verbatim}
grid_resource = lsf
\end{verbatim}


%------------------

\index{SGE (Sun Grid Engine)}
\index{grid computing!submitting jobs to SGE}

The popular Grid Engine batch system (formerly known as Sun Grid Engine and
abbreviated SGE) is available in two varieties:
Oracle Grid Engine
(\URL{http://www.oracle.com/us/products/tools/oracle-grid-engine-075549.html})
and Univa Grid Engine
(\URL{http://www.univa.com/?gclid=CLXg6-OEy6wCFWICQAodl0lm9Q}).

As an alternative to the submission details given above,
HTCondor jobs may be submitted to a local SGE system
using the \SubmitCmd{grid} universe and adding the
\SubmitCmd{grid\_resource} command by placing
into the submit description file:
\begin{verbatim}
grid_resource = sge
\end{verbatim}

%-------------

The \Condor{qsub} command line tool will take PBS/SGE style batch files or 
command line arguments and submit the job to HTCondor instead.
See the \Condor{qsub} manual page at \ref{man-condor-qsub} for details.
