%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:Gce}The BOINC Grid Type }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{BOINC}
\index{BOINC grid jobs}
\index{grid computing!submitting jobs to BOINC}
\index{grid type!boinc}

HTCondor jobs may be submitted to BOINC (Berkeley Open Infrastructure
for Network Computing) servers.
BOINC is a software system for volunteer computing.
More information about BOINC is available at
\URL{http://boinc.berkeley.edu/}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\label{sec:Boinc-submit}BOINC Job Submission}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

HTCondor jobs are submitted to a BOINC service
with the \SubmitCmd{grid} universe, setting the
\SubmitCmd{grid\_resource} command to \SubmitCmd{boinc}, followed 
by the service's URL.

%Since the HTCondor job is a virtual machine image,
%most of the submit description file commands
%specifying input or output files are not applicable.
%The \SubmitCmd{executable} command is still required,
%but its value is ignored. 
%It identifies different jobs in the output of \Condor{q}.

%The VM image for the job must already reside in Google's Cloud Storage
%service and be registered with GCE.
%In the submit description file,
%provide the full URL identifier for the image using 
%the \SubmitCmd{gce\_image} command.

To use this grid type, you must have an account on the BOINC server
that is authorized to submit jobs.
You have to provide the authenticator string for that account for
HTCondor to use.
Write the authenticator string in a file and specify its location in
the submit description file using the
\SubmitCmd{boinc\_authenticator\_file} command, as in the example:
\begin{verbatim}
boinc_authenticator_file = /path/to/auth-file
\end{verbatim}

Before you can submit BOINC jobs, you must register your application
with the BOINC server.
This includes describing the application's resource requirements and
input and output files, and placing application files on the server.
This is a manual process that is done on the BOINC server.
See the BOINC documentation for details.

In the submit description file, the \SubmitCmd{executable} command
gives the registered name of the application on the BOINC server.
Input and output files can be described as in the vanilla universe,
but the filenames must match the application description on the
BOINC server.
If \SubmitCmd{transfer\_output\_files} is omitted, then all output
files are transferred.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\label{sec:Boinc-config}BOINC Configuration Variables}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The following configuration parameters are specific to the \SubmitCmd{boinc}
grid type. 
The values listed here are the defaults. 
Different values may be specified in the HTCondor configuration files.

\footnotesize
\begin{verbatim}
BOINC_GAHP = $(SBIN)/boinc_gahp
\end{verbatim}
\normalsize
