\index{HTCondor-G|(}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:HTCondor-G}HTCondor-G, the gt2, and gt5 Grid Types}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

HTCondor-G is the name given to HTCondor when \SubmitCmd{grid}
\SubmitCmd{universe} jobs are sent to grid resources utilizing
Globus software for job execution.
The Globus Toolkit provides a framework for building grid systems
and applications.
See the Globus Alliance web page at
\URL{http://www.globus.org}
for descriptions and details of the Globus software.

HTCondor provides the same job management capabilities for HTCondor-G
jobs as for other jobs.
From HTCondor, a user may effectively submit jobs, manage jobs,
and have jobs execute on widely distributed machines.

% HTCondor-G is a ``window to the grid.''
% The function of HTCondor-G becomes clear
% with a brief overview of the software that forms an HTCondor pool.
% For this discussion, the software of an HTCondor pool is divided
% into two parts.
% The first part does job management.
% It keeps track of a user's jobs.
% You can ask the job management part of HTCondor to show
% you the job queue, to submit new jobs to the system,
% to put jobs on hold,
% and to request information about jobs that have completed.
% The other part of the HTCondor software
% does resource management.
% It keeps track of which machines are available to run jobs,
% how the available machines should be utilized given all the users
% who want to run jobs on them,
% and when a machine is no longer available.
% HTCondor-G works with grid resources, allowing users to
% effectively submit jobs, manage jobs, and have jobs execute
% on widely distributed machines.

% A machine with the job management part installed
% is called a submit machine.
% A machine with the resource management part installed 
% is called an execute machine.
% Each machine may have one part or both.
% HTCondor-G is the job management part of HTCondor.
% \index{HTCondor-G!functionality}
% HTCondor-G lets you submit jobs into a queue,
% have a log detailing the life cycle of your jobs,
% manage your input and output files,
% along with everything else you expect from a job queuing system.

% HTCondor-G is a program that manages both a queue of jobs
% and the resources from one or more sites where those jobs can execute. 
% For some of these jobs,
% it communicates with these resources and transfers files
% to and from these resources using Globus mechanisms.
% (In particular, HTCondor-G uses the GRAM protocol for job submission,
% and it runs a local GASS server for file transfers).

It may appear that HTCondor-G is a simple replacement
for the Globus Toolkit's \Prog{globusrun} command.
However, HTCondor-G does much more.
It allows the submission of many jobs at once,
along with the monitoring of those jobs with a convenient interface.
There is notification when jobs complete or fail
and maintenance of Globus credentials
that may expire while a job is running.
On top of this, HTCondor-G is a fault-tolerant system;
if a machine crashes,
all of these functions are again available as the machine returns.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{grids/using.tex}
\input{grids/grid-monitor.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\label{sec:HTCondor-G-Limits}Limitations of HTCondor-G}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This subsubsection used to reside in the file limitations.tex.
\index{HTCondor-G!limitations}
Submitting jobs to run under the grid universe has not yet
been perfected.
The following is a list of known limitations:

\begin{enumerate}
\item{No checkpoints.}
\item{No job exit codes.}
Job exit codes are not available when using
\SubmitCmd{gt2}.
\item{Limited platform availability.}
Windows support is not yet available.
\end{enumerate}

\index{HTCondor-G|)}


