
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:CREAM}The cream Grid Type }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{cream}
\index{grid computing!submitting jobs to cream}

CREAM is a job submission interface being developed at INFN for the
gLite software stack. 
The CREAM homepage is \URL{http://grid.pd.infn.it/cream/}.
The protocol is based on web services.

The protocol requires an X.509 proxy for the job,
so the submit description file command \SubmitCmd{x509userproxy}
will be used.

A CREAM resource specification is of the form:
\footnotesize
\begin{verbatim}
grid_resource = cream <web-services-address> <batch-system> <queue-name>
\end{verbatim}
\normalsize
The \verb@<web-services-address>@ appears the same for most servers,
differing only in the host name, as
\begin{verbatim}
<machinename[:port]>/ce-cream/services/CREAM2
\end{verbatim}
Future versions of HTCondor may require only the host name, 
filling in other aspects of the web service for the user.

The \verb@<batch-system>@ is the name of the batch system that sits behind
the CREAM server,
into which it submits the jobs.
Normal values are \verb@pbs@, \verb@lsf@, and \verb@condor@.

The \verb@<queue-name>@ identifies which queue within the batch system
should be used.
Values for this will vary by site, with no typical values.

A full example for the specification of a CREAM \SubmitCmd{grid\_resource} is
\footnotesize
\begin{verbatim}
grid_resource = cream https://cream-12.pd.infn.it:8443/ce-cream/services/CREAM2
   pbs cream_1
\end{verbatim}
\normalsize
This is a single line within the submit description file,
although it is shown here on two lines for formatting reasons.

CREAM uses ClassAd syntax to describe jobs, although the attributes used
are different than those for HTCondor.
The submit description file command
\SubmitCmd{cream\_attributes}
adds additional attributes to the CREAM-style job ClassAd that HTCondor
constructs. 
The format for this submit description file command is
\begin{verbatim}
cream_attributes = name=value;name=value
\end{verbatim}
