%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:Condor-G-Glossary}A Condor-G Glossary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The glossary of terms (in alphabetical order):

\begin{description} 

\item[certificate] definition of certificate.
\index{certificate!glossary definition}
\index{Condor-G!certificate}

\item[certification authority (CA)] definition of certification authority.
\index{certification authority!glossary definition}

\item[Condor-G]
\index{Condor-G!glossary definition}
A subset of the Condor system that deals with
submitting, managing, and executing jobs on grid-managed resources.

\item[GAHP] definition of GAHP
\index{GAHP!glossary definition}
\index{Condor-G!GAHP}

\item[GASS] definition of GASS (Global Access to Secondary Storage).
\index{GASS!glossary definition}
\index{Condor-G!GASS}

\item[GPT] definition of GPT (Grid Packaging Technologies).
\index{GPT!glossary definition}
\index{Condor-G!GPT}

\item[GRAM] definition of GRAM (Grid Resource Allocation and Management
protocol).
\index{GRAM!glossary definition}
\index{Condor-G!GRAM}

\item[GSI] GSI (Grid Security Infrastructure) is 
\index{GSI!glossary definition}
\index{Condor-G!GSI}
authentication and authorization software provided by Globus.
It allows a user to authenticate once,
handling further site-specific requirements.

\item[PKI] PKI (Public Key Infrastructure) is 
\index{PKI!glossary definition}
\index{Condor-G!PKI}

\item[proxy] A proxy (more formally, a proxy certificate) is
\index{proxy!glossary definition}
\index{Condor-G!proxy}
a temporary binding of a new key pair to an existing user identity.
Use of proxy certificates allow an entity to temporary delegate
their rights to remote processes or resources on the Internet. 


\item[VDT] definition of VDT.
\index{VDT!glossary definition}
\index{Condor-G!VDT}

\item[X.509] definition of X.509.
\index{X.509!glossary definition}
\index{Condor-G!X.509}

\end{description} 

