
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:LSF}The lsf Grid Type }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{LSF}
\index{grid computing!submitting jobs to Platform LSF}

Condor jobs may be submitted to the Platform LSF batch system.
See the Products page of the Platform web page at
\URL{http://www.platform.com/Products/}
for more information about Platform LSF.

Condor jobs are submitted to a local Platform LSF system
using the \SubmitCmd{grid} universe and the
\SubmitCmd{grid\_resource} command  by placing the following
into the submit description file.
\begin{verbatim}
grid_resource = lsf
\end{verbatim}

The lsf grid type requires two variables to be set in the Condor
configuration file.
\Macro{LSF\_GAHP} is the path to the LSF GAHP server binary that is to be
used to submit Platform LSF jobs.
\Macro{GLITE\_LOCATION} is the path to the directory containing the GAHP's
configuration file and auxillary binaries.
In the Condor distribution, these files are located in 
\File{\MacroUNI{LIB}/glite}.
The LSF GAHP's configuration file is in
\File{\MacroUNI{GLITE\_LOCATION}/etc/batch\_gahp.config}.
The LSF GAHP's auxillary binaries
are to be in the directory \File{\MacroUNI{GLITE\_LOCATION}/bin}.
The Condor configuration file appears

\footnotesize
\begin{verbatim}
GLITE_LOCATION = $(LIB)/glite
LSF_GAHP       = $(GLITE_LOCATION)/bin/batch_gahp
\end{verbatim}
\normalsize

The LSF GAHP's configuration file contains two variables that must be
modified to tell it where to find LSF on the local system.
\MacroNI{lsf\_binpath} is the directory that contains the LSF binaries.
\MacroNI{lsf\_confpath} is the location of the LSF configuration file.
