
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:PBS}The pbs grid type }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{PBS}

PBS (Portable Batch System) is a popular batch system. It comes in
several varieties: OpenPBS (\URL{http://www.openpbs.org}),
PBS Pro (\URL{http://www.altair.com/software/pbspro.htm}), and
Torque
(\URL{http://www.clusterresources.com/pages/products/torque-resource-manager.php}).

Condor jobs may be submitted to a local PBS system
using the \SubmitCmd{grid} universe and the
\SubmitCmd{grid\_resource} command as follows:
\begin{verbatim}
grid_resource = pbs
\end{verbatim}

The pbs grid type requires two variables to be set in the Condor
configuration file.
\Macro{PBS\_GAHP} is the path to the PBS GAHP server binary that should be
used to submit PBS jobs.
\Macro{GLITE\_LOCATION} is the path to the directory containing the GAHP's
configuration file and auxillary binaries.
In the Condor distribution, these files are located in \$(LIB)/glite.
The PBS GAHP's configuration file should be located in
\$(GLITE\_LOCATION)/etc/batch\_gahp.config. The PBS GAHP's auxillary binaries
should be located in the directory \$(GLITE\_LOCATION)/bin.

\begin{verbatim}
GLITE_LOCATION = $(LIB)/glite
PBS_GAHP       = $(GLITE_LOCATION)/bin/batch_gahp
\end{verbatim}

The PBS GAHP's configuration file contains two variables that have to be
modified to tell GAHP where to find PBS on the local system.
\Macro{pbs\_binpath} is the directory that contains the PBS binaries.
\Macro{pbs\_spoolpath} is the PBS spool directory.

%Details on where PBS is installed on the local system are
%given in the file \$(GLITE\_LOCATION)/etc/batch\_gahp.config.
