
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:Unicore}The unicore Grid Type }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{Unicore}
\index{grid computing!submitting jobs to Unicore}

Unicore is a Java-based grid scheduling system.
See \URL{http://www.unicore.eu/} for more information about Unicore.

HTCondor jobs may be submitted to
Unicore resources using the \SubmitCmd{grid} universe.
The \SubmitCmd{grid\_resource} command specifies the name of the
Unicore resource as follows:
\begin{verbatim}
grid_resource = unicore usite.example.com vsite
\end{verbatim}
\SubmitCmd{usite.example.com} is the host name of the Unicore gateway
machine to which the HTCondor job is to be submitted.
\SubmitCmd{vsite} is the name of the Unicore virtual resource to which
the HTCondor job is to be submitted.

Unicore uses certificates stored in a Java keystore file for
authentication. 
The following submit description file commands
are required to properly use the keystore file.

\begin{description}
\item[\SubmitCmd{keystore\_file}] 
  Specifies the complete path and file name of the Java keystore file to use. 
\item[\SubmitCmd{keystore\_alias}] 
  A string that specifies which certificate in the
  Java keystore file to use. 
\item[\SubmitCmd{keystore\_passphrase\_file}]
  Specifies the complete path and file name of the 
  file containing the passphrase protecting the certificate in the  
  Java keystore file.
\end{description}
