\begin{ManPage}{\label{man-condor-top}\Condor{top}}{1}
{Display status and runtime statistics of a HTCondor daemon}

\index{HTCondor commands!condor\_top}
\index{condor\_top command}

\Synopsis \SynProg{\Condor{top}}
\oOpt{-h}

\SynProg{\Condor{top}}
\oOpt{-l}
\oOptArg{-p}{centralmanagerhostname[:portname]}
\oOptArg{-n}{name}
\oOptArg{-d}{delay}
\oOptArg{-c}{columnset}
\oOptArg{-s}{sortcolumn}
[\verb@--@\textbf{attrs=\lt{}attr1,attr2,...\gt{}}]
\oArg{daemon options}

\SynProg{\Condor{top}}
\oOptArg{-c}{columnset}
\oOptArg{-s}{sortcolumn}
[\verb@--@\textbf{attrs=\lt{}attr1,attr2,...\gt{}}]
\oArg{classad-filename classad-filename}

\Description
\Condor{top} displays the status 
(e.g. memory usage and duty cycle) 
of a HTCondor daemon
and calculates and displays runtime statistics 
for the daemon's subprocesses.

When no arguments are specified,
\Condor{top} displays the status 
for the primary daemon
based on the role of the current machine
by scanning the \MacroNI{DAEMON\_LIST}
configuration setting.
If multiple daemons are listed,
\Condor{top} will monitor one of (in decreasing priority): 
\Condor{schedd}, 
\Condor{startd}, 
\Condor{collector}, 
\Condor{negotiator}, 
\Condor{master}.

If the \Condor{collector} returns multiple ClassAds 
for the chosen daemon type,
\Condor{top} will display stats from the first ClassAd returned.
Results can be constrained
by passing the \MacroNI{NAME} of a specific daemon with \Opt{-n}.

The default \Arg{delay} is \MacroNI{STATISTICS\_WINDOW\_QUANTUM},
which is 4 minutes (240 seconds)
in a default HTCondor configuration.
Setting the delay smaller 
can be helpful 
for finding spikes of activity,
but setting the delay too small
will lead to poor measurements
of the duty cycle
and of the runtime statistics.

\Condor{top} can run in a top-like ``live'' mode
by passing \Opt{-l}.
The live mode is similar to the *nix top command,
with stats updating every \Arg{delay} seconds.
Redirecting stdout will disable live mode
even if \Opt{-l} is set.
To exit \Condor{top} while in live mode,
issue Ctrl-C.

\Condor{top} can be passed two files containing ClassAds
from the same HTCondor daemon,
in which case the \Condor{collector} will not be queried
but rather the statistics will be computed and displayed immediately
from the two ClassAds.
Only -c, -s, and --attrs options are considered 
when passing ClassAds via files.

The following subprocess stat columns may be displayed (*default):
\begin{description}
\item[Item]{*Name of the subprocess}
\item[InstRt]{*Total runtime between the two ClassAds}
\item[InstAvg]{*Mean runtime per execution between the two ClassAds}
\item[TotalRt]{Total runtime since daemon start}
\item[TotAvg]{*Mean runtime per execution since daemon start}
\item[TotMax]{*Max runtime per execution since daemon start}
\item[TotMin]{Min runtime per execution since daemon start}
\item[RtPctAvg]{*Percent of mean runtime per execution. The ratio of InstAvg to TotAvg, expressed as a percentage}
\item[RtPctMax]{Percent of max runtime per execution. The ratio of (InstAvg - TotMin) to (TotMax - TotMin), expressed as a percentage}
\item[RtSigmas]{Standard deviations from mean runtime. The ratio of (InstAvg - TotAvg) to the standard deviation in runtime per execution since daemon start}
\item[InstCt]{Executions between the two ClassAds}
\item[InstRate]{*Executions per second between the two ClassAds}
\item[TotalCt]{Total executions (counts) since daemon start}
\item[AvgRate]{*Mean count rate. Executions per second since daemon start}
\item[CtPctAvg]{Percent of mean count rate. The ratio of InstRate to AvgRate, expressed as a percentage.}
\end{description}

\begin{Options}

    \OptItem{\Opt{-h}}
            {Displays the list of options.}
    \OptItem{\Opt{-l}}
            {Puts \Condor{top} in to a live, continually updating mode.}
    \OptItem{\OptArg{-p}{centralmanagerhostname[:portname]}}
            {Query the daemon via the specified central manager. If
              omitted, the value of the configuration variable
              \MacroNI{COLLECTOR\_HOST} is used.}
    \OptItem{\OptArg{-n}{name}}
            {Query the daemon named \Arg{name}. If omitted, the value
              used will depend on the type of daemon queried (see
              Daemon Options).}
    \OptItem{\OptArg{-d}{delay}}
            {Specifies the \Arg{delay} between ClassAd updates, in
              integer seconds. If omitted, the value of the
              configuration variable \MacroNI{STATISTICS\_WINDOW\_QUANTUM} is
              used.}
    \OptItem{\OptArg{-c}{columnset}}
            {Display \Arg{columnset} set of columns. Valid \Arg{columnset}s are: 
              default, runtime, count, all.}
    \OptItem{\OptArg{-s}{sortcolumn}}
            {Sort table by \Arg{sortcolumn}. Defaults to InstRt.}
    \OptItem{\Opt{---attrs=\lt{}attr1,attr2,...\gt{}}}
            {Comma-delimited list of additional ClassAd attributes
              to monitor.}

    \textbf{Daemon Options}
    \OptItem{\Opt{---collector}}
            {Monitor \Condor{collector} ClassAds. If -n is not set,
              the constraint ``Machine == \MacroNI{COLLECTOR\_HOST}''
              will be used.}
    \OptItem{\Opt{---negotiator}}
            {Monitor \Condor{negotiator} ClassAds. If -n is not set,
              the constraint ``Machine == \MacroNI{COLLECTOR\_HOST}''
              will be used.}
    \OptItem{\Opt{---master}}
            {Monitor \Condor{master} ClassAds. If -n is not set,
              the constraint ``Machine == \MacroNI{COLLECTOR\_HOST}''
              will be used.}
    \OptItem{\Opt{---schedd}}
            {Monitor \Condor{schedd} ClassAds. If -n is not set,
              the constraint ``Machine == \MacroNI{FULL\_HOSTNAME}''
              will be tried, 
              otherwise the first \Condor{schedd} ClassAd
              returned from the \Condor{collector} will be used.}
    \OptItem{\Opt{---startd}}
            {Monitor \Condor{startd} ClassAds. If -n is not set,
              the constraint ``Machine == \MacroNI{FULL\_HOSTNAME}''
              will be tried, 
              otherwise the first \Condor{startd} ClassAd
              returned from the \Condor{collector} will be used.}

\end{Options}

\end{ManPage}
