\begin{ManPage}{\label{man-condor-vacate}\Condor{vacate}}{1}
{Vacate jobs that are running on the specified hosts}
\Synopsis \SynProg{\Condor{vacate}}
\ToolArgsBase

\SynProg{\Condor{vacate}}
\oOptnm{-graceful $|$ -fast}
\ToolDebugOption
\ToolWhere

\index{HTCondor commands!condor\_vacate}
\index{condor\_vacate command}

\Description
\Condor{vacate} causes HTCondor to checkpoint any running jobs
on a set of machines
and force the jobs to vacate the machine.
The job(s) remains in
the submitting machine's job queue. 

Given the (default) \Opt{-graceful} option,
a job running under the standard universe
will first produce a checkpoint and then the job will be killed.
HTCondor will then restart the job somewhere else, using the checkpoint to
continue from where it left off.
A job running under the vanilla universe
is killed, and HTCondor
restarts the job from the beginning somewhere else.
\Condor{vacate} has no effect on a machine with 
no HTCondor job currently running. 

There is generally no need for the user or administrator to explicitly run
\Condor{vacate}.
HTCondor takes care of jobs in this way
automatically following the policies given in configuration files.   

\begin{Options}
	\ToolArgsBaseDesc
    \OptItem{\Opt{-graceful}}{Inform the job to checkpoint, then soft-kill it.}
    \OptItem{\Opt{-fast}}{Hard-kill jobs instead of checkpointing them}
	\ToolDebugDesc
	\ToolArgsLocateDesc
\end{Options}

\ExitStatus

\Condor{vacate} will exit with a status value of 0 (zero) upon success,
and it will exit with the value 1 (one) upon failure.

\Examples
To send a \Condor{vacate} command to two named machines:
\begin{verbatim}
% condor_vacate  robin cardinal
\end{verbatim}

To send the \Condor{vacate} command to a machine
within a pool of machines other than the local pool,
use the \Opt{-pool} option.
The argument is the name of the central manager for the pool.
Note that one or more machines within the pool must be
specified as the targets for the command.
This command sends the command to
a the single machine named \Opt{cae17} within the
pool of machines that has \Opt{condor.cae.wisc.edu} as
its central manager:
\begin{verbatim}
% condor_vacate -pool condor.cae.wisc.edu -name cae17
\end{verbatim}

\end{ManPage}
