\begin{ManPage}{\label{man-condor-prio}\Condor{prio}}{1}
{change priority of jobs in the HTCondor queue} 
\Synopsis \SynProg{\Condor{prio}}
\OptArg{-p}{priority} $|$ \OptArg{+}{value} $|$ \OptArg{-}{value}
\oOptArg{-n}{schedd\_name}
\Arg{cluster \Bar cluster.process \Bar username \Bar -a}

\SynProg{\Condor{prio}}
\OptArg{-p}{priority} $|$ \OptArg{+}{value} $|$ \OptArg{-}{value}
\Lbr \OptArg{-pool}{pool\_name}  \OptArg{-n}{schedd\_name} \Rbr
\Arg{cluster \Bar cluster.process \Bar username \Bar -a}

\index{HTCondor commands!condor\_prio}
\index{condor\_prio command}

\Description

\Condor{prio} changes the priority of one or more jobs in the HTCondor queue.
If the job identification is given by \Arg{cluster.process},
\Condor{prio} attempts to change the priority of the single job
with job ClassAd attributes \Attr{ClusterId} and \Attr{ProcId}.
If described by \Arg{cluster},
\Condor{prio} attempts to change the priority of all processes with the
given \Attr{ClusterId} job ClassAd attribute.
If \Arg{username} is specified, \Condor{prio} attempts to change priority
of all jobs belonging to that user.
For \Arg{-a}, \Condor{prio} attempts to change priority of
all jobs in the queue.

The user must set a new priority with the \Opt{-p} option,
or specify a priority adjustment. 
The priority of a job can be any integer, with higher numbers
corresponding to greater priority.
For adjustment of the current priority,
\OptArg{+}{value} increases the priority by the amount given with \Arg{value}.
\OptArg{-}{value} decreases the priority by the amount given with \Arg{value}.

Only the owner of a job or the super user can change the priority.

The priority changed by \Condor{prio} is only used when
comparing to the priority
jobs owned by the same user and submitted from the same machine.

\begin{Options}
  \OptItem{\OptArg{-n}{schedd\_name}}{Change priority of jobs queued
    at the specified \Condor{schedd} in the local pool.}
  \OptItem{\OptArg{-pool}{pool\_name} \OptArg{-n}{schedd\_name}}{Change 
    priority of jobs queued at the specified \Condor{schedd} 
    in the specified pool.} 
\end{Options}

\ExitStatus

\Condor{prio} will exit with a status value of 0 (zero) upon success,
and it will exit with the value 1 (one) upon failure.

\end{ManPage}
