7\begin{ManPage}{\Condor{now}}{man-condor-now}{1}
{Start a job \emph{now}.}
\index{HTCondor commands!condor\_now}
\index{condor\_now ommand}

\Synopsis

\SynProg{\Condor{now}} \Opt{-help}

\SynProg{\Condor{now}} \oOptArg{-name}{scheduler \oOptArg{-pool}{central-manager}}
	\oOpt{-debug}
	\Arg{now-job} \Arg{vacate-job} \oArg{vacate-job+}

\Description

\Condor{now} tries to run the \Arg{now-job} \emph{now}.  The \Arg{vacate-job}
is immediately vacated; after it terminates, if the schedd still has the
claim to the vacated job's slot -- and it usually will -- the schedd will
immediately start the now-job on that slot.

If you specify multiple \Arg{vacate-job}s, each will be immediately vacated;
after they all terminate, the schedd will try to coalesce their slots into a
single, larger, slot and then use that slot to run the now-job.

You must specify each job using both the cluster and proc IDs.

\begin{Options}
	\OptItem {\Opt{-help}}
		{Print a usage reminder.}
	\OptItem {\Opt{-debug}}
		{Print debugging output.  Control the verbosity with the environment variables \_CONDOR\_TOOL\_DEBUG, as usual.}
	\OptItem {\OptArg{-name}{scheduler \oOptArg{-pool}{central-manager}}}
		{Specify the scheduler('s name) and (optionally) the pool to find it in.}
\end{Options}

\GenRem

The now-job and the vacated-job must have the same owner; if you are not
the queue super-user, you must own both jobs.  The jobs must be on the same
schedd, and both jobs must be in the vanilla universe.  The now-job must be
idle and the vacated-job must be running.

\Examples

To begin running job 17.3 as soon as possible using job 4.2's slot:

\begin{verbatim}
  condor_now 17.3 4.2
\end{verbatim}

To try to figure out why that doesn't work for the `magic' scheduler in
the 'gandalf' pool, set the environment variable \_CONDOR\_TOOL\_DEBUG
to `D\_FULLDEBUG' and then:

\begin{verbatim}
  condor_now -debug -schedd magic -pool gandalf 17.3 4.2
\end{verbatim}

\ExitStatus

\Condor{now} will exit with a status value of 0 (zero) if the schedd accepts
its request to vacate the vacate-job and start the now-job in its place.  It
does \emph{not} wait for the now-job to have started running.

\end{ManPage}
