\begin{ManPage}{\label{man-condor-tail}\Condor{tail}}{1}
{Display the last contents of a running job's standard output or file }
\index{HTCondor commands!condor\_tail}
\index{condor\_tail command}

\Synopsis \SynProg{\Condor{tail}}
\oOpt{-help} | \oOpt{-version}

\SynProg{\Condor{tail}}
\oOptArg{-pool}{centralmanagerhostname\Lbr:portnumber\Rbr}
\oOptArg{-name}{name}
\oOpt{-debug}
\oOptArg{-maxbytes}{numbytes}
\oOpt{-auto-retry}
\oOpt{-follow}
\oOpt{-no-stdout}
\oOpt{-stderr}
\Arg{job-ID}
\oArg{-filename1}
\oArg{, -filename2 \Dots}

\Description

\Condor{tail} displays the last bytes of a file in the sandbox
of a running job identified by the command line argument \Arg{job-ID}.
\File{stdout} is tailed by default.
The number of bytes displayed is limited to 1024, unless changed
by specifying the \Opt{-maxbytes} option.
This limit is applied for each individual tail of a file;
for example, when following a file, the limit is applied each
subsequent time output is obtained. 

\begin{Options}
    \OptItem{\Opt{-help}}{Display usage information and exit.}
    \OptItem{\Opt{-version}}{Display version information and exit.}
    \OptItem{\OptArg{-pool}{centralmanagerhostname[:portnumber]}}
        {Specify a pool by giving the
        central manager's host name and an optional port number.}
    \OptItem{\OptArg{-name}{name}}{Query the \Condor{schedd} daemon
        identified with \Arg{name}.}
    \OptItem{\Opt{-debug}}{Display extra debugging information.}
    \OptItem{\OptArg{-maxbytes}{numbytes}}{Limits the maximum number of bytes
        transferred per tail access.  
        If not specified, the maximum number of bytes is 1024.}
    \OptItem{\Opt{-auto-retry}}{Retry the tail of the file(s) 
        every 2 seconds, if the job is not yet running.}
    \OptItem{\Opt{-follow}}{Repetitively tail the file(s), 
        until interrupted.}
    \OptItem{\Opt{-no-stdout}}{Do not tail \File{stdout}. }
    \OptItem{\Opt{-stderr}}{Tail \File{stderr} instead of \File{stdout}. }
\end{Options}

\ExitStatus

The exit status of \Condor{tail} is zero on success.

\end{ManPage}

