\begin{ManPage}{\Condor{suspend}}{man-condor-suspend}{1}
{suspend jobs from the HTCondor queue}
\index{HTCondor commands!condor\_suspend}
\index{condor\_suspend command}

\Synopsis \SynProg{\Condor{suspend}}
\ToolArgsBase

\SynProg{\Condor{suspend}}
\ToolDebugOption
\ToolLocate
\Argnm{ cluster \Bar{} cluster.process \Bar{} user
\Bar{} \OptArg{-constraint}{expression} \Bar{} \Opt{-all} }

\Description

\Condor{suspend} suspends one or more jobs from the HTCondor job queue.  
When a job is suspended,
the match between the \Condor{schedd} and machine is not been broken,
such that the claim is still valid.
But, the job is not making any progress and HTCondor is no longer 
generating a load on the machine.
If the \Opt{-name} option is specified, the named \Condor{schedd} is targeted
for processing.  
Otherwise, the local \Condor{schedd} is targeted.
The job(s) to be suspended are identified by one of the job identifiers, as
described below.
For any given job, only the owner of the job or one of the queue super users
(defined by the \MacroNI{QUEUE\_SUPER\_USERS} macro) can suspend the job.

\begin{Options}
	\ToolArgsBaseDesc
	\ToolLocateDesc
    \ToolDebugDesc
	\OptItem{\Arg{cluster}}{Suspend all jobs in the specified cluster}
	\OptItem{\Arg{cluster.process}}{Suspend the specific job in the cluster}
	\OptItem{\Arg{user}}{Suspend jobs belonging to specified user}
	\OptItem{\OptArg{-constraint}{expression}} {Suspend all jobs which match
	                the job ClassAd expression constraint}
	\OptItem{\Opt{-all}}{Suspend all the jobs in the queue}
\end{Options}

\ExitStatus

\Condor{suspend} will exit with a status value of 0 (zero) upon success,
and it will exit with the value 1 (one) upon failure.

\Examples
To suspend all jobs except for a specific user:
\footnotesize
\begin{verbatim}
% condor_suspend -constraint 'Owner =!= "foo"'
\end{verbatim}
\normalsize

Run \Condor{continue} to continue execution.
\end{ManPage}
