\begin{ManPage}{\Condor{update\_machine\_ad}}{1}{update a machine ClassAd}
\label{man-condor-update-machine-ad}
\index{HTCondor commands!condor\_update\_machine\_ad}
\index{condor\_update\_machine\_ad command}

\Synopsis \SynProg{\Condor{update\_machine\_ad}}
\ToolArgsBase

\SynProg{\Condor{update\_machine\_ad}}
\oOptArg{-pool}{centralmanagerhostname[:portnumber]}
\oOptArg{-name}{startdname}
\Arg{path/to/update-ad}

\Description
\Condor{update\_machine\_ad} modifies the specified \Condor{startd}
daemon's machine ClassAd.
The ClassAd in the file given by \File{path/to/update-ad}
represents the changed attributes.
The changes persists until the \Condor{startd} restarts.
If no file is specified on the command line, \Condor{update\_machine\_ad}
reads the update ClassAd from \File{stdin}.

Contents of the file or \File{stdin} must contain a complete
ClassAd.
Each line \emph{must} be terminated by a newline character,
including the last line of the file.
Lines are of the form

\begin{verbatim}
<attribute> = <value>
\end{verbatim}

Changes to certain ClassAd attributes will cause the 
\Condor{startd} to regenerate values for other ClassAd attributes.
An example of this is setting \Attr{HasVM}.
This will cause \Attr{OfflineUniverses},
\Attr{VMOfflineTime}, and \Attr{VMOfflineReason} to change.

\begin{Options}
  \OptItem{\Opt{-help}}{Display usage information and exit}
  \OptItem{\Opt{-version}}{Display the HTCondor version and exit}
  \OptItem{\OptArg{-pool}{centralmanagerhostname[:portnumber]}}
    {Specify a pool by giving the
     central manager's host name and an optional port number}
  \OptItem{\OptArg{-name}{startdname}}{Send the command to a machine 
     identified by \Arg{startdname}}
\end{Options}

\GenRem

This tool is intended for the use of system administrators when dealing
with offline universes.  

\Examples

To re-enable matching with the VM universe jobs,
place on \File{stdin} a complete
ClassAd (including the ending newline character) to
change the value of ClassAd attribute \Attr{HasVM}:

\begin{verbatim}
echo "HasVM = True
" | condor_update_machine_ad
\end{verbatim}

To prevent vm universe jobs from matching with the machine:

\begin{verbatim}
echo "HasVM = False
" | condor_update_machine_ad
\end{verbatim}

To prevent vm universe jobs from matching with the machine
and specify a reason:

\begin{verbatim}
echo "HasVM = False
VMOfflineReason = \"Cosmic rays.\"
" | condor_update_machine_ad
\end{verbatim}

Note that the quotes around the reason are required by ClassAds, 
and they must be escaped because of the shell.
Using a file instead of \File{stdin} may be preferable
in these situations, 
because neither quoting nor escape characters are needed.

\ExitStatus

\Condor{update\_machine\_ad} will exit with a status value of 0 (zero) upon
success, and it will exit with the value 1 (one) upon failure.

\end{ManPage}
