\begin{ManPage}{\label{man-condor-set-shutdown}\Condor{set\_shutdown}}{1}
{Set a program to execute upon \Condor{master} shut down}
\Synopsis \SynProg{\Condor{set\_shutdown}}
\ToolArgsBase

\SynProg{\Condor{set\_shutdown}}
\OptArg{-exec}{programname} 
\ToolDebugOption
\ToolWhere

\index{HTCondor commands!condor\_set\_shutdown}
\index{condor\_set\_shutdown command}

\Description 

\Condor{set\_shutdown} sets a program (typically a script) to execute
when the \Condor{master} daemon shuts down.
The \OptArg{-exec}{programname} argument is required,
and specifies the program to run.  
The string \Arg{programname} must match the
string that defines \MacroNI{Name} in the configuration variable
\MacroNI{MASTER\_SHUTDOWN\_$<$Name$>$} in the \Condor{master} daemon's
configuration. 
If it does not match, the \Condor{master} will log an error and ignore the
request.

For security reasons of authentication and authorization,
this command requires ADMINISTRATOR level of access.

\begin{Options}
  \ToolArgsBaseDesc
  \ToolDebugDesc
  \ToolArgsLocateDesc
\end{Options}

\ExitStatus
\Condor{set\_shutdown} will exit with a status value of 0 (zero) upon
success, and it will exit with the value 1 (one) upon failure.


\Examples
To have all \Condor{master} daemons run the program
\Prog{/bin/reboot} upon shut down, configure the \Condor{master} 
to contain a definition similar to:
\begin{verbatim}
MASTER_SHUTDOWN_REBOOT = /sbin/reboot
\end{verbatim}
where \MacroNI{REBOOT} is an invented name for this program that
the \Condor{master} will execute.
On the command line, run
\begin{verbatim}
% condor_set_shutdown -exec reboot -all
% condor_off -graceful -all
\end{verbatim}
where the string \verb@reboot@ matches the invented name.

\end{ManPage}
