\begin{ManPage}{\label{man-condor-findhost}\Condor{findhost}}{1}
{find machine(s) in the pool that 
can be used with minimal impact on currently running HTCondor jobs
and best meet any specified constraints}
\Synopsis \SynProg{\Condor{findhost}}
\oOpt{-help}
\oOpt{-m}
\oOptArg{-n}{num}
\oOptArg{-c}{c\_expr}
\oOptArg{-r}{r\_expr}
\oOptArg{-p}{centralmanagerhostname}

\index{HTCondor commands!condor\_findhost}
\index{condor\_findhost command}

\Description

\Condor{findhost} searches an HTCondor pool of machines for the
best machine or machines that
will have the minimum impact on running HTCondor jobs
if the machine or machines are taken out of the pool.
The search may be limited to the machine or machines 
that match a set of constraints and rank expression.

\Condor{findhost}
returns a fully-qualified domain name for each machine.
The search is limited (constrained) to a specific set of machines
using the \Arg{-c} option.
The search can use the \Arg{-r} option for rank,
the criterion used for selecting a machine or machines from the
constrained list.

\begin{Options}
    \OptItem{\Opt{-help}}{Display usage information and exit}
    \OptItem{\Opt{-m}}{Only search for entire machines.  
        Slots within an entire machine are not considered.}
    \OptItem{\OptArg{-n}{num}}{Find and list up to \Arg{num} machines that
	fulfill the specification. \Arg{num} is an integer greater than zero.}
    \OptItem{\OptArg{-c}{c\_expr}}{Constrain the search to only consider
        machines that result from the evaluation of \Arg{c\_expr}.
        \Arg{c\_expr} is a ClassAd expression.
	}
    \OptItem{\OptArg{-r}{r\_expr}}{\Arg{r\_expr} is the rank expression
        evaluated to use as a basis for machine selection.
        \Arg{r\_expr} is a ClassAd expression.
	}
    \OptItem{\OptArg{-p}{centralmanagerhostname}}{Specify the pool to
        be searched by giving the central manager's host name.
	Without this option, the current pool is searched.}
\end{Options}

\GenRem

% general remarks go here
\Condor{findhost} is used to locate a machine
within a pool that can be taken out of the pool with the least
disturbance of the pool.

An administrator should set preemption requirements for
the HTCondor pool.
The expression 
\begin{verbatim}
(Interactive =?= TRUE )
\end{verbatim}
will let \Condor{findhost} know that it can claim a machine even
if HTCondor would not normally preempt a job running on that machine.

\ExitStatus

The exit status of \Condor{findhost} is zero on success.
If not able to identify as many machines as requested,
it returns one more than the number of machines identified.
For example, if 8 machines are requested, and \Condor{findhost}
only locates 6, the exit status will be 7.
If not able to locate any machines, or an error is encountered,
\Condor{findhost} will return the value 1.

\Examples
To find and list four machines, preferring those with the highest
mips (on Drystone benchmark) rating:
\begin{verbatim}
condor_findhost -n 4 -r "mips"
\end{verbatim}
To find and list 24 machines, considering only those
where the \AdAttr{kflops} attribute is not defined:
\begin{verbatim}
condor_findhost -n 24 -c "kflops=?=undefined"
\end{verbatim}

\end{ManPage}

%  Usage: condor_findhost [-m] -[n number] [-c c_expr] [-r r_expr] [-p pool] 
%  -m: Return entire machine, not slots
%  -n num: Return num machines, where num is an integer greater than zero
%  -c c_expr: Use c_expr as the constraint expression
%  -r r_expr: Use r_expr as the rank expression
%  -p pool: Contact the HTCondor pool "pool"
%  -h: this screen

