\begin{ManPage}{\label{man-condor-restart}\Condor{restart}}{1}
{Restart a set of HTCondor daemons}
\Synopsis \SynProg{\Condor{restart}}
\ToolArgsBase

\SynProg{\Condor{restart}}
\ToolDebugOption
\oOptnm{-graceful $|$ -fast  $|$ -peaceful}
\ToolWhere
\ToolArgsAffect

\index{HTCondor commands!condor\_restart}
\index{condor\_restart command}

\Description 

\Condor{restart} restarts a set of HTCondor daemons on a set
of machines.
The daemons will be put into a consistent state,
killed, and then invoked anew.

If, for example, the \Condor{master} needs to be restarted again with
a fresh state, this is the command that should be used to do so.
If the \MacroNI{DAEMON\_LIST} variable in the configuration file has
been changed, this command is used to restart the \Condor{master}
in order to see this change.
The \Condor{reconfigure} command cannot be used in the case where the
\MacroNI{DAEMON\_LIST} expression changes.

The command
\Condor{restart} with no arguments or with the 
\OptArg{-daemon}{master} option
will safely shut down all running jobs and all submitted
jobs from the machine(s) being restarted, then shut down
all the child daemons of the \Condor{master},
and then restart the \Condor{master}.
This, in turn, will allow the \Condor{master} to start up
other daemons as specified in the \MacroNI{DAEMON\_LIST} configuration
file entry.

For security reasons of authentication and authorization, 
this command requires ADMINISTRATOR level of access.

\begin{Options}
    \ToolArgsBaseDesc
    \ToolDebugDesc
    \OptItem{\Opt{-graceful}}{Gracefully shutdown daemons (the default)
before restarting them}
    \OptItem{\Opt{-fast}}{Quickly shutdown daemons
before restarting them}
    \OptItem{\Opt{-peaceful}}{Wait indefinitely for jobs to finish
before shutting down daemons, prior to restarting them}
    \ToolArgsLocateDesc
    \ToolArgsAffectDesc

\end{Options}

\ExitStatus

\Condor{restart} will exit with a status value of 0 (zero) upon success,
and it will exit with the value 1 (one) upon failure.

\Examples
To restart the \Condor{master} and all its children
on the local host:
\begin{verbatim}
% condor_restart
\end{verbatim}

To restart only the \Condor{startd} on a named machine:
\begin{verbatim}
% condor_restart -name bluejay -daemon startd
\end{verbatim}

To restart a machine within a pool
other than the local pool, use the \Opt{-pool} option.
The argument is the name of the central manager for the pool.
Note that one or more machines within the pool must be
specified as the targets for the command.
This command restarts
the single machine named \Opt{cae17} within the
pool of machines that has \Opt{condor.cae.wisc.edu} as
its central manager:
\begin{verbatim}
% condor_restart -pool condor.cae.wisc.edu -name cae17
\end{verbatim}

\end{ManPage}
