\begin{ManPage}{\label{man-condor-on}\Condor{on}}{1}
{Start up HTCondor daemons}
\Synopsis \SynProg{\Condor{on}}
\ToolArgsBase

\SynProg{\Condor{on}}
\ToolDebugOption
\ToolWhere \ToolArgsAffect

\index{HTCondor commands!condor\_on}
\index{condor\_on command}

\Description 

\Condor{on} starts up a set of the HTCondor daemons on a set of
machines.
This command assumes that the \Condor{master} is already
running on the machine.
If this is not the case, \Condor{on} will
fail complaining that it cannot find the address of the master.
The command \Condor{on} with no arguments or with
 the \OptArg{-daemon}{master} option will
tell the \Condor{master} to start up the HTCondor daemons specified
in the configuration variable \MacroNI{DAEMON\_LIST}.
If a daemon other than the \Condor{master} is specified
with the \Opt{-daemon} option,
\Condor{on} starts up only that daemon.

This command cannot be used to start up the \Condor{master} daemon.

For security purposes (authentication and authorization),
this command requires an administrator's level of access.
See
section~\ref{sec:Config-Security} on page~\pageref{sec:Config-Security}
for further explanation.

\begin{Options}
    \ToolArgsBaseDesc
    \ToolDebugDesc
    \ToolArgsLocateDesc
    \ToolArgsAffectDesc
\end{Options}

\ExitStatus

\Condor{on} will exit with a status value of 0 (zero) upon success,
and it will exit with the value 1 (one) upon failure.

\Examples
To begin running all daemons (other than \Condor{master}) given
in the configuration variable \MacroNI{DAEMON\_LIST}
on the local host:
\begin{verbatim}
% condor_on
\end{verbatim}

To start up only the \Condor{negotiator} on two named machines:
\begin{verbatim}
% condor_on  robin cardinal -daemon negotiator
\end{verbatim}

To start up only a daemon within a pool of machines
other than the local pool, use the \Opt{-pool} option.
The argument is the name of the central manager for the pool.
Note that one or more machines within the pool must be
specified as the targets for the command.
This command starts up only the \Condor{schedd} daemon
on the single machine named \Opt{cae17} within the
pool of machines that has \Opt{condor.cae.wisc.edu} as
its central manager:
\begin{verbatim}
% condor_on -pool condor.cae.wisc.edu -name cae17 -daemon schedd
\end{verbatim}

\end{ManPage}
