\begin{ManPage}{\label{man-condor-job-router-tool}\Condor{job\_router\_tool}}{1}
{Discover and display information related to job routing}
\index{HTCondor commands!condor\_job\_router\_tool}
\index{condor\_job\_router\_tool command}
\Synopsis
\SynProg{\Condor{job\_router\_tool}}
\ToolArgsBase

\SynProg{\Condor{job\_router\_tool}}
\Opt{-config}

\SynProg{\Condor{job\_router\_tool}}
\Opt{-match-jobs \OptArg{-jobads}{filename} }
\oOpt{-ignore-prior-routing}

\Description
\Condor{job\_router\_tool} displays information about job routing.
The information will be either the available, configured routes or
the routes for specified jobs.

\begin{Options}
  \OptItem{\Opt{-help}}{Display usage information and exit.}
  \OptItem{\Opt{-version}}{Display HTCondor version information and exit.}
  \OptItem{\Opt{-config}}{Display configured routes.}
  \OptItem{\Opt{-match-jobs}}{For each job listed in the file specified
    by the \Opt{-jobads} option, display the first route found.}
  \OptItem{\Opt{-ignore-prior-routing}}{For each job, remove any existing
    routing ClassAd attributes,  
    and set attribute \Attr{JobStatus} 
    to the Idle state before finding the first route.}
  \OptItem{\OptArg{-jobads}{filename}}{Read job ClassAds
    from file \Arg{filename}. If \Arg{filename} is \File{-},
    then read from \File{stdin}. }
\end{Options}

\ExitStatus

\Condor{job\_router\_tool} will exit with a status value of 0 (zero) upon 
success,
and it will exit with the value 1 (one) upon failure.

\end{ManPage}
