\begin{ManPage}{\label{man-condor-reschedule}\Condor{reschedule}}{1}
{Update scheduling information to the central manager}

\Synopsis \SynProg{\Condor{reschedule}}
\ToolArgsBase

\SynProg{\Condor{reschedule}}
\ToolDebugOption
\ToolWhere

\index{HTCondor commands!condor\_reschedule}
\index{condor\_reschedule command}

\Description 

\Condor{reschedule} updates the information about a set of machines' resources
and jobs to the central manager.
This command is used to force an update before viewing the
current status of a machine.
Viewing the status of a machine is done with 
the \Condor{status} command.
\Condor{reschedule} also
starts a new negotiation cycle between resource owners and resource providers
on the central managers, so that jobs can be matched with machines right
away.
This can be useful in situations where the time between negotiation
cycles is somewhat long, and an administrator wants to see if a job 
in the queue will get matched without waiting for the next negotiation cycle.

A new negotiation cycle cannot occur more frequently than
every 20 seconds.
Requests for new negotiation cycle within that
20 second window will be deferred until 20 seconds have passed
since that last cycle.

\begin{Options}
	\ToolArgsBaseDesc
	\ToolDebugDesc
	\ToolArgsLocateDesc
\end{Options}

\ExitStatus

\Condor{reschedule} will exit with a status value of 0 (zero) upon success,
and it will exit with the value 1 (one) upon failure.

\Examples

To update the information on three named machines:
\begin{verbatim}
% condor_reschedule robin cardinal bluejay
\end{verbatim}

To reschedule on a machine within a pool
other than the local pool, use the \Opt{-pool} option.
The argument is the name of the central manager for the pool.
Note that one or more machines within the pool must be
specified as the targets for the command.
This command reschedules 
the single machine named \Opt{cae17} within the
pool of machines that has \Opt{condor.cae.wisc.edu} as
its central manager:
\begin{verbatim}
% condor_reschedule -pool condor.cae.wisc.edu -name cae17
\end{verbatim}

\end{ManPage}
