\begin{ManPage}{\label{man-condor-userlog}\Condor{userlog}}{1}
{Display and summarize job statistics from job log files.}
\Synopsis \SynProg{\Condor{userlog}}
\oOpt{-help} 
\oOpt{-total \Bar -raw} 
\oOpt{-debug} 
\oOpt{-evict} 
\oOptArg{-j}{cluster \Bar cluster.proc}
\oOpt{-all} 
\oOpt{-hostname} 
\Arg{logfile \Dots}

\Description
\Condor{userlog} parses the information in job log files and displays
summaries for each workstation allocation and for each job.  See the
manual page for \Condor{submit} on page~\pageref{man-condor-submit} for
instructions for specifying that HTCondor write a log file for your
jobs.

If \Opt{-total} is not specified, \Condor{userlog} will first display
a record for each workstation allocation, which includes the following
information:

\begin{description}
\item[Job] The cluster/process id of the HTCondor job.
\item[Host] The host where the job ran.  By default, the host's IP
address is displayed.  If \Opt{-hostname} is specified, the host name
will be displayed instead.
\item[Start Time] The time (month/day hour:minute) when the job began
running on the host.
\item[Evict Time] The time (month/day hour:minute) when
the job was evicted from the host.
\item[Wall Time] The time (days+hours:minutes) for which this workstation was
allocated to the job.
\item[Good Time] The allocated time (days+hours:min) which
contributed to the completion of this job.  If the job exited during
the allocation, then this value will equal ``Wall Time.''  If the job
performed a checkpoint, then the value equals the work saved in
the checkpoint during this allocation.  If the job did not exit or
perform a checkpoint during this allocation, the value will be 0+00:00.
This value can be greater than 0 and less than ``Wall Time'' if the
application completed a periodic checkpoint during the allocation but
failed to checkpoint when evicted.
\item[CPU Usage] The CPU time (days+hours:min) which contributed to
the completion of this job.
\end{description}

\Condor{userlog} will then display summary statistics per host:

\begin{description}
\item[Host/Job] The IP address or host name for the host.
\item[Wall Time] The workstation time (days+hours:minutes) allocated by
this host to the jobs specified in the query.  By default, all jobs in
the log are included in the query.
\item[Good Time] The time (days+hours:minutes) allocated on this host which
contributed to the completion of the jobs specified in the query.
\item[CPU Usage] The CPU time (days+hours:minutes) obtained from this
host which
contributed to the completion of the jobs specified in the query.
\item[Avg Alloc] The average length of an allocation on this host
(days+hours:minutes).
\item[Avg Lost] The average amount of work lost (days+hours:minutes) when a job
was evicted from this host without successfully performing a checkpoint.
\item[Goodput] This percentage is computed as Good Time divided by
Wall Time.
\item[Util.] This percentage is computed as CPU Usage divided by Good
Time.
\end{description}

\Condor{userlog} will then display summary statistics per job:

\begin{description}
\item[Host/Job] The cluster/process id of the HTCondor job.
\item[Wall Time] The total workstation time (days+hours:minutes) allocated to
this job.
\item[Good Time] The total time (days+hours:minutes) allocated to this
job which 
contributed to the job's completion.
\item[CPU Usage] The total CPU time (days+hours:minutes) which
contributed to this 
job's completion.
\item[Avg Alloc] The average length of a workstation allocation
obtained by this job in minutes (days+hours:minutes).
\item[Avg Lost] The average amount of work lost (days+hours:minutes)
when this job 
was evicted from a host without successfully performing a checkpoint.
\item[Goodput] This percentage is computed as Good Time divided by
Wall Time.
\item[Util.] This percentage is computed as CPU Usage divided by Good
Time.
\end{description}

Finally, \Condor{userlog} will display a summary for all hosts and
jobs.

\begin{Options}
    \OptItem{\Opt{-help}}{Get a brief description of the supported options}
    \OptItem{\Opt{-total}}{Only display job totals}
    \OptItem{\Opt{-raw}}{Display raw data only}
    \OptItem{\Opt{-debug}}{Debug mode}
    \OptItem{\Opt{-j}}{Select a specific cluster or cluster.proc}
    \OptItem{\Opt{-evict}}{Select only allocations which ended due to eviction}
    \OptItem{\Opt{-all}}{Select all clusters and all allocations}
    \OptItem{\Opt{-hostname}}{Display host name instead of IP address}
\end{Options}

\GenRem
Since the HTCondor job log file format does not contain a year field in
the timestamp, all entries are assumed to occur in the current year.
Allocations which begin in one year and end in the next will be
silently ignored.

\ExitStatus

\Condor{userlog} will exit with a status value of 0 (zero) upon success,
and it will exit with the value 1 (one) upon failure.

\end{ManPage}
