\begin{ManPage}{\label{man-condor-analyze}\Condor{analyze}}{1}
{Display information about jobs in queue}

\Synopsis \SynProg{\Condor{analyze}}
\oOpt{-help} 

\SynProg{\Condor{analyze}}
\oOpt{-global} 
\oOptArg{-submitter}{submitter}
\oOptArg{-name}{name} 
\oOptArg{-pool}{centralmanagerhostname[:portnumber]}
\oOpt{-long}
\oOpt{-run}
\oOpt{-expert}
\oArg{\{cluster $|$ cluster.process $|$ owner $|$
  \OptArg{-constraint}{expression} \Dots \} }

\index{Condor commands!condor\_analyze}
\index{condor\_analyze command}

\Description

\Condor{analyze} displays analysis information about jobs in the
Condor job queue.  on a per machine basis.
By default, \Condor{analyze} queries the local job queue,
but this behavior may be modified.

\begin{Options}
    \OptItem{\Opt{-global}}{Provides an analysis of all jobs in
       all queues.  Note that this can be a lengthy analysis for large queues.}
    \OptItem{\OptArg{-submitter}{submittername}}{Does an analysis on all jobs
       of the given job submitter.}
    \OptItem{\Opt{-help}}{Prints a short help screen and exits.}
    \OptItem{\OptArg{-name}{name}}{Restricts the analysis to jobs in the
       queue of given host name's \Condor{schedd} daemon.}
    \OptItem{\OptArg{-pool}{centralmanagerhostname[:portnumber]}}{Analyzes
       jobs in a specific pool by giving the central manager's host name
       and an optional port number.
       The default is given by the value of the \Macro{COLLECTOR\_HOST}
       macro as specified in the configuration file.}
    \OptItem{\Opt{-long}}{Requests a verbose output.}
    \OptItem{\Opt{-expert}}{Displays shorter error messages.}

To restrict the display to jobs of interest, a list of zero or more 
restrictions may be supplied.  Each restriction may be one of:

	\OptItem{\Arg{cluster}}{Matches all jobs belonging
		to the specified cluster.}
	\OptItem{\Arg{cluster.process}}{Matches jobs which
		belong to the specified cluster and have the specified process number.}
	\OptItem{\Arg{owner}}{Matches all jobs owned by the specified owner.}
	\OptItem{\OptArg{-constraint}{expression}}{Matches all jobs that
		satisfy the specified ClassAd expression. (See section~\ref{sec:classad-reference}
		for a discussion of ClassAd expressions.)}

\end{Options}

\GenRem
Although \Condor{analyze} provides a very good first approximation,
the analyzer 
cannot diagnose all possible situations because the analysis is based on 
instantaneous and local information.  Therefore, there are some situations 
(such as when several submitters are contending for resources, or if the pool 
is rapidly changing state) which cannot be accurately diagnosed.

\Examples

\ExitStatus

\Condor{analyze} will exit with a status value of 0 (zero) upon success,
and it will exit with the value 1 (one) upon failure.

\end{ManPage}
