\begin{ManPage}{\label{man-install-release}\Prog{install\_release}}{1}
{install an arbitrary software release into a named directory}

\Synopsis \SynProg{\Prog{install\_release}}
\oOpt{-help}

\SynProg{\Prog{install\_release}}
\oOpt{-f}
\oOptArg{-basedir}{directory}
\oOptArg{-log}{filename}
\oOpt{-wget}
\oOptArg{-globuslocation}{directory}
\oOptArg{-o}{otherfile1\ldots}
\Arg{package}

\index{Deployment commands!install\_release}
\index{install\_release}

\Description

\Prog{install\_release} installs an arbitrary software release into a
named directory.  In addition it creates a log of the installed files
for easy uninstallation.  This program can install packages of type
tar, gzip, or gzip'ed tar.  The installation package can be located on
a mounted file system, an http server, an ftp server, or a grid ftp
server.

\begin{Options}
  \OptItem{\OptArg{-basedir}{directory}}{
    The directory where the package should be installed.
  }
  \OptItem{\Opt{-f}}{
    Forcefully overwrite files if they exist.
  }
  \OptItem{\OptArg{-globuslocation}{directory}}{
    This program does not come prepackaged with globus-url-copy or the
    supporting libraries.  If globus is not installed in the
    \File{/opt/globus} directory, the user must specify the installation
    location of globus using this option.
  }
  \OptItem{\Opt{-help}}{
    Display brief usage information and exit.
  }
  \OptItem{\OptArg{-log}{filename}}{
    The name this program should use when creating the installation
    log.
  }
  \OptItem{\OptArg{-o}{otherfile1\ldots}}{
    A list of files that will be installed alongside the installation
    package.  They will only be copied, no extraction or decompression
    will be performed on these files.  These files will be logged in the
    installation log.
  }
  \OptItem{\Arg{package}}{
    The full path to the installation package.
    Locations on file systems can be specified without the
    \File{file:} prefix, but other locations must prefix with the
    appropriate protocol (\File{http:}, \File{ftp:}, or \File{gsiftp:}).
  }
  \OptItem{\Opt{-wget}}{
    This program defaults to using \Prog{globus-url-copy}
    to fetch the installation package.  This option specifies that this
    program should use \Prog{wget} for http and ftp requests and Perl's
    copy function for file system requests.  \Prog{wget} must be
    installed on the machine and must be in the user's path.
  }
\end{Options}
  
\ExitStatus

\Prog{install\_release} will exit with a status value of 0 (zero) upon
success, and non-zero otherwise.

\SeeAlso
\Prog{cleanup\_release} (on page~\pageref{man-cleanup-release})

\end{ManPage}
