\begin{ManPage}
{\label{man-procd-ctl}procd\_ctl}{1}
{command line interface to the \Condor{procd}}
\Synopsis \SynProg{procd\_ctl} 
\Opt{-h}

\SynProg{procd\_ctl} 
\OptArg{-A}{address-file}
\oOpt{command}

\index{HTCondor commands!procd\_ctl}
\index{procd\_ctl command}

\Description 

This is a programmatic interface to the \Condor{procd} daemon. 
It may be used to 
cause the \Condor{procd} to do anything that the \Condor{procd}
is capable of doing,
such as tracking and managing process families.

This is a program only available for the Linux ports of HTCondor.

\Prog{procd\_ctl} honors the discovery algorithm for HTCondor's configuration
files, which specify debugging information.
As such, if HTCondor is not installed or the configuration files are
unavailable,
then set the environment variable \Env{CONDOR\_CONFIG} 
to \File{/dev/null} to be utilized by the discovery algorithm.

The \Opt{-h} option prints out usage information and exits.
The  \Arg{address-file} specification within the \Opt{-A} argument
specifies the path and file name of the address file
which the named pipe clients must use to speak with the \Condor{procd}.

One command is given to the \Condor{procd}. 
The choices for the command are defined by the Options. 

\begin{Options}

  \OptItem{\Opt{TRACK\_BY\_ASSOCIATED\_GID} \Arg{GID} \oArg{PID}}
  {Use the specified \Arg{GID} to track the specified family rooted at 
  \Arg{PID}.  
  If the optional \Arg{PID} is not specified, 
  then the PID used is the one given or assumed by \Condor{procd}.}

  \OptItem{\Opt{GET\_USAGE} \oArg{PID}}
  {Get the total usage information about the PID family at \Arg{PID}.
  If the optional \Arg{PID} is not specified, 
  then the PID used is the one given or assumed by \Condor{procd}.}

  \OptItem{\Opt{DUMP} \oArg{PID}}
  {Print out information about both the root \Arg{PID} being watched 
  and the tree of processes under this root \Arg{PID}.
  If the optional \Arg{PID} is not specified, 
  then the PID used is the one given or assumed by \Condor{procd}.}

  \OptItem{\Opt{LIST} \oArg{PID}}
  {With no \Arg{PID} given, print out information about all 
  the watched processes.  
  If the optional \Arg{PID} is specified,
  print out information about the process specified by \Arg{PID} 
  and all its child processes.}

  \OptItem{\Opt{SIGNAL\_PROCESS} \Arg{signal} \oArg{PID}}
  {Send the \Arg{signal} to the process specified by \Arg{PID}.
  If the optional \Arg{PID} is not specified, 
  then the PID used is the one given or assumed by \Condor{procd}.}

  \OptItem{\Opt{SUSPEND\_FAMILY} \Arg{PID}}
  {Suspend the process family rooted at \Arg{PID}.}

  \OptItem{\Opt{CONTINUE\_FAMILY} \Arg{PID}}
  {Continue execution of the process family rooted at \Arg{PID}.}

  \OptItem{\Opt{KILL\_FAMILY} \Arg{PID}}
  {Kill the process family rooted at \Arg{PID}.}

  \OptItem{\Opt{UNREGISTER\_FAMILY} \Arg{PID}}
  {Stop tracking the process family rooted at \Arg{PID}.}

  \OptItem{\Opt{SNAPSHOT}}
  {Perform a snapshot of the tracked family tree.}

  \OptItem{\Opt{QUIT}}
  {Disconnect from the \Condor{procd} and exit.}

\end{Options}
	

\GenRem

This program may be used in a standalone mode, independent of
HTCondor, to track process families. The programs \Prog{procd\_ctl} and
\Prog{gidd\_alloc} are used with the \Condor{procd} in standalone mode
to interact with the daemon and inquire about certain state of running
processes on the machine, respectively.

\ExitStatus

\Prog{procd\_ctl} will exit with a status value of 0 (zero) upon success,
and it will exit with the value 1 (one) upon failure.

\end{ManPage}
