\begin{ManPage}{\label{man-stork-store-cred}\Stork{store\_cred}}{1}
{store a credential on the \Stork{credd} daemon for use by Stork}
\Synopsis \SynProg{\Stork{store\_cred}}
\ToolArgsBase

\SynProg{\Stork{store\_cred}}
\oOpt{-debug}
\oOptArg{-N}{credential-name}
\oOptArg{-m}{\Lbr user@\Rbr hostname\Lbr :portnumber\Rbr}
\oOptArg{-D}{proxy-server-name}
\oOpt{-S}
\OptArg{-n}{hostname:portnumber}
\OptArg{-f}{filename}
\Opt{-t x509}


\index{Condor commands!stork\_store\_cred}
\index{Stork commands!stork\_store\_cred}
\index{stork\_store\_cred command}

\Description 

\Stork{store\_cred} stores a credential to a \Stork{credd}
daemon.

The required \Opt{-t} option identifies that the credential
is an X.509 certificate.

\begin{Options}
  \ToolArgsBaseDesc
  \OptItem{\Opt{-debug}}{Show extra debugging information.}
  \OptItem{\OptArg{-n}{hostname:portnumber}}{Identify the \Stork{credd} daemon
    by host name and port number.}
  \OptItem{\OptArg{-f}{filename}}{A full path and file name where the
    credential is stored.}
  \OptItem{\OptArg{-N}{credential-name}}{A unique name used by
    the \Stork{credd} daemon to identify the credential.
    When not specified, the \Stork{credd} daemon uses the string
    "DEFAULT" as the unique name.}
  \OptItem{\OptArg{-m}{\Lbr user@\Rbr hostname\Lbr :portnumber\Rbr}}
    {An identification of the \Prog{MyProxy} server. }
  \OptItem{\OptArg{-D}{proxy-server-name}}{The distinguished name of
    the \Prog{MyProxy} server.}
  \OptItem{\Opt{-S}}{Read the \Prog{MyProxy} password from
  standard input.}
\end{Options}

\ExitStatus

\Stork{store\_cred} will exit with a status value of 0 (zero) upon success,
and it will exit with the value 1 (one) upon failure.

\end{ManPage}
