%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:platform-linux}Linux}
\index{platform-specific information!Linux}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This section provides information specific to the Linux port of
Condor.
Linux is a difficult platform to support.
It changes very frequently, and Condor has some extremely
system-dependent code (for example, the checkpointing library).

Condor is sensitive to changes in the following elements of the
system: 
\begin{itemize}
\item The kernel version
\item The version of the GNU C library (glibc)
\item the version of GNU C Compiler (GCC) used to build and link
  Condor jobs (this only matters for Condor's Standard universe which
  provides checkpointing and remote system calls)
\end{itemize}

The Condor Team tries to provide support for various releases of the
distribution of Linux.
Red Hat is probably the most popular Linux distribution, and it
provides a common set of versions for the above system components
at which Condor can aim support.
Condor will often work with Linux distributions other than Red Hat (for
example, Debian or SuSE) that have the same versions of the above
components.
However, we do not usually test Condor on other Linux distributions
and we do not provide any guarantees about this.

New releases of Red Hat usually change the versions of some or all of
the above system-level components.
A version of Condor that works with one release of Red Hat might not
work with newer releases.
The following sections describe the details of Condor's support for
the currently available versions of Red Hat Linux on x86 architecture
machines.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:platform-linux-activity}Linux Kernel-specific Information}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{platform-specific information!Linux keyboard and mouse activity}
\index{Linux!keyboard and mouse activity}

Distributions that rely on the Linux 2.4.x and all Linux 2.6.x kernels
through version 2.6.10
do not modify the \Code{atime} of the input device file.
This leads to difficulty when Condor is run using one of these
kernels. 
The problem manifests itself in that Condor cannot properly
detect keyboard or mouse activity.
Therefore, using the activity in policy setting cannot
signal that Condor should stop running a job on a machine.

Condor version 6.6.8 implements a workaround for PS/2 devices.
A better fix is the Linux 2.6.10 kernel
patch linked to from the directions posted at
\URL{http://www.cs.wisc.edu/condor/kernel.patch.html}.
This patch works better for PS/2 devices, and
may also work for USB devices.
A future version of Condor will implement better recognition
of USB devices,
such that the kernel patch will also definitively work for USB devices.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:platform-linux-rh6}Red Hat Version 6.x}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{platform-specific information!Red Hat 6.x}

Red Hat version 6.x is an older release of Red Hat, but it is still used
by a number of sites.
Since Condor has worked on this platform since it was first released,
we still provide binaries that support it.
Red Hat 6.2 uses the 2.2.x Linux kernel series, glibc version 2.1.x,
and GCC version egcs-1.1.2.
To run Condor on this platform and be able to use \Condor{compile},
you should download the Condor \VersionNotice\  binaries listed for use
with ``Linux 2.0.x and 2.2.x (glibc 2.1)''.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:platform-linux-rh7}Red Hat Version 7.x}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{platform-specific information!Red Hat 7.x}

Red Hat version 7.x is fully supported in Condor \VersionNotice.
\Condor{compile} works to link user jobs for the Standard universe
with the versions of GCC and glibc that comes with Red Hat 7.x.
Both the statically linked and dynamically linked versions of the
Condor binaries listed for use with ``Linux 2.4.x (glibc 2.2) - Red Hat
7.1, 7.2, 7.3'' will work with no additional effort.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:platform-linux-rh8}Red Hat Version 8.x}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{platform-specific information!Red Hat 8.x}

Red Hat version 8.x is fully supported in Condor \VersionNotice.
\Condor{compile} works to link user jobs for the Standard universe
with the versions of gcc and glibc that come with Red Hat 8.x.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:platform-linux-rh9}Red Hat Version 9.x}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{platform-specific information!Red Hat 9.x}

Red Hat version 9.x is fully supported in Condor \VersionNotice.
\Condor{compile} works to link user jobs for the Standard universe
with the versions of gcc and glibc that come with Red Hat 9.x.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:platform-linux-fed}Red Hat Fedora 1, 2, and 3}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{platform-specific information!Red Hat Fedora 1, 2, and 3}

Redhat Fedora Core 1, 2, and 3 now support the checkpointing of statically
linked executables just like previous revisions of Condor for Red Hat.
\Condor{compile} works to link user jobs for the Standard universe with
the versions of gcc that are distributed with Red Hat Fedora Core 1, 2,
and 3.

However, there are some caveats: A) You must install and use the dynamic
Red Hat 9.x binaries on the Fedora machine and B) if you wish to do
run a \Condor{compile}d binary in standalone mode(either initially
or in resumption mode), then you must prepend the execution of said
binary with \Bold{setarch i386}. Here is an example: suppose we have a
Condor-linked binary called \Bold{myapp}, running this application as a
standalone executable will result in this command: \Bold{setarch i386
myapp}. The subsequent resumption command will be: 
\Bold{setarch i386 myapp -\_condor\_restart myapp.ckpt}.

When standard universe executables \Condor{compile}d under any currently
supported Linux architecture of the same kind (including Fedora 1,
2, and 3) are running inside Condor, they will automatically execute
in the i386 execution domain. This means that the \Bold{exec\_shield}
functionality (if available) will be turned off and the shared segment
layout will default to Red Hat 9 style. There is no need to do the
above instructions concerning \Bold{setarch} if the executables are
being submitted directly into Condor via \Condor{submit}.





