%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{ClassAd Types}\label{sec:ClassAd-Types}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

ClassAd attributes vary, 
depending on the entity producing the ClassAd.
Therefore, each ClassAd has an attribute named \AdAttr{MyType},
which describes the type of ClassAd.
In addition, the \Condor{collector} appends attributes to
any daemon's ClassAd, whenever the \Condor{collector} is
queried. These additional attributes are listed in
the unnumbered subsection labeled ClassAd Attributes Added by the \Condor{collector}
on page~\pageref{sec:Collector-Added-Attributes}.

Here is a list of defined values for \AdAttr{MyType},
as well as a reference to a list attributes relevant to
that type.

\begin{description}
  \item[\AdAttr{Job}]
  Each submitted job describes its state, for use by the
  \Condor{negotiator} daemon in finding a machine upon which to
  run the job.
  ClassAd attributes that appear in a job ClassAd are listed and described in
  the unnumbered subsection labeled Job ClassAd Attributes
  on page~\pageref{sec:Job-ClassAd-Attributes}.

  \item[\AdAttr{Machine}]
   Each machine in the pool (and hence, the \Condor{startd} daemon running
   on that machine) describes its state.
  ClassAd attributes that appear in a machine ClassAd 
  are listed and described in
  the unnumbered subsection labeled Machine ClassAd Attributes
  on page~\pageref{sec:Machine-ClassAd-Attributes}.

  \item[\AdAttr{DaemonMaster}]
   Each \Condor{master} daemon describes its state.
  ClassAd attributes that appear in a DaemonMaster ClassAd 
  are listed and described in
  the unnumbered subsection labeled DaemonMaster ClassAd Attributes
  on page~\pageref{sec:DaemonMaster-ClassAd-Attributes}.

  \item[\AdAttr{Scheduler}]
   Each \Condor{schedd} daemon describes its state.
  ClassAd attributes that appear in a Scheduler ClassAd 
  are listed and described in
  the unnumbered subsection labeled Scheduler ClassAd Attributes
  on page~\pageref{sec:Scheduler-ClassAd-Attributes}.

  \item[\AdAttr{Negotiator}]
   Each \Condor{negotiator} daemon describes its state.
  ClassAd attributes that appear in a Negotiator ClassAd 
  are listed and described in
  the unnumbered subsection labeled Negotiator ClassAd Attributes
  on page~\pageref{sec:Negotiator-ClassAd-Attributes}.

  \item[\AdAttr{Submitter}]
   Each submitter is described by a ClassAd.
  ClassAd attributes that appear in a Submitter ClassAd 
  are listed and described in
  the unnumbered subsection labeled Submitter ClassAd Attributes
  on page~\pageref{sec:Submitter-ClassAd-Attributes}.

  \item[\AdAttr{Defrag}]
   Each \Condor{defrag} daemon describes its state.
  ClassAd attributes that appear in a Defrag ClassAd 
  are listed and described in
  the unnumbered subsection labeled Defrag ClassAd Attributes
  on page~\pageref{sec:Defrag-ClassAd-Attributes}.

  \item[\AdAttr{Collector}]
   Each \Condor{collector} daemon describes its state.
  ClassAd attributes that appear in a Collector ClassAd 
  are listed and described in
  the unnumbered subsection labeled Collector ClassAd Attributes
  on page~\pageref{sec:Collector-ClassAd-Attributes}.

  \item[\AdAttr{Query}]
  \Todo
  % Prose here about a \Attr{Query} value.

\end{description}

In addition, statistics are published for each DaemonCore daemon.
These attributes are listed and described in
the unnumbered subsection labeled DaemonCore Statistics Attributes
on page~\pageref{sec:DaemonCore-Statistics-Attributes}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Job ClassAd Attributes}\label{sec:Job-ClassAd-Attributes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{misc/jobad.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Machine ClassAd Attributes}\label{sec:Machine-ClassAd-Attributes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{misc/machad.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{DaemonMaster ClassAd Attributes}\label{sec:DaemonMaster-ClassAd-Attributes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{misc/masterad.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Scheduler ClassAd Attributes}\label{sec:Scheduler-ClassAd-Attributes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{misc/scheddad.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Negotiator ClassAd Attributes}\label{sec:Negotiator-ClassAd-Attributes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{misc/negotiatorad.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Submitter ClassAd Attributes}\label{sec:Submitter-ClassAd-Attributes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{misc/submitterad.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Defrag ClassAd Attributes}\label{sec:Defrag-ClassAd-Attributes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{misc/defragad.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Collector ClassAd Attributes}\label{sec:Collector-ClassAd-Attributes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{misc/collectorad.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{ClassAd Attributes Added by the \Condor{collector}}\label{sec:Collector-Added-Attributes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{ClassAd attribute added by the condor\_collector}

\begin{description}

\index{ClassAd attribute added by the condor\_collector!AuthenticatedIdentity}
\item[\AdAttr{AuthenticatedIdentity}:] The authenticated name assigned
  by the \Condor{collector} to the daemon that published the ClassAd.

\index{ClassAd attribute added by the condor\_collector!AuthenticationMethod}
\item[\AdAttr{AuthenticationMethod}:] The authentication method used
    by the \Condor{collector} to determine the \AdAttr{AuthenticatedIdentity}.

\index{ClassAd attribute added by the condor\_collector!LastHeardFrom}
\item[\AdAttr{LastHeardFrom}:] The time inserted into a daemon's
  ClassAd representing the time that this \Condor{collector}
  last received a message from the daemon.
  Time is  represented as the number of second elapsed since
  the Unix epoch (00:00:00 UTC, Jan 1, 1970).
  This attribute is added if \MacroNI{COLLECTOR\_DAEMON\_STATS} is \Expr{True}.

\index{ClassAd attribute added by the condor\_collector!UpdatesHistory}
\item[\AdAttr{UpdatesHistory}:] A bitmap representing the status of
  the most recent updates received from the daemon. 
  This attribute is only added if \Macro{COLLECTOR\_DAEMON\_HISTORY\_SIZE}
  is non-zero. 
  See page~\pageref{param:CollectorDaemonHistorySize} for more information on
  this setting.
  This attribute is added if \MacroNI{COLLECTOR\_DAEMON\_STATS} is \Expr{True}.

\index{ClassAd attribute added by the condor\_collector!UpdatesLost}
\item[\AdAttr{UpdatesLost}:] An integer count of the number of updates
  from the daemon that the \Condor{collector} can definitively determine
  were lost since the \Condor{collector} started running.
  This attribute is added if \MacroNI{COLLECTOR\_DAEMON\_STATS} is \Expr{True}.

\index{ClassAd attribute added by the condor\_collector!UpdatesSequenced}
\item[\AdAttr{UpdatesSequenced}:] An integer count of the number of updates
  received from the daemon,
  for which the \Condor{collector} can tell how many were or were not lost,
  since the \Condor{collector} started running.
  This attribute is added if \MacroNI{COLLECTOR\_DAEMON\_STATS} is \Expr{True}.

\index{ClassAd attribute added by the condor\_collector!UpdatesTotal}
\item[\AdAttr{UpdatesTotal}:] An integer count started when the
  \Condor{collector} started running, representing the sum
  of the number of updates actually received from the daemon plus
  the number of updates that the \Condor{collector} determined were lost.
  This attribute is added if \MacroNI{COLLECTOR\_DAEMON\_STATS} is \Expr{True}.

\end{description}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{DaemonCore Statistics Attributes}\label{sec:DaemonCore-Statistics-Attributes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{misc/statsattributes.tex}

