%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{ckpt-reference}
HTCondor's Checkpoint Mechanism}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{checkpoint}

A checkpoint is a snapshot of the current state of a program,
taken in such a way that the program can be restarted from that state at a
later time.  
Taking checkpoints gives the HTCondor scheduler the freedom to
reconsider scheduling decisions through preemptive-resume scheduling.
If the scheduler decides to no longer allocate a machine to a job (for
example, when the owner of that machine returns), it can take a checkpoint
of the job and preempt the job without losing the work the job has already
accomplished.  
The job can be resumed later when the scheduler allocates it a new machine.
Additionally, periodic checkpoints provides fault tolerance in HTCondor.  
Snapshots are taken periodically,
and after an interruption in service the program can continue from the
most recent snapshot.

HTCondor provides checkpoint services to single process jobs on some
Unix platforms.
To enable the taking of checkpoints, the user must link the program with the
HTCondor system call library (\File{libcondorsyscall.a}), using the
\Condor{compile} command.
This means that the
user must have the object files or source code of the program to use
HTCondor checkpoints.  
However, the checkpoint services provided by
HTCondor are strictly optional.  
So, while there are some classes of
jobs for which HTCondor does not provide checkpoint services, 
these jobs may still be submitted to HTCondor to take advantage of HTCondor's
resource management functionality.  
See section~\ref{sec:standard-universe} on
page~\pageref{sec:standard-universe} for a description of the
classes of jobs for which HTCondor does not provide checkpoint services.

\index{checkpoint!implementation}
The taking of process checkpoints is implemented in the HTCondor 
system call library as a signal handler.
When HTCondor sends a checkpoint signal to a
process linked with this library, the provided signal handler writes
the state of the process out to a file or a network socket.  This
state includes the contents of the process stack and data segments,
all shared library code and data mapped into the process's address
space, the state of all open files, and any signal handlers and
pending signals.  On restart, the process reads this state from the
file, restoring the stack, shared library and data segments, file
state, signal handlers, and pending signals.  The checkpoint signal
handler then returns to user code, which continues from where it left
off when the checkpoint signal arrived.

HTCondor processes for which the taking of checkpoints is enabled 
take a checkpoint when preempted from a machine.
When a suitable replacement
execution machine is found of the same architecture and operating
system, the process is restored on this new machine using the
checkpoint, and computation resumes from where it left off.  
Jobs that can not take checkpoints are preempted and restarted from the
beginning.

\index{checkpoint!periodic}
HTCondor's taking of periodic checkpoints provides fault tolerance.
Pools may be configured with the \Macro{PERIODIC\_CHECKPOINT} variable,
which controls when and how often jobs which can take and use
checkpoints do so periodically.
Examples of when are never, and every three hours.
When the time to take a periodic checkpoint occurs, the job
suspends processing, takes the checkpoint, and immediately
continues from where it left off.  There is also a \Condor{ckpt} command
which allows the user to request that an HTCondor job immediately take
a periodic checkpoint.

In all cases, HTCondor jobs continue execution from the most recent
complete checkpoint.  If service is interrupted while a checkpoint is
being taken, causing that checkpoint to fail, the process will
restart from the previous checkpoint.  HTCondor uses a commit style
algorithm for writing checkpoints: a previous checkpoint is deleted
only after a new complete checkpoint has been written successfully.

In certain cases, taking a checkpoint may be delayed until a more appropriate
time.  For example, an HTCondor job will defer a checkpoint request if
it is communicating with another process over the network.  When the
network connection is closed, the checkpoint will be taken.

The HTCondor checkpoint feature can also be used for any Unix process
outside of the HTCondor batch environment. Standalone checkpoints
are described in section~\ref{sec:standalone-ckpt}.

\index{checkpoint!compression}
HTCondor can produce and use compressed checkpoints.
Configuration variables (detailed in 
section~\ref{sec:Shadow-Config-File-Entries}
control whether compression is used.
The default is to not compress.

By default, a checkpoint is written to a file on the local disk of the
machine where the job was submitted.  An HTCondor pool can also be
configured with a checkpoint server or servers that
serve as a repository for checkpoints, as described in
section~\ref{sec:Ckpt-Server} on page~\pageref{sec:Ckpt-Server}.
When a host is configured to use a checkpoint server, jobs submitted
on that machine write and read checkpoints to and from the server,
rather than the local disk of the submitting machine, taking the
burden of storing checkpoint files off of the submitting machines and
placing it instead on server machines (with disk space dedicated for
the purpose of storing checkpoints).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:standalone-ckpt}Standalone Checkpoint Mechanism}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\index{checkpoint!stand alone}
Using the HTCondor checkpoint library without the remote system call
functionality and outside of the HTCondor system is known as the standalone
mode checkpoint mechanism.

To prepare a program for taking standalone checkpoints, 
use the \Condor{compile} utility as for a standard HTCondor job, 
but do not use \Condor{submit}.
Run the program from the command line.
The checkpoint library will print a message to let you know
that taking checkpoints is enabled and to inform you of the default
name for the checkpoint image.
The message is of the form:

\footnotesize
\begin{verbatim}
HTCondor: Notice: Will checkpoint to program_name.ckpt
HTCondor: Notice: Remote system calls disabled.
\end{verbatim}
\normalsize

Platforms that use address space randomization will need
a modified invocation of the program,
as described in section~\ref{sec:platform-linux-addrspace-random} on
page~\pageref{sec:platform-linux-addrspace-random}.
The invocation disables the address space randomization.
 
To force the program to write a checkpoint image and stop, send it
the SIGTSTP signal or press control-Z.  To force the program to 
write a checkpoint image and continue executing, send it the
SIGUSR2 signal.

To restart a program using a checkpoint, invoke the program
with the command line argument
\Arg{-\_condor\_restart},
followed by the name of the checkpoint image file.
As an example, if the program is called \Prog{P1} and
the checkpoint is called \File{P1.ckpt}, use
\begin{verbatim}
P1 -_condor_restart P1.ckpt
\end{verbatim}
Again, platforms that implement address space randomization will
need a modified invocation,
as described in section~\ref{sec:platform-linux-addrspace-random}.

By default, the program will restart in the same directory 
in which it originally ran, 
and the program will fail if it can not change to that absolute path.
To suppress this behavior, 
also pass the \Arg{-\_condor\_relocatable} argument 
to the program. 
Not all programs will continue to work.  
Doing this may simplify moving standalone checkpoints between machines.
Continuing the example given above,
the command would be
\begin{verbatim}
P1 -_condor_restart P1.ckpt -_condor_relocatable
\end{verbatim}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:ckpt-safety}Checkpoint Safety}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Some programs have fundamental limitations that make them
unsafe for taking checkpoints.
For example, a program that both reads
and writes a single file may enter an unexpected state. Here
is an example of the ordered events that exhibit this issue.

\begin{enumerate}
\item Record a checkpoint image.
\item Read data from a file.
\item Write data to the same file.
\item Execution failure, so roll back to step 2.
\end{enumerate}

In this example, the program would re-read data from the file, but
instead of finding the original data, would see data created in the
future, and yield unexpected results.

To prevent this sort of accident, HTCondor displays a warning
if a file is used for both reading and writing.  You can ignore or disable
these warnings if you choose as described in  section \ref{sec:ckpt-warnings},
but please understand that your program may compute incorrect results.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:ckpt-warnings}Checkpoint Warnings}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

HTCondor displays warning messages upon encountering unexpected
behaviors in the program.  For example, if file \File{x}
is opened for reading
and writing, this message will be displayed:

\footnotesize
\begin{verbatim}
HTCondor: Warning: READWRITE: File '/tmp/x' used for both reading and writing.
\end{verbatim}
\normalsize

Control how these messages are displayed with the
\verb$-_condor_warning$ command line argument.  This argument
accepts a warning category and a mode.  The category describes a certain
class of messages, such as READWRITE or ALL.  The mode describes what
to do with the category.  It may be ON, OFF, or ONCE.
If a category is ON, it is always displayed.
If a category is OFF, it is never displayed.
If a category is ONCE, it is displayed only once.
To show all the available categories and modes, use
\verb$-_condor_warning$ with no arguments.

For example, the additional command line argument 
to limit read/write warnings to one instance is

\begin{verbatim}
-_condor_warning READWRITE ONCE
\end{verbatim}

To turn all ordinary notices off:

\begin{verbatim}
-_condor_warning NOTICE OFF
\end{verbatim}

The same effect can be accomplished within a program by using the function
\Procedure{\_condor\_warning\_config}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:ckpt-api}Checkpoint Library Interface}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\index{checkpoint!library interface}
A program need not be rewritten to take advantage of checkpoints.
However, the checkpoint library provides several C entry points
that allow for a program to control its own checkpoint behavior.
These functions are provided.

\begin{itemize}

\item \Code{void init\_image\_with\_file\_name( char *ckpt\_file\_name )}\\
This function explicitly sets a file name to use when
producing or using a checkpoint.
\Procedure{ckpt} or
\Procedure{ckpt\_and\_exit} must be called to produce the
checkpoint, and
\Procedure{restart} must be called to perform the
actual restart.

\item \Code{void init\_image\_with\_file\_descriptor( int fd )}\\
This function explicitly sets a file descriptor to use when
producing or using a checkpoint.
\Procedure{ckpt} or
\Procedure{ckpt\_and\_exit} must be called to produce the
checkpoint, and
\Procedure{restart} must be called to perform the
actual restart.

\item \Code{void ckpt()}\\
This function causes a checkpoint image to be written to disk.
The program will continue to execute.  This is identical to sending
the program a SIGUSR2 signal.

\item \Code{void ckpt\_and\_exit()}\\
This function causes a checkpoint image to be written to disk.
The program will then exit.  This is identical to sending the program
a SIGTSTP signal.

\item \Code{void restart()}\\
This function causes the program to read the checkpoint
image and to resume
execution of the program from the point where the checkpoint
was taken.
This function does not return.

\item \Code{void \_condor\_ckpt\_disable()}\\
This function temporarily disables the taking of checkpoints.  This can
be handy if the program does something that is not checkpoint-safe.
For example, if a program must not be interrupted while accessing
a special file, call \Procedure{\_condor\_ckpt\_disable}, access the
file, and then call \Procedure{\_condor\_ckpt\_enable}.  Some program
actions, such as opening a socket or a pipe, implicitly cause
the taking of checkpoints to be disabled.

\item \Code{void \_condor\_ckpt\_enable()}\\
This function re-enables the taking of checkpoints after a call to
\Procedure{\_condor\_ckpt\_disable}.  If a checkpoint signal arrived
while the taking of checkpoints was disabled, the checkpoint will be taken when
this function is called.  Disabling and enabling the taking of checkpoints
must occur in matched pairs.  \Procedure{\_condor\_ckpt\_enable} must
be called once for every time that \Procedure{\_condor\_ckpt\_disable}
is called.

\item \Code{int \_condor\_warning\_config( const char *kind, const char *mode )}\\
This function controls what warnings are displayed by HTCondor.
The \Code{kind} and \Code{mode} arguments are the same as for the
\Code{-\_condor\_warning} option described in section \ref{sec:ckpt-warnings}.  This function returns \Code{true}
if the arguments are understood and accepted.  
Otherwise, it returns \Code{false}.

\item \Code{extern int condor\_compress\_ckpt}\\
Setting this variable to 1 (one) causes checkpoint images to be compressed.
Setting it to 0 (zero) disables compression.

\end{itemize}

