\index{ClassAd!Collector attributes}
\begin{description}

\index{ClassAd Collector attribute!CollectorIpAddr}
\item[\AdAttr{CollectorIpAddr}:] String with the IP and port address of the
  \Condor{collector} daemon which is publishing this ClassAd.

\index{ClassAd Collector attribute!CondorVersion}
\item[\AdAttr{CondorVersion}:] A string containing the HTCondor version
number, the release date, and the build identification number.

\index{ClassAd Collector attribute!CurrentJobsRunningAll}
\item[\AdAttr{CurrentJobsRunningAll}:] An integer value representing the sum of
  all jobs running under all universes.

\index{ClassAd Collector attribute!CurrentJobsRunning<universe>}
\item[\AdAttr{CurrentJobsRunning<universe>}:] An integer value representing
  the current number of jobs running under the universe which forms 
  the attribute name.  For example
\begin{verbatim}
  CurrentJobsRunningVanilla = 567
\end{verbatim}
  identifies that the \Condor{collector} counts 567 vanilla universe jobs
  currently running.
  \Attr{<universe>} is one of 
  \Expr{Unknown}, \Expr{Standard}, \Expr{Vanilla}, \Expr{Scheduler},
  \Expr{Java}, \Expr{Parallel}, \Expr{VM}, or \Expr{Local}.
  There are other universes, but they are not listed here, as they represent
  ones that are no longer used in Condor.

\index{ClassAd Collector attribute!DaemonStartTime}
\item[\AdAttr{DaemonStartTime}:] The time that this daemon was
  started, represented as the number of second elapsed since
  the Unix epoch (00:00:00 UTC, Jan 1, 1970).

\index{ClassAd Collector attribute!HostsClaimed}
\item[\AdAttr{HostsClaimed}:] Description is not yet written.

\index{ClassAd Collector attribute!HostsOwner}
\item[\AdAttr{HostsOwner}:] Description is not yet written.

\index{ClassAd Collector attribute!HostsTotal}
\item[\AdAttr{HostsTotal}:] Description is not yet written.

\index{ClassAd Collector attribute!HostsUnclaimed}
\item[\AdAttr{HostsUnclaimed}:] Description is not yet written.

\index{ClassAd Collector attribute!IdleJobs}
\item[\AdAttr{IdleJobs}:] Description is not yet written.

\index{ClassAd Collector attribute!Machine}
\item[\AdAttr{Machine}:] A string with the machine's fully qualified 
  host name.

\index{ClassAd Collector attribute!MaxJobsRunningAll}
\item[\AdAttr{MaxJobsRunning<universe}:] An integer value representing 
  the sum of all \Attr{MaxJobsRunning<universe>} values.

\index{ClassAd Collector attribute!MaxJobsRunning<universe>}
\item[\AdAttr{MaxJobsRunning<universe>}:] An integer value representing 
  largest number of currently running jobs ever seen
  under the universe which forms the attribute name, 
  over the life of this \Condor{collector} process.
  For example
\begin{verbatim}
  MaxJobsRunningVanilla = 401
\end{verbatim}
  identifies that the \Condor{collector} saw 401 vanilla universe jobs
  currently running at one point in time, and that was the largest
  number it had encountered.
  \Attr{<universe>} is one of 
  \Expr{Unknown}, \Expr{Standard}, \Expr{Vanilla}, \Expr{Scheduler},
  \Expr{Java}, \Expr{Parallel}, \Expr{VM}, or \Expr{Local}.
  There are other universes, but they are not listed here, as they represent
  ones that are no longer used in Condor.

\index{ClassAd Collector attribute!MyAddress}
\item[\AdAttr{MyAddress}:] Description is not yet written.

\index{ClassAd Collector attribute!MyCurrentTime}
\item[\AdAttr{MyCurrentTime}:]  The time, represented as the number of 
  second elapsed since the Unix epoch (00:00:00 UTC, Jan 1, 1970),
  at which the \Condor{schedd} daemon last sent a ClassAd update to the
  \Condor{collector}.

\index{ClassAd Collector attribute!Name}
\item[\AdAttr{Name}:] The name of this resource; typically the same value as
  the \AdAttr{Machine} attribute, but could be customized by the site
  administrator.
  On SMP machines, the \Condor{startd} will divide the CPUs up into separate
  slots, each with with a unique name.
  These names will be of the form ``slot\#@full.hostname'', for example,
  ``slot1@vulture.cs.wisc.edu'', which signifies slot number 1 from
  vulture.cs.wisc.edu.

\index{ClassAd Collector attribute!RunningJobs}
\item[\AdAttr{RunningJobs}:] Description is not yet written.

\index{ClassAd Collector attribute!UpdateInterval}
\item[\AdAttr{UpdateInterval}:] Description is not yet written.

\index{ClassAd Collector attribute!UpdateSequenceNumber}
\item[\AdAttr{UpdateSequenceNumber}:] An integer that begins at 0,
   and increments by one each time the same ClassAd is again advertised.

\end{description}

