\index{ClassAd!Defrag attributes}
\begin{description}

\index{ClassAd Defrag attribute!AvgDrainingBadput}
\item[\AdAttr{AvgDrainingBadput}:] Fraction of time CPUs
  in the pool have spent on jobs that were killed during draining of the
  machine.  This is calculated in each polling interval by looking
  at \AdAttr{TotalMachineDrainingBadput}.  
  Therefore, it treats evictions of jobs that do and do not produce
  checkpoints the same.
  When the \Condor{startd} restarts, its counters start over from 0, so the
  average is only over the time since the daemons have been alive.

\index{ClassAd Defrag attribute!AvgDrainingUnclaimedTime}
\item[\AdAttr{AvgDrainingUnclaimedTime}:] Fraction of time CPUs
  in the pool have spent unclaimed by a user during
  draining of the machine.  This is calculated in each polling interval
  by looking at \AdAttr{TotalMachineDrainingUnclaimedTime}.  
  When the \Condor{startd} restarts, its counters start over from 0, so the
  average is only over the time since the daemons have been alive.

\index{ClassAd Defrag attribute!DaemonStartTime}
\item[\AdAttr{DaemonStartTime}:] The time that this daemon was started, 
  represented as the number of seconds elapsed since
  the Unix epoch (00:00:00 UTC, Jan 1, 1970).

\index{ClassAd Defrag attribute!DrainedMachines}
\item[\AdAttr{DrainedMachines}:] A count of the number of fully drained 
machines which have arrived during the run time of this \Condor{defrag} daemon.

\index{ClassAd Defrag attribute!DrainFailures}
\item[\AdAttr{DrainFailures}:] Total count of failed attempts
  to initiate draining during the lifetime of this \Condor{defrag} daemon.

\index{ClassAd Defrag attribute!DrainSuccesses}
\item[\AdAttr{DrainSuccesses}:] Total count of successful attempts
  to initiate draining during the lifetime of this \Condor{defrag} daemon.

\index{ClassAd Defrag attribute!Machine}
\item[\AdAttr{Machine}:] A string with the machine's fully qualified 
  host name.

\index{ClassAd Defrag attribute!MachinesDraining}
\item[\AdAttr{MachinesDraining}:] Number of machines that were observed
  to be draining in the last polling interval.

\index{ClassAd Defrag attribute!MachinesDrainingPeak}
\item[\AdAttr{MachinesDrainingPeak}:] Largest number of machines that were
ever observed to be draining.

\index{ClassAd Defrag attribute!MeanDrainedArrived}
\item[\AdAttr{MeanDrainedArrived}:] The mean time in seconds 
between arrivals of fully drained machines.

\index{ClassAd Defrag attribute!MonitorSelfAge}
\item[\AdAttr{MonitorSelfAge}:] The number of seconds that this daemon
  has been running.

\index{ClassAd Defrag attribute!MonitorSelfCPUUsage}
\item[\AdAttr{MonitorSelfCPUUsage}:] The fraction of recent CPU time utilized
  by this daemon. 

\index{ClassAd Defrag attribute!MonitorSelfImageSize}
\item[\AdAttr{MonitorSelfImageSize}:] The amount of virtual memory consumed by
  this daemon in Kbytes.

\index{ClassAd Defrag attribute!MonitorSelfRegisteredSocketCount}
\item[\AdAttr{MonitorSelfRegisteredSocketCount}:] The current number of sockets
  registered by this daemon.

\index{ClassAd Defrag attribute!MonitorSelfResidentSetSize}
\item[\AdAttr{MonitorSelfResidentSetSize}:] The amount of resident memory
  used by this daemon in Kbytes.

\index{ClassAd Defrag attribute!MonitorSelfSecuritySessions}
\item[\AdAttr{MonitorSelfSecuritySessions}:] The number of open (cached)
  security sessions for this daemon.

\index{ClassAd Defrag attribute!MonitorSelfTime}
\item[\AdAttr{MonitorSelfTime}:] The  time, represented as the number of
  seconds elapsed since the Unix epoch (00:00:00 UTC, Jan 1, 1970),
  at which this daemon last checked and set the attributes with names that
  begin with the string \Attr{MonitorSelf}.
  
\index{ClassAd Defrag attribute!MyAddress}
\item[\AdAttr{MyAddress}:] Description is not yet written.

\index{ClassAd Defrag attribute!MyCurrentTime}
\item[\AdAttr{MyCurrentTime}:]  The time, represented as the number of 
  seconds elapsed since the Unix epoch (00:00:00 UTC, Jan 1, 1970),
  at which the \Condor{defrag} daemon last sent a ClassAd update to the
  \Condor{collector}.

\index{ClassAd Defrag attribute!Name}
\item[\AdAttr{Name}:] The name of this daemon; typically the same value as
  the \AdAttr{Machine} attribute, but could be customized by the site
  administrator via the configuration variable \Macro{DEFRAG\_NAME}.

\index{ClassAd Defrag attribute!RecentDrainFailures}
\item[\AdAttr{RecentDrainFailures}:] Count of failed attempts
  to initiate draining during the past \AdAttr{RecentStatsLifetime} seconds.

\index{ClassAd Defrag attribute!RecentDrainSuccesses}
\item[\AdAttr{RecentDrainSuccesses}:] Count of successful attempts
  to initiate draining during the past \AdAttr{RecentStatsLifetime} seconds.

\index{ClassAd Defrag attribute!RecentStatsLifetime}
\item[\AdAttr{RecentStatsLifetime}:] A Statistics attribute defining 
  the time in seconds over which statistics values have been collected 
  for attributes with names that begin with \Expr{Recent}. 

\index{ClassAd Defrag attribute!UpdateSequenceNumber}
\item[\AdAttr{UpdateSequenceNumber}:] An integer, starting at zero,
  and incremented with each ClassAd update sent to the \Condor{collector}.
  The \Condor{collector} uses this value to sequence the updates it
  receives.

\index{ClassAd Defrag attribute!WholeMachines}
\item[\AdAttr{WholeMachines}:] Number of machines that were observed
  to be defragmented in the last polling interval.

\index{ClassAd Defrag attribute!WholeMachinesPeak}
\item[\AdAttr{WholeMachinesPeak}:] Largest number of machines that were
  ever observed to be simultaneously defragmented.

\end{description}

