\begin{description}
%
\index{ClassAd!machine attributes}
\index{ClassAd machine attribute!Activity}
\item[\AdAttr{Activity}:] String which describes Condor job activity on the machine.
Can have one of the following values:
	\begin{description}
	\item[\AdStr{Idle}:] There is no job activity
	\item[\AdStr{Busy}:] A job is busy running
	\item[\AdStr{Suspended}:] A job is currently suspended
	\item[\AdStr{Vacating}:] A job is currently checkpointing
	\item[\AdStr{Killing}:] A job is currently being killed
	\item[\AdStr{Benchmarking}:] The startd is running benchmarks
	\item[\AdStr{Retiring}:] Waiting for a job to finish or for the maximum retirement time to expire
	\end{description}
%
\index{ClassAd machine attribute!Arch}
\item[\AdAttr{Arch}:] String with the architecture of the machine.  
Currently supported architectures have the following string
definitions:
	\begin{description}
	\item[\AdStr{INTEL}:] Intel x86 CPU (Pentium, Xeon, etc).
	\item[\AdStr{X86\_64}:] AMD/Intel 64-bit X86
	\end{description}
These strings show definitions for architectures no longer supported:
	\begin{description}
	\item[\AdStr{IA64}:] Intel Itanium
	\item[\AdStr{SUN4u}:] Sun UltraSparc CPU
	\item[\AdStr{SUN4x}:] A Sun Sparc CPU other than an UltraSparc, i.e.
sun4m or sun4c CPU found in older Sparc workstations such as the Sparc~10, 
Sparc~20, IPC, IPX, etc.
	\item[\AdStr{PPC}:] 32-bit PowerPC
	\item[\AdStr{PPC64}:] 64-bit PowerPC
	\end{description}
%
\index{ClassAd machine attribute!CheckpointPlatform}
\item[\AdAttr{CheckpointPlatform}:] A string which opaquely encodes various
aspects about a machine's operating system, hardware, and kernel
attributes.
It is used to identify systems where previously taken checkpoints for
the standard universe may resume.
%
\index{ClassAd machine attribute!ClockDay}
\item[\AdAttr{ClockDay}:] The day of the week, 
where 0 = Sunday, 1 = Monday, \Dots, and 6 = Saturday. 
%
\index{ClassAd machine attribute!ClockMin}
\item[\AdAttr{ClockMin}:] The number of minutes passed since midnight.
%
\index{ClassAd machine attribute!CondorLoadAvg}
\item[\AdAttr{CondorLoadAvg}:] The portion of the load average generated 
by Condor, either from remote jobs or running benchmarks.
%
\index{ClassAd machine attribute!ConsoleIdle}
\item[\AdAttr{ConsoleIdle}:] The number of seconds since activity on the system
console keyboard or console mouse has last been detected.
%
\index{ClassAd machine attribute!Cpus}
\item[\AdAttr{Cpus}:]  The number of CPUs in this slot.
It is 1 for a single CPU slot, 2 for a dual CPU slot, etc.
%
\index{ClassAd machine attribute!CurrentRank}
\item[\AdAttr{CurrentRank}:] A float which represents this machine
owner's affinity
for running the Condor job which it is currently hosting.  If not
currently hosting a Condor job, \AdAttr{CurrentRank} is 0.0.
When a machine is claimed,
the attribute's value is computed by evaluating the machine's
\AdAttr{Rank} expression with respect to the current job's ClassAd.
%
\index{ClassAd machine attribute!Disk}
\item[\AdAttr{Disk}:] The amount of disk space on this machine available for
the job in Kbytes ( e.g. 23000 = 23 megabytes ).  Specifically, this
is the amount of disk space available in the directory specified in
the Condor configuration files by the \Macro{EXECUTE} macro, minus any
space reserved with the \Macro{RESERVED\_DISK} macro.
%
\index{ClassAd machine attribute!Draining}
\item[\AdAttr{Draining}:] This attribute is \Expr{True} when the slot
is draining and undefined if not.
%
\index{ClassAd machine attribute!DrainingRequestId}
\item[\AdAttr{DrainingRequestId}:] This attribute contains a string that
is the request id of the draining request that put this slot in a draining
state.  It is undefined if the slot is not draining.
%
\index{ClassAd machine attribute!DotNetVersions}
\item[\AdAttr{DotNetVersions}:] The .NET framework versions
currently installed on this computer. 
Default format is a comma delimited list. 
Current definitions:
  \begin{description}
  \item[\AdStr{1.1}:] for .Net Framework 1.1
  \item[\AdStr{2.0}:] for .Net Framework 2.0
  \item[\AdStr{3.0}:] for .Net Framework 3.0
  \item[\AdStr{3.5}:] for .Net Framework 3.5
  \item[\AdStr{4.0Client}:] for .Net Framework 4.0 Client install
  \item[\AdStr{4.0Full}:] for .Net Framework 4.0 Full install
  \end{description}
%
\index{ClassAd machine attribute!DynamicSlot}
\label{DynamicSlot-machine-attribute} 
\item[\AdAttr{DynamicSlot}:] For SMP machines that allow dynamic
partitioning of a slot,
this boolean value identifies that this dynamic slot may be partitioned.
%
\index{ClassAd machine attribute!EnteredCurrentActivity}
\item[\AdAttr{EnteredCurrentActivity}:] Time at which the machine
entered the current Activity (see \AdAttr{Activity} entry above).  On
all platforms (including NT), this is measured in the number of
integer seconds since the Unix epoch (00:00:00 UTC, Jan 1, 1970).
%
\index{ClassAd machine attribute!ExpectedMachineGracefulDrainingBadput}
\item[\AdAttr{ExpectedMachineGracefulDrainingBadput}:] The
job runtime in cpu-seconds that would be lost if graceful draining
were initiated at the time this ad was published.  This calculation assumes
that jobs will run for the full retirement time and then be evicted
without saving a checkpoint.
%
\index{ClassAd machine attribute!ExpectedMachineGracefulDrainingCompletion}
\item[\AdAttr{ExpectedMachineGracefulDrainingCompletion}:] Time at
which graceful draining of the machine could complete if it were
initiated at the time this ad was published.  This is measured in the
number of integer seconds since the Unix epoch (00:00:00 UTC, Jan 1,
1970).
%
\index{ClassAd machine attribute!ExpectedMachineQuickDrainingBadput}
\item[\AdAttr{ExpectedMachineGracefulQuickBadput}:] The
job runtime in cpu-seconds that would be lost if quick draining
were initiated at the time this ad was published.  This calculation assumes
that all evicted jobs will not save a checkpoint.
%
\index{ClassAd machine attribute!ExpectedMachineQuickDrainingCompletion}
\item[\AdAttr{ExpectedMachineQuickDrainingCompletion}:] Time at
which quick draining of the machine could complete if it were
initiated at the time this ad was published.  This is measured in the
number of integer seconds since the Unix epoch (00:00:00 UTC, Jan 1,
1970).
%
\index{ClassAd machine attribute!FileSystemDomain}
\item[\AdAttr{FileSystemDomain}:] A domain name configured by the
Condor administrator which describes a cluster of machines which all
access the same, uniformly-mounted, networked file systems usually via
NFS or AFS.  This is useful for Vanilla universe jobs which require
remote file access.
%
\index{ClassAd machine attribute!HasVM}
\item[\AdAttr{HasVM}:] A boolean value added to the machine ClassAd
when the configuration triggers the detection of virtual machine
software.
%
\index{ClassAd machine attribute!JobVM\_VCPUS}
\item[\AdAttr{JobVM\_VCPUS}:] An attribute defined if a vm universe job
is running on this slot.  Defined by the number of virtualized CPUs
in the virtual machine.
%
\index{ClassAd machine attribute!KeyboardIdle}
\item[\AdAttr{KeyboardIdle}:] The number of seconds since activity on any
keyboard or mouse associated with this machine has last been detected.
Unlike \AdAttr{ConsoleIdle}, \AdAttr{KeyboardIdle} also takes activity 
on pseudo-terminals into
account (i.e. virtual ``keyboard'' activity from telnet and rlogin
sessions as well).  Note that \AdAttr{KeyboardIdle} will always be equal to or
less than \AdAttr{ConsoleIdle}.
%
\index{ClassAd machine attribute!KFlops}
\item[\AdAttr{KFlops}:] Relative floating point performance as determined via a
Linpack benchmark.
%
\index{ClassAd machine attribute!LastHeardFrom}
\item[\AdAttr{LastHeardFrom}:] Time when the Condor central manager last
received a status update from this machine.  
Expressed as 
the number of integer seconds since the Unix epoch (00:00:00 UTC, Jan 1, 1970).
Note: This attribute is only inserted by the central manager once it
receives the ClassAd.
It is not present in the \Condor{startd} copy of the ClassAd.
Therefore, you could not use this attribute in defining \Condor{startd}
expressions (and you would not want to).
%
\index{ClassAd machine attribute!LoadAvg}
\item[\AdAttr{LoadAvg}:] A floating point number with the machine's current load
average.
%
\index{ClassAd machine attribute!Machine}
\item[\AdAttr{Machine}:] A string with the machine's fully qualified host name.
%
\index{ClassAd machine attribute!MachineMaxVacateTime}
\item[\AdAttr{MachineMaxVacateTime}:] An integer expression that specifies
the time in seconds the machine will allow the job to gracefully shut
down.
%
\index{ClassAd machine attribute!Memory}
\item[\AdAttr{Memory}:] The amount of RAM in megabytes.
%
\index{ClassAd machine attribute!Mips}
\item[\AdAttr{Mips}:] Relative integer performance as determined via a Dhrystone
benchmark.

\index{ClassAd machine attribute!MonitorSelfAge}
\item[\AdAttr{MonitorSelfAge}:] The number of seconds that this daemon
  has been running.

\index{ClassAd machine attribute!MonitorSelfCPUUsage}
\item[\AdAttr{MonitorSelfCPUUsage}:] The fraction of recent CPU time utilized
  by this daemon. 

\index{ClassAd machine attribute!MonitorSelfImageSize}
\item[\AdAttr{MonitorSelfImageSize}:] The amount of virtual memory consumed by
  this daemon in Kbytes.

\index{ClassAd machine attribute!MonitorSelfRegisteredSocketCount}
\item[\AdAttr{MonitorSelfRegisteredSocketCount}:] The current number of sockets
  registered by this daemon.

\index{ClassAd machine attribute!MonitorSelfResidentSetSize}
\item[\AdAttr{MonitorSelfResidentSetSize}:] The amount of resident memory
  used by this daemon in Kbytes.

\index{ClassAd machine attribute!MonitorSelfSecuritySessions}
\item[\AdAttr{MonitorSelfSecuritySessions}:] The number of open (cached)
  security sessions for this daemon.

\index{ClassAd machine attribute!MonitorSelfTime}
\item[\AdAttr{MonitorSelfTime}:] The  time, represented as the number of
  second elapsed since the Unix epoch (00:00:00 UTC, Jan 1, 1970),
  at which this daemon last checked and set the attributes with names that
  begin with the string \Attr{MonitorSelf}.
  
\index{ClassAd machine attribute!MyAddress}
\item[\AdAttr{MyAddress}:] String with the IP and port address of the
\Condor{startd} daemon which is publishing this machine ClassAd.
When using CCB, \Condor{shared\_port}, and/or an additional private
network interface, that information will be included here as well.

\index{ClassAd machine attribute!MyType}
\item[\AdAttr{MyType}:] The ClassAd type; always set to the literal string \AdStr{Machine}.
%
\index{ClassAd machine attribute!Name}
\item[\AdAttr{Name}:] The name of this resource; typically the same value as
the \AdAttr{Machine} attribute, but could be customized by the site
administrator.
On SMP machines, the \Condor{startd} will divide the CPUs up into separate
slots, each with with a unique name.
These names will be of the form ``slot\#@full.hostname'', for example,
``slot1@vulture.cs.wisc.edu'', which signifies slot number 1 from
vulture.cs.wisc.edu.
%
\index{ClassAd machine attribute!OpSys}
\item[\AdAttr{OpSys}:] String describing the operating system running on this
machine.  
Currently supported operating systems have the following string
definitions:
	\begin{description}
	\item[\AdStr{LINUX}:] for LINUX 2.0.x, LINUX 2.2.x,
	LINUX 2.4.x, or LINUX 2.6.x kernel systems
	\item[\AdStr{OSX}:] for Darwin
	\item[\AdStr{WINDOWS}:] for all versions of Windows
	\end{description}
These strings show definitions for operating systems no longer supported:
	\begin{description}
	\item[\AdStr{SOLARIS28}:] for Solaris 2.8 or 5.8
	\item[\AdStr{SOLARIS29}:] for Solaris 2.9 or 5.9
	\end{description}
%
\index{ClassAd machine attribute!OpSysAndVer}
\item[\AdAttr{OpSysAndVer}:] A string with previously implemented values
for the \Attr{OpSys} attribute.
String definitions for operating systems have the following values:
	\begin{description}
	\item[\AdStr{WINNT50}:] for Windows 2000
	\item[\AdStr{WINNT51}:] for Windows XP
	\item[\AdStr{WINNT52}:] for Windows Server 2003
	\item[\AdStr{WINNT60}:] for Windows Vista
	\item[\AdStr{WINNT61}:] for Windows 7
	\end{description}
%
\index{ClassAd machine attribute!OpSysVer}
\item[\AdAttr{OpSysVer}:] An integer value representing the operating system
version number.
Currently supported operating systems have the following values:
	\begin{description}
	\item[\Expr{500}:] for Windows 2000 
	\item[\Expr{501}:] for Windows XP
	\item[\Expr{502}:] for Windows Server 2003
	\item[\Expr{600}:] for Windows Vista or Windows Server 2008
	\item[\Expr{601}:] for Windows 7 or Windows Server 2008
	\end{description}
%
\index{ClassAd machine attribute!Requirements}
\item[\AdAttr{Requirements}:] A boolean, which when evaluated within the context
of the machine ClassAd and a job ClassAd, must evaluate to
TRUE before Condor will allow the job to use this machine.
%
\index{ClassAd machine attribute!MaxJobRetirementTime}
\item[\AdAttr{MaxJobRetirementTime}:] An expression giving the
maximum time in seconds that the startd will wait for the job to
finish before kicking it off if it needs to do so.  This is evaluated
in the context of the job ClassAd, so it may refer to job attributes
as well as machine attributes.
%
\index{ClassAd machine attribute!PartitionableSlot}
\label{PartitionableSlot-machine-attribute} 
\item[\AdAttr{PartitionableSlot}:] For SMP machines,
a boolean value identifying that this slot may be partitioned.
%
\index{ClassAd machine attribute!SlotID}
\item[\AdAttr{SlotID}:] For SMP machines, the integer
that identifies the slot.
The value will be \verb@X@ for the slot with 
\begin{verbatim}
name="slotX@full.hostname"
\end{verbatim}
For non-SMP machines with one slot, the value will be 1.
\Note This attribute was added in Condor version 6.9.3.
For older versions of Condor, see \AdAttr{VirtualMachineID} below.
%
\index{ClassAd machine attribute!SlotWeight}
\item[\AdAttr{SlotWeight}:]
  This specifies the weight of the slot when
  calculating usage, computing fair shares, and enforcing group
  quotas.  For example, claiming a slot with \Expr{SlotWeight = 2} is
  equivalent to claiming two \Expr{SlotWeight = 1} slots.
  See the description of \MacroNI{SlotWeight} on
  page~\pageref{param:SlotWeight}.

%
\index{ClassAd machine attribute!StartdIpAddr}
\item[\AdAttr{StartdIpAddr}:] String with the IP and port address of the
\Condor{startd} daemon which is publishing this machine ClassAd.
When using CCB, \Condor{shared\_port}, and/or an additional private
network interface, that information will be included here as well.

%
\index{ClassAd machine attribute!State}
\item[\AdAttr{State}:] String which publishes the machine's Condor state.
Can be:
	\begin{description}
	\item[\AdStr{Owner}:] The machine owner is using the machine, and
it is unavailable to Condor.
	\item[\AdStr{Unclaimed}:] The machine is available to run Condor jobs,
but a good match is either not available or not 
yet found.
	\item[\AdStr{Matched}:] The Condor central manager has found a good
match for this resource, but a Condor scheduler has not yet claimed it.
	\item[\AdStr{Claimed}:] The machine is claimed by a remote
\Condor{schedd} and is probably running a job.
	\item[\AdStr{Preempting}:] A Condor job is being preempted (possibly
via checkpointing) in order to clear the machine for either a higher
priority job or because the machine owner wants the machine back.
	\item[\AdStr{Drained}:] This slot is not accepting jobs,
because the machine is being drained.
	\end{description}   % of State
%
\index{ClassAd machine attribute!TargetType}
\item[\AdAttr{TargetType}:] Describes what type of ClassAd to match with.
Always set to the string literal \AdStr{Job}, because machine ClassAds
always want to be matched with jobs, and vice-versa.
%
\index{ClassAd machine attribute!TotalCpus}
\item[\AdAttr{TotalCpus}:] The number of CPUs that are on the machine.
This is in contrast with \Attr{Cpus},
which is the number of CPUs in the slot.
%
\index{ClassAd machine attribute!TotalMachineDrainingBadput}
\item[\AdAttr{TotalMachineDrainingBadput}:] The
total job runtime in cpu-seconds that has been lost due to job evictions
caused by draining since this \Condor{startd} began executing.  In
this calculation, it is assumed that jobs are evicted without
checkpointing.
%
\index{ClassAd machine attribute!TotalMachineDrainingUnclaimedTime}
\item[\AdAttr{TotalMachineDrainingUnclaimedTime}:] The
total machine-wide time in cpu-seconds that has not been used
(i.e. not matched to a job submitter) due to draining since this
\Condor{startd} began executing.
%
\index{ClassAd machine attribute!TotalTimeBackfillBusy}
\item[\AdAttr{TotalTimeBackfillBusy}:] The number of seconds
that this machine (slot) has accumulated within the
backfill busy state and activity pair since the \Condor{startd}
began executing.
This attribute will only be defined if it has a value greater than 0.
%
\index{ClassAd machine attribute!TotalTimeBackfillIdle}
\item[\AdAttr{TotalTimeBackfillIdle}:] The number of seconds
that this machine (slot) has accumulated within the
backfill idle state and activity pair since the \Condor{startd}
began executing.
This attribute will only be defined if it has a value greater than 0.
%
\index{ClassAd machine attribute!TotalTimeBackfillKilling}
\item[\AdAttr{TotalTimeBackfillKilling}:] The number of seconds
that this machine (slot) has accumulated within the
backfill killing state and activity pair since the \Condor{startd}
began executing.
This attribute will only be defined if it has a value greater than 0.
%
\index{ClassAd machine attribute!TotalTimeClaimedBusy}
\item[\AdAttr{TotalTimeClaimedBusy}:] The number of seconds
that this machine (slot) has accumulated within the
claimed busy state and activity pair since the \Condor{startd}
began executing.
This attribute will only be defined if it has a value greater than 0.
%
\index{ClassAd machine attribute!TotalTimeClaimedIdle}
\item[\AdAttr{TotalTimeClaimedIdle}:] The number of seconds
that this machine (slot) has accumulated within the
claimed idle state and activity pair since the \Condor{startd}
began executing.
This attribute will only be defined if it has a value greater than 0.
%
\index{ClassAd machine attribute!TotalTimeClaimedRetiring}
\item[\AdAttr{TotalTimeClaimedRetiring}:] The number of seconds
that this machine (slot) has accumulated within the
claimed retiring state and activity pair since the \Condor{startd}
began executing.
This attribute will only be defined if it has a value greater than 0.
%
\index{ClassAd machine attribute!TotalTimeClaimedSuspended}
\item[\AdAttr{TotalTimeClaimedSuspended}:] The number of seconds
that this machine (slot) has accumulated within the
claimed suspended state and activity pair since the \Condor{startd}
began executing.
This attribute will only be defined if it has a value greater than 0.
%
\index{ClassAd machine attribute!TotalTimeMatchedIdle}
\item[\AdAttr{TotalTimeMatchedIdle}:] The number of seconds
that this machine (slot) has accumulated within the
matched idle state and activity pair since the \Condor{startd}
began executing.
This attribute will only be defined if it has a value greater than 0.
%
\index{ClassAd machine attribute!TotalTimeOwnerIdle}
\item[\AdAttr{TotalTimeOwnerIdle}:] The number of seconds
that this machine (slot) has accumulated within the
owner idle state and activity pair since the \Condor{startd}
began executing.
This attribute will only be defined if it has a value greater than 0.
%
\index{ClassAd machine attribute!TotalTimePreemptingKilling}
\item[\AdAttr{TotalTimePreemptingKilling}:] The number of seconds
that this machine (slot) has accumulated within the
preempting killing state and activity pair since the \Condor{startd}
began executing.
This attribute will only be defined if it has a value greater than 0.
%
\index{ClassAd machine attribute!TotalTimePreemptingVacating}
\item[\AdAttr{TotalTimePreemptingVacating}:] The number of seconds
that this machine (slot) has accumulated within the
preempting vacating state and activity pair since the \Condor{startd}
began executing.
This attribute will only be defined if it has a value greater than 0.
%
\index{ClassAd machine attribute!TotalTimeUnclaimedBenchmarking}
\item[\AdAttr{TotalTimeUnclaimedBenchmarking}:] The number of seconds
that this machine (slot) has accumulated within the
unclaimed benchmarking state and activity pair since the \Condor{startd}
began executing.
This attribute will only be defined if it has a value greater than 0.
%
\index{ClassAd machine attribute!TotalTimeUnclaimedIdle}
\item[\AdAttr{TotalTimeUnclaimedIdle}:] The number of seconds
that this machine (slot) has accumulated within the
unclaimed idle state and activity pair since the \Condor{startd}
began executing.
This attribute will only be defined if it has a value greater than 0.
%
\index{ClassAd machine attribute!UidDomain}
\item[\AdAttr{UidDomain}:] a domain name configured by the Condor 
administrator which describes a cluster of machines which all have 
the same \File{passwd} file entries, and therefore all have the same logins.
%
\index{ClassAd machine attribute!VirtualMachineID}
\item[\AdAttr{VirtualMachineID}:] 
Starting with Condor version 6.9.3, this attribute is now longer used.
Instead, use \AdAttr{SlotID}, as described above.
This will only be present if \Macro{ALLOW\_VM\_CRUFT} is TRUE.
%
\index{ClassAd machine attribute!VirtualMemory}
\item[\AdAttr{VirtualMemory}:] The amount of currently available virtual memory 
(swap space) expressed in Kbytes.
%
\index{ClassAd machine attribute!VM\_AvailNum}
\item[\AdAttr{VM\_AvailNum}:] The maximum number of vm universe jobs that
can be started on this machine. This maximum is set by the configuration
variable \Macro{VM\_MAX\_NUMBER}. 
%
\index{ClassAd machine attribute!VM\_Guest\_Mem}
\item[\AdAttr{VM\_Guest\_Mem}:] An attribute defined if a vm universe job
is running on this slot.  Defined by the amount of memory in use by the 
virtual machine, given in Mbytes.
%
\index{ClassAd machine attribute!VM\_Memory}
\item[\AdAttr{VM\_Memory}:] Gives the amount of memory available for starting 
additional VM jobs on this machine, given in Mbytes.
The maximum value is set by the configuration variable \Macro{VM\_MEMORY}.
%
\index{ClassAd machine attribute!VM\_Networking}
\item[\AdAttr{VM\_Networking}:] A boolean value indicating whether networking 
is allowed for virtual machines on this machine.
%
\index{ClassAd machine attribute!VM\_Type}
\item[\AdAttr{VM\_Type}:] The type of virtual machine software that can run
on this machine.  The value is set by the configuration variable
\Macro{VM\_TYPE}.
%
\index{ClassAd machine attribute!WindowsBuildNumber}
\item[\AdAttr{WindowsBuildNumber}:] An integer, extracted from the
platform type, representing a build number 
for a Windows operating system.
This attribute only exists on Windows machines.
%
\index{ClassAd machine attribute!WindowsMajorVersion}
\item[\AdAttr{WindowsMajorVersion}:] An integer, extracted from the
platform type, representing a major version number (currently 5 or 6)
for a Windows operating system.
This attribute only exists on Windows machines.
%
\index{ClassAd machine attribute!WindowsMinorVersion}
\item[\AdAttr{WindowsMinorVersion}:] An integer, extracted from the
platform type, representing a minor version number (currently 0, 1, or 2)
for a Windows operating system.
This attribute only exists on Windows machines.

\end{description}

In addition, there are a few attributes that are automatically
inserted into the machine ClassAd whenever a resource is in the
Claimed state:

\begin{description}

\index{ClassAd machine attribute (in Claimed State)!ClientMachine}
\item[\AdAttr{ClientMachine}:] The host name of the machine that has
claimed this resource

\index{ClassAd machine attribute (in Claimed State)!RemoteOwner}
\item[\AdAttr{RemoteOwner}:] The name of the user who originally
claimed this resource.

\index{ClassAd machine attribute (in Claimed State)!RemoteUser}
\item[\AdAttr{RemoteUser}:] The name of the user who is currently
using this resource.
In general, this will always be the same as the \AdAttr{RemoteOwner},
but in some cases, a resource can be claimed by one entity that hands
off the resource to another entity which uses it.
In that case, \AdAttr{RemoteUser} would hold the name of the entity
currently using the resource, while \AdAttr{RemoteOwner} would hold
the name of the entity that claimed the resource.

\index{ClassAd machine attribute (in Claimed State)!PreemptingOwner}
\item[\AdAttr{PreemptingOwner}:] The name of the user who is preempting
the job that is currently running on this resource.

\index{ClassAd machine attribute (in Claimed State)!PreemptingUser}
\item[\AdAttr{PreemptingUser}:] The name of the user who is preempting
the job that is currently running on this resource.  The relationship
between \AdAttr{PreemptingUser} and \AdAttr{PreemptingOwner} is the same
as the relationship between \AdAttr{RemoteUser} and \AdAttr{RemoteOwner}.

\index{ClassAd machine attribute (in Claimed State)!PreemptingRank}
\item[\AdAttr{PreemptingRank}:] A float which represents this machine
owner's affinity for running the Condor job which is waiting for the
current job to finish or be preempted.  If not currently hosting a
Condor job, \AdAttr{PreemptingRank} is undefined.  When a machine is
claimed and there is already a job running, the attribute's value is
computed by evaluating the machine's \AdAttr{Rank} expression with
respect to the preempting job's ClassAd.

\index{ClassAd machine attribute (in Claimed State)!TotalClaimRunTime}
\item[\AdAttr{TotalClaimRunTime}:] A running total of the amount of
time (in seconds) that all jobs (under the same claim) ran
(have spent in the Claimed/Busy state).


\index{ClassAd machine attribute (in Claimed State)!TotalClaimSuspendTime}
\item[\AdAttr{TotalClaimSuspendTime}:] A running total of the amount of
time (in seconds) that all jobs (under the same claim) have been
suspended (in the Claimed/Suspended state).

\index{ClassAd machine attribute (in Claimed State)!TotalJobRunTime}
\item[\AdAttr{TotalJobRunTime}:] A running total of the amount of
time (in seconds) that a single job ran
(has spent in the Claimed/Busy state).

\index{ClassAd machine attribute (in Claimed State)!TotalJobSuspendTime}
\item[\AdAttr{TotalJobSuspendTime}:] A running total of the amount of
time (in seconds) that a single job has been suspended
(in the Claimed/Suspended state).

\end{description}

There are a few attributes that are only inserted into the
machine ClassAd if a job is currently executing.  
If the resource is claimed but no job are running, none of these
attributes will be defined.

\begin{description}

\index{ClassAd machine attribute (when running)!JobId}
\item[\AdAttr{JobId}:] The job's identifier (for example,
\verb@152.3@), as seen from \Condor{q}
on the submitting machine.

\index{ClassAd machine attribute (when running)!JobStart}
\item[\AdAttr{JobStart}:] The time stamp in integer seconds of when the job began
executing, since the Unix epoch (00:00:00 UTC, Jan 1, 1970).  For idle
machines, the value is \Expr{UNDEFINED}.

\index{ClassAd machine attribute (when running)!LastPeriodicCheckpoint}
\item[\AdAttr{LastPeriodicCheckpoint}:] If the job has performed a
periodic checkpoint, this attribute will be defined and will hold the
time stamp of when the last periodic checkpoint was begun.
If the job has yet to perform a periodic checkpoint, or cannot
checkpoint at all, the \AdAttr{LastPeriodicCheckpoint} attribute will
not be defined.

\end{description}

\index{offline ClassAd}
There are a few attributes that are applicable to machines that
are offline, that is, hibernating.

\begin{description}

\index{ClassAd machine attribute (when offline)!MachineLastMatchTime}
\item[\AdAttr{MachineLastMatchTime}:] The Unix epoch time when this offline 
ClassAd
would have been matched to a job, if the machine were online.  
In addition,
the slot1 ClassAd of a multi-slot machine will have 
\AdAttr{slot<X>\_MachineLastMatchTime} defined,
where \Expr{<X>} is replaced by the slot id of each of the slots
with \AdAttr{MachineLastMatchTime} defined.

\index{ClassAd machine attribute (when offline)!Offline}
\item[\AdAttr{Offline}:] A boolean value, that when \Expr{True},
indicates this machine is in an offline state in the \Condor{collector}.
Such ClassAds are stored persistently, 
such that they will continue to exist after the \Condor{collector} restarts.

\index{ClassAd machine attribute (when offline)!Unhibernate}
\item[\AdAttr{Unhibernate}:] A boolean expression that specifies when
a hibernating machine should be woken up, for example, by \Condor{rooster}.

\end{description}

Finally, the single attribute, 
\Attr{CurrentTime}, is defined by the ClassAd
environment.
\begin{description}
\index{ClassAd attribute!CurrentTime}
\item[\AdAttr{CurrentTime}:] Evaluates to the 
the number of integer seconds since the Unix epoch (00:00:00 UTC, Jan 1, 1970).
\end{description}
