\index{ClassAd!DaemonMaster attributes}
\begin{description}

\index{ClassAd DaemonMaster attribute!CkptServer}
\item[\AdAttr{CkptServer}:] A string with with the fully qualified
  host name of the machine running a checkpoint server.

\index{ClassAd DaemonMaster attribute!CondorVersion}
\item[\AdAttr{CondorVersion}:] A string containing the HTCondor version
number, the release date, and the build identification number.

\index{ClassAd DaemonMaster attribute!DaemonStartTime}
\item[\AdAttr{DaemonStartTime}:] The time that this daemon was
  started, represented as the number of second elapsed since
  the Unix epoch (00:00:00 UTC, Jan 1, 1970).

\index{ClassAd DaemonMaster attribute!Machine}
\item[\AdAttr{Machine}:] A string with the machine's fully qualified 
  host name.

\index{ClassAd DaemonMaster attribute!MasterIpAddr}
\item[\AdAttr{MasterIpAddr}:] String with the IP and port address of the
\Condor{master} daemon which is publishing this DaemonMaster ClassAd.

\index{ClassAd DaemonMaster attribute!MonitorSelfAge}
\item[\AdAttr{MonitorSelfAge}:] The number of seconds that this daemon
  has been running.

\index{ClassAd DaemonMaster attribute!MonitorSelfCPUUsage}
\item[\AdAttr{MonitorSelfCPUUsage}:] The fraction of recent CPU time utilized
  by this daemon. 

\index{ClassAd DaemonMaster attribute!MonitorSelfImageSize}
\item[\AdAttr{MonitorSelfImageSize}:] The amount of virtual memory consumed by
  this daemon in Kbytes.

\index{ClassAd DaemonMaster attribute!MonitorSelfRegisteredSocketCount}
\item[\AdAttr{MonitorSelfRegisteredSocketCount}:] The current number of sockets
  registered by this daemon.

\index{ClassAd DaemonMaster attribute!MonitorSelfResidentSetSize}
\item[\AdAttr{MonitorSelfResidentSetSize}:] The amount of resident memory
  used by this daemon in Kbytes.

\index{ClassAd DaemonMaster attribute!MonitorSelfSecuritySessions}
\item[\AdAttr{MonitorSelfSecuritySessions}:] The number of open (cached)
  security sessions for this daemon.

\index{ClassAd DaemonMaster attribute!MonitorSelfTime}
\item[\AdAttr{MonitorSelfTime}:] The  time, represented as the number of
  second elapsed since the Unix epoch (00:00:00 UTC, Jan 1, 1970),
  at which this daemon last checked and set the attributes with names that
  begin with the string \Attr{MonitorSelf}.
  

\index{ClassAd DaemonMaster attribute!MyAddress}
\item[\AdAttr{MyAddress}:] Description is not yet written.

\index{ClassAd DaemonMaster attribute!MyCurrentTime}
\item[\AdAttr{MyCurrentTime}:] The time, represented as the number of
  second elapsed since the Unix epoch (00:00:00 UTC, Jan 1, 1970),
  at which the \Condor{master} daemon last sent a ClassAd update to the
  \Condor{collector}.

\index{ClassAd DaemonMaster attribute!Name}
\item[\AdAttr{Name}:] The name of this resource; typically the same value as
  the \AdAttr{Machine} attribute, but could be customized by the site
  administrator.
  On SMP machines, the \Condor{startd} will divide the CPUs up into separate
  slots, each with with a unique name.
  These names will be of the form ``slot\#@full.hostname'', for example,
  ``slot1@vulture.cs.wisc.edu'', which signifies slot number 1 from
  vulture.cs.wisc.edu.

\index{ClassAd DaemonMaster attribute!PublicNetworkIpAddr}
\item[\AdAttr{PublicNetworkIpAddr}:] Description is not yet written.

\index{ClassAd DaemonMaster attribute!RealUid}
\item[\AdAttr{RealUid}:] The UID under which the \Condor{master} is started.

\index{ClassAd DaemonMaster attribute!UpdateSequenceNumber}
\item[\AdAttr{UpdateSequenceNumber}:] An integer, starting at zero,
  and incremented with each ClassAd update sent to the \Condor{collector}.
  The \Condor{collector} uses this value to sequence the updates it
  receives.

\end{description}

