\index{ClassAd!Negotiator attributes}
\begin{description}

\index{ClassAd Negotiator attribute!DaemonStartTime}
\item[\AdAttr{DaemonStartTime}:] The time that this daemon was
  started, represented as the number of second elapsed since
    the Unix epoch (00:00:00 UTC, Jan 1, 1970).


\label{attr:LastNegotiationCycleActiveSubmitterCount<X>}
\index{ClassAd Negotiator attribute!LastNegotiationCycleActiveSubmitterCount<X>}
\item[\AdAttr{LastNegotiationCycleActiveSubmitterCount<X>}:] The integer
  number of submitters
  the \Condor{negotiator} attempted to negotiate with in the negotiation cycle.
  The number \AdAttr{<X>} appended to the attribute name indicates how
  many negotiation cycles ago this cycle happened.

\index{ClassAd Negotiator attribute!LastNegotiationCycleDuration<X>}
\item[\AdAttr{LastNegotiationCycleDuration<X>}:] The number of seconds
  that it took to complete the negotiation cycle.  The number \AdAttr{<X>}
  appended to the attribute name indicates how many negotiation cycles
  ago this cycle happened.

\index{ClassAd Negotiator attribute!LastNegotiationCycleMatches<X>}
\item[\AdAttr{LastNegotiationCycleMatches<X>}:] The number of successful
  matches that were made in the negotiation cycle.  The number \AdAttr{<X>}
  appended to the attribute name indicates how many negotiation cycles
  ago this cycle happened.

\index{ClassAd Negotiator attribute!LastNegotiationCycleRejections<X>}
\item[\AdAttr{LastNegotiationCycleDuration<X>}:] The number of
  rejections that occurred in the negotiation cycle.  The number \AdAttr{<X>}
  appended to the attribute name indicates how many negotiation cycles
  ago this cycle happened.

\index{ClassAd Negotiator attribute!LastNegotiationCycleStartTime<X>}
\item[\AdAttr{LastNegotiationCycleStartTime<X>}:]
  The time, represented as the number of second elapsed since the Unix
  epoch (00:00:00 UTC, Jan 1, 1970), at which the negotiation cycle
  started.  The number \AdAttr{<X>} appended to the attribute name
  indicates how many negotiation cycles ago this cycle happened.

\index{ClassAd Negotiator attribute!LastNegotiationCycleSubmittersFailed<X>}
\item[\AdAttr{LastNegotiationCycleSubmittersFailed<X>}:] A string containing
  a space and comma-separated list of the names of all submitters who
  failed to negotiate in the negotiation cycle.  One possible cause of
  failure is a communication timeout.  This list does not include
  submitters who ran out of time due
  to \Macro{NEGOTIATOR\_MAX\_TIME\_PER\_SUBMITTER}.  Those are listed
  separately in \AdAttr{LastNegotiationCycleSubmittersOutOfTime<X>}.
  The number \AdAttr{<X>} appended to the attribute name indicates how
  many negotiation cycles ago this cycle happened.

\index{ClassAd Negotiator attribute!LastNegotiationCycleSubmittersOutOfTime<X>}
\item[\AdAttr{LastNegotiationCycleSubmittersOutOfTime<X>}:] A string containing
  a space and comma-separated list of the names of all submitters who
  ran out of time due to \Macro{NEGOTIATOR\_MAX\_TIME\_PER\_SUBMITTER}
  in the negotiation cycle.  The number \AdAttr{<X>} appended to the
  attribute name indicates how many negotiation cycles ago this cycle
  happened.
\index{ClassAd Negotiator attribute!Machine}
\item[\AdAttr{Machine}:] A string with the machine's fully qualified 
  host name.

\index{ClassAd Negotiator attribute!MyAddress}
\item[\AdAttr{MyAddress}:] Description is not yet written.

\index{ClassAd Negotiator attribute!MyCurrentTime}
\item[\AdAttr{MyCurrentTime}:]  The time, represented as the number of 
  second elapsed since the Unix epoch (00:00:00 UTC, Jan 1, 1970),
  at which the \Condor{schedd} daemon last sent a ClassAd update to the
  \Condor{collector}.

\index{ClassAd Negotiator attribute!Name}
\item[\AdAttr{Name}:] The name of this resource; typically the same value as
  the \AdAttr{Machine} attribute, but could be customized by the site
  administrator.
  On SMP machines, the \Condor{startd} will divide the CPUs up into separate
  slots, each with with a unique name.
  These names will be of the form ``slot\#@full.hostname'', for example,
  ``slot1@vulture.cs.wisc.edu'', which signifies slot number 1 from
  vulture.cs.wisc.edu.

\index{ClassAd Negotiator attribute!NegotiatorIpAddr}
\item[\AdAttr{NegotiatorIpAddr}:] String with the IP and port address of the
\Condor{negotiator} daemon which is publishing this Negotiator ClassAd.

\index{ClassAd Negotiator attribute!PublicNetworkIpAddr}
\item[\AdAttr{PublicNetworkIpAddr}:] Description is not yet written.

\index{ClassAd Negotiator attribute!UpdateSequenceNumber}
\item[\AdAttr{UpdateSequenceNumber}:] An integer, starting at zero,
  and incremented with each ClassAd update sent to the \Condor{collector}.
  The \Condor{collector} uses this value to sequence the updates it
  receives.

\end{description}

