\index{ClassAd!Scheduler attributes}
\begin{description}

\index{ClassAd Scheduler attribute!DaemonStartTime}
\item[\AdAttr{DaemonStartTime}:] The time that this daemon was
  started, represented as the number of second elapsed since
    the Unix epoch (00:00:00 UTC, Jan 1, 1970).

\index{ClassAd Scheduler attribute!DetectedCpus}
\item[\AdAttr{DetectedCpus}:] The number of detected machine CPUs/cores.

\index{ClassAd Scheduler attribute!DetectedMemory}
\item[\AdAttr{DetectedMemory}:] The amount of detected machine RAM in MBytes.

\index{ClassAd Scheduler attribute!ExitCode<N>}
\item[\AdAttr{ExitCode<N>}:] The number of jobs with exit code
  \Expr{<N>} from this \Condor{schedd},
   within the last \Attr{WindowedStatWidth} seconds.

\index{ClassAd Scheduler attribute!ExitCodeCumulative<N>}
\item[\AdAttr{ExitCodeCumulative<N>}:] The number of jobs with exit 
  code \Expr{<N>} from this \Condor{schedd}, over the lifetime of this
  \Condor{schedd}.

\index{ClassAd Scheduler attribute!JobCompletionRate}
\item[\AdAttr{JobCompletionRate}:] The rate at which jobs completed
  successfully on this \Condor{schedd}, 
  calculated over the previous \AdAttr{WindowedStatWidth} seconds.
  Given in jobs per second.

\index{ClassAd Scheduler attribute!JobQueueBirthdate}
\item[\AdAttr{JobQueueBirthdate}:] Description is not yet written.

\index{ClassAd Scheduler attribute!JobsCompleted}
\item[\AdAttr{JobsCompleted}:] The number of jobs successfully completed
  on this \Condor{schedd} in the previous \AdAttr{WindowedStatWidth} seconds.

\index{ClassAd Scheduler attribute!JobsCompletedCumulative}
\item[\AdAttr{JobsCompletedCumulative}:] The number of jobs 
  successfully completed on this \Condor{schedd} over the lifetime of this 
  \Condor{schedd}.

\index{ClassAd Scheduler attribute!JobsExited}
\item[\AdAttr{JobsExited}:] The number of jobs that exited
  on this \Condor{schedd}, successfully or otherwise, in the 
  previous \AdAttr{WindowedStatWidth} seconds.

\index{ClassAd Scheduler attribute!JobsExitedCumulative}
\item[\AdAttr{JobsExitedCumulative}:] The number of jobs that exited
  on this \Condor{schedd}, successfully or otherwise, over
  the lifetime of this \Condor{schedd}.

\index{ClassAd Scheduler attribute!JobsStarted}
\item[\AdAttr{JobsStarted}:] The number of jobs started on this
  \Condor{schedd} in the previous \AdAttr{WindowedStatWidth} seconds.

\index{ClassAd Scheduler attribute!JobsStartedCumulative}
\item[\AdAttr{JobsStartedCumulative}:] The number of jobs started on this
  \Condor{schedd} over the lifetime of this \Condor{schedd}.

\index{ClassAd Scheduler attribute!JobsSubmitted}
\item[\AdAttr{JobsSubmitted}:] The number of jobs submitted to
  this \Condor{schedd} in the previous \AdAttr{WindowedStatWidth} seconds.

\index{ClassAd Scheduler attribute!JobsSubmittedCumulative}
\item[\AdAttr{JobsSubmittedCumulative}:] The number of jobs submitted to
  this \Condor{schedd} over the lifetime of this \Condor{schedd}.

\index{ClassAd Scheduler attribute!JobStartRate}
\item[\AdAttr{JobStartRate}:] The rate at which jobs were started
  on this \Condor{schedd}, 
  calculated over the previous \AdAttr{WindowedStatWidth} seconds.
  Given in jobs per second.

\index{ClassAd Scheduler attribute!JobSubmissionRate}
\item[\AdAttr{JobSubmissionRate}:] The rate at which jobs were
  submitted on this \Condor{schedd}, 
  calculated over the previous \AdAttr{WindowedStatWidth} seconds.
  Given in jobs per second.

\index{ClassAd Scheduler attribute!Machine}
\item[\AdAttr{Machine}:] A string with the machine's fully qualified 
  host name.

\index{ClassAd Scheduler attribute!MaxJobsRunning}
\item[\AdAttr{MaxJobsRunning}:] The same integer value as set by the
  evaluation of the configuration variable \Macro{MAX\_JOBS\_RUNNING}.
  See the definition at section~\ref{param:MaxJobsRunning} on
  page~\pageref{param:MaxJobsRunning}.

\index{ClassAd Scheduler attribute!MeanRunningTime}
\item[\AdAttr{MeanRunningTime}:] Average time in seconds
  from job start to job completion for all jobs
  on this \Condor{schedd} over the previous \AdAttr{WindowedStatWidth} seconds.

\index{ClassAd Scheduler attribute!MeanRunningTimeCumulative}
\item[\AdAttr{MeanRunningTimeCumulative}:] Average time in seconds
  from job start to job completion for all jobs
  on this \Condor{schedd} over the lifetime of this \Condor{schedd}.

\index{ClassAd Scheduler attribute!MeanTimeToStart}
\item[\AdAttr{MeanTimeToStart}:] Average time in seconds
  from job submission to job start for all jobs
  on this \Condor{schedd} over the previous \AdAttr{WindowedStatWidth} seconds.

\index{ClassAd Scheduler attribute!MeanTimeToStartCumulative}
\item[\AdAttr{MeanTimeToStartCumulative}:] Average time in seconds 
  from job submission to job start, 
  for all jobs on this \Condor{schedd} over the 
  lifetime of this \Condor{schedd}.

\index{ClassAd Scheduler attribute!MonitorSelfAge}
\item[\AdAttr{MonitorSelfAge}:] The number of seconds that this daemon
  has been running.

\index{ClassAd Scheduler attribute!MonitorSelfCPUUsage}
\item[\AdAttr{MonitorSelfCPUUsage}:] The fraction of recent CPU time utilized
  by this daemon. 

\index{ClassAd Scheduler attribute!MonitorSelfImageSize}
\item[\AdAttr{MonitorSelfImageSize}:] The amount of virtual memory consumed by
  this daemon in Kbytes.

\index{ClassAd Scheduler attribute!MonitorSelfRegisteredSocketCount}
\item[\AdAttr{MonitorSelfRegisteredSocketCount}:] The current number of sockets
  registered by this daemon.

\index{ClassAd Scheduler attribute!MonitorSelfResidentSetSize}
\item[\AdAttr{MonitorSelfResidentSetSize}:] The amount of resident memory
  used by this daemon in Kbytes.

\index{ClassAd Scheduler attribute!MonitorSelfSecuritySessions}
\item[\AdAttr{MonitorSelfSecuritySessions}:] The number of open (cached)
  security sessions for this daemon.

\index{ClassAd Scheduler attribute!MonitorSelfTime}
\item[\AdAttr{MonitorSelfTime}:] The  time, represented as the number of
  second elapsed since the Unix epoch (00:00:00 UTC, Jan 1, 1970),
  at which this daemon last checked and set the attributes with names that
  begin with the string \Attr{MonitorSelf}.
  
\index{ClassAd Scheduler attribute!MyAddress}
\item[\AdAttr{MyAddress}:] Description is not yet written.

\index{ClassAd Scheduler attribute!MyCurrentTime}
\item[\AdAttr{MyCurrentTime}:]  The time, represented as the number of 
  second elapsed since the Unix epoch (00:00:00 UTC, Jan 1, 1970),
  at which the \Condor{schedd} daemon last sent a ClassAd update to the
  \Condor{collector}.

\index{ClassAd Scheduler attribute!Name}
\item[\AdAttr{Name}:] The name of this resource; typically the same value as
  the \AdAttr{Machine} attribute, but could be customized by the site
  administrator.
  On SMP machines, the \Condor{startd} will divide the CPUs up into separate
  slots, each with with a unique name.
  These names will be of the form ``slot\#@full.hostname'', for example,
  ``slot1@vulture.cs.wisc.edu'', which signifies slot number 1 from
  vulture.cs.wisc.edu.

\index{ClassAd Scheduler attribute!NumUsers}
\item[\AdAttr{NumUsers}:] The integer number of distinct users with jobs in
  this \Condor{schedd}'s queue.

\index{ClassAd Scheduler attribute!PublicNetworkIpAddr}
\item[\AdAttr{PublicNetworkIpAddr}:] Description is not yet written.

\index{ClassAd Scheduler attribute!QuillEnabled}
\item[\AdAttr{QuillEnabled}:] The same boolean value as set in the
  configuration variable \Macro{QUILL\_ENABLED}.
  See the definition at section~\ref{param:QuillEnabled} on
  page~\pageref{param:QuillEnabled}.

\index{ClassAd Scheduler attribute!ScheddIpAddr}
\item[\AdAttr{ScheddIpAddr}:] String with the IP and port address of the
\Condor{schedd} daemon which is publishing this Scheduler ClassAd.

\index{ClassAd Scheduler attribute!ServerTime}
\item[\AdAttr{ServerTime}:] Description is not yet written.

\index{ClassAd Scheduler attribute!ShadowExceptions}
\item[\AdAttr{ShadowExceptions}:] The number of \Condor{shadow} exceptions 
  on this \Condor{schedd}, 
  in the previous \AdAttr{WindowedStatWidth} seconds.

\index{ClassAd Scheduler attribute!ShadowExceptionsCumulative}
\item[\AdAttr{ShadowExceptionsCumulative}:] The number of \Condor{shadow} 
  exceptions on this \Condor{schedd}, over the lifetime of this \Condor{schedd}.

\index{ClassAd Scheduler attribute!StartLocalUniverse}
\item[\AdAttr{StartLocalUniverse}:] The same boolean value as set in the
  configuration variable \Macro{START\_LOCAL\_UNIVERSE}.
  See the definition at section~\ref{param:StartLocalUniverse} on
  page~\pageref{param:StartLocalUniverse}.

\index{ClassAd Scheduler attribute!StartSchedulerUniverse}
\item[\AdAttr{StartSchedulerUniverse}:] The same boolean value as set in the
  configuration variable \Macro{START\_SCHEDULER\_UNIVERSE}.
  See the definition at section~\ref{param:StartSchedulerUniverse} on
  page~\pageref{param:StartSchedulerUniverse}.

\index{ClassAd Scheduler attribute!SumRunningTimeCumulative}
\item[\AdAttr{SumRunningTimeCumulative}:] The sum in seconds
  from job start to job completion for all jobs
  on this \Condor{schedd} over the lifetime of this \Condor{schedd}.

\index{ClassAd Scheduler attribute!SumTimeToStartCumulative}
\item[\AdAttr{SumTimeToStartCumulative}:] The sum in seconds
  from job submission to job start for all jobs 
  on this \Condor{schedd} over the lifetime of this \Condor{schedd}.

\index{ClassAd Scheduler attribute!TotalFlockedJobs}
\item[\AdAttr{TotalFlockedJobs}:] The total number of jobs from this
  \Condor{schedd} daemon that are currently flocked to other pools.

\index{ClassAd Scheduler attribute!TotalHeldJobs}
\item[\AdAttr{TotalHeldJobs}:] The total number of jobs from this
  \Condor{schedd} daemon that are currently on hold.

\index{ClassAd Scheduler attribute!TotalIdleJobs}
\item[\AdAttr{TotalIdleJobs}:] The total number of jobs from this
  \Condor{schedd} daemon that are currently idle.

\index{ClassAd Scheduler attribute!TotalJobAds}
\item[\AdAttr{TotalJobAds}:] The total number of all jobs (in all 
  states) from this \Condor{schedd} daemon.

\index{ClassAd Scheduler attribute!TotalLocalIdleJobs}
\item[\AdAttr{TotalLocalIdleJobs}:] The total number of 
  \SubmitCmd{local} \SubmitCmd{ universe} jobs from this
  \Condor{schedd} daemon that are currently idle.

\index{ClassAd Scheduler attribute!TotalLocalRunningJobs}
\item[\AdAttr{TotalLocalRunningJobs}:] The total number of 
  \SubmitCmd{local} \SubmitCmd{ universe} jobs from this
  \Condor{schedd} daemon that are currently running.

\index{ClassAd Scheduler attribute!TotalRemovedJobs}
\item[\AdAttr{TotalRemovedJobs}:] The current number of all running jobs
  from this \Condor{schedd} daemon that have remove requests.

\index{ClassAd Scheduler attribute!TotalRunningJobs}
\item[\AdAttr{TotalRunningJobs}:] The total number of jobs from this
  \Condor{schedd} daemon that are currently running.

\index{ClassAd Scheduler attribute!TotalSchedulerIdleJobs}
\item[\AdAttr{TotalSchedulerIdleJobs}:] The total number of 
  \SubmitCmd{scheduler} \SubmitCmd{ universe} jobs from this
  \Condor{schedd} daemon that are currently idle.

\index{ClassAd Scheduler attribute!TotalSchedulerRunningJobs}
\item[\AdAttr{TotalSchedulerRunningJobs}:] The total number of 
  \SubmitCmd{scheduler} \SubmitCmd{ universe} jobs from this
  \Condor{schedd} daemon that are currently running.

\index{ClassAd Scheduler attribute!UpdateInterval}
\item[\AdAttr{UpdateInterval}:] The interval, in seconds,
  between publication of this \Condor{schedd} ClassAd and
  the previous publication.

\index{ClassAd Scheduler attribute!UpdateSequenceNumber}
\item[\AdAttr{UpdateSequenceNumber}:] An integer, starting at zero,
  and incremented with each ClassAd update sent to the \Condor{collector}.
  The \Condor{collector} uses this value to sequence the updates it
  receives.

\index{ClassAd Scheduler attribute!VirtualMemory}
\item[\AdAttr{VirtualMemory}:] Description is not yet written.

\index{ClassAd Scheduler attribute!WantResAd}
\item[\AdAttr{WantResAd}:] A boolean value that when \Expr{True}
  causes the \Condor{negotiator} daemon to send to this \Condor{schedd}
  daemon a full machine ClassAd corresponding to a matched job.

\index{ClassAd Scheduler attribute!WindowedStatWidth}
\item[\AdAttr{WindowedStatWidth}:] The time window, in seconds,
  for window-based performance statistics on this \Condor{schedd}.
  Set by the configuration variable \Macro{WINDOWED\_STAT\_WIDTH}.

\end{description}

