\index{ClassAd!DaemonCore statistics attributes}

Every HTCondor daemon keeps a set of operational statistics, some of which are common to all daemons, others are specific to the
running of a particular daemon. In some cases, the statistics can reveal buggy or slow performance of the HTCondor system. The following statistics are available for all daemons, and can be accessed directly with 
the condor\_status command with a direct query, such as

\begin{verbatim}
condor\_status -direct somehostname.example.com -schedd -statistics DC:2 -l
\end{verbatim}

\begin{description}

\index{ClassAd statistics attribute!DCUdpQueueDepth}
\item[\AdAttr{DCUdpQueueDepth}:] This attribute is the number of bytes in the incoming UDP receive queue for this daemon, 
if it has a UDP command port.  This attribute is polled once a minute by default, so may be out of date.
The attribute DCUdpQueueDepthPeak records the peak depth since the daemon has started.

\index{ClassAd statistics attribute!DebugOuts}
\item[\AdAttr{DebugOuts}:] This attribute is the count of debugging messages printed to the daemon's
debug log, such as the ScheddLog. There is a moderate cost to writing these logging messages, 
if the debug level is very high for an active daemon, the logging will slow performance. 
The corresponding attribute RecentDebugOuts is the count of the messages in the last 20 minutes.

\index{ClassAd statistics attribute!PipeMessages}
\item[\AdAttr{PipeMessages}:] This attribute is the number of messages received on a Unix pipe by this daemon since start time.  The corresponding attribute RecentPipeMessages is the count of message in the last 20 minutes.

\index{ClassAd statistics attribute!PipeRuntime}
\item[\AdAttr{PipeRuntime}:] This attribute respresents the total number of wall clock seconds this daemon has spent processing pipe message since start.  The corresponding attribute RecentPipeRuntime is the total time in the last 20 minutes.

\index{ClassAd statistics attribute!SelectWaittime}
\item[\AdAttr{SelectWaittime}:] This attribute represents the total number of wall clock seconds this daemon has spent completely
idle, waiting to process incoming requests or internal timers.  The attribute DaemonCoreDutyCycle, which may be easier to
write policy around, is based off of this.

\index{ClassAd statistics attribute!SignalRuntime}
\item[\AdAttr{SignalRuntime}:] This attribute respresents the total number of wall clock time seconds this daemon has spent processing signals since start.  The corresponding attribute RecentSignalRuntime is the total time in the last 20 minutes.

\index{ClassAd statistics attribute!Signals}
\item[\AdAttr{Signals}:] This attribute is the number of signals, either Unix signals, or HTCondor simulated signals received by this daemon since start time.  The corresponding attribute RecentSignals is the number of signals in the last 20 minutes.

\index{ClassAd statistics attribute!SocketRuntime}
\item[\AdAttr{SocketRuntime}:] This attribute respresents the total number of wall clock time seconds this daemon has spent processing socket messages since start.  The corresponding attribute RecentTimerRuntime is the total time in the last 20 minutes.

\index{ClassAd statistics attribute!SockMessages}
\item[\AdAttr{SockMessages}:] This attribute is the number of messages received on socket by this daemon since start time.  The corresponding attribute RecentSockMessages is the count of message in the last 20 minutes.

\index{ClassAd statistics attribute!TimerRuntime}
\item[\AdAttr{TimerRuntime}:] This attribute respresents the total number of wall clock time seconds this daemon has spent processing timers since start.  The corresponding attribute RecentTimerRuntime is the total time in the last 20 minutes.

\index{ClassAd statistics attribute!TimersFired}
\item[\AdAttr{TimersFired}:] This attribute is the number of internal timers which have fired, in this daemon since start time.  The corresponding attribute RecentTimersFired in the number of timers fired in the last 20 minutes.

\end{description}
