\index{ClassAd!submitter attributes}

\begin{description}

\index{ClassAd submitter attribute!CondorVersion}
\item[\AdAttr{CondorVersion}:] A string containing the HTCondor version
number, the release date, and the build identification number.

\index{ClassAd submitter attribute!FlockedJobs}
\index{FlockedJobs@\Attr{FlockedJobs}!submitter ClassAd attribute}
\item[\AdAttr{FlockedJobs}:] The number of jobs from this submitter 
that are running in another pool.

\index{ClassAd submitter attribute!HeldJobs}
\index{HeldJobs@\Attr{HeldJobs}!submitter ClassAd attribute}
\item[\AdAttr{HeldJobs}:] The number of jobs from this submitter 
that are in the hold state.

\index{ClassAd submitter attribute!IdleJobs}
\index{IdleJobs@\Attr{IdleJobs}!submitter ClassAd attribute}
\item[\AdAttr{IdleJobs}:] The number of jobs from this submitter 
that are now idle.

\index{ClassAd submitter attribute!Name}
\index{Name@\Attr{Name}!submitter ClassAd attribute}
\item[\AdAttr{Name}:] The fully qualified name of the user or accounting group.
It will be of the form \Expr{name@submit.domain}.

\index{ClassAd submitter attribute!RunningJobs}
\index{RunningJobs@\Attr{RunningJobs}!submitter ClassAd attribute}
\item[\AdAttr{RunningJobs}:] The number of jobs from this submitter 
that are running now.

\index{ClassAd submitter attribute!ScheddIpAddr}
\index{ScheddIpAddr@\Attr{ScheddIpAddr}!submitter ClassAd attribute}
\item[\AdAttr{ScheddIpAddr}:] The IP address associated with the
\Condor{schedd} daemon used by the submitter.

\index{ClassAd submitter attribute!ScheddName}
\index{ScheddName@\Attr{ScheddName}!submitter ClassAd attribute}
\item[\AdAttr{ScheddName}:] The fully qualified host name of the machine 
that the submitter submitted from.
It will be of the form \Expr{submit.domain}.

\index{ClassAd submitter attribute!SubmitterTag}
\index{SubmitterTag@\Attr{SubmitterTag}!submitter ClassAd attribute}
\item[\AdAttr{SubmitterTag}:] The fully qualified host name of the
central manager of the pool used by the submitter,
if the job flocked to the local pool.
Or, it will be the empty string if submitter submitted from within
the local pool.

\index{ClassAd submitter attribute!WeightedIdleJobs}
\index{WeightedIdleJobs@\Attr{WeightedIdleJobs}!submitter ClassAd attribute}
\item[\AdAttr{WeightedIdleJobs}:] A total number of requested
cores across all Idle jobs from the submitter.

\index{ClassAd submitter attribute!WeightedRunningJobs}
\index{WeightedRunningJobs@\Attr{WeightedRunningJobs}!submitter ClassAd attribute}
\item[\AdAttr{WeightedRunningJobs}:] A total number of requested
cores across all Running jobs from the submitter.

\end{description}
