Copyright \copyright\ 1990-2001 Condor Team, Computer Sciences
Department, University of Wisconsin-Madison, Madison, WI. All Rights
Reserved. No use of the Condor Software Program Object Code (Condor)
is authorized without the express consent of the Condor Team. For more
information contact: Condor Team, Attention: Professor Miron Livny,
7367 Computer Sciences, 1210 W. Dayton St., Madison, WI 53706-1685,
(608) 262-0856 or miron@cs.wisc.edu. 

Some distributions of Condor include a compiled, unmodified version of 
the GNU C library.  The complete source code to GNU glibc can be 
found at \Url{http://www.gnu.org/software/libc/}.

Allowed Uses: User may use Condor only in accordance with the
appropriate Usage License, which are detailed below.  Academic
institutions should agree to the \Term{Academic Use License for
Condor}, while all others should agree to the \Term{Internal Use
License for Condor}.

Use Restrictions: User may not and User may not permit others to (a)
decipher, disassemble, decompile, translate, reverse engineer or
otherwise derive source code from Condor, (b) modify or prepare
derivative works of Condor, (c) copy Condor, except to make a single
copy for archival purposes only, (d) rent or lease Condor, (e)
distribute Condor electronically, (f) use Condor in any manner that
infringes the intellectual property or rights of another party, or (g)
transfer Condor or any copy thereof to another party. 

Warranty Disclaimer: USER ACKNOWLEDGES AND AGREES THAT: (A) NEITHER
THE Condor TEAM NOR THE BOARD OF REGENTS OF THE UNIVERSITY OF
WISCONSIN SYSTEM (REGENTS) MAKE ANY REPRESENTATIONS OR WARRANTIES
WHATSOEVER ABOUT THE SUITABILITY OF Condor FOR ANY PURPOSE; (B) Condor
IS PROVIDED ON AN "AS IS, WITH ALL DEFECTS" BASIS WITHOUT EXPRESS OR
IMPLIED WARRANTIES, INCLUDING WARRANTIES OF MERCHANTABILITY AND
FITNESS FOR A PARTICULAR PURPOSE OR NONINFRINGEMENT; (C) NEITHER THE
Condor TEAM NOR THE REGENTS SHALL BE LIABLE FOR ANY DAMAGE OR LOSS OF
ANY KIND ARISING OUT OF OR RESULTING FROM USER'S POSSESSION OR USE
OF Condor (INCLUDING DATA LOSS OR CORRUPTION), REGARDLESS OF WHETHER
SUCH LIABILITY IS BASED IN TORT, CONTRACT, OR OTHERWISE; AND (D)
NEITHER THE Condor TEAM NOR THE REGENTS HAVE AN OBLIGATION TO PROVIDE
DEBUGGING, MAINTENANCE, SUPPORT, UPDATES, ENHANCEMENTS, OR
MODIFICATIONS. 

Damages Disclaimer: USER ACKNOWLEDGES AND AGREES THAT IN NO EVENT WILL
THE Condor TEAM OR THE REGENTS BE LIABLE TO USER FOR ANY SPECIAL,
CONSEQUENTIAL, INDIRECT OR SIMILAR DAMAGES, INCLUDING ANY LOST PROFITS
OR LOST DATA ARISING OUT OF THE USE OR INABILITY TO USE Condor EVEN IF
THE Condor TEAM OR THE REGENTS HAVE BEEN ADVISED OF THE POSSIBILITY OF
SUCH DAMAGES. 

Attribution Requirement: User agrees that any reports, publications,
or other disclosure of results obtained with Condor will attribute its
use by an appropriate citation. The appropriate reference for Condor
is "The Condor Software Program (Condor) was developed by the Condor
Team at the Computer Sciences Department of the University of
Wisconsin-Madison. All rights, title, and interest in Condor are owned
by the Condor Team." 

Compliance with Applicable Laws: User agrees to abide by copyright law
and all other applicable laws of the United States including, but not
limited to, export control laws. User acknowledges that Condor in
source code form remains a confidential trade secret of the Condor
Team and/or its licensors and therefore User agrees not to modify
Condor or attempt to decipher, decompile, disassemble, translate, or
reverse engineer Condor, except to the extent applicable laws
specifically prohibit such restriction. 

U.S. Government Rights Restrictions: Use, duplication, or disclosure
by the U.S. Government is subject to restrictions as set forth in
subparagraph (c)(1)(ii) of The Rights in Technical Data and Computer
Software clause at DFARS 252.227-7013 or subparagraphs (c)(1) and (2)
of Commercial Computer Software-Restricted Rights at 48 CFR 52.227-19,
as applicable, Condor Team, Attention: Professor Miron Livny, 7367
Computer Sciences, 1210 W. Dayton St., Madison, WI 53706-1685, (608)
262-0856 or miron@cs.wisc.edu. 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\label{Condor-Usage-Licenses}Condor Usage Licenses}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Following are licenses for use of Condor Version 6.  Academic
institutions should agree to the Academic Use License for Condor,
while all others should agree to the Internal Use License for Condor. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\label{Internal-Use-License}Internal Use License for Condor}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This is an Internal Use License for Condor Version 6.  This License is
to be signed by RECIPIENT (the "RECIPIENT"), and returned to the
Condor Team at the Computer Sciences Department of the University of
Wisconsin-Madison (the "PROVIDER").  The Condor Version 6 software
program was developed by the Condor Team.  All rights, title, and
interest in Condor Version 6 are owned by the Condor Team.  The
subject computer program, including source code, executables, and
documentation shall be referred to as the "SOFTWARE."

RECIPIENT and PROVIDER agree as follows:

\begin{enumerate}
\item Definitions.
  \begin{enumerate} 
  \item The "Object Code" of the SOFTWARE means the SOFTWARE assembled
  or compiled in magnetic or electronic binary form on software media,
  which are readable and usable by machines, but not generally
  readable by humans without reverse assembly, reverse compiling, or
  reverse engineering.
  \item The "Source Code" of the SOFTWARE means the SOFTWARE written
  in programming languages, such as C and FORTRAN, including all
  comments and procedural code, such as job control language
  statements, in a form intelligible to trained programmers and
  capable of being translated into Object Code for operation on
  computer equipment through assembly or compiling, and accompanied by
  documentation, including flow charts, schematics, statements of
  principles of operations, and architecture standards, describing the
  data flows, data structures, and control logic of the SOFTWARE in
  sufficient detail to enable a trained programmer through study of
  such documentation to maintain and/or modify the SOFTWARE without
  undue experimentation.
  \item A "Derivative Work" means a work that is based on one or more
  preexisting works, such as a revision, enhancement, modification,
  translation, abridgment, condensation, expansion, or any other form
  in which such preexisting works may be recast, transformed, or
  adapted, and that, if prepared without authorization of the owner of
  the copyright in such preexisting work, would constitute a copyright
  infringement.  For purposes hereof, a Derivative Work shall also
  include any compilation that incorporates such a preexisting work.
  Unless otherwise provided in this License, all references to the
  SOFTWARE include any Derivative Works provided by PROVIDER or
  authorized to be made by RECIPIENT hereunder.
  \item "Support Materials" means documentation that describes the
  function and use of the SOFTWARE in sufficient detail to permit use
  of the SOFTWARE.  
  \end{enumerate}

\item Copying of SOFTWARE and Support Materials.  PROVIDER grants
RECIPIENT a non-exclusive, non-transferable use license to copy and
distribute internally the SOFTWARE and related Support Materials in
support of RECIPIENT's use of the SOFTWARE.  RECIPIENT agrees to
include all copyright, trademark, and other proprietary notices of
PROVIDER in each copy of the SOFTWARE as they appear in the version
provided to RECIPIENT by PROVIDER.  RECIPIENT agrees to maintain
records of the number of copies of the SOFTWARE that RECIPIENT makes,
uses, or possesses. 

\item Use of Object Code.  PROVIDER grants RECIPIENT a royalty-free,
non-exclusive, non-transferable use license in and to the SOFTWARE, in
Object Code form only, to: 
  \begin{enumerate}
  \item Install the SOFTWARE at RECIPIENT's offices listed below;
  \item Use and execute the SOFTWARE for research or other internal
  purposes only;
  \item In support of RECIPIENT's authorized use of the SOFTWARE,
  physically transfer the SOFTWARE from one (1) computer to another;
  store the SOFTWARE's machine-readable instructions or data on a
  temporary basis in main memory, extended memory, or expanded memory
  of such computer system as necessary for such use; and transmit such
  instructions or data through computers and associated devices.
  \end{enumerate}

\item Delivery.  PROVIDER will deliver to RECIPIENT one (1) executable
copy of the SOFTWARE in Object Code form, one (1) full set of the
related documentation, and one (1)
set of Support Materials relating to the SOFTWARE within fifteen (15)
business days after the receipt of the signed License. 

\item Back-up Copies.  RECIPIENT may make up to two (2) copies of the
SOFTWARE in Object Code form for nonproductive backup purposes only. 

\item Term of License.  The term of this License shall be one (1) year
from the date of this License.  However, PROVIDER may terminate
RECIPIENT's License without cause at any time.  All copies of the
SOFTWARE, or Derivative Works thereof, shall be destroyed by the
RECIPIENT upon termination of this License.   

\item Proprietary Protection.  PROVIDER shall have sole and exclusive
ownership of all right, title, and interest in and to the SOFTWARE and
Support Materials, all copies thereof, and all modifications and
enhancements thereto (including ownership of all copyrights and other
intellectual property rights pertaining thereto).  Any modifications
or Derivative Works based on the SOFTWARE shall be considered a part
of the SOFTWARE and ownership thereof shall be retained by the
PROVIDER and shall be made available to the PROVIDER upon request.
This License does not provide RECIPIENT with title or ownership of the
SOFTWARE, but only a right of internal use. 

\item Limitations on Use, Etc.  RECIPIENT may not use, copy, modify,
or distribute the SOFTWARE (electronically or otherwise) or any copy,
adaptation, transcription, or merged portion thereof, except as
expressly authorized in this License.  RECIPIENT's license may not
be transferred, leased, assigned, or sublicensed without PROVIDER's
prior express authorization. 

\item Data.  RECIPIENT acknowledges that data conversion is subject to
the likelihood of human and machine errors, omissions, delays, and
losses, including inadvertent loss of data or damage to media, that
may give rise to loss or damage.  PROVIDER shall not be liable for any
such errors, omissions, delays, or losses, whatsoever.  RECIPIENT is
also responsible for complying with all local, state, and federal laws
pertaining to the use and disclosure of any data.

\item Warranty Disclaimer.  RECIPIENT ACKNOWLEDGES AND AGREES THAT:
(A) NEITHER THE CONDOR TEAM NOR THE BOARD OF REGENTS OF THE UNIVERSITY
OF WISCONSIN SYSTEM (REGENTS) MAKE ANY REPRESENTATIONS OR WARRANTIES
WHATSOEVER ABOUT THE SUITABILITY OF THE SOFTWARE FOR ANY PURPOSE; (B)
THE SOFTWARE IS PROVIDED ON AN "AS IS, WITH ALL DEFECTS" BASIS WITHOUT
EXPRESS OR IMPLIED WARRANTIES, INCLUDING WARRANTIES OF MERCHANTABILITY
AND FITNESS FOR A PARTICULAR PURPOSE OR NONINFRINGEMENT; (C) NEITHER
THE CONDOR TEAM NOR THE REGENTS SHALL BE LIABLE FOR ANY DAMAGE OR LOSS
OF ANY KIND ARISING OUT OF OR RESULTING FROM RECIPIENT'S POSSESSION
OR USE OF THE SOFTWARE (INCLUDING DATA LOSS OR CORRUPTION), REGARDLESS
OF WHETHER SUCH LIABILITY IS BASED IN TORT, CONTRACT, OR OTHERWISE;
AND (D) NEITHER THE CONDOR TEAM NOR THE REGENTS HAVE AN OBLIGATION TO
PROVIDE DEBUGGING, MAINTENANCE, SUPPORT, UPDATES, ENHANCEMENTS, OR
MODIFICATIONS.

\item Damages Disclaimer.  RECIPIENT ACKNOWLEDGES AND AGREES THAT IN
NO EVENT WILL THE CONDOR TEAM OR THE REGENTS BE LIABLE TO RECIPIENT
FOR ANY SPECIAL, CONSEQUENTIAL, INDIRECT OR SIMILAR DAMAGES, INCLUDING
ANY LOST PROFITS OR LOST DATA ARISING OUT OF THE USE OR INABILITY TO
USE THE SOFTWARE EVEN IF THE CONDOR TEAM OR THE REGENTS HAVE BEEN
ADVISED OF THE POSSIBILITY OF SUCH DAMAGES.

\item Compliance with Applicable Laws.  RECIPIENT agrees to abide by
copyright law and all other applicable laws of the United States
including, but not limited to, export control laws.

\item U.S. Government Rights Restrictions.  Use, duplication, or
disclosure by the U.S. Government is subject to restrictions as set
forth in subparagraph (c)(1)(ii) of The Rights in Technical Data and
Computer Software clause at DFARS 252.227-7013 or subparagraphs (c)(1)
and (2) of Commercial Computer Software-Restricted Rights at 48 CFR
52.227-19, as applicable, Condor Team, Attention: Professor Miron
Livny, 7367 Computer Sciences, 1210 W. Dayton St., Madison, WI
53706-1685, (608) 262-0856 or miron@cs.wisc.edu.

\item Governing Law.  This License shall be governed by and construed and enforced in accordance with the laws of the State of Wisconsin as it applies to a contract made and performed in such state, except to the extent such laws are in conflict with federal law.

\item Modifications and Waivers.  This License may not be modified
except by a writing signed by authorized representatives of both
parties.  A waiver by either party of its rights hereunder shall not
be binding unless contained in a writing signed by an authorized
representative of the party waiving its rights.  The nonenforcement or
waiver of any provision on one (1) occasion shall not constitute a
waiver of such provision on any other occasions unless expressly so
agreed in writing.  It is agreed that no use of trade or other regular
practice or method of dealing between the parties hereto shall be used
to modify, interpret, supplement, or alter in any manner the terms of
this License.

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\label{Academic-Use-License}
Academic Use License for Condor}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This is an Academic Object Code Use License for Condor. This license
is between you (the "RECIPIENT"), and the Condor Team at the Computer
Sciences Department of the University of Wisconsin-Madison (the
"PROVIDER"). The Condor software program was developed by the Condor
Team. All rights, title, and interest in Condor are owned by the
Condor Team. The subject computer program, including executables and
supporting documentation, shall be referred to as the "SOFTWARE".

RECIPIENT and PROVIDER agree as follows:

\begin{enumerate}

\item A non-exclusive, non-transferable academic use license is
granted to the RECIPIENT to install and use the SOFTWARE on any
appropriate computer systems located at the RECIPIENT's institution
to which the RECIPIENT has authorized access. Use of the SOFTWARE is
restricted to the RECIPIENT and collaborators at RECIPIENT's
institution who have agreed to accept the terms of this license.

\item The PROVIDER shall retain ownership of all materials (including
magnetic tape, unless provided by the RECIPIENT) and SOFTWARE
delivered to the RECIPIENT. Any modifications or derivative works
based on the SOFTWARE shall be considered part of the SOFTWARE and
ownership thereof shall be retained by the PROVIDER and shall be made
available to the PROVIDER upon request.

\item The RECIPIENT may make a reasonable number of copies of the
SOFTWARE for the purpose of backup and maintenance of the SOFTWARE, or
for development of derivative works based on the SOFTWARE. The
RECIPIENT agrees to include all copyright or trademark notices on any
copies of the SOFTWARE or derivatives thereof. All copies of the
SOFTWARE, or derivatives thereof, shall be destroyed by the RECIPIENT
upon termination of this license.

\item The RECIPIENT shall use the SOFTWARE for research, educational,
or other non-commercial purposes only. The RECIPIENT acknowledges that
this license grants no rights whatsoever for commercial use of the
SOFTWARE or in any commercial version(s) of the SOFTWARE. The
RECIPIENT is strictly prohibited from deciphering, disassembling,
decompiling, translating, reverse engineering or otherwise deriving
source code from the SOFTWARE, except to the extent applicable laws
specifically prohibit such restriction.

\item The RECIPIENT shall not disclose in any form either the
delivered SOFTWARE or any modifications or derivative works based on
the SOFTWARE to any third party without prior express authorization
from the PROVIDER.

\item If the RECIPIENT receives a request to furnish all or any
portion of the SOFTWARE to any third party, RECIPIENT shall not
fulfill such a request, and further agrees to refer the request to the
PROVIDER.

\item The RECIPIENT agrees that the SOFTWARE is furnished on an "as
is, with all defects" basis, without maintenance, debugging, support
or improvement, and that neither the PROVIDER nor the Board of Regents
of the University of Wisconsin System warrant the SOFTWARE or any of
its results and are in no way liable for any use that the RECIPIENT
makes of the SOFTWARE.

\item The RECIPIENT agrees that any reports, publications, or other
disclosure of results obtained with the SOFTWARE will acknowledge its
use by an appropriate citation. The appropriate reference for the
SOFTWARE is "The Condor Software Program (Condor) was developed by the
Condor Team at the Computer Sciences Department of the University of
Wisconsin-Madison. All rights, title, and interest in Condor are owned
by the Condor Team."

\item The term of this license shall not be limited in time. However,
PROVIDER may terminate RECIPIENT's license without cause at any
time.

\item Source code for the SOFTWARE is available upon request and at
the sole discretion of the PROVIDER.

\item This license shall be construed and governed in accordance with
the laws of the State of Wisconsin.

\end{enumerate}

\begin{flushleft}
For more information: \\

Condor Team \\
Attention: Professor Miron Livny \\
7367 Computer Sciences \\ 
1210 W. Dayton St. \\
Madison, WI 53706-1685 \\
\Email{miron@cs.wisc.edu} \\
\Url{http://www.cs.wisc.edu/\Tilde miron/miron.html} \\
\end{flushleft}




