\section{\label{sec:clouds-config}HTCondor Annex Configuration}

While the configuration macros in this section may be set by the HTCondor
administrator, they are intended for the user-specific HTCondor configuration
file (usually {\tt \textasciitilde/.condor/user\_config}).

\begin{description}

\label{param:AnnexDefaultLeaseDuration}
\item[\Macro{ANNEX\_DEFAULT\_LEASE\_DURATION}]
  The duration of an annex if not specified on the command-line; specified
  in seconds.  Defaults to 50 minutes.

\label{param:AnnexDefaultUnclaimedTimeout}
\item[\Macro{ANNEX\_DEFAULT\_UNCLAIMED\_TIMEOUT}]
  How long an annex instances should stay idle before shutting down;
  specified in seconds.  Defaults to 15 minutes.

\label{param:AnnexDefaultEC2URL}
\item[\Macro{ANNEX\_DEFAULT\_EC2\_URL}]
  The AWS EC2 endpoint that \Condor{annex} should use.  Defaults to
  `https://ec2.us-east-1.amazonaws.com'.

\label{param:AnnexDefaultCWEURL}
\item[\Macro{ANNEX\_DEFAULT\_CWE\_URL}]
  The AWS CloudWatch Events endpoint that \Condor{annex} should use.
  Defaults to `https://events.us-east-1.amazonaws.com'.

\label{param:AnnexDefaultLambdaURL}
\item[\Macro{ANNEX\_DEFAULT\_LAMBDA\_URL}]
  The AWS Lambda endpoint that \Condor{annex} should use.  Defaults to
  `https://lambda.us-east-1.amazonaws.com'.

\label{param:AnnexDefaultS3URL}
\item[\Macro{ANNEX\_DEFAULT\_S3\_URL}]
  The AWS S3 endpoint that \Condor{annex} should use.  Defaults to
  `https://s3.amazonaws.com'.

\label{param:AnnexDefaultCFURL}
\item[\Macro{ANNEX\_DEFAULT\_CF\_URL}]
  The AWS CloudFormation endpoint that \Condor{annex} should use.  Defaults to
  `https://cloudformation.us-east-1.amazonaws.com'.

\label{param:AnnexDefaultConnectivityFunctionARN}
\item[\Macro{ANNEX\_DEFAULT\_CONNECTIVITY\_FUNCTION\_ARN}]
  Never change this.  The name (or ARN) of the Lambda function on AWS which
  \Condor{annex} should use to check if the configured collector can be
  contacted from AWS.

\label{param:AnnexDefaultAccessKeyFile}
\item[\Macro{ANNEX\_DEFAULT\_ACCESS\_KEY\_FILE}]
  The full path to the AWS access key file \Condor{annex} should use.
   No default.

\label{param:AnnexDefaultSecretKeyFile}
\item[\Macro{ANNEX\_DEFAULT\_SECRET\_KEY\_FILE}]
  The full path ot the AWS secret key file \Condor{annex} should use.
  No default.

\label{param:AnnexDefaultODIInstanceProfileARN}
\item[\Macro{ANNEX\_DEFAULT\_ODI\_INSTANCE\_PROFILE\_ARN}]
  Never change this.  The ARN of the instance profile \Condor{annex} should use.
  No default.

\label{param:AnnexDefaultODIKeyName}
\item[\Macro{ANNEX\_DEFAULT\_ODI\_KEY\_NAME}]
  The name of the SSH key pair \Condor{annex} should use by default.
  No default.

\label{param:AnnexDefaultS3Bucket}
\item[\Macro{ANNEX\_DEFAULT\_S3\_BUCKET}]
  A private S3 bucket that the \MacroNI{ANNEX\_DEFAULT\_ACCESS\_KEY\_FILE}
  and \MacroNI{ANNEX\_DEFAULT\_SECRET\_KEY\_FILE} may write to.  No default.

\label{param:AnnexDefaultODISecurityGroupIDs}
\item[\Macro{ANNEX\_DEFAULT\_ODI\_SECURITY\_GROUP\_IDS}]
  The default security group for on-demand annexes.  Must permit inbound
  HTCondor (port 9618).

\label{param:AnnexDefaultODILeaseFunctionARN}
\item[\Macro{ANNEX\_DEFAULT\_ODI\_LEASE\_FUNCTION\_ARN}]
  Never change this.  The Lambda function which implements the lease
  (duration) for on-demand instances.  No default.

\label{param:AnnexDefaultSFRLeaseFunctionARN}
\item[\Macro{ANNEX\_DEFAULT\_SFR\_LEASE\_FUNCTION\_ARN}]
  Never change this.  The Lambda function which implements the lease
  (duration) for Spot instances.  No default.

\label{param:AnnexDefaultODIInstanceTypes}
\item[\Macro{ANNEX\_DEFAULT\_ODI\_INSTANCE\_TYPE}]
  The AWS instance type to use for on-demand instances if not specified.
  No default, but the \Condor{annex} setup tool sets this to `m4.large'.

\label{param:AnnexDefaultODIImageID}
\item[\Macro{ANNEX\_DEFAULT\_ODI\_IMAGE\_ID}]
  The AWS AMI to use for on-demand instance if not specified.
  No default, but the \Condor{annex} setup tool sets this to `ami-35b13223'.

\label{param:AnnexDefaultSFRConfigFile}
\item[\Macro{ANNEX\_DEFAULT\_SFR\_CONFIG\_FILE}]
  The JSON config file use by \Condor{annex} when creating a Spot-based
  annex.  No default.

\end{description}
