%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!
%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!
%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!
%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!
%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:History-8-0}Stable Release Series 8.0}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This is a stable release series of HTCondor.
As usual, only bug fixes (and potentially, ports to new platforms)
will be provided in future 8.0.x releases.
New features will be added in the 8.1.x development series.

The details of each version are described below.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-0-6}Version 8.0.6}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.0.6 not yet released.
%\item HTCondor version 8.0.6 released on Month Date, 2013.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item None.

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug with concurrency limits and partitionable slots,
in which the partitionable slot would consume a concurrency token,
even though the slot never runs jobs.  This would cause fewer jobs
than desired to run.
\Ticket{4145}

\item Fixed a bug in which the Job Exit work fetch hook was prematurely killed.
\Ticket{3669}

\item When the Windows installer was told to use VMware,
it configured a requirement for a 
\File{condor\_vmware\_local\_settings} file that it did not provide.
This caused the \Condor{vm-gahp} to fail to start,
unless the user created this file.
This configuration has been removed, so that the file is no longer required. 
\Ticket{4109}

\item Fixed a crash of the \Condor{shadow}, triggered when a disconnect
from the \Condor{starter} occurs just as the job terminates.
\Ticket{4127}

\item Modified the output of \Condor{q},
such that when invoked with options \Opt{-userlog} and \Opt{-af},
a blank line and a totals summary line are not displayed.
\Ticket{4045}

\item For hierarchical group quotas, 
fixed an incorrect count of the number of jobs when applying a quota.
\Ticket{4117}

\item Fixed the HTCondor module \Procedure{send\_command} python binding;
an incorrect argument was only the first character of the daemon's name,
instead of the full name. 
This affected the ability to turn off specific daemons,
as sent to the \Condor{master}.
\Ticket{4160}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-0-5}Version 8.0.5}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.0.5 released on December 12, 2013.

\item Helper script \Condor{ckpt\_probe} has been missing
from HTCondor releases since version 7.8.1, and it is once again 
in this release.
As a result, the machine ClassAd attribute \Attr{CheckpointPlatform}
will change for standard universe jobs upon upgrade to HTCondor version 8.0.5.
This will prevent standard universe jobs started before the upgrade
from continuing, because the attribute change eliminates a match 
with upgraded machines. 
To work around this issue,
change the \Attr{LastCheckpointPlatform} attribute to be current,
such that all jobs that have produced a checkpoint will qualify to 
continue on the upgraded machines.
Make the change by using \Condor{qedit}. 
For example, use
\footnotesize
\begin{verbatim}
condor_qedit -constraint 'LastCheckpointPlatform == "LINUX INTEL 2.6.x normal N/A"'
    LastCheckpointPlatform "LINUX INTEL 2.6.x normal N/A ssse3 sse4_1 sse4_2"
\end{verbatim}
\normalsize
where \Attr{CheckpointPlatform} after upgrade shows as
\Expr{LINUX INTEL 2.6.x normal N/A ssse3 sse4\_1 sse4\_2}.
\Ticket{4025}

\end{itemize}


\noindent New Features:

\begin{itemize}

\item None.

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug that resulted in incorrect values for ClassAd attributes
\Attr{RemoteGroupQuota} and \Attr{SubmitterGroupQuota}.
These attributes are commonly used in an expression that defines
\Macro{PREEMPTION\_REQUIREMENTS}.
\Ticket{4093}

\item Fixed a permissions bug that prevented Java universe jobs
from running.
\Ticket{4087}

\item Fixed a bug in which job output files may not have been properly truncated
at start up on Windows platforms. 
\Ticket{4097}

\item Fixed bug with \Condor{submit} 
when invoked with the \Opt{-interactive} option and cgroups where enabled.
The shell was terminated immediately after it started.
\Ticket{4028}

\item Prevent illegal values from being written into the job queue
or accounting recovery logs, in order to minimize the chance of errors when
the \Condor{schedd} or \Condor{negotiator} are restarted. Also
have \Condor{qedit} validate attribute names and values.
\Ticket{3616}

\item The \Condor{starter} now writes to the log file
\File{StarterLog.slotX} when running work fetch jobs, mirroring the
behavior when running jobs that come from a \Condor{schedd}.
Previously, log file \File{StarterLog} was used for all work fetch
jobs.
\Ticket{3091}

\item Fixed a Python binding crash due to a segmentation fault, when evaluating an expression tree with an undefined reference.
\Ticket{3910}

\item Fixed the cURL file transfer plugin such that it now works
on Windows platforms.
\Ticket{3979}
\Ticket{4012}

\item Fixed a bug that caused cream grid universe jobs to fail, 
if the submit description file contained 
submit commands of \SubmitCmd{environment} or \SubmitCmd{cream\_attributes}.
\Ticket{4037}

\item Fixed a bug that could cause the \Condor{schedd} to crash when
starting a local universe job.
\Ticket{4088}

\item Fixed a bug that caused \File{stdout} and \File{stderr} of
nordugrid grid universe jobs to be lost when the remote 
NorduGrid ARC server was using HTCondor as its local batch scheduler.
\Ticket{4017}

\item \Condor{status} with the \Opt{-t} option now consistently 
specifies the \Opt{-total} option. 
The \Opt{-target} option will now be distinguished, as it requires
at least \Opt{-targ} in its specification.
\Ticket{4096}

\item Restored the omitted HTCondor Perl module.
\Ticket{4098}

\item For RPM installations, the post-install script now
checks to make sure that the
SELinux \Code{unconfined\_execmem\_exec\_t type} exists before trying to
add it to the \File{/usr/sbin/condor\_startd} file context.
\Ticket{4034}

\item Fixed a bug in which both daemons and tools may have crashed due to
the inability to resolve a host name defined by 
configuration variable \Macro{COLLECTOR\_HOST} to an IP address.
\Ticket{3946}

\item Changed the algorithm for calculating the value of attribute
\Attr{RecentDaemonCoreDutyCycle} such
that the published value will never be negative.
\Ticket{4052}

\item For VMware vm universe jobs,
the \Condor{vm-gahp} removed from the vm description file any cdrom, 
floppy drive, serial or parallel devices.
Now, only devices that do not refer to image files are removed,
as the devices may be useful to the virtual machine.
\Ticket{4002}

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-0-4}Version 8.0.4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.0.4 released on October 24, 2013.

\item A clipped version of HTCondor is now provided for Ubuntu 12.04 
on the x86\_64 architecture.
\Ticket{3972}

\end{itemize}


\noindent New Features:

\begin{itemize}

\item None.

\end{itemize}

\noindent Configuration Variable and ClassAd Attribute Additions and Changes:

\begin{itemize}

\item The new configuration variable \Macro{DYNAMIC\_RUN\_ACCOUNT\_LOCAL\_GROUP}
permits an administrator of a Windows machine to specify a local group other 
than the default \Expr{Users} for the \Expr{condor-reuse-slot<X>} run account.
\Ticket{3998}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Added a retry to work around problems with slow
DHCP servers.  The result of the problem was that daemons
would not be able to determine their own host names,
and, among other problems, machine ClassAds would appear
in the output of \Condor{status} with blank host names.
\Ticket{3956}

\item A spurious warning in the log of the \Condor{startd} 
about undefined \MacroNI{PREEMPT\_VANILLA} expressions
is no longer generated.
\Ticket{3984}

\item EC2 grid universe jobs may provide data in files.
File contents of null-terminated strings worked correctly,
but binary data did not.
This bug fix makes sure that both kinds of data are read correctly.
\Ticket{3924}

\item EC2 grid universe jobs on OpenNebula work better for user data
specified with \SubmitCmd{ec2\_user\_data},
where the size of the data is larger than 2Kbytes.
\Ticket{3923}

\item Fixed a bug preventing HTTP file transfers from following redirects.
HTTP file transfers also now fail if the file does not exist,
but the server does exist.
\Ticket{3904}

\item Fixed a rare bug in which the \Condor{schedd} would exit
with an ERROR message pertaining to \Procedure{select},
when running with a very heavy load and many \Condor{shadow} daemons
time out.
\Ticket{3947}

\item Fixed a bug in \Condor{ssh\_to\_job}
that caused it to kill the job when the ssh session exited,
if cgroups were enabled.
\Ticket{3921}

\item If a standard universe job exited without producing any checkpoints 
and no checkpoint server was used, 
two spurious error messages would be logged to the \File{SchedLog}, 
as it tried to remove the old checkpoint images from the 
non-existent checkpoint server. 
These error messages are no longer logged.
\Ticket{3919}

\item The configuration file for Windows erroneously had two entries
for configuration variable \Macro{JAVA\_CLASSPATH\_SEPARATOR},
with the second entry specifying the
separator used on Unix platforms, which overrode the first entry. 
The Unix separator no longer affects this configuration file
for Windows platforms.
\Ticket{3957}

\item The NorduGrid GAHP no longer consumes all of the CPU when run
with threaded Globus libraries.
\Ticket{3958}

\item Fixed a bug that could cause ClassAd function \Procedure{quantize} to not
evaluate properly when its second argument was a list and ClassAd caching
was enabled.
\Ticket{3967}

\item Fixed a bug that caused the configuration variable setting 
\Expr{STARTD\_CRON\_AUTOPUBLISH = If\_Changed} to not work correctly.  
Updates were incorrectly sent to the \Condor{collector}
in many cases when no attribute value had changed.
\Ticket{3983}

\item Fixed a bug that could cause \Condor{q} \Opt{-analyze} or 
\Opt{-better-analyze}
to sometimes crash on an Illegal Instruction, 
when the \Attr{Requirements} expression contained a function.
\Ticket{3985}

\item The configuration variables \Macro{UPDATE\_COLLECTOR\_WITH\_TCP}
and \Macro{TCP\_UPDATE\_COLLECTORS} are now respected when forwarding
ClassAds to an HTCondorView server and setting \Macro{CONDOR\_VIEW\_HOST}.
\Ticket{3986}

\item \Condor{who} now prints an error message when passed an invalid argument.
\Ticket{3987}

\item Changed the script that finds the VMware tools to use the standard
environment variables to find \File{Program Files}, instead of using a
hard coded path.
This fixes installation for both 64-bit and non-English language Windows 
platforms.
\Ticket{272}

\end{itemize}

\noindent Known Bugs:

\begin{itemize}

\item None.

\end{itemize}

\noindent Additions and Changes to the Manual:

\begin{itemize}

\item None.

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-0-3}Version 8.0.3}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.0.3 released on September 23, 2013.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item None.

\end{itemize}

\noindent Configuration Variable and ClassAd Attribute Additions and Changes:

\begin{itemize}

\item None.

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item When expressions for \Macro{SUSPEND},
\Macro{CONTINUE}, \Macro{PREEMPT}, and \Macro{KILL}
were evaluated by the \Condor{startd},
a resulting value of
\Expr{UNDEFINED} or \Expr{ERROR} caused an exception in the \Condor{startd}.
These values are now treated as \Expr{False},
eliminating the exception.
This fix addresses CVE-2013-4255.
\Ticket{3869}

\item Fixed a bug that prevented the use of simple host names to identify
machines when using the command-line tools. Before the fix,
\Expr{condor\_status bar.foo.org} would show machine ClassAds, but
\Expr{condor\_status bar} would not.
Both now show machine ClassAds.
\Ticket{3694}

\item Fixed a bug with \Condor{ssh\_to\_job} that occurs when
\Macro{USE\_PID\_NAMESPACES} is enabled.
The bug presented itself as \Condor{ssh\_to\_job}
running in a private pid namespace, 
and the user running \Condor{ssh\_to\_job} not being able to see 
their job with \Prog{ps} or \Prog{gdb}.
As a fix, \Condor{ssh\_to\_job} now runs in the global namespace, 
so that it can see the processes in the user's job.
\Ticket{3872}

\item Fixed a performance problem with the \Condor{qedit} command 
that would cause the \Condor{schedd} to run very slowly when 
\Condor{qedit} is run on a large number of jobs.  
\Condor{qedit} no longer writes an event to the job event log. 
\Ticket{3827}

\item Fixed a problem where the \Code{classad} python module would return
incorrect results when ClassAd caching is enabled.
\Ticket{3879}

\item DAGMan's updating of its job ClassAd with DAG status attributes no
longer causes extra events to be written to the job event log and event log.
\Ticket{3863}

\item Fixed a bug that caused the command
\begin{verbatim}
  condor_submit -
\end{verbatim}
to be interpreted as an interactive submit,
rather than a request to read input from \File{stdin}.
\Condor{qsub} was also modified to be immune to this bug,
such that it will still work with other versions of HTCondor containing
the bug.
\Ticket{3902}

\item Value 032 of the job ClassAd attribute \Attr{HoldReasonCode}
was being used for two different reasons.
Now, value 032 identifies that the maximum total input file 
transfer size was exceeded. 
Value 034 identifies that memory usage exceeds a memory limit.
\Ticket{3858}

\item The values of the job ClassAd attributes \Attr{RemoteSysCpu} 
and \Attr{RemoteUserCpu} are sometimes impossibly large.
This bug rarely occurs and is not well understood.
Code changes attempt to fix this problem.
\Ticket{3814}

\item Fixed a bug that caused DAG recovery mode to fail on
Pegasus-generated sub-DAGs.  (Recovery mode is invoked, for example,
when a \Condor{dagman} is held and released, or when a schedd is
restarted, as happens on a version upgrade.)
\Ticket{3882}

\end{itemize}

\noindent Known Bugs:

\begin{itemize}

\item None.

\end{itemize}

\noindent Additions and Changes to the Manual:

\begin{itemize}

\item None.

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-0-2}Version 8.0.2}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

%\item HTCondor version 8.0.2 not yet released.
\item HTCondor version 8.0.2 released on August 22, 2013.

\item Debian 5 is past its end of life. 
Starting with this release, we no longer provide native packages or
tarballs for Debian 5.
\Ticket{3852}

\end{itemize}


\noindent New Features:

\begin{itemize}

\item None.

\end{itemize}

\noindent Configuration Variable and ClassAd Attribute Additions and Changes:

\begin{itemize}

\item The default value of \Macro{ENABLE\_DEPRECATION\_WARNINGS} 
has been changed to \Expr{False}.
\Ticket{3848}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Implemented a workaround to avoid triggering a Linux kernel defect 
when using cgroups and suspending jobs.
\Ticket{3847}

\item Fixed a python bindings problem of missing converters by providing
\Code{pyclassad} as a shared library.
\Ticket{3780}

\item Fixed a file permission bug introduced in HTCondor version 7.9.2 that
prevented vm universe jobs from working when using the Xen or KVM
hypervisor.
\Ticket{3781}

\item Fixed a bug that could cause the \Condor{collector} to 
become unresponsive if the remote HTCondorView server, 
specified with configuration variable \Macro{CONDOR\_VIEW\_HOST},
becomes unavailable.
\Ticket{3758}

\item Code to publish Linux distribution attributes in the machine ClassAd
is now more robust in the event that the \File{/etc/issue} file was edited.
\Ticket{3854}

\item Fixed a bug that could cause jobs to be incorrectly placed on hold upon
	completion with a hold reason claiming an out-of-memory event.
\Ticket{3824}

\item Fixed a bug that prevented work fetch scripts from running
on systems where cgroup based tracking and management was enabled.
\Ticket{3819}

\item Fixed a bug that could cause the \Condor{negotiator} to give out the same
slot twice, and result in a scary entry in the \File{NegotiatorLog} file 
with the wording:
\begin{verbatim}
  INSANE: bestCached != bestSoFar
\end{verbatim}
\Ticket{2245}

\item Fixed a bug introduced in HTCondor version 7.9.3,
in which concurrency limits were not respected across negotiation cycles when
\Macro{NEGOTIATOR\_CONSIDER\_PREEMPTION} was \Expr{False}.
\Ticket{3815}

\item Fixed a bug from HTCondor version 7.9.6. 
The bug exhibited itself when using CCB to connect to the \Condor{startd};
the \Condor{negotiator} and \Condor{schedd} would sometimes crash and then be restarted
with the following error message in the log:

\begin{verbatim}
ERROR "Selector::add_fd(): fd -1 outside valid range 0-1023"
\end{verbatim}

A workaround for the problem is relevant to HTCondor versions 7.9.6 through
8.0.1. Configure
\begin{verbatim}
  SERVICE_COMMAND_SOCKET_MAX_SOCKET_INDEX = -1
\end{verbatim}
\Ticket{3801}

\item Fixed a bug in the \Condor{qsub} script that caused it to exit
with a syntax error when a job with a memory requirement was
submitted.
\Ticket{3808}

\item Fix a bug causing security groups for EC2 jobs to be ignored.  
Also, the code respects the use of commas, as documented, 
to separate the items in the list of security groups specified by
the submit description file command \SubmitCmd{ec2\_security\_groups}. 
\Ticket{3787}

\item When invoking \Prog{glexec}, environment variable
\Env{GLEXEC\_TARGET\_PROXY} is now set to \File{/dev/null}.  
In some situations, it was previously set
to a nonexistent path, which caused errors in some configurations.
\Ticket{3794}

\item HTCondor daemons are now less vulnerable to long connection delays
when attempting to connect to hosts that are off-line.  A specific case
where this helps is when \Condor{schedd} is using a high availability
configuration, and the primary machine running the \Condor{collector} 
is off-line.
\Ticket{3828}

\item Fixed a bug that could cause \Condor{dagman} to hang 
due to a rarely seen event ordering.
This bug could have been triggered when using the
configuration variable \Macro{DAGMAN\_MAX\_JOBS\_IDLE},
or its equivalent command line option \Opt{-maxidle}.
\Ticket{3834}

\item Fixed a bug that caused job submission from Windows platforms
using \Condor{submit} with the \Opt{-spool} option to always fail.
\Ticket{3791}

\end{itemize}

\noindent Known Bugs:

\begin{itemize}

\item DAGMan recovery mode does not work for Pegasus-generated SUBDAGs.
For SUBDAGs, doing \Condor{hold} or \Condor{release} on
the \Condor{dagman} job, or stopping and re-starting the 
\Condor{schedd} with the DAGMan
job in the queue will result in failure of the DAG.  This can be
avoided by doing a \Condor{rm} of the DAGMan job, which produces a Rescue
DAG, and re-submitting the DAG; the Rescue DAG is automatically run.
This bug was introduced in HTCondor version 8.0.1.
\Ticket{3882}

\end{itemize}

\noindent Additions and Changes to the Manual:

\begin{itemize}

\item None.

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-0-1}Version 8.0.1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.0.1 released on July 17, 2013.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item HTCondor now provides the Debian Linux 7.0 (wheezy) platform,
including support for the standard universe.
\Ticket{3665}

\end{itemize}

\noindent Configuration Variable and ClassAd Attribute Additions and Changes:

\begin{itemize}

\item None.

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug that prevented per-slot settings of the 
\MacroNI{STARTD\_ATTRS} configuration variable from being set
correctly for partitionable slots named with a \Expr{SLOTX\_} prefix.
\Ticket{3726}

\item Fixed a bug that caused \Condor{status} \Opt{-submitters} to report twice
as many jobs running as were actually running. 
This bug appeared in HTCondor versions 7.9.6 and 8.0.0.
\Ticket{3713}

\item Fixed a bug with hierarchical group quotas in the \Condor{negotiator}
in which group hierarchies with parent groups that set 
configuration variable \Macro{GROUP\_ACCEPT\_SURPLUS} to
\Expr{False} would be assigned allocations above their quota.
\Ticket{3695}

\item Fixed a bug in which scheduler universe jobs that
have an \SubmitCmd{on\_exit\_hold}
expression that evaluates to \Expr{True} could have duplicate hold messages
in the user log.
\Ticket{3651}

\item Fixed a bug in which \Condor{dagman} would submit multiple copies of the
same job, fail, write a Rescue DAG, and leave the jobs in the queue. 
This was due to a warning from \Condor{submit} that the submit description file
was not using lines containing the string \Expr{"cluster"}. 
As a fix, \Condor{dagman} will search for the
string \Expr{" submitted to cluster "}.
This will generate fewer false alarms. 
If the submission succeeds and \Condor{dagman} gets confused, 
the jobs will be removed when \Condor{dagman} writes a Rescue DAG.
\Ticket{3658}

\item Added \Expr{libdate-manip-perl} as a dependency to the Debian packages.
It is required in order to run the \Condor{gather\_info} script.
\Ticket{3692}

\item Configuration variable \Macro{CCB\_ADDRESS} did not correctly 
support a list of CCB servers.  Only the first one in the list was used.
\Ticket{3699}

\item Fixed a bug that caused some communication layer log messages 
to end with binary characters.
\Ticket{3706}

\item Fixed a bug that can cause the \Condor{procd} to erroneously exit
on Mac OS X when many processes are created in a short period of time.
\Ticket{3725}

\item Removed a bug that caused \Condor{dagman} to have problems restarting
after an upgrade from HTCondor version 7.8.
\Ticket{3707}

\item Fixed a bug that caused the command 
\begin{verbatim}
  condor_q -dag -run
\end{verbatim}
to print garbage.
\Ticket{3578}

\item Fixed a bug that prevented jobs with an invalid \SubmitCmd{ec2\_keypair}
from being removed.
\Ticket{3485}

\item Fixed a memory leak and potential crash in the \Condor{gridmanager}
when requests to an EC2 service fail.
\Ticket{3701}

\item Fixed a bug in the \Condor{gridmanager} that can cause EC2 jobs to be
submitted a second time during recovery.
\Ticket{3705}

\item Fixed a memory leak in the \Condor{gridmanager} that was triggered when
submitting EC2 grid universe jobs.
\Ticket{3720}

\end{itemize}

\noindent Known Bugs:

\begin{itemize}

\item None.

\end{itemize}

\noindent Additions and Changes to the Manual:

\begin{itemize}

\item None.

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-0-0}Version 8.0.0}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

%\item HTCondor version 8.0.0 not yet released.
\item HTCondor version 8.0.0 released on June 6, 2013.

\end{itemize}


\noindent New Features:

\begin{itemize}

% would have been in 7.9.7, but there was no 7.9.7 release
\item The \Condor{chirp} \Opt{write} command now accepts an 
optional \Arg{numbytes} parameter following the local file name.
This allows the write to be limited to the specified number of bytes.
\Ticket{3548}

% would have been in 7.9.7, but there was no 7.9.7 release
\item The HTCondor Python bindings now build on Mac OS X.
\Ticket{3584}

\item Updated the sample \File{condor.plist} file to work better with
current versions of Mac OS X.
\Ticket{3624}

\end{itemize}

\noindent Configuration Variable and ClassAd Attribute Additions and Changes:

\begin{itemize}

\item The new configuration variable
\Macro{DEDICATED\_SCHEDULER\_WAIT\_FOR\_SPOOLER}
permits the specification of a very strict execution order for 
parallel universe jobs handed to a remote scheduler.
\Ticket{2946}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug that happened with partitionable slots, jobs that
requested more than one cpu, and a negotiator with
\Macro{NEGOTIATOR\_CONSIDER\_PREEMPTION} was false.  This would
cause the negotiator to incorrectly assume that each slot had
a slot weight of one.
\Ticket{3737}

\item The redundant configuration variable \Macro{CheckpointPlatform} has
been removed and the configuration variable \Macro{CHECKPOINT\_PLATFORM}
documented.
\Ticket{3544}

\item A standard universe job will no longer crash, and it will no longer 
cause the \Condor{shadow} to crash
if the job calls \Procedure{mmap} with an unsupported combination of flags.
\Ticket{3565}

\item Support for \Prog{VMware Workstation} and \Prog{VMware Player} 
under the \SubmitCmd{vm} universe now works properly on Windows platforms.
\Ticket{3627}

% would have been in 7.9.7, but there was no 7.9.7 release
\item For grid universe jobs intended for an EC2 grid resource,
errors which have no response body now report the HTTP code.
\Ticket{3541}

% would have been in 7.9.7, but there was no 7.9.7 release
\item \Condor{chirp} \Opt{put} would experience an assertion failure when
used on an empty file.  This bug has been fixed, and \Opt{put} can now be
used on an empty file.
\Ticket{3542}

% would have been in 7.9.7, but there was no 7.9.7 release
\item The 32-bit \Condor{starter} could fail to execute jobs when the initial
working directory of the job was on a subsystem containing 64-bit metadata,
such as inode numbers.
\Ticket{3605}

% would have been in 7.9.7, but there was no 7.9.7 release
\item \Condor{dagman} failed to react correctly if a nested DAG file
did not exist. It now reacts correctly and prints a more
helpful error message.
\Ticket{3623}

% would have been in 7.8.9, but there was no 7.8.9 release
\item Fixed a bug that caused the \Condor{master} daemon on Windows platforms
to think there were new binaries
when changing to and from daylight savings time.
The \Condor{master} daemon would then kill and restart itself,
as well as all of the daemons,
if configuration variable \Macro{MASTER\_NEW\_BINARY\_RESTART} was set
to its default value of \Expr{GRACEFUL}.
\Ticket{3572}

\item Fixed a bug that caused redundant lines to show up in the user log
at the end of the partitionable resource usage summary.
\Ticket{3621}

\item Fixed several bugs that can cause the \Condor{procd} to fail on Mac OS X
and not be restartable.
\Ticket{3617}
\Ticket{3618}
\Ticket{3620}

\item The \Condor{procd} now ignores process id 0 on Mac OS X.
\Ticket{3516}

\item Fixed memory leaks in the \Condor{shadow} and the \Condor{startd};
fixed a file descriptor leak in the standard universe \Condor{starter}.
\Ticket{3590}

\item Fixed a bug in which \Condor{dagman} would miscount the number
of held jobs when
multiple copies of hold events were written to the user log.
\Ticket{3650}

\end{itemize}

\noindent Known Bugs:

\begin{itemize}

\item The following obsolete binaries have not yet been removed from
the HTCondor tarballs:  
  \begin{itemize}
  \item \emph{classad\_functional\_tester}
  \item \emph{classad\_version}
  \item \Condor{test\_match}
  \item \Condor{userlog\_job\_counter}
  \end{itemize}
\Ticket{3670}

\item \Condor{status} \Opt{-submitters} reports twice
as many jobs running as were actually running.
\Ticket{3713}

\end{itemize}

\noindent Additions and Changes to the Manual:

\begin{itemize}

\item Fixed the \Condor{configure} man page and added a corresponding
\Condor{install} man page.
\Ticket{3619}

\item Added stub man pages for the Bosco commands.
\Ticket{3634}

\end{itemize}


