%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!
%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!
%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!
%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!
%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:History-8-5}Development Release Series 8.5}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This is the development release series of HTCondor.
The details of each version are described below.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-5-8}Version 8.5.8}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.5.8 released on December 13, 2016.

\end{itemize}

\noindent New Features:

\begin{itemize}

\item On Linux, the starter now puts all jobs in a cgroup by default.  The default
for CGROUP\_MEMORY\_LIMIT\_POLICY is now "none".  To disable cgroups, an admin
can set the BASE\_CGROUP parameter to the empty string.
\Ticket{5936}

\item Added first-class \Condor{submit} commands supporting job retries.
(See section~\ref{condor-submit-max-retries} for details.)
\Ticket{5912}

\item \Condor{qedit} now defaults to editing only jobs owned by the current user in the same way that
\Condor{q} does. It also honors the \Macro{CONDOR\_Q\_ONLY\_MY\_JOBS} configuration variable.
\Ticket{5889}

\item Added new parameter \Macro{DOCKER\_VOLUME\_DIR\_XXX\_MOUNT\_IF} which is an expression,
evaluated in the context of the machine and job ad, which if it evaluates to a string,
becomes a docker volume mount.  This allows admins to conditionally add docker volumes
for certain types of jobs.
\Ticket{5758}

\item Added initial support for Singularity containers.
\Ticket{5828}

\item The XferStatsLog file on the submit side now contains TCP statistics for both the
shadow point of view, and the starter point of view.  The starter side line is prefixed
with the words "peer stats from starter".
\Ticket{5917}

\item Configuration variables of the form \verb@SUBSYS.LOCALNAME.VARIABLE@ no longer work.
The use of the SUBSYS prefix before LOCALNAME never worked fully, and was only necessary for while
as a workaround for a bug that was fixed many years ago. \Condor{config\_val} and the \Condor{master} will
now produce warning messages when the configuration has variables that appear to of this form and
begin with a known SUBSYS name like MASTER or COLLECTOR.
\Ticket{5969}

\item The \Macro{SLOT\_WEIGHT} parameter can now be set on the central manager,
instead of all the execute nodes.  If the execute nodes set this parameter, it
will override the central manager setting.
\Ticket{5953}

\item New submit command \SubmitCmdNI{gce\_json\_file} can be used with
grid-type gce jobs to specify a file that contains JSON object members
that should be added to the instance description submitted to the GCE
service.
\Ticket{5893}

\item A number of command-line tools now support bash auto-completion.
\Ticket{5924}

\item The minimum update time for \Condor{dagman} node status files
now defaults to 60 seconds.
\Ticket{5929}

\item Added the new \MacroNI{DAGMAN\_REMOVE\_NODE\_JOBS} configuration
macro, which allows users to configure whether \Condor{dagman} itself
removes its node jobs when it is removed (note that the
node jobs are also removed by the \Condor{schedd}).
This configuration macro defaults to \Expr{True}, which represents
a change in behavior compared to previous HTCondor versions.
(See section~\ref{sec:DAGMonitoring} for more details.)
\Ticket{5175}

\item The \Arg{-AllowLogError} argument to \Condor{submit\_dag} and
\Condor{dagman}, and the DAGMAN\_ALLOW\_LOG\_ERROR configuration
macro, are no longer supported, and generate warnings if used.
\Ticket{5630}

\item \Condor{dagman} now ignores the
\MacroNI{DAGMAN\_LOG\_ON\_NFS\_IS\_ERROR} configuration setting if
\MacroNI{ENABLE\_USERLOG\_LOCKING} is set to \Expr{False}.
\Ticket{5641}

\item Added the \Arg{ALL\_NODES} option to a number of \Condor{dagman}
commands (see~\ref{sec:DAGAllNodes} for details).
\Ticket{5729}

\item Changed the previous term "metaknob" to "configuration template"
and improved the configuration template documentation.
\Ticket{5865}

\item The \Condor{schedd} receiving a refreshed X.509 proxy credential
is now done in a non-blocking fashion.
\Ticket{5930}

\item The Job Router now performs its automatic job ad transformations
when the TRANSLATE\_JOB hook is used.
These are changes that should happen to all job ads being transformed
by the Job Router.
\Ticket{5235}

\item The \verb@$F()@ configuration macro has new options to support
conversions of paths to Windows style path separators or to Unix style.
When used in \Condor{submit} files it can do path completion as well.
\Ticket{5938}

\item The \verb@$ENV()@ configuration macro now supports default values.
\Ticket{5882}

\item A certificate mapfile can now use literal values rather than regular
expressions for the second field. This is useful when only a single identity
should be matched.  The use of a literal is both more secure and faster to
search. The new configuration variable \Macro{CERTIFICATE\_MAPFILE\_ASSUME\_HASH\_KEYS}
enables this behavior, it defaults to false. It will most likely default
to true in a future version of HTCondor.
\Ticket{5992}

\item The ClassAd \Code{userMap} function now uses only commas as the separator for the
third field of the map file. This makes it possible to have values with spaces in them.
\Ticket{5988}

\item The \Condor{collector} will now allow more than one \Condor{negotiator} to be registered.
And a new A new configuration variable \Macro{COLLECTOR\_ALLOW\_ONLY\_ONE\_NEGOTIATOR}, which defaults
to false has been added so that the old behavior can still be configured.
\Ticket{5967}

\item The Requirements expression for Job transforms in the \Condor{schedd} will now ignore the TARGET
prefix for attributes in the expression. This makes it easier to convert \Condor{job\_router} rules
to job transforms because the TARGET prefix is required in the \Condor{job\_router} but refers to nothing
in the job transform.
\Ticket{5980}

\item The \Opt{-better-analyze} option of \Condor{q} has been improved and the output reorganized.
\Ticket{5290}

\item A new tool - \Condor{transform\_ads} has been added.
(See section~\ref{man-condor-transform-ads} for details.)
\Ticket{5805}

\item A join function has been added to the ClassAd language.
\Ticket{6018}

\item \Condor{who} has additional options for querying the state and readiness of the various daemons.
It has a command that can be used to wait for the daemons to startup with a timeout.
\Ticket{5416}

\item When submitting a job that has an associated X.509 proxy, or when
authenticating to the \Condor{schedd} using X.509, the X.509 and VOMS
attributes are securely extracted and carried along in the job ClassAd.  This
allows them to be used, for example, in matchmaking policy and job routing.
\Ticket{5064}

\item Made \Condor{credd} configuration easier by automatically configuring
network connections to use encryption.
\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item When the Google Compute Engine breaks the results of a query into
multiple pages, the \Prog{gce\_gahp} now retrieves all of the results,
instead of just the first page.
\Ticket{6010}

\item Fixed a bug that caused file transfer to fail when a job created
by the Job Router has a different \Attr{Owner} than the original job.
\Ticket{5348}

\item Fixed a bug that could result in "orphan" node jobs staying
in the queue when an instance of \Condor{dagman} is removed.
\Ticket{5702}

\item Fixed a regression introduced in v8.5.7 that prevents job preemption
due to priority from occurring, because 
user priority and resources in use information cannot be referenced in 
\MacroNI{PREEMPTION\_REQUIREMENTS}.
\Ticket{6014}

\item Fixed \Macro{COLLECTOR\_FORWARD\_FILTERING} so that a startd ad
update is always forwarded when any of the Claim IDs change.
\Ticket{5913}

\item Fixed a bug that made the Requirements keyword for job transforms
in the \Condor{schedd} only work if it was all uppercase on Red Hat 7 and
some other platforms that use a newer version of the C++ compiler.
\Ticket{5973}

\item Fixed a bug that allowed a user to bypass the \Macro{MAX\_RUNNING\_SCHEDULER\_JOBS\_PER\_OWNER}
limit by specifying an accounting group or nice\_user in their submit file.
\Ticket{5949}

\item Fixed a bug in \Condor{c} and the \Condor{job\_router} that could cause inaccurate
job totals to be reported by \Condor{q} \Opt{-batch}.
\Ticket{6020}


\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-5-7}Version 8.5.7}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.5.7 released on September 29, 2016.

\end{itemize}

\noindent Known Issues:

\begin{itemize}

\item Preemption due to job priority is likely to fail if \MacroNI{PREEMPTION\_REQUIREMENTS}
attempts to reference any resource usage or priority attributes. This issue has
been fixed in v8.5.8.  If you cannot upgrade to v8.5.8, a work-around for v8.5.7
is to set configuration macro \MacroNI{NEGOTIATOR\_CROSS\_SLOT\_PERI'S} to \Expr{True}.
\Ticket{6014}

\end{itemize}

\noindent New Features:

\begin{itemize}

\item Added the capability for the schedd to perform job ClassAd
transformations upon job submission (see~\ref{sec:Schedd-Config}
for details).
\Ticket{5885}

\item Added the capability for more flexible connections between
splices in DAGs (see ~\ref{sec:DAGSpliceConnections} for details).
Also added an INCLUDE command to the DAG language (see
~\ref{sec:DAG-include} for details).
\Ticket{5213}

\item Simplified the DAG node priority algorithm:  the "effective" priority
of a node is now simply the sum of the explicit node priority and the
overall DAG priority.  (See section ~\ref{sec:DAG-SetNodePriority} for
more details.)
\Ticket{4024}
\Ticket{5749}

\item Allow the second argument of the ClassAd ternary operator
(expression ? value1 : value2) to be omitted.  This new syntax means:
evaluate the expression, and if it evaluated to a defined value or
error, return it.  If undefined, return value2.
\Ticket{5782}

\item The time is now included after the SCHEDD or SUBMITTER name
in the banner of \Condor{q} output.
\Ticket{5895}

\item \Condor{status} has a new \Opt{-data} option that, when used with \Opt{-schedd}
will show data transfer information; and \Opt{-run} will show information about running
jobs when used with \Opt{-schedd}.
\Ticket{3938}

\item \Condor{q} \Opt{-batch} will now show Total and Completed counts for non-DAG jobs
when querying a scheduler that is at least version 8.5.7
\Ticket{5874}

\item \Condor{status} and \Condor{q} now support reading and writing ClassAds
in xml, json, and "new ClassAd" form as well as the traditional long form.
\Ticket{5844}
\Ticket{5820}

\item HTCondor daemons now respect \MacroNI{<LOCALNAME>.<SUBSYSTEM>\_LOG}
if passed a -local-name parameter, and default to using
\MacroNI{\$(LOG)/<Localname>Log} if the former is not set.
\Ticket{5768}

\item HTCondor now automatically passes the -local-name parameter to a
DC daemon if its entry in the \MacroNI{DAEMON\_LIST} is not in the default
\MacroNI{DC\_DAEMON\_LIST}.  This should result in simpler and less
error-prone configuration.
\Ticket{5768}

\item HTCondor now detects if an entry in \MacroNI{DAEMON\_LIST} shares a
binary with an entry in \MacroNI{DC\_DAEMON\_LIST} and marks the former as
a DC daemon if so.  This should result in simpler and less error-prone
configuration.
\Ticket{5767}

\item Increase the resolution of file transfer timing statistics in
the XferStatsLog to hundreds of a second.
\Ticket{5898}

\item The default host based security meta-knob now works in IPv6
only networks out of the box.
\Ticket{5894}

\item Old HAD configurations, with or without replication, should now work
by default (without shared port).
\Ticket{5769}

\item HTCondor no longer gives up if a bad networking configuration is
detected while running a tool.  This allows \Condor{config\_val} to be
used to debug the problem.
\Ticket{5532}

\item The \Condor{negotiator} by default no longer cross advertises the
user priority and resources in use from every slot in a machine ad to every
other slot in that machine ad.  \Macro{NEGOTIATOR\_CROSS\_SLOT\_PRIOS} = true
re-enables the old behavior.  The accounting information for the current
user of the slot remains advertised.
\Ticket{5785}

\item New submit attribute \SubmitCmd{gce\_preemptible} allows the
creation of preemptible Google Compute Engine (GCE) instances.
These instances have a lower price, but can be interrupted at any time.
Also added support for service accounts with GCE.
\Ticket{5821}

\item When submitting jobs to Slurm via the grid universe, the Slurm
partition can now be specified using the \SubmitCmdNI{batch\_queue}
submit command.
\Ticket{5780}

\item Some old STARTD policy helper configuration variables were moved
into two new configuration templates --
\Macro{FEATURE : UWCS\_DESKTOP\_POLICY\_VALUES}
and \Macro{FEATURE : TESTINGMODE\_POLICY\_VALUES}
\Ticket{5871}

\item \Condor{submit} on Windows will no longer insert the OSVERSIONINFO
fields like \Attr{WindowsMajorVersion} into each job automatically. This
is controlled by a new configuration variable \Macro{SUBMIT\_PUBLISH\_WINDOWS\_OSVERSIONINFO}
which defaults to false.
\Ticket{5873}

\item Added the option to cache the output of commands used in configuration
files, so that the command doesn't have to be re-run every time the
configuration file is referenced.  Also added error and warning keywords
to allow configuration files to report errors and warnings.
\Ticket{5781}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug in how the HAD daemon checks to see if it and its
corresponding replication daemon were configured to be on the same host.
\Ticket{5849}

\item The EC2 GAHP now handles integer overflows when checking deadlines.
This prevents spurious time-outs on 32-bit systems which have been up for
more than 28 days.
\Ticket{5824}

\item Lengthened the watchdog timeout in the systemd service file to 20 minutes.
Also, ping systemd at a third of the watchdog interval.
\Ticket{5837}

\item Fixed a bug that could cause daemons to create a file named
\File{dprintf\_failure.SUBSYS} if they failed to find the \Prog{mail}
program.
\Ticket{5854}

\item For grid-type \Expr{batch} jobs, improved handling of command
line arguments and environment variables that contain characters that
have meaning to the shell.
Previously, the presence of these characters would cause job execution
to fail.
\Ticket{5747}

\item Fixed a bug that caused \Condor{config\_val} to segfault when the \Opt{-name}
argument was used and the machine did not exist
\Ticket{5818}

\item Fixed a bug that caused \Condor{q} \Opt{-autocluster} to crash unless the \Opt{-nobatch}
option was also used.
\Ticket{5839}

\item Fixed a bug in the Python bindings where a thread executed python
byte code without holding the global interpreter lock.
\Ticket{5864}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-5-6}Version 8.5.6}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.5.6 released on August 2, 2016.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item The default output of \Condor{q} is now the \Opt{-batch} output.
To change the default back to its pre-8.5.6 value, set the new
configuration variable \MacroNI{CONDOR\_Q\_DASH\_BATCH\_IS\_DEFAULT} to
\Expr{False}.
\Ticket{5708}

\item A new class -- the Submit class -- was added to the Python
bindings. It allows for the submission of HTCondor jobs via the
Python bindings using the same keywords and automatic behavior as
\Condor{submit}.
See section~\ref{Python-OtherModule} for details.
\Ticket{5666}

\item The ability to send \Condor{drain} commands is now exposed
through the Python bindings.
See section~\ref{Python-OtherModule} for details.
\Ticket{5507}

\item The value of the configuration parameter 
\Macro{DOCKER\_DROP\_ALL\_CAPABILITIES} is now no longer just
true or false, but a ClassAd expression evaluated in the context
of the machine (my) and the job (target).
\Ticket{5759}

\item When running Docker Universe containers on docker version 1.11
and newer, HTCondor now also sets --no-new-privs, to prevent
setuid and setgid programs from running in containers, unless
\Macro{DOCKER\_DROP\_ALL\_CAPABILITIES} evaluated to false.
\Ticket{5680}

\item The hostname of the container that Docker Universe jobs
run in is now set to a more useful name.  Instead of a hash, it
now contains the job's owner, the cluster and proc of the job,
and the hostname of the machine the container runs on.
\Ticket{5760}

\item New options have been added to \Condor{history}, so that \Condor{history} can be used as the
the \Macro{HISTORY\_HELPER} for remote \Condor{history}. The options are:
  \begin{itemize}
  \item \Opt{-since} Scanning of the history file stops when an expression becomes true or a job id is read.
  \item \Opt{-completedsince} Scanning of the history file stops when a job completed earlier than this time is read.
  \item \Opt{-scanlimit} Used by remote \Condor{history} to limit the number of jobs read from the history file.
  \item \Opt{-attributes} Used by remote \Condor{history} to limit the attributes transferred back.
  \item \Opt{-inherit} Used by remote \Condor{history} to define the socket to write results to.
  \item \Opt{-stream-results} Used by remote \Condor{history} so that results can be printed as they arrive.
  \end{itemize}
\Ticket{5642}

\item Condor{history} will default to doing a remote query if there is a \Macro{SCHEDD\_HOST} configured. This behavior
can be defeated by passing the new \Opt{-local} argument.
\Ticket{5765}

\item The high-availability and replication daemons may now use shared port.
\Ticket{5726}

\item ClassAds can now be represented in JSON format.
\condor{q}, \condor{status}, and \condor{history} have a \Arg{-json}
command line option, which causes their output to be printed in JSON.
\Ticket{5688}

\item \Condor{dagman} now allows commands to be more flexibly ordered
within a DAG file.  (See section~\ref{dagman:command order} for details.)
\Ticket{5732}

\item Any \SubmitCmd{accounting\_group} and
\SubmitCmd{accounting\_group\_user} values specified for a
DAG are now propagated to all jobs of the workflow, including sub-DAGs.
\Ticket{5077}

\item A new configuration variable \Macro{MAX\_RUNNING\_SCHEDULER\_JOBS\_PER\_OWNER}
can be used to limit the number of DAGs that any single user can have running at
a time.
\Ticket{5568}

\item Monitoring the status of PBS and Slurm jobs is now much more efficient.
Now, one query to the batch system is done for all jobs, instead of a
separate query for each job.
\Ticket{5722}

\item Simplified how job leases are handled for grid universe jobs.
Now, all jobs going to the same remote resource share a single lease
time.
\Ticket{5625}

\item Added several statistics about commands issued to the GAHP server
to the grid ads that the \Condor{gridmanager} sends to the \Condor{collector}:
  \begin{itemize}
  \item GahpCommandsIssued
  \item GahpCommandsTimedOut
  \item GahpCommandsInFlight
  \item GahpCommandsQueued
  \item GahpCommandRuntime
  \end{itemize}
\Ticket{5698}

\item The \Condor{shadow}, \Condor{starter} and \Condor{c-gahp} daemons
now log TCP statistics for file transfers.  See ~\ref{dflag:stats} for
more details.
\Ticket{5663}

\item Job ads now include \Attr{NumJobCompletions}, which counts the
number of times a job exited of its own accord (successfully or not) and
then successfully completed file transfer (if any was requested).
\Ticket{5705}

\item Kerberos authentication is now non-blocking, allowing an HTCondor
daemon authenticating clients with Kerberos to handle more simultaneous
incoming connections.
\Ticket{5737}

\item Password authentication is now non-blocking, allowing an HTCondor
daemon authenticating clients with the PASSWORD method to handle more
simultaneous incoming connections.
\Ticket{5602}

\item The full path to the submit file is now available as an automatic
submit variable.
\Ticket{5677}

\item A new function \Code{userMap()} has been added to the ClassAd language
to facilitate the mapping of users to groups in the \Condor{schedd} and
\Condor{job\_router} (see ~\ref{sec:classadFunctions} for details).
\Ticket{5751}

\item Configuration files now support the declaration of multi-line values, the is primarily of use when
configuring the \Condor{job\_router}.
\Ticket{5721}

\item Configuration templates can now take arguments.
\Ticket{5739}

\item Improved the performance of the \Condor{negotiator} when running
with a large number of users or groups.  The accounting data is only
written to disk when it changes, not unconditionally.
\Ticket{5719}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug in Docker universe that required the name
of a transferred executable to begin with "./"
\Ticket{5761}

\item Fixed a bug the prevented Docker universe jobs from reporting
their network usage correctly.
\Ticket{5750}

\item \Condor{who} now reports docker universe jobs more completely.
\Ticket{5740}

\item Fixed bugs preventing HTCondor daemons from recognizing an address in
Sinful format as its own when operating in mixed (IPv4 and IPv6) mode.  One
manifestation of this would be errors from the HAD daemon when specifying
hosts by name in the \MacroNI{HAD\_LIST} or \MacroNI{REPLICATION\_LIST}.
\Ticket{5728}
\Ticket{5776}

\item \Condor{user\_prio} now more correctly shows information
about submitters flocking to a pool, but who haven't used 
any resources.
\Ticket{5743}

\item No longer leak a file in the user's home directory each time a
job is submitted to Slurm.
\Ticket{5742}

\item Fix a bug that prevented HTCondor from removing jobs from Slurm.
\Ticket{5804}

\item Fixed a bug when attempting to authenticate using multiple
methods wherein if a method failed, the remaining methods were not
always attempted.
\Ticket{5673}

\item Fixed a bug that prevented the \condor{schedd} from reading the
job's X.509 proxy file when writing information to the
\MacroNI{SCHEDD\_AUDIT\_LOG}.
\Ticket{5770}

\item Fixed a bug in \Condor{q} where the SIZE column would not grow as needed to fit the data.
\Ticket{5667}

\item Fixed a bug where the \Condor{schedd} did not treat a user as a queue superuser when it
should have if the configuration included a map file, which is common for GSI authentication.
\Ticket{5530}

\item Lengthen the watchdog timeout in the systemd service file to 1 minute.
The previous value of 5 seconds has taken down HTCondor for a single slow DNS
query.
\Ticket{5819}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-5-5}Version 8.5.5}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.5.5 released on June 6, 2016.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item The EC2 GAHP now rate-limits its requests, and responds to overload
warnings with an exponential back-off.  Additionally, fewer operations are
now performed on a per-job basis (as few as one in some cases).  The
resulting scalability improvements have been demonstrated to permit a single
GAHP to manage ten thousand instances.  Because the overload condition is
account- and region- specific, the grid manager now launches a GAHP for
each account-region pair.  We therefore recommend adding \Expr{D\_PID} to
\MacroNI{EC2\_GAHP\_DEBUG}, for disambiguation, and this is now the default.
\Ticket{5561}
\Ticket{5588}
\Ticket{5620}

\item The grid manager now assigns \Attr{HoldReasonCode}s and
\Attr{HoldReasonSubCode}s to EC2 jobs when they go on hold.  Values are
subject to change until the stable release.
\Ticket{5628}

\item The grid manager now advertises some metrics from the EC2 GAHP.
\Ticket{5580}

\item Some Linux distributions for supercomputer compute nodes and
others distributions for docker images have no /var/run/utmp. HTCondor no longer
aborts when this file is missing, when it tries to determine keyboard
idle times, it just assumes these kinds of machines have no keyboards.
\Ticket{5624}

\item Docker Universe jobs now correctly advertise \Macro{RemoteUserCpu}
and \Macro{RemoteSysCpu} in their job ad and in the job log file.
\Ticket{5609}

\item A batch name specified for a DAG (with the \Condor{submit\_dag}
\Opt{-batch-name} option) is now propagated to all jobs of that DAG,
including sub-DAGs.
\Ticket{5493}

\item The batch name for a \Condor{dagman} job (if not set) now
defaults to \Arg{DagFile}+\Arg{cluster} (where \Arg{DagFile}
is the primary DAG file of the \Condor{dagman} job, and \Arg{cluster}
is the HTCondor cluster of the \Condor{dagman} job).
Because the batch name is now propagated throughout a workflow, if
no batch name is specified, the batch name for all jobs in the
workflow will be \Arg{DagFile}+\Arg{cluster} of the top-level
\Condor{dagman} job.
\Ticket{5605}

\item The files named in the submit file attributes \SubmitCmdNI{vm\_disk},
\SubmitCmdNI{xen\_kernel}, and \SubmitCmdNI{xen\_initrd} now refer to
locations on the execute machine.
\Condor{submit} no longer modifies these values or checks for their
existence on the submit machine.
If these files need to be transferred by HTCondor, then they should be
listed in \SubmitCmdNI{transfer\_input\_files} and their presence in
these vm universe attributes shouldn't include any path information.
\Ticket{4167}

\item In the python bindings, an \texttt{ExprTree} can be cast to an integer
or floating point value.
\Ticket{5636}

\item HTCondor now supports the following systemd features: Socket Activation,
Watchdog, Status message, and journald logging. In these release, the
Socket Activation is not configured, because the security system is not
prepared to properly handle the socket passed in from outside HTCondor.
\Ticket{4144}

\item Added config knob \MacroNI{DEFAULT\_MASTER\_SHUTDOWN\_SCRIPT} to
specify a default program to exec as root upon \Condor{master} exit.
See Section~\ref{param:DefaultMasterShutdownScript} for details.
\Ticket{5590}

\item The python bindings now support a per-thread security context,
allowing the modification of various parameters such as the pool password
and the X509UserProxy location.
\Ticket{5632}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug that caused file transfers to fail when using Bosco.
\Ticket{5704}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-5-4}Version 8.5.4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.5.4 released on May 2, 2016.

\item The \SubmitCmdNI{deltacloud} type in the grid universe, which allowed
submission to Deltacloud services, has been removed.
\Ticket{5569}

\end{itemize}


\noindent New Features:

\begin{itemize}

\item \Condor{status} can now display the utilization of a \Condor{startd} with
a single line of output for each machine rather than a line per slot.
In this release this output is enabled by passing \Opt{-compact} to \Condor{status}
but in a future release this will be the default output of \Condor{status}.
\Ticket{5596}

\item Improved the performance of the \Condor{collector} by
not computing dropped update statistics, statistics which 
have never been accessible by users.
\Ticket{5566}

\item The performance of the \Condor{history} tool has been
significantly improved.
\Ticket{5536}

\item \Condor{user\_prio} now queries the \Condor{collector} for 
accounting information by default, when appropriate.  This should be
much faster than the older way of querying the \Condor{negotiator}. The
old path is still available by passing the -negotiator option to the
tool.
\Ticket{5508}.

\item The default value of \MacroNI{DAGMAN\_ALWAYS\_RUN\_POST} has been
changed from \Expr{True} to \Expr{False}.  This means that, by
default, if the PRE script of a DAG node fails, the POST script
of the node will \emph{not} be run.  (This had been the default
behavior until version 7.7.2.  The 7.7.2-8.5.3 behavior can be
restored by setting \MacroNI{DAGMAN\_ALWAYS\_RUN\_POST} to 
\Expr{True}, or by passing the new \Opt{-AlwaysRunPost}
argument to \Condor{submit\_dag}.)
\Ticket{5477}

\item The \Prog{batch\_gahp} can now submit multi-core jobs to HTCondor.
\Ticket{5638}

\item The \Prog{batch\_gahp}'s ability to generate a limited X.509 proxy
for use by the job on the execute machine can now be disabled, which is now
the default.
\Ticket{5601}

\item The \Condor{schedd} will now send submitter ad updates for idle submitters
less frequently than updates for submitters that have jobs in the queue. There
are two new configuration variables to control this behavior.
\MacroNI{ABSENT\_SUBMITTER\_LIFETIME} is the number of seconds after the last
job for that submitter leaves the queue that the submitter will continue to
send updates to the \Condor{collector}.  It defaults to 1 week.
\MacroNI{ABSENT\_SUBMITTER\_UPDATE\_RATE} is the maximum rate in seconds at which
the \Condor{schedd} will send updates to the \Condor{collector} for a submitter
that has no jobs in the queue. It defaults to 5 minutes. 
\Ticket{5559}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug that caused the \Condor{schedd} to exit when receiving
an updated X.509 proxy for a job.
\Ticket{5645}

\item In expressions in the Job Router's configuration, attributes no
longer require a 'TARGET.' scope prefix.
\Ticket{5550}

\item Fixed a bug in \Condor{q} \Opt{-xml} that would put the XML header
after the body unless \Opt{-stream} was passed.
\Ticket{5597}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-5-3}Version 8.5.3}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.5.3 released on March 24, 2016.

\end{itemize}

\noindent New Features:

\begin{itemize}

\item \MacroNI{ENABLE\_IPV4} and \MacroNI{ENABLE\_IPV6} both now accept
the special value "AUTO", which is true if an interface with the corresponding
protocol exists on the host, and false otherwise.
\Ticket{5524}

\item \MacroNI{ENABLE\_IPV4} and \MacroNI{ENABLE\_IPV6} both now default
to the special value "AUTO".  Additionally, the new configuration macro
\MacroNI{PREFER\_IPV4} is true by default.  This macro causes HTCondor to
prefer IPv4 over IPv6 when choosing an address to advertise, when choosing
the address of daemon looked up in the collector, and when resolving DNS
queries.
\Ticket{5104}

\item New configuration macros added: \MacroNI{IPV4\_ADDRESS},
\Macro{IPV6\_ADDRESS}, \MacroNI{IP\_ADDRESS\_IS\_V6}.
\Ticket{5512}

\item New attributes have been added to the Submitter ClassAd to indicate
the number of Idle and Running jobs for Scheduler universe and for Local
universe.
\Ticket{5519}

\item Jobs can now be submitted to the Slurm batch scheduling system via
the new \SubmitCmdNI{slurm} type in the grid universe.
\Ticket{5515}

\item In addition to logging to the file \MacroNI{KERNEL\_TUNING\_LOG},
the default \MacroNI{LINUX\_KERNEL\_TUNING\_SCRIPT} now also logs to
syslog and \File{/etc/systcl.d/99-htcondor.conf}.
\Ticket{5489}

\item \Condor{history} \Opt{-autoformat} now supports the j option to print
job ids like \Condor{q} does.
\Ticket{5558}

\item HTCondor is now built and linked with Globus 6.0.
\Ticket{5520}

\item Pre-size the ClassAd hash table to improve the performance of the
\Condor{collector} when getting ClassAd updates.
\Ticket{5551}

\item The negotiator now forwards accounting information to the collector,
where it can be easily queried and monitored.
\Ticket{5491}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug on \Condor{history} that could result in truncation of
the job id field.
\Ticket{5527}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-5-2}Version 8.5.2}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.5.2 released on February 18, 2015.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item \Bold{\Condor{q} now defaults to showing only the current user's
jobs, unless the current user is a queue superuser.} This behavior
can be turned off by setting the new configuration option \Macro{CONDOR\_Q\_ONLY\_MY\_JOBS}
to \Expr{False} in the configuration for either the \Condor{schedd} or \Condor{q}. It can also be 
turned off by passing the new \Opt{-allusers} command line option to \Condor{q}.
\Ticket{5271}

\item Added support for immutable job attributes and protected job attributes.
\Ticket{5065}

\item Improved the speed of \Condor{q} and other tools when
querying non-local servers.
\Ticket{5150}

\item The new \Opt{-batch} command line option to \Condor{q} can be used to show a single
line of progress information for a batch of jobs, where a batch is either an entire workflow (a DAG, including sub-DAGs), all
of the jobs in a cluster, all of the jobs from a single user that have the same executable specified in their submit file,
or all of the jobs from a single user that have the same batch name.
\Ticket{4976}

\item \Condor{submit} and \Condor{submit\_dag} both have a new command line option \Opt{-batch-name}
which can be used to set the batch name used by \Condor{q} \Opt{-batch}.
\Ticket{5490}

\item \Condor{q} and \Condor{status} now attempt to avoid truncating data by making use of the
full width of the terminal.
\Ticket{5429}
\Ticket{5459}

\item Docker Universe jobs now report and update
ResidentSetSize, ImageSize, MemoryUsage, NetworkInput, and 
NetworkOutput attributes in the job ad and log file.
\Ticket{5456}

\item Added the capability to set ClassAd attributes for a
\Condor{dagman} job within the DAG file by using the new
\MacroNI{SET\_JOB\_ATTR} command.  (See section~\ref{sec:DAG-SetAttributes}
for details.)
\Ticket{5107}

\item The \File{dagman.out} file produced by \Condor{dagman} now has event
timestamps added to the lines that report \Condor{dagman} reading
a log event.  For example:
\begin{verbatim}
  01/13/16 11:29:03 Event: ULOG_SUBMIT for HTCondor Node NodeA (674.0.0) {01/13/16 11:28:59}
\end{verbatim}
The timestamp in curly brackets at the end is the actual timestamp
of the event.
\Ticket{5439}

\item The \Opt{-run} and \Opt{-hold} arguments of \Condor{q} used to produce garbage output
when used with other formatting options such as \Opt{-format}.  Now they will always constrain
the query, and will also set the output format when used by themselves.
\Ticket{11}

\item The \Condor{status} \Opt{-verbose} argument has been removed;
the equivalent \Opt{-long} argument should be used instead.
% No ticket for this -- wenger 2016-02-11

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item On Windows, configuring HTCondor to restrict the range of outbound
port numbers may cause substantial delays when using the command-line
tools.  Since we now know that it's not free to do so, \MacroNI{LOWPORT}
and \MacroNI{HIGHPORT} no longer restrict the port numbers of outbound
connections on Windows.  If you still require this functionality, use
\MacroNI{OUT\_LOWPORT} and \MacroNI{OUT\_HIGHPORT}.
\Ticket{4711}

\item Fixed a bug that could cause a daemon to be in the wrong
privilege state when attempting to act as the user.
\Ticket{5467}

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-5-1}Version 8.5.1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.5.1 released on December 21, 2015.

\item Shared port is enabled by default.
\Ticket{3813}
\Ticket{5103}

\end{itemize}


\noindent New Features:

\begin{itemize}

\item The \Condor{startd} history file now contains the peak
memory usage, by an exited job, not the more recent.
\Ticket{5436}

\item When the \Condor{starter} evicts a job, perhaps because
it has exceeded a memory limit, it does not transfer back to
the submit machine the sandbox of working files.  This is
consistent with other types of holds.
\Ticket{5437}

\item The \Condor{startd} now advertises the following attributes
on Linux machines: CpuFamily CpuModelNumber CacheSize.  These are
pulled from the /proc/cpuinfo file.
\Ticket{5323}

\item \Condor{q} has a new option \Opt{-schedd-constraint} which can be used
to constrain the queues displayed when using the \Opt{-global} option.
\Ticket{5043}

\item When an HTCondor-C job is submitted to a remote \Condor{schedd},
the remote job ad now includes the attribute \AdAttr{SubmitterGlobalJobId},
whose value is the same as the attribute \AdAttr{GlobalJobId} in the
original HTCondor-C job.
\Ticket{3472}

\item The \Condor{schedd} now sets environment variables for scheduler
universe jobs so that the jobs can more easily find the \Condor{schedd}'s
contact information.
On machines where there are multiple \Condor{schedd}s running, this helps
DAGMan and similar applications contact the \Condor{schedd} that started
them.
\Ticket{5166}

\item When \MacroNI{SEC\_ENABLE\_MATCH\_PASSWORD\_AUTHENTICATION} is set
to \Expr{True}, the related authorizations are now automatically enabled.
Previously, \Expr{submit-side@matchsession} and
\Expr{execute-side@matchsession} entries had to be added to the
\MacroNI{ALLOW\_DAEMON} and \MacroNI{ALLOW\_CLIENT} (if set)
authorization parameters in order for this feature to work.
\Ticket{5304}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item 

\Condor{history} \-run on a pool with partitionable slots now shows
the correct dynamic slot.
\Ticket{4261}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-5-0}Version 8.5.0}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

%\item HTCondor version 8.5.0 not yet released.
\item HTCondor version 8.5.0 released on October 12, 2015.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item The \Condor{startd} history file contains two new attributes: BadputCausedByDraining and BadputCausedByPreemption, two boolean-valued attributes which are true if the job was evicted not by a user request.
\Ticket{5255}

\item The python bindings have a new Claim API, allowing Computing-On-Demand (COD) to be
invoked via python.
\Ticket{5130}

\item The python bindings can now submit multiple distinct processes using the \texttt{submitMany}
method, similar to a \Condor{submit} file with multiple \texttt{queue} statements.
\Ticket{4916}

\item The python bindings now provide improved support for managing multiple concurrent queries.
\Ticket{5187}

\item As an experimental feature, the python bindings implement the HTCondor negotiation protocol.
\Ticket{5125}

\item Changed \AdStr{Condor} to \AdStr{HTCondor} in \Condor{dagman}
output (mainly in the \File{dagman}.out file).
\Ticket{5144}

\item The new configuration parameter \MacroNI{JOB\_SPOOL\_PERMISSIONS}
controls the permissions on a job's spool directory managed by the
\Condor{schedd} on unix.
It defaults to the value \Expr{user}, which results in a permissions
value of \Expr{0700}.
Other valid values are \Expr{group} (permissions \Expr{0750}) and
\Expr{world} (permissions \Expr{0755}).
Previously, all job spool directories had access permissions of \Expr{0755}.
\Ticket{4896}

\item The \Condor{schedd} no longer changes the ownership of spooled job
files that it manages.
Now, the files are always owned by the submitting user.
The previous behavior of changing ownership to/from the \Expr{condor}
account can be restored by setting the new configuration parameter
\Macro{CHOWN\_JOB\_SPOOL\_FILES} to \Expr{True}.
\Ticket{5226}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item None.

\end{itemize}
