%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!
%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!
%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!
%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!
%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Stable Release Series 8.6}\label{sec:History-8-6}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This is a stable release series of HTCondor.
As usual, only bug fixes (and potentially, ports to new platforms)
will be provided in future 8.6.x releases.
New features will be added in the 8.7.x development series.

The details of each version are described below.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-6-13}Version 8.6.13}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.6.13 released on October 31, 2018.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item Python bindings are now available on Debian 9, Ubuntu 16, and
Ubuntu 18.
\Ticket{6751}

\item Grid-type cream jobs are now supported on all linux platforms.
\Ticket{6799}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug in the Python classad module that caused the Python \Expr{in}
operator to be case sensitive when used to see if a ClassAd contains a given
attribute.
\Ticket{6535}

\item Fixed a bug in the Python bindings that would leak one or more ClassAds
each time the submit or submitMany methods of the schedd class were called
without passing an explicit list to return the result ClassAds.
\Ticket{6729}

\item Fixed a problem processing the whitelist of user modules for the Python
bindings.
\Ticket{6387}

\item Fixed a bug that caused output and error files with full path names
to be transferred to the wrong directory on Windows.  This would usually
cause output file transfer to fail.
\Ticket{6747}

\item Fixed a bug that could cause grid-type \Expr{condor} jobs under the grid
universe to fail if the job's sandbox is transferred more than once.
\Ticket{6791}

\item Fixed a bug where Singularity would not be usable if Docker was not
installed.
\Ticket{6772}

\item Fixed a bug where \MacroNI{MOUNT\_UNDER\_SCRATCH} would not be
interpreted as an expression for Singularity jobs.
\Ticket{6740}

\item Fixed a bug where Docker Universe jobs would not bind mount the
scratch directory when the jobs did not transfer files.
\Ticket{6776}

\item Fixed a bug where short-lived Docker jobs would report spuriously
high usage.
\Ticket{6796}

\item Fixed how job start timestamps are recorded in the job ad in the
grid universe and the job router.
\Ticket{6773}

\item Fixed a bug that resulted in core files on Windows being mostly empty
when the files were made by the 64-bit Windows binaries.
\Ticket{6801}

\item Fixed a bug in how jobs are sorted in priority order in the
\Condor{schedd} when any of these job attributes are set:
\AdAttr{PreJobPrio1}, \AdAttr{PreJobPrio2}, \AdAttr{PostJobPrio1}, and
\AdAttr{PostJobPrio2}.
\Ticket{6800}

\item Fixed a bug where the negotiator would erroneously preempt some
dynamic slots when \Macro{ALLOW\_PSLOT\_PREEMPTION} is set.
\Ticket{6793}

\item Updated the systemd unit file to start HTCondor daemons after NFS
and the automounter was available.
\Ticket{6794}

\item Fixed a bug which would cause the \Condor{negotiator} to crash if the
second argument of an ternary operator is omitted in a \MacroNI{START}
expression.  \Expr{(expression ?: value)}
\Ticket{6798}

\item Fixed a bug which would cause certain valid URLs not be recognized.  This
allows, for example, `s3' to be used as a custom file transfer plug-in.
\Ticket{6722}

\item Fixed a bug in file transfer where jobs would go on hold if they created
a domain socket, which the FileTransfer module would subsequently try (and fail)
to send back to the submit machine.
\Ticket{6744}

\item Prevented the combination of -forward and -since flags when calling
\condor{history}, which is ambiguous as to how it should work.
\Ticket{6417}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-6-12}Version 8.6.12}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.6.12 released on August 1, 2018.

\end{itemize}

\noindent Known Issues:

\begin{itemize}

\item Policies implemented by the startd may not function as desired while
the machine is draining.  Specifically, if the \MacroNI{PREEMPT} expression
becomes true for a particular slot while a machine is draining, the
corresponding job will not vacate the slot until draining completes.  For
example, this renders the policy macro \MacroNI{HOLD\_IF\_MEMORY\_EXCEEDED}
ineffective.  This has been a problem since v8.6.
\Ticket{6697}

\item Policies implemented by the startd may not function as desired while
the startd is shutting down peacefully.  Specifically, if the \MacroNI{PREEMPT}
expression becomes true for a particular slot while the startd is shutting
down peacefully, the corresponding job will never be vacated.  For example,
this renders renders the policy macro \MacroNI{HOLD\_IF\_MEMORY\_EXCEEDED}
ineffective.  This has been a problem since v8.6.
\Ticket{6701}

\end{itemize}

\noindent New Features:

\begin{itemize}

\item Support for Debian 9, Ubuntu 16, and Ubuntu 18.

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a memory leak when SSL authentication fails.
\Ticket{6717}

\item Fixed a bug where a job transform with an invalid Requirements expression would not log an
error, and would match all jobs as if Requirements had not been specified.
\Ticket{6671}

\item Fixed a bug where \Condor{qedit} would not allow attempts to change protected attributes even
when the user had the right to change them.
\Ticket{6674}

\item Fixed a bug that would prevent environment variables defined in a job
submit file from appearing in jobs running in Singularity containers using
Singularity version 2.4 and greater.
\Ticket{6656}

\item Fixed a bug causing the shared port daemon to crash immediately when
built and run on Fedora 28.
\Ticket{6696}

\item Updated the systemd configuration to prevent the rare escape of a job
from its cgroup.
\Ticket{6708}

\item Fix a bug in the \Condor{qsub} wrapper that prevented users from requesting more
than one CPU core.
\Ticket{6693}

\item Fixed a bug where \Condor{transfer\_data} always wrote the job
user log in the initialdir, even if the original submit file specified
a different directory.
\Ticket{6695}

\item Blank lines in a security or user map file no longer generate
an error message.
\Ticket{6672}

\item Fixed a bug that prevented the \Condor{starter} from determining
the status of a VM that has previously been shut down.
\Ticket{6704}

\item Fixed a bug where the \Condor{gridmanager} would consider grid-type
gce jobs as completed when a query of the instances' status failed.
\Ticket{6712}

\item Fixed a bug where using the warning keyword in a submit file would cause
the subsequent queue statement to be reported as invalid.
\Ticket{6677}

\item Fixed a bug in \Condor{preen} where it did not clean up core dump files.
It now erases all core files that exceed a certain size (defined by 
\MacroNI{PREEN\_COREFILE\_MAX\_SIZE}), a certain age (defined by 
\MacroNI{PREEN\_COREFILE\_STALE\_AGE}) or a maximum number of core files per
process (defined by \MacroNI{PREEN\_COREFILES\_PER\_PROCESS}).
\Ticket{6540}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-6-11}Version 8.6.11}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.6.11 released on May 10, 2018.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item The MSI installer for Windows now appends the directory needed to use the
HTCondor Python bindings libraries into the \Env{PYTHONPATH} environment variable.
\Ticket{6607}

\item If the user sets the environment variable \Env{OMP\_NUM\_THREADS} to some value
in the submit file, trust the user, and do not overwrite this environment
variable to the actual number of provisioned CPUs when the job runs.
\Ticket{6606}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug where \Condor{submit} \Opt{-i} would enter the wrong Singularity
container.
\Ticket{6595}

\item When using configuration parameter \MacroNI{SINGULARITY\_TARGET\_DIR}
to mount the job scratch directory into the Singularity container,
update the \Env{X509\_USER\_PROXY} environment variable to point to the
proxy file's location inside the container.
\Ticket{6625}

\item Corrected a bug which could cause the shared port daemon to hang if
it had been restarted, HTCondor had been configured with an allowable
port range, and that port range had filled up.
\Ticket{6596}

\item Fixed a bug that caused TCP port exhaustion when running a large
number of instances of the \Condor{chirp\_client} program.
\Ticket{6627}

\item \Condor{submit} \Opt{-i} jobs now track their resource usage as normal jobs do.
\Ticket{6590}

\item Fixed a bug that prevented HTCondor from running jobs if
HTCondor was started within a Docker container, or more generally,
with a root user id, but without \Env{CAP\_SYSADMIN}.
\Ticket{6603}

\item Fixed a bug that caused corruption of the XferStatsLog.
\Ticket{6608}

\item Fixed bugs in \Condor{q} where the \Opt{-global} option would sometimes
truncate the job cluster id and the \Opt{-hold} option would truncate the hold reason.
\Ticket{6634}
\Ticket{6641}

\item Fixed a bug where \MacroNI{STARTD\_CRON\_JOBLIST} was not ignoring
duplicate entries.
\Ticket{6604}

\item Fixed a bug when running inside a docker container that would prevent
the master from started unless \Env{DISCARD\_SESSION\_KEYRING\_ON\_STARTUP} was set to
false.
\Ticket{6602}

\item Fixed a bug specific to the HTCondor Python bindings on Windows, where
the call htcondor.reload\_config() would fail to see 
environment variable changes made by the Python program.
\Ticket{6610}

\item DAGMan did not previously check the user log file (which it depends on for
coordination with the \Condor{schedd}) for corruption. Now, it checks to see if the user log
file has been overwritten or deleted, and if so, exits immediately with an error.
\Ticket{6579}

\item Fixed a bug in the ReadUserLog class where it failed to detect if a file
file has been overwritten.
\Ticket{6582}

\item Fixed a bug where \Condor{submit} would not add needed file transfer plugins to the
Requirements expression when should\_transfer\_files was \MacroNI{IF\_NEEDED}, which is the default.
\Ticket{4692}

\item Fixed a bug where the configuration parameter \MacroNI{STARTD\_RECOMPUTE\_DISK\_FREE} was
not honored when creating a dynamic slot from a partitionable slot, which would sometimes result
in the dynamic slot being provisioned with not enough disk space and then failing to match the job.
\Ticket{6614}

\item Fixed a bug that caused the job ad attribute
\Attr{JobCurrentStartTransferOutputDate} to be set incorrectly.
\Ticket{6617}

\item Fixed a bug that could cause \Attr{RemoteWallClockTime} to have
the wrong value in the history file.
\Ticket{6626}

\item The \Condor{schedd} now considers custom machine resources when
selecting the next job to run on an idle claimed dynamic slot.
\Ticket{6630}

\item The attribute \Attr{SlotType} is now set correctly in the slot
ad when the \Condor{schedd} is selecting the next job to run on a an
idle claimed dynamic slot.
\Ticket{6611}

\item Fixed a bug where \Condor{submit} with the \Opt{-spool} or
\Opt{-remote} option would fail when there were no input files to
transfer.
\Ticket{6655}

\item Fixed a bug that could cause the \Condor{gridmanager} to falsely
believe that grid-type boinc jobs were submitted to the BOINC server.
\Ticket{6669}

\item Fixed a bug that could cause the HOLD column to be missing from \Condor{q}
output when the \Opt{-global} option was used.
\Ticket{6661}

\item Fixed a bug that caused the \Condor{collector} to reject
accounting ads when configuration parameter
\MacroNI{COLLECTOR\_REQUIREMENTS} is in use.
\Ticket{6673}

\item Updated the systemd configuration to set the \Env{TasksMax} and \Env{LimitNOFile}
to unlimited. Under some versions of systemd, the \Env{TasksMax} defaults to 512,
which is too small for a busy submit host.
\Ticket{6645}

\item Reduced the \Env{RPATH} in RPM builds to just the needed directories.
Previously, the tarball \Env{RPATH} was used.
\Ticket{6662}

\item On the Windows platform, the HTCondor daemons will attempt a \Env{NETWORK}
login to impersonate a user if the \Env{INTERACTIVE} login fails.
\Ticket{6640}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-6-10}Version 8.6.10}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.6.10 released on March 13, 2018.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item None.

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug that caused \Condor{preen} to crash before it finished
cleaning the spool directory and leave a core file of its own in the log
directory.
This problem occurred on submit nodes that had running jobs when
\Condor{preen} was invoked.
\Ticket{6521}

\item Improved the systemd configuration to clean up HTCondor processes
on shutdown in the event that the \Condor{master} fails to do so.
\Ticket{6539}

\item HTCondor daemons will do fast shutdown whenever their parent process
exits unexpectedly.
\Ticket{6539}

\item Fixed a bug that would cause \Condor{q} to crash if the hostname
was longer than 64 bytes.
\Ticket{6594}

\item Fixed a bug where if an administrator configured a Concurrency Limit
whose name ended in a number, \Condor{userprio} \Opt{-allusers} would show
additional bogus user entries.
\Ticket{6542}

\item Fixed a bug where the \Condor{starter} would crash when talking
to a shadow running a condor version older than 8.5 and match authentication
was enabled.
\Ticket{6520}

\item Fixed a bug in Python API \Prog{htcondor.Secman().ping()} method which
would sometimes result in a RunTimeError exception.
\Ticket{6562}

\item Fixed a bug where \MacroNI{policy:\ want\_hold\_if} would always
evict standard universe jobs instead of putting them on hold.  Instead,
this policy now ignores standard universe jobs entirely.  This means
that the metaknobs \MacroNI{policy:\ hold\_if\_memory\_exceeded} and
\MacroNI{policy:\ hold\_if\_cpus\_exceeded} will also ignore
standard universe jobs entirely (instead of its previous bad behavior
of of letting standard universe jobs use more than their requested
memory until the first time they were evicted, whereafter each restart
would be immediately evicted).
\Ticket{6583}

\item The metaknob \MacroNI{policy:\ hold\_if\_memory\_exceeded} and
\MacroNI{policy:\ preempt\_if\_memory\_exceeded} now ignore VM universe
jobs.  These jobs can't exceed their requested memory.
\Ticket{6583}

\item Fixed a bug which mischaracterized the \Attr{MemoryUsage} of VM
universe jobs.  This should allow VM universe jobs to run when
\MacroNI{feature:\ Hold\_If\_Memory\_Exceeded} is enabled.
\Ticket{6577}

\item Fixed a bug where the \Condor{shadow} could accidentally kill itself
by not checking if it was attempting to change immutable attributes.
\Ticket{6557}

\item Fixed a bug that could cause the \Condor{collector} to exit with an 
assertion error under certain (rare) conditions when it has no
outgoing connectivity to the Internet.
\Ticket{6511}

\item Fixed a bug that would cause any daemons interfacing with the CREDMON to
retry indefinitely when polling for credentials.
\Ticket{6523}

\item Fixed a bug that prevented grid-type batch jobs from being removed
after an attempt to submit to the underlying batch system failed.
\Ticket{6586}

\item Fixed a bug in Python plugin support for the \Condor{collector} that would result
in the \Condor{collector} switching from writing from the CollectorLog to writing to
the ToolLog after a reconfig.
\Ticket{6588}

\item Fixed a bug in the \verb@$F()@ macro expansion in submit and configuration files
that would cause a crash if the argument to the macro was a file literal rather than
a variable name.
\Ticket{6531}

\item Fixed a bug that allowed the \Condor{schedd} to attempt to run jobs
on a dynamic slot that requested more resources than the slot provided.
\Ticket{6593}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-6-9}Version 8.6.9}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.6.9 released on January 4, 2018.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item When a daemon crashes, more information about the cause is now
written to its log file.
\Ticket{6483}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug in the group quotas that would give too much surplus
quota to some groups when \MacroNI{ACCEPT\_SURPLUS} is on and
\MacroNI{NEGOTIATOR\_ALLOW\_QUOTA\_OVERSUBSCRIPTION} is true (the default)
\Ticket{6514}

\item Fixed a bug in the Python bindings when doing queries that specify a
projection with the ``attr\_list'' argument. The bug could could
potentially result in memory corruption of the Python interpreter process.
\Ticket{6468}

\item Reduced the amount of time that \Condor{preen} will block the
\Condor{schedd}.
\Condor{preen} now connects only when specifically needed,
and automatically disconnects after
\MacroNI{PREEN\_MAX\_SCHEDD\_CONNECTION\_TIME} seconds.
\Ticket{6490}

\item Fixed a bug on Windows that would often result in the job sandbox
on the execute node not being deleted when the \Condor{schedd} relinquished
its claim on the slot before the \Condor{starter} had exited.
\Ticket{6497}

\item Fixed a bug where the \Condor{master} stopped sending watchdog
notifications to systemd after restarting itself.
This resulted in systemd killing the \Condor{master} shortly after
the restart.
\Ticket{6476}

\item Updated the systemd configuration to only restart HTCondor upon
failure. Otherwise, systemd would restart HTCondor if \Condor{off}
requested the \Condor{master} to exit.
\Ticket{6503}

\item Fixed a bug with the use of the scheduler parameter
\MacroNI{MAX\_JOBS\_SUBMITTED}. If this limit was ever reached by a
submit with more than one proc in the cluster, the limit would be
reduced by the difference until the \Condor{schedd} was restarted.
\Ticket{6460}

\item Fixed a bug that caused very large RequestDisk requests
to fail, and cause the Disk attribute in the machine ad to go
negative.
\Ticket{6467}

\item Fixed a bug with the \MacroNI{RESERVED\_DISK} parameter that would not
accept an argument larger than 2 Gigabytes.
\Ticket{6472}

\item Improved validation of the lengths of messages in \MacroNI{PASSWORD}
and \MacroNI{SSL} authentication methods.
\Ticket{6493}

\item Fixed a problem where the VM universe would be taken offline
on the execute node, if the qcow2 disk image was corrupt.
The offending job is now put on hold with an appropriate hold message.
\Ticket{6505}

\item Fixed a problem which would prevent Java universe jobs from working
when using a relative path name to a jar file and submitting from Linux to
Windows or vice versa.
\Ticket{6474}

\item Fixed a bug on 32 bit Linux systems that caused the starter to crash
on startup if cgroup limits were enabled.
\Ticket{6501}

\item Fixed a bug in \Term{Startd Cron} (see \ref{sec:daemon-classad-hooks})
where, in effect, \MacroNI{SlotMergeConstraint} was ignored.
\Ticket{6488}

\item Fixed a bug when IPv6 is enabled which could cause the
\Condor{startd} to crash when spawning a starter.
\Ticket {6462}

\item Fixed a bug in \Condor{q} which could cause the DONE amount to be
incorrect when multiple clusters shared a batch name.
\Ticket{6469}

\item Fixed issue on newer versions of Linux where core files generated
by a daemon were not usable by gdb.
A side effect of this fix is that the configuration parameter
\MacroNI{CORE\_FILE\_NAME} no longer has any effect on Linux.
\Ticket{6482}

\item \Condor{chirp} will now no longer abort when given a command that it
cannot successfully execute, such as fetching a file that does not exist.
\Ticket{6402}

\item Removed unneeded \MacroNI{copy\_to\_spool} statement from default
interactive submit file.
\Ticket{6315}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-6-8}Version 8.6.8}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.6.8 released on November 14, 2017.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item None.

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item \Security
This release of HTCondor fixes a security-related bug described at 
\URL{http://htcondor.org/security/vulnerabilities/HTCONDOR-2017-0001.html}.
\Ticket{6455}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-6-7}Version 8.6.7}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.6.7 released on October 31, 2017.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item Added support for HTTPS transfers in the \MacroNI{curl\_plugin} utility.
\Ticket{6253}

\item Job attributes that are recognized by the \Prog{batch\_gahp}
but not by HTCondor can now be specified in the job ad without using
a prefix of \Attr{Remote\_}.
\Ticket{6422}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug that caused systems using cgroup memory limits to
not properly reset the memory limit after the first use of a slot.  The memory
limit would get reused from the previous slot value.
\Ticket{6414}

\item Added SELinux type enforcement rules to allow \Prog{condor\_ssh\_to\_job}
to function on Enterprise Linux 7.
\Ticket{6362}

\item Asking systemd to stop condor now allows the HTCondor daemons to properly
clean up, instead of simply immediately sending a SIGKILL.  As a result,
HTCondor daemons stopped via systemd will no longer continue to appear
alive with \Condor{status}.
\Ticket{6096}

\item Fixed problems in Python bindings when using the Submit class
to submit jobs specifying environment variables or file redirection.
\Ticket{6420}

\item Change the default value of STARTD\_RECOMPUTE\_DISK\_FREE to false, so
that the Disk attribute is mostly correct for partitionable slots.
\Ticket{6424}

\item Docker universe now sets the cgroup cpu-shares field to 100 times the
number of requested cores, which matches vanilla universe.
\Ticket{6423}

\item MOUNT\_UNDER\_SCRATCH when used in Docker universe can now be an
expression, not just a literal string.
This matches the way it works in vanilla universe.
\Ticket{6401}

\item Fixed a bug that could cause the \Condor{startd} to crash when spawning
a \Condor{starter} with mixed mode networking.
\Ticket{6461}

\item Fixed a bug that caused the \Condor{collector} on Windows to refuse
connections whenever the number of open sockets was more than 820 even though
space was allocated for 1024 open sockets.
\Ticket{6425}

\item Fixed a bug that caused the configuration variable
\MacroNI{DEFAULT\_MASTER\_SHUTDOWN\_SCRIPT} to be ignored on Windows when the
\Condor{master} was running as a service.
\Ticket{6458}

\item \Condor{status} will now print longer lines when its output is
redirected into a pipe, rather than its input coming from one.
\Ticket{6381}

\item Fixed a crash in \Condor{transferer} when a connection can't be
established with its peer.
\Ticket{6412}

\item Fixed a bug that caused \Condor{job\_router\_info} to crash if
configuration parameter \MacroNI{JOB\_ROUTER\_ENTRIES\_REFRESH} was
set to a positive value.
\Ticket{6444}

\item Fixed a bug in \Condor{history} that caused it to print invalid
XML or JSON syntax when reading from multiple history files.
\Ticket{6437}

\item Fixed a bug in the \Condor{schedd} which resulted in the \Attr{IsNoopJob}
job attribute sometimes being ignored if the the value of this attribute was
changed after the job was submitted.
\Ticket{6396}

\item Fixed a bug that rarely caused slurm jobs to be held.
When slurm reports memory utilization and it is a multiple of 1024k,
Slurm uses the 'M' suffix.
The parsing logic was extended to also interpret the 'M', 'G', 'T', and 'P'
suffixes for memory utilization.
\Ticket{6431}

\item The condor-bosco RPM ensures the \Prog{rsync} is installed as required
by the Bosco scripts.
\Ticket{6439}

\item To avoid unnecessary transfers when \MacroNI{copy\_to\_spool} is set in
the submit file, HTCondor no longer copies the executable to the
local spool directory more than once for a cluster.
\Ticket{6454}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-6-6}Version 8.6.6}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.6.6 released on September 12, 2017.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item None.

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug that might cause the \Condor{schedd} or other daemons to
crash when logging on Linux to the syslog facility, and the \Condor{reconfig}
command was run.
\Ticket{6364}

\item Fixed a bug that prevented condor daemons from writing out a
core file for debugging in the very unlikely event that one of them
crashed.
\Ticket{6365}

\item Fixed a bug where the negotiator would make matches where the daemons
involved did not share an IP version, and thus could not talk to each other.
\Ticket{6351}

\item HTCondor now works properly with systemd's watchdog feature on
all flavors of Linux.
Previously, the \Condor{master} wouldn't send alive messages to systemd
if systemd wasn't part of the Linux distribution's standard configuration.
This would result in systemd killing the HTCondor daemons after a
short period of time.
\Ticket{6385}

\item Fixed handling of backslashes in string values in old ClassAds
format in the Python bindings.
\Ticket{6382}

\item Fixed a bug in how the CPU usage of Slurm jobs is interpreted.
\Ticket{6380}

\item Fixed a bug that caused a machine claimed by a parallel universe
job to stick in the Claimed/Idle state forever.  This could only happen
if the job was removed as it was in the process of claiming resources.
\Ticket{6376}

\item Fixed a bug that caused a machine to stick in the
Preempting/Vacating state after a job was removed
when a \MacroNI{JOB\_EXIT\_HOOK} was defined.
\Ticket{6383}

\item Added type enforcement rules for cgroups to HTCondor's SELinux
profile.
\Ticket{6168}

\item Fixed a bug where setting \MacroNI{delegate\_job\_gsi\_credentials\_lifetime}
to 0 in a submit description file was treated the same as not setting
it at all.
\Ticket{6375}

\item Fixed handling of octal escape sequences in ClassAd strings.
\Ticket{6384}

\item Updated Boost external to version 1.64.
\Ticket{6369}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-6-5}Version 8.6.5}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.6.5 released on August 1, 2017.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item Added avx2 to the set of processor flags advertised by the
\Condor{startd}.
\Ticket{6317}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug in socket clean-up that was causing a memory leak.  This
may have been particularly noticeable in the \Condor{collector}.
\Ticket{6342}

\item Fixed a bug that caused an infinite loop in the \Condor{starter} when
cgroups were enabled on systems (such as Debian) where the kernel has disabled
the memory accounting controller.  A job on such a system would go into the
"R" state, but never actually start running.
\Ticket{6347}

\item Fixed a bug where setting \MacroNI{NETWORK\_INTERFACE} to an
IPv6 address could cause HTCondor daemons to except.
\Ticket{6339}

\item Fixed a bug where a cross protocol CCB connection would cause the
\Condor{shadow} or \Condor{schedd} to except.
\Ticket{6344}

\item Fixed a bug where the wildcard '*' in ALLOW or DENY lists was
being interpreted as only matching IPv4 addresses.  It now properly
matches any address family.
\Ticket{6340}

\item Fixed a bug where reverse resolutions could return the string
representation of the address in question instead of failing.  This
resulted in spurious warnings of the form "WARNING: forward resolution of
2001:630:10:f001::19a0 doesn't match 2001:630:10:f001::19a0!"
\Ticket{6338}

\item Fixed a bug which prevented using an ImDisk RAM disk
as the execute directory on Windows.
\Ticket{6324}

\item Fixed a bug where removal of a job could cause another job from
the same user to also be removed.
This was mostly likely to happen when the \Condor{schedd} is under
heavy load.
\Ticket{6353}

\item Fixed a bug that cause parallel universe jobs not to start on
pools with partitionable slots.
\Ticket{6308}

\item Fixed a problem, introduced in HTCondor 8.6.4, where the
\Condor{collector} plugins where loaded but not used.
\Ticket{6343}

\item Fixed a bug where "\Condor{q} \Opt{-grid}" did not display the
status column for any non-Globus job.
\Ticket{6306}

\item Fixed bugs in the \Condor{schedd} and \Condor{negotiator} that
could cause jobs to not be negotiated for when
\MacroNI{NEGOTIATOR\_PREFETCH\_REQUESTS} is set to \Expr{TRUE}.
\Ticket{6336}
\Ticket{6312}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-6-4}Version 8.6.4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.6.4 released on June 22, 2017.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item Python bindings are now available on MacOSX.
\Ticket{6244}

\item Allow Python modules to be used as \Condor{collector} plugin.
This undocumented feature is to be used by expert developers only.
\Ticket{6213}
\Ticket{6295}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug with PASSWORD authentication that would sporadically cause
it to fail to exchange keys, due to whether or not the first round-trip of
communications blocked on reading from the network.
\Ticket{6265}

\item Pslot preemption now properly handles machine custom resources,
such as GPUs.
\Ticket{6297}

\item Fixed a bug that prevented HTCondor from correctly setting
virtual memory cgroup limits when soft physical memory limits
were being used.
\Ticket{6294}

\item Fixed a bug that prevented parallel universe jobs from running
that used \$\$() expansion in submit files.
\Ticket{6299}

\item Added a new knob, \MacroNI{STARTD\_RECOMPUTE\_DISK\_FREE}, which defaults
to true, which tells the startd to periodically recompute and advertise free
disk space.  Admins can set this to false for partitionable slots whose execute
directory is used by HTCondor alone.
\Ticket{6301}

\item Fixed a bug that could cause \Condor{submit} to fail to submit a
job with a proxy file to a \Condor{schedd} older than 8.5.8, due to the
absence of an X.509 CA certificates directory.
\Ticket{6258}

\item Restored a check in \Condor{submit} about whether the job's X.509
proxy has sufficient lifetime remaining.
\Ticket{6283}

\item Fixed a bug in \Condor{dagman} where the DAG status file showed an
incorrect status code if submit attempts failed for the final node.
\Ticket{6069}

\item Bosco now properly identifies CentOS 7 as a supported platform.
\Ticket{6303}

\item Fixed a bug when Bosco is used to submit jobs to multiple remote
clusters. When arguments to \Prog{remote\_gahp} are provided in the
GridResource attribute, jobs could be submitted to the wrong cluster.
\Ticket{6277}

\item To speed up the installation process on Enterprise Linux 7, the
SELinux profile is now reloaded only once, when setting the HTCondor
daemons to run in permissive mode.
\Ticket{6304}

\item Update the systemd configuration on Enterprise Linux 7 to start the
\Condor{master} after time synchronization is achieved. This prevents
unnecessary daemon restarts due to sudden time shifts.
\Ticket{6255}

\item The \Condor{shadow} will now ignore updates of \Attr{JobStartDate}
from the \Condor{starter} since the \Condor{schedd} already sets this
attribute correctly and the \Condor{starter} incorrectly tries to set it
even if the job has already run once. A consequence of this fix is that the
value of \Attr{JobStartDate} that the \Condor{startd} uses for policy
expressions will be different than the value that the \Condor{schedd} uses.
Resolving this problem will potentially break existing policy expressions
in the \Condor{startd}, so it will be be not be changed in the 8.6 series,
but fixed in the 8.7 series.
\Ticket{6280}

\item Fixed a bug where per-instance job attributes like \AdAttr{RemoteHost}
would show up in the history file for completed jobs.  This bug occurred if
a job happened to complete while the \Condor{schedd} was in the process of a
graceful shutdown.
\Ticket{6251}

\item The \Condor{convert\_history} command is present again in this release.
\Ticket{6282}

\item The parameter \MacroNI{SETTABLE\_ATTRS\_ADMINISTRATOR} is now correctly
appears in \Condor{config\_val}.
\Ticket{6286}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-6-3}Version 8.6.3}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.6.3 released on May 9, 2017.

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug that rarely corrupts the \Condor{schedd}'s job queue
log file when the input sandbox of a job with an X.509 proxy file is
spooled.
\Ticket{6240}

\item Fixed a memory leak in the Python bindings related to logging.
\Ticket{6227}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-6-2}Version 8.6.2}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.6.2 released on April 24, 2017.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item Added metaknobs for defining map files for use with the ClassAd usermap function
in the \Condor{schedd}, and a metaknob for automatically assigning an accounting group to
a job based on a mapping of the owner name of the job.
\Ticket{6179}

\item When the \Condor{credd} is polling for credentials, the timeout is now
configurable using \MacroNI{CREDD\_POLLING\_TIMEOUT}.

\item The \Opt{reverse} option for \Condor{q} was changed to \Opt{reverse-analyze},
and it now implies \Opt{better-analyze}. Formerly, the \Opt{reverse} option was ignored
unless \Opt{-better-analyze} was also specified.
\Ticket{6167}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug that could cause \Condor{store\_cred} to fail on
Windows due to a case-sensitive check of the user's account name.
\Ticket{6200}

\item Updated Open MPI helper script to catch and handle SIGTERM and
to use bash explicitly.
\Ticket{6194}

\item Docker Universe jobs now update the RemoteSysCpu attributes for job
and in the job log. Previously, this field was always 0.
\Ticket{6173}

\item Docker universe detection is now more robust in the
face of extraneous output to standard error on docker startup.
This was preventing Condor from detecting that docker was properly
working on hosts.
\Ticket{6185}

\item Fixed a bug that prevented \MacroNI{SUBMIT\_REQUIREMENT} and
\MacroNI{JOB\_TRANSFORM} expressions from referencing job attributes
describing the job's X.509 proxy credential.
\Ticket{6188}

\item The Linux kernel tuning script no longer adjusts some kernel parameters
unless a \Condor{schedd} will be started by the master.
\Ticket{6208}

\item Fixed a bug that caused all but the first in a list of metaknobs to be ignored
unless there were commas separating the list items. So \MacroNI{use ROLE : Execute CentralManager}
would incorrectly add only the Execute role.
Previously, \MacroNI{use ROLE : Execute, CentralManager} would correctly add both roles.
\Ticket{6171}

\item Worked around a problem with FORTRAN programs built with \Condor{compile}
and recent versions of gfortran (4.7.2 was OK, 4.8.5 was not), where those
executables would not write to standard out if started in the standard universe.
Also, updated the checkpointing library to permit \Condor{compile} to
successfully link FORTRAN (and other) programs calling certain math
functions and built against up-to-date versions of glibc.
\Ticket{6026}

\item The default values for \MacroNI{HAD\_SOCKET\_NAME} and
\MacroNI{REPLICATION\_SOCKET\_NAME} have changed to enable the documented
configuration for using these services with shared port to work.
\Ticket{6186}

\item Fixed a bug that caused \Condor{dagman} to sometimes (rarely, but
repeatably) crash when parsing DAGs containing splices.
\Ticket{6170}

\item The configuration parameters that control when job policy expressions
are evaluated now work as documented.
Previously, the default value for \MacroNI{PERIODIC\_EXPR\_INTERVAL} was
300, not 60 as intended.
Also, the parameters \MacroNI{MAX\_PERIODIC\_EXPR\_INTERVAL} and
\MacroNI{PERIODIC\_EXPR\_TIMESLICE} were ignored for grid universe jobs.
\Ticket{6199}

\item Fixed a bug that could cause the Job Router to crash if the
\File{job\_queue.log} contained invalid or incomplete records.
\Ticket{6195}

\item Fixed a bug that caused updates of the job attribute
\Attr{x509UserProxyExpiration} to be ignored for job policy evaluation
when the job was managed by the Job Router.
\Ticket{6209}

\item Changed the default value of configuration parameters
\MacroNI{CREAM\_GAHP\_WORKER\_THREADS} to the value of
\MacroNI{GRIDMANAGER\_MAX\_PENDING\_REQUESTS}.
This should prevent a back-log of commands in the CREAM GAHP observed
by some users.
\Ticket{6071}

\item Fixed modification of \Env{PYTHONPATH} environment variable that
could fail in bash if \Prog{set -u} is enabled.
\Ticket{6211}

\item \Prog{bosco\_quickstart} no longer assumes that submitting to a Slurm
cluster requires the PBS emulation module.
\Ticket{6211}

\item Fixed a bug that caused \Condor{submit} \Opt{-dump} to crash when
the submit file had an attribute to enable the use of an x509 user proxy.
\Ticket{6197}

\item Updated the supported platform list in the Bosco installer script to
include Ubuntu 16 and Mac OSX 10.12. Also, dropped Ubuntu 12 and Mac OSX
10.6 through 10.9.
\Ticket{6178}

\item Fixed a bug which in some obscure configurations caused a spurious
PERMISSION DENIED error was printed in the StartLog when activating a claim.
\Ticket{6172}.

\item Fixed a bug which forced the administrator to restart (rather than
reconfigure) running daemons after adding an entry to a \MacroNI{DENY\_*}
authorization list.
\Ticket{6172}.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-6-1}Version 8.6.1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.6.1 released on March 2, 2017.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item \Condor{q} now checks to see if authentication and security negotiation are enabled before attempting to
request only the current users jobs from the \Condor{schedd}.  Prior to this change, configurations that disabled
security or authentication would also need to set \MacroNI{CONDOR\_Q\_ONLY\_MY\_JOBS} to false.
\Ticket{6125}

\item The CLAIMTOBE authentication method is now in the list of methods for READ access if no list of
authentication methods for READ or DEFAULT is specified in the configuration.  This change allows sites that
use the default host based security model to use \Condor{q} \Opt{-global} with the only-my-jobs feature
without making changes to their security configuration.
\Ticket{6125}

\item The collector now records the authentication method used to determine the authenticated identity.
\Ticket{6122}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Update Docker interface to be able to retrieve usage information
from running containers and to remove containers when certain errors
occurred when using Docker version 1.13.
\Ticket{6088}

\item In Docker universe, all writes to files in \File{/tmp} and \File{/var/tmp} by default
write inside the container.  There is a limit on the file size within the container,
and jobs that write a lot to \File{/tmp} may hit that.  If a docker universe job now runs
on a system with \MacroNI{MOUNT\_UNDER\_SCRATCH} defined, HTCondor now adds those
mounts as volume mounts, so file writes do not go to the container, but to the host
file system.
\Ticket{6080}

\item Fixed a bug in \Condor{status} \Opt{-format} and \Condor{q} \Opt{-format} that caused the
tools to truncate output to the width specified in the format specifier. The most likely manifestation of
this bug was that punctuation after the format would not be printed when the format had an explicit width.
\Ticket{6120}

\item Fixed a bug that caused spurious shared port-related error
messages to appear in the \File{dagman.out} file (by adding the
new \MacroNI{DAGMAN\_USE\_SHARED\_PORT} configuration macro).
\Ticket{6156}

\item Fixed a bug that caused VM universe jobs to fail if the
\SubmitCmdNI{vm\_disk} submit command contained spaces after a comma.
\Ticket{6132}

\item Fixed a bug that can cause the Job Router and \Condor{c-gahp} to
crash if they fail to submit a job due to submit transforms or
submit requirements.
\Ticket{6152}

\item Fixed a bug that caused the Job Router to not route any jobs if
the \MacroNI{JOB\_ROUTER\_DEFAULTS} configuration parameter value
started with white space.
\Ticket{6128}

\item Fixed several bugs in how the Job Router writes to job event logs.
\Ticket{6092}

\item Removed Bosco's attempt to configure a default value for
\SubmitCmdNI{grid\_resource} in the submit description file, as
\Condor{submit} no longer supports this ability.
Also, Bosco now works with Slurm clusters.
\Ticket{6106}

\item Changed Bosco's configuration of the \Condor{ft-gahp} to eliminate
worrying error messages in the \Condor{ft-gahp}'s log file.
\Ticket{6107}

\item Fixed a bug that could cause a grid batch job submitted to PBS or
Slurm to go on hold when the job's X.509 proxy is refreshed.
\Ticket{6136}

\item Fixed a bug where the \Condor{gridmanager} fails to put a job on
hold due to the desired hold reason containing invalid characters.
\Ticket{6142}

\item Improved the hold reason when submission of a grid-type batch
job fails.
\Ticket{3377}

\item Update helper scripts to work with current versions of Open MPI and MPICH2.
\Ticket{6024}

\item Fixes a bug that could cause events for local universe jobs to not
be written to the global event log.
\Ticket{6100}

\item Fixed a bug on execute machines that enable PID namespaces that
    would generate a spurious error message in the daemon log when \Condor{off} -fast was issued.
\Ticket{6137}

\item Fixed a bug that could corrupt the job queue log file such that
the \Condor{schedd} cannot restart.
The bug is mostly likely to occur if the disk becomes full.
\Ticket{6153}

\item Incremented the ClassAd library version number, since the deprecated
iostream interface has been removed.
\Ticket{6050}
\Ticket{6115}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-6-0}Version 8.6.0}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.6.0 released on January 26, 2017.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item Added two new job ClassAd attributes, \MacroNI{CumulativeRemoteSysCpu} and
\MacroNI{CumulativeRemoteUserCpu}, which keep a running total of system and user
CPU usage, respectively, across all job restarts.  Also, immediately clear attributes
\MacroNI{RemoteSysCpu} and \MacroNI{RemoveUserCpu} on job start, instead of on first update.
\Ticket{6022}

\item Added a new configuration knob, \MacroNI{ALWAYS\_REUSEADDR}, which defaults
to \Expr{True}.  When \Expr{True}, it tells HTCondor to set the
\MacroNI{SO\_REUSEADDR} socket option, so that
the schedd can run large numbers of very short jobs without exhausting the
number of local ports needed for shadows.
\Ticket{6040}

\item Changed the default value of \MacroNI{IGNORE\_LEAF\_OOM} to \Expr{True}.
\Ticket{5775}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug causing unnecessarily slow updates from the \Condor{startd}.
If you depend on the old behavior, set \MacroNI{UPDATE\_SPREAD\_TIME} to 8.  A
value of 0 enables the fix.
\Ticket{6062}

\item Fixed a race condition when running multiple concurrent jobs on the same claim.
When the starter exits, it notifies the shadow, which tells the startd to kill the starter.
Immediately after the shadows tells the startd, it fetches the next job, and tries to start it.
If the starter hasn't completely exited yet (perhaps it needs to clean up a large sandbox),
it will notice the shadow has closed the command socket, and the starter will go into disconnected
mode, and get confused.  This has been fixed.
\Ticket{6049}

\item Fixed an infelicity with \Condor{submit} -i and docker universe,
where it would start an interactive shell without a container.  Added error
message expressing that this combination is not currently supported.
\Ticket{6083}

\item When a job claimed by the Job Router is held or removed, it is no
longer considered a failure of the job route chosen for that job.
\Ticket{5968}

\item Fixed a bug in recovering a Google Compute Engine (GCE) job if the
\Condor{gridmanager} restarts during submission of the instance request.
\Ticket{6078}

\item Fixed a bug that could cause re-installation of a remote cluster
to fail in Bosco.
\Ticket{6042}

\item Fixed a bug with handling the proxy files of grid-type batch jobs
when the proxy's file name is a relative path.
\Ticket{6053}

\item Fixed a bug that caused the \Prog{batch\_gahp} to crash when a job's
X.509 proxy is refreshed and the \Prog{batch\_gahp} is configured to not
create a limited copy of the proxy.
\Ticket{6051}

\item Fixed a bug in the virtual machine universe where \Attr{RequestMemory}
and \Attr{RequestCPUs} were not changing the resources assigned to the VM
created by HTCondor.  Now, \Attr{VM\_Memory} defaults to \Attr{RequestMemory},
and the number of CPUs defaults to \Attr{RequestCPUs}.
\Ticket{5998}

\end{itemize}
