%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!
%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!
%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!
%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!
%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:History-8-7}Development Release Series 8.7}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This is the development release series of HTCondor.
The details of each version are described below.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-7-8}Version 8.7.8}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.7.8 not yet released.
%\item HTCondor version 8.7.8 released on Month Date, 2018.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item Added the machine attribute \Attr{AcceptedWhileDraining}
(see page~\pageref{acceptedwhiledraining-machine-attribute}),
configuration macro \Macro{DEFRAG\_DRAINING\_START\_EXPR}
(see page~\pageref{param:DefragDrainingStartExpr}),
and command-line option \Opt{-start} to \Condor{drain}
(see page~\pageref{man-condor-drain})
to support running jobs on draining resources.  See
section \ref{sec:SMP-defrag} for details.
\Ticket{6628}

\item \Condor{annex} may now be setup in multiple regions simultaneously.
Use the \Opt{-aws-region} flag with \Opt{-setup} to add new regions.  Use the
\Opt{-aws-region} flag with other \Condor{annex} commands to choose which
region to operate in.  You may change the default region by setting
\MacroNI{ANNEX\_DEFAULT\_AWS\_REGION}.
\Ticket{6632}

\item Added default AMIs for all four US regions to simplify using
\Condor{annex} in those regions.
\Ticket{6633}

\item HTCondor will no longer mangle \Expr{CUDA\_VISIBLE\_DEVICES} or
\Expr{GPU\_DEVICE\_ORDINAL} if those environment variables are set when
it starts up.  As a result, HTCondor will report GPU usage with the
original device index (rather than starting over at 0).
\Ticket{6584}

\item When reporting \Attr{GPUsUsage}, HTCondor now also reports
\Attr{GPUsMemoryUsage}.  This is like \Attr{MemoryUsage}, except it is
the peak amount of GPU memory used by the job.  This feature only works
for NVidia GPUs.
\Ticket{6544}

\item Improved error messages when delegation of an X.509 proxy fails.
\Ticket{6575}

\item Condor{q} will no longer limit the width of the output to 80 columns when it
outputs to a file or pipe.
\Ticket{6643}

\item Submission of jobs via the Python bindings Submit class will now attempt to put all
 jobs submitted in a single transaction under the same ClusterId.
 \Ticket{6649}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a problem where, when starting enough \Condor{annex} instances
simultaneously, some (approximately 1 in 100) instances would neither join
the pool nor terminate themselves.
\Ticket{6638}

\item When running in a HAD setup, there is a configuration parameter,
\Macro{COLLECTOR\_HOST\_FOR\_NEGOTIATOR} which tells the active negotiator
which collector to prefer.  Previously, this parameter had no default,
so the negotiator might arbitrarily chose a far-away collector.  Now
this knob defaults to the local collector in a HAD setup.
\Ticket{6616}

\item Fixed a bug when running in a configuration with more than one
\Condor{collector}, the \Condor{negotiator} would only send the
accounting ads to one of them.  The result of this bug is that the
\Condor{userprio} tool would show now results about half of the time it
was run.
\Ticket{6615}

\item Fixed a bug where \Condor{annex} would fail with a malformed
authorization header when using AWS resources in a region other than
\Expr{us-east-1}.
\Ticket{6629}

\item Fixed a bug where the \Condor{starter} would fail with an error
after a docker job exits.
\Ticket{6623}

\item Fixed a bug where \Condor{userprio} would always show zero resources
in use when NEGOTIATOR\_CONSIDER\_PREEMPTION=false was set.
\Ticket{6621}

\item Fixed a bug where ``.update.ad'' was not being updated atomically.
\Ticket{6591}

\item Fixed a bug that could cause a machine slot to become stuck in the
Claimed/Busy state after a job completes.
\Ticket{6597}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-7-7}Version 8.7.7}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.7.7 released on March 13, 2018.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item \Condor{ssh\_to\_job} now works with Docker Universe, the interactive
shell is started inside the container.  This assume that there is a shell
executable inside the container, but not necessarily an sshd.
\Ticket{6558}

\item Improved error messages in the job log for Docker universe jobs
that do not start.
\Ticket{6567}

\item Release a 32-bit \Condor{shadow} for Enterprise Linux 7 platforms.
\Ticket{6495}

\item HTCondor now reports, in the job ad and user log, which custom machine
resources were assigned to the slot in which the job ran.
\Ticket{6549}

\item HTCondor now reports \Attr{CPUsUsage} for each job.  This attribute is
like \Attr{MemoryUsage} and \Attr{DiskUsage}, except it is the average number
of CPUs used by the job.
\Ticket{6477}

\item The \MacroNI{use feature: GPUs} metaknob now causes HTCondor to report
\Attr{GPUsUsage} for each job.  This is like \Attr{CPUsUsage}, except it is
the average number of GPUs used by the job.  This feature only works for
NVIDIA GPUs.
\Ticket{6477}

\item Administrators may now, for each custom machine resource, define a
custom resource monitor.  Such a script reports the usage(s) of each
instance of the corresponding machine resource since the last time it
reported; HTCondor aggregates these reports between resource instances and
over time to produce a \Attr{<Resource>Usage} attribute, which is like
\Attr{GPUsUsage}, except for the custom machine resource in question.
\Ticket{6477}

\item The \Condor{startd} now periodically writes a file to each job's
sandbox named ``.update.ad''.  This file is a copy of the slot's machine ad,
but unlike ``.machine.ad'', it is regularly updated.  Jobs may read this
file to observe their own usage attributes.
\Ticket{6477}

\item A new option \Opt{-unmatchable} was added to \Condor{q} that causes \Condor{q} to show
only jobs that will not match any of the available slots.
\Ticket{6529}

\item OpenMPI jobs launched in the parallel universe via \File{openmpiscript}
now work with shared file systems (again).
\Ticket{6556}

\item Allow a parallel universe job with parallel scheduling group to
select a new parallel scheduling group when held and released.
\Ticket{6516}

\item Allow p-slot preemption to work with parallel universe.
\Ticket{6517}

\item Added the ability in \Condor{dagman} to specify submit files with spaces
in their path names. Paths that include spaces must be wrapped in quotes
(i.e. JOB A "/path to/job.sub").
\Ticket{6389}

\item Added the ability in \Condor{submit} to specify executable, error and
output files with spaces in their paths. Previously, adding whitespace to these
fields would result in an error claiming certain attributes could only take
exactly one argument. Now, whitespace is
treated as part of the path.
\Ticket{6389}

\item An IPv6 address can now be specified in the configuration file
either with or without square brackets in most cases.
If specifying a port number in the same value, the square brackets are
required.
If using a wild card to specify a range of possible addresses, square
brackets are not allowed.
\Ticket{5697}

\item Improved support for IPv6 link-local addresses, in particular
using the correct scope id.
Using a wild card or device name in \MacroNI{NETWORK\_INTERFACE} now
works properly when \MacroNI{NO\_DNS} is set to \Expr{True}.
\Ticket{6518}

\item Python bindings installed via pip on a system without a
HTCondor install (i.e. without a \File{condor\_config} present)
will use a ``null'' config and print a warning.
\Ticket{6515}

\item The new configuration parameter \MacroNI{NEGOTIATOR\_JOB\_CONSTRAINT}
defines an expression which constrains which job ads are considered for
matchmaking by the \Condor{negotiator}.
\Ticket{6250}

\item The \Condor{startd} will now keep trying to delete a job sandbox until it succeeds.
The retries are attempted with an exponential back off in frequency.
\Ticket{6500}

\item \Condor{q} will no longer batch jobs with different cluster ids together unless they
have the same JobBatchName attribute or are in the same DAG.
\Ticket{6532}

\item \Condor{q} will now sort jobs by job id when the \Opt{-long} argument is used.
\Ticket{6287}

\item Improve the performance of reading and writing ClassAds to the network.
The performance of reading ClassAds from UDP is particularly improved, up
to 20\% faster than previously.
\Ticket{6555}
\Ticket{6561}

\item Several minor performance improvements.
\Ticket{6550}
\Ticket{6551}
\Ticket{6565}
\Ticket{6566}

\item Removed configuration parameters \MacroNI{ENABLE\_ADDRESS\_REWRITING}
and \MacroNI{SHARED\_PORT\_ADDRESS\_REWRITING}.
\Ticket{6525}

\item Removed the deprecated AvailStats attribute from the machine ad. This
was being computing incorrectly, and apparently never used.
\Ticket{6526}

\item Added basic support for a "Credential Management" subsystem which will
eventually be used to support interaction with OAuth services (like SciTokens,
Box.com, Google Drive, DropBox, etc.).  Still in preliminary phases and not
really ready for public use.
\Ticket{6513}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug where Docker universe jobs that exited via a signal
did not properly report the signal.
\Ticket{6538}

\item Fixed a bug where HTCondor would misreport the number of custom
machine resources (GPUs) allocated to a job in certain cases.
\Ticket{6549}

\item IPv4 addresses are now ignored when resolving a hostname and
\MacroNI{ENABLE\_IPV4} is set to \Expr{False}.
\Ticket{4881}

\item Fixed a race condition in the \Condor{startd} that could result in skipping the
code that makes sure that a job sandbox was deleted in the event that the \Condor{starter} did
not delete it.
\Ticket{6524}

\item Fixed a bug in \Condor{q} when both the \Opt{-tot} and \Opt{-global} options were used, that would
result in no output when querying a \Condor{schedd} running version 8.7 or later.
\Ticket{6494}

\item Fixed a bug that could prevent grid universe batch jobs from working
properly on Debian and Ubuntu.
\Ticket{6560}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-7-6}Version 8.7.6}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.7.6 released on January 4, 2018.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item Changed the default value of configuration parameter \MacroNI{IS\_OWNER}
to \Expr{False}. The previous default value is now set as part of the
\texttt{use POLICY : Desktop} configuration template.
\Ticket{6463}

\item You may now use SCHEDD and JOB instead of MY and TARGET in
\MacroNI{SUBMIT\_REQUIREMENTS} expressions.
\Ticket{4818}

\item Added cmake build option \MacroNI{WANT\_PYTHON\_WHEELS} and make target
\Expr{pypi\_staging} to build the framework for Python wheels.
This option and target
are not enabled by default and are not likely to work outside of Linux
environments with a single Python installation.
\Ticket{6486}

\item Added new job attributes BatchProject and BatchRuntime for grid-type
batch jobs.
They specify the project/allocation name and maximum runtime in seconds
for the job that's submited to the underlying batch system.
\Ticket{6451}

\item HTCondor now respects \Attr{ATTR\_JOB\_SUCCESS\_EXIT\_CODE} when sending
job notifications.
\Ticket{6432}

\item Added some graph metrics (height, width, etc.) to DAGMan's metrics file
output.
\Ticket{6470}

\item Removed Quill from HTCondor codebase.
\Ticket{6496}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item HTCondor now reports all submit warnings, not just the first one.
\Ticket{6446}

\item The job log will no longer contain empty submit warnings.
\Ticket{6465}

\item DAGMan previously connected to \Condor{schedd} every time it detected
an update in its internal state. This is too aggressive for rapidly changing
DAGs, so we've changed the connection to happen in time intervals defined by
\MacroNI{DAGMAN\_QUEUE\_UPDATE\_INTERVAL}, by default once every five minutes.
\Ticket{6464}

\item DAGMan now enforces the \MacroNI{DAGMAN\_MAX\_JOB\_HOLDS} limit by the
number of held jobs in a cluster at the same time. Previously it counted all
holds over the lifetime of a cluster, even if only a small number of them are
active at the same time.
\Ticket{6492}

\item Fixed a bug where on rare occasions the \File{ShadowLog} would
become owned by \Login{root}.
\Ticket{6485}

\item Fixed a bug where using \Condor{qedit}
to change any of the concurrency limits of a job would have no effect.
\Ticket{6448}

\item When \MacroNI{copy\_to\_spool} is set to \Expr{True},
\Condor{submit} now attempts to transfer the job exectuable only once per
job cluster, instead of once per job.
\Ticket{6459}

\item Fixed a bug that could result in an incorrect total reported by
\condor{rm} when the \Opt{-totals} option is used.
\Ticket{6450}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-7-5}Version 8.7.5}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.7.5 released on November 14, 2017.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item None.

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item \Security
This release of HTCondor fixes a security-related bug described at 
\URL{http://htcondor.org/security/vulnerabilities/HTCONDOR-2017-0001.html}.
\Ticket{6455}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-7-4}Version 8.7.4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.7.4 released on October 31, 2017.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item Added support for late materialization into \Condor{dagman}. DAGs that
include late materialized jobs now work correctly in both normal and recovery
conditions.
\Ticket{6274}

\item We now produce run time statistics in \Condor{dagman}, tracking how
much time DAGMan spends idle, how much time it spends submitting jobs and
processing log files. This information could be used to determine why a DAG
is submitting jobs slowly and how to optimize it. These statistics currently get
dumped into the .dagman.out file at the end of a DAGs execution.
\Ticket{6411}

\item Added a new knob to \Condor{dagman}, \MacroNI{DAGMAN\_AGGRESSIVE\_SUBMIT}.
When set to True, this tells DAGMan to ignore the interval time limit for
submitting jobs (defined by \MacroNI{DAGMAN\_USER\_LOG\_SCAN\_INTERVAL}) and to
continuously submit jobs until no more are ready, or until it hits a different
limit.
\Ticket{6386}

\item Added \Arg{status} command to \Condor{annex}.  This command invokes
\Condor{status} to display information about annex instances that have
reported to the collector.  It also gathers information about annex instances
from EC2 and forwards that data to \Condor{status} to detect instances which
the collector does not yet or any longer know about.  The annex instance ads
fabricated for this purpose are not real slot ads, so some options you may
know from \Condor{status} do not apply to the \Arg{status} command of
\Condor{annex}.  See section~\ref{cloud-computing} for details.
\Ticket{6321}

\item Added a ``merge'' mode to \Condor{status}.  When invoked with the
\oOptArg{-merge}{<file>} option, ads will be read from \Arg{file}, which
can be \Expr{-} to indicate standard in, and compared to the ads selected
by the query specified as usual by the remainder of the command-line.  Ads
will be compared on the basis of the sort key (which you can change with
\oOptArg{-sort}{<key>}).  \Condor{status} will print three tables based on
that comparison: the first table will be generated from those ads whose key
was in the query but not in \Arg{file}; the second table will be generated
from those ads whose key was appeared in both the query and in \Arg{file},
and the third table will be generated from those ads whose key appeared
only in \Arg{file}.
\Ticket{6321}

\item Added \Arg{off} command to \Condor{annex}.  This command invokes
\Condor{off} \Arg{-annex} appropriately.
\Ticket{6408}

\item Updated \Condor{annex} \Arg{-check-setup} to check collector security
as well as connectivity.
\Ticket{6322}

\item Added submit warnings.  See section \ref{sec:Schedd-Config-Submit-Warnings}.
\Ticket{5971}

\item \File{openmpiscript} now uses \Condor{chirp} to run Open MPI's execute daemons
(orted) directly under the \Condor{starter} (instead of using SSH). \File{openmpiscript}
now also puts information about the number of CPUs in the hostfile given to \File{mpirun}
and now includes an option for jobs that intend to use hybrid Open MPI+OpenMP.
\Ticket{6403}

\item The High Availability \Condor{replication} daemon now works on machines
using mixed IPV6/IPV4 addressing or using the \Condor{shared\_port} daemon.
\Ticket{6413}

\item When Docker universe starts a job, it no longer uses the docker
run command line to do so.  Now, it first creates a container with
docker create, then starts it with docker start.  This allows HTCondor
to better isolate errors at container creation time, but should not
result in any user visible changes at run time.  The \File{StarterLog} will
now always print the docker command line for the start and create,
and not the run that it used to.
\Ticket{6377}

\item When docker universe reports memory usage, it now reports the
RSS (Resident Set Size) of the container, previously it reported
RSS + page cache size
\Ticket{6430}

\item Added support for both user and daemon authentication using the MUNGE service.
\Ticket{6404}

\item Added a new \Opt{-macro} argument to \Condor{config\_val}.  This argument causes
\Condor{config\_val} to show the results of doing \Expr{\$()} expansion of its arguments
as if they were the result of a look up rather than the names of configuration variables
to look up.
\Ticket{6416}

\item CErequirements for the BLAHP can now be expressed in a simple form
such as a string or nested ClassAd.
\Ticket{6133}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug introduced in 8.7.0 where the job attributes RemoteUserCpu
and RemoteSysCpu where never updated in the history file, or in condor\_q
output.  The user log would show the correct values.
\Ticket{6426}

\item The new behavior of the \Opt{-expand} command line argument of \Condor{config\_val} was breaking some
scripts, so that functionality has been moved and \Opt{-expand} reverted to the pre 8.7.2 behavior.
\Ticket{6416}

\item Grid type boinc jobs are now considered running when they are reported as
IN\_PROGRESS.
\Ticket{6405}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-7-3}Version 8.7.3}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.7.3 released on September 12, 2017.

\end{itemize}

\noindent Known Issues:

\begin{itemize}

\item Our current implementation of late materialization is incompatible with
\Condor{dagman} and will cause unexpected behavior, including failing without
warning. This is a top-priority issue which aim to resolve in an upcoming
release.
\Ticket{6292}

\end{itemize}

\noindent New Features:

\begin{itemize}

\item Changed \Condor{top} tool
to monitor the \Condor{schedd} by default,
to show more useful columns in the default view,
to better format output when redirected or piped, and
to optionally take input of two ClassAd files.
\Ticket{6352}

\item Changed how \Expr{auto} works for \MacroNI{ENABLE\_IPV4} and
\MacroNI{ENABLE\_IPV6}.  HTCondor now ignores addresses that are likely
to be useless (loopback or link-local) unless no address is likely to be
useful (private or public).
\Ticket{6348}

\item Added support for Public Input Files in HTCondor jobs. This allows
users to transfer input files over a publicly-available HTTP web service,
which can benefit from caching proxies, load balancers, and other tools
to improve file transfer performance.
\Ticket{6356}

\item Added \Opt{-grid:ec2} to \Condor{q} to avoid truncating AWS' new,
longer, instance IDs.  Replaced useless (given the instance ID) instance
host name with the CMD column, to help distinguish EC2 jobs from each other.
\Ticket{5478}

\item Added statistical output for job input files transferred from web servers
using the curl\_plugin tool. Statistics are stored in ClassAd format, saved by
default to a transfer\_history file in the local logs folder.
\Ticket{6229}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed some small memory leaks in the HTCondor daemons.
\Ticket{6361}

\item Fixed a bug that would prevent dollar-dollar expansion from
working correctly for parallel universe jobs running on partitionable
slots.
\Ticket{6370}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-7-2}Version 8.7.2}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.7.2 released on June 22, 2017.

\end{itemize}

\noindent Known Issues:

\begin{itemize}

\item Our current implementation of late materialization is incompatible with
\Condor{dagman} and will cause unexpected behavior, including failing without
warning. This is a top-priority issue which aim to resolve in an upcoming
release.
\Ticket{6292}

\end{itemize}

\noindent New Features:

\begin{itemize}

\item Improved the performance of the \Condor{schedd} by setting the
default for the knob \MacroNI{SUBMIT\_SKIP\_FILECHECKS} to true.  This prevents
the \Condor{schedd} from checking the readability of all input files, and skips
the creation of the output files on the submit side at submit time.
Output files are now created either at transfer time, when file transfer
is on, or by the job itself, if a shared filesystem is used.  As a result
of this change, it is possible that a job will run to completion, and only
then is put on hold because the output file on the submit machine cannot
be written.
\Ticket{6220}

\item Changed \Condor{submit} to not create empty stdout and stderr files before
submitting jobs by default.  This caused confusion for users, and slowed down
the submission process.  The older behavior, where \Condor{submit} would fail
if it could not create this files, is available when the parameter
\MacroNI{SUBMIT\_SKIP\_FILECHECKS} is set to false.  The default is now true.
\Ticket{6220}

\item \Condor{q} will now show expanded totals when querying a \Condor{schedd} that is version 8.7.1 or later.
The totals for the current user and for all users are provided by the \Condor{schedd}.
To get the old totals display set the configuration parameter \MacroNI{CONDOR\_Q\_SHOW\_OLD\_SUMMARY} to true.
\Ticket{6254}

\item The \Condor{annex} tool now logs to the user configuration directory.  Added an
audit log of \Condor{annex} commands and their results.
\Ticket{6267}

\item Changed \Condor{off} so that the \Expr{-annex} flag implies the
\Expr{-master} flag, since this is more likely to be the right thing.
\Ticket{6266}

\item Added \Expr{-status} flag to \Condor{annex}, which reports on
instances which are running but not in the pool.
\Ticket{6257}

\item If invoked with an annex name and duration (but not an instance or slot
count), \Condor{annex} will now adjust the duration of the named annex.
\Ticket{6161}

\item Job input files which are downloaded from http:// web addresses now
have mechanisms to recover from transfer failures. This should increase the
reliability of using web-based input files, especially under slow and/or
unstable network conditions.
\Ticket{5886}

\item Reduced load on the \Condor{collector} by optimizing queries performed when
an HTCondor daemon needs to look up the address of another daemon.
\Ticket{6223}

\item Reduced load on the \Condor{collector} by optimizing queries performed
when using \condor{q} with several different command-line options such as
\Opt{-submitter} and \Opt{-global}.
\Ticket{6222}

\item Added the \Condor{top} tool,
an automated version of the now-defunct \Condor{top.pl}
which uses the python bindings to monitor the status of daemons.
\Ticket{6205}

\item Added a new option \Opt{-cron} to \Condor{gpu\_discovery} that allows it to be
used directly as an executable of a \Condor{startd} cron job.
\Ticket{6012}

\item The configuration variable \MacroNI{MAX\_RUNNING\_SCHEDULER\_JOBS\_PER\_OWNER}
was set to default to 100. It formerly had no default value.
\Ticket{6260}

\item Added a parameter \MacroNI{DEDICATED\_SCHEDULER\_USE\_SERIAL\_CLAIMS} which
defaults to false.  When true, allows the dedicated schedule to use claimed/idle
slots that the serial scheduler has claimed.
\Ticket{6276}

\item The \Condor{advertise} tool now assumes an update command if one is not
specified on the command-line and attempts to determine exact command by
inspecting the first ad to be advertised.
\Ticket{6296}

\item Improved support for running several \Condor{negotiator}s in a
single pool.
\MacroNI{NEGOTIATOR\_NAME} now works like \MacroNI{MASTER\_NAME}.
\Condor{userprio} has a -name option to select a specific
\Condor{negotiator}.
Accounting ads from multiple \Condor{negotiator}s can co-exist in the
\Condor{collector}.
\Ticket{5717}

\item Package EC2 Annex components in the condor-annex-ec2 sub RPM.
\Ticket{6202}

\item Added configuration parameter \MacroNI{ALTERNATE\_JOB\_SPOOL},
an expression evaluated against the job ad, which specifies an alternate
spool directory to use for files related to that job.
\Ticket{6221}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item With an empty configuration file, HTCondor would behave as if
\MacroNI{ALLOW\_ADMINISTRATOR} were \Expr{*}.  Changed the default to
\Expr{\$(CONDOR\_HOST)}, which is much less insecure.
\Ticket{6230}

\item Fixed a bug in the \Condor{schedd} where it did not account for the initial state of
late materialize jobs when calculating the running totals of jobs by state. This bug
resulted in \Condor{q} displaying incorrect totals when \MacroNI{CONDOR\_Q\_SHOW\_OLD\_SUMMARY}
was set to false.
\Ticket{6272}

\item Fixed a bug where the \Condor{schedd} would incorrectly try to check the
validity of output files and directories for late materialize jobs. The \Condor{schedd}
will now always skip file checks for late materialize jobs.
\Ticket{6246}

\item Changed the output of the \Condor{status} command so that the Load Average
field now displays the load average of just the condor job running in that
slot.  Previously, load associated from outside of condor was proportionately
distributed into the condor slots, resulting in much confusion.
\Ticket{6225}

\item Illegal chars ('+', '.') are now prohibited in DAGMan node names.
\Ticket{5966}

\item Improve audit log messages by including the connection ID and properly
filtering out shadow and gridmanager modifications to the job queue log.
\Ticket{6289}

\item \Condor{root\_switchboard} has been removed from the release, since
PrivSep is no longer supported.
\Ticket{6259}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-7-1}Version 8.7.1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.7.1 released on April 24, 2017.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item Previously, when the number of forked children processing Collector
queries surpassed the maximum set by the configuration knob \MacroNI{COLLECTOR\_QUERY\_WORKERS}, the
Collector handled all new incoming queries in-processes (i.e. without
forking). As processing a query and sending out the result to the network
could take a long time, the result of servicing such queries in-process in
the Collector is likely to drop a lot of updates. So now in v8.7.1, instead of
servicing such queries in-process, they are queued up for servicing as soon as
query worker child processes become available.  The configuration knob
\MacroNI{COLLECTOR\_QUERY\_WORKERS\_PENDING} was introduced; see
section\~ref{param:CollectorQueryWorkersPending}.
\Ticket{6192}

\item Default value for \MacroNI{COLLECTOR\_QUERY\_WORKERS} changed from 2 to 4.
\Ticket{6192}

\item Introduced configuration macro
\MacroNI{COLLECTOR\_QUERY\_WORKERS\_RESERVE\_FOR\_HIGH\_PRIO} so that the
collector prioritizes queries that are important for the operation of the
pool (such as queries from the negotiator) ahead of servicing user
invocations of \Condor{status}.
\Ticket{6192}

\item Introduced configuration macro \MacroNI{COLLECTOR\_QUERY\_MAX\_WORKTIME} to
define the maximum amount of time the collector may service a query from a
client like condor\_status.  See section\~ref{param:CollectorQueryMaxWorktime}.
\Ticket{6192}

\item Added several new statistics on collector query performance into the Collector
ClassAd, including \AdAttr{ActiveQueryWorkers}, \AdAttr{ActiveQueryWorkersPeak},
\AdAttr{PendingQueries}, \AdAttr{PendingQueriesPeak}, \AdAttr{DroppedQueries},
and \AdAttr{RecentDroppedQueries}.  See section\~ref{sec:Collector-ClassAd-Attributes}.
\Ticket{6192}

\item Further refinement and initial documentation of the HTCondor Annex.
\Ticket{6147}
\Ticket{6149}
\Ticket{6150}
\Ticket{6155}
\Ticket{6157}
\Ticket{6184}
\Ticket{6196}
\Ticket{6216}
\Ticket{6218}

\item Docker universe jobs can now use condor\_chirp command
(if it is in the image).
\Ticket{6162}

\item In the Job Router, when a candidate job matches multiple routes,
the first route is now always selected.
The old behavior of spreading jobs across all matching routes round-robin
style can be enabled by setting the new configuration parameter
\MacroNI{JOB\_ROUTER\_ROUND\_ROBIN\_SELECTION} to \Expr{True}.
\Ticket{6190}

\item The \Condor{schedd} now keeps a count of jobs by state for each owner and submitter
and will report them to \Condor{q}. Condor{q} will display these totals unless the new
configuration parameter \MacroNI{CONDOR\_Q\_SHOW\_OLD\_SUMMARY} is set to true. In 8.7.1
this parameter defaults to true.
\Ticket{6160}

\item Milestone 1 for late materialization in the \Condor{schedd} was completed. This milestone adds the
undocumented option \Opt{-factory} to \Condor{q} that can be used to submit a late materializing job cluster
to the \Condor{schedd}.  The \Condor{schedd} will refuse the submission unless the configuration parameter
\MacroNI{SCHEDD\_ALLOW\_LATE\_MATERIALIZATION} is set to true.
\Ticket{6212}

\item Increased the default value for configuration parameter
\MacroNI{NEGOTIATOR\_SOCKET\_CACHE\_SIZE} to 500.
\Ticket{6165}

\item Added new DaemonCore statistics UdpQueueDepth to measure the
number of bytes in the UDP receive queue for daemons with a UDP command port.
\Ticket{6183}

\item Improved speed of handling queries to the collector by caching the
the configuration knob SHARED\_PORT\_ADDRESS\_REWRITING.
\Ticket{6187}

\item The \Condor{collector} on Linux now handles some queries in process and some
by forking a child process. This allows it to avoid the overhead of forking to handle
queries that will take little time. The policy for deciding which queries to handle in process
is controlled by a new configuration parameter \MacroNI{HANDLE\_QUERY\_IN\_PROC\_POLICY}.
\Ticket{6191}

\item Added \Opt{-limit} option to \Condor{status} and changed the \Condor{collector} to honor it.
\Ticket{6198}

\item \Condor{submit} was changed to use the same utility library that the submit python bindings use.
This should help insure that submit via python bindings will give the same results as using \Condor{submit}.
\Ticket{6181}.

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item None.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-7-0}Version 8.7.0}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.7.0 released on March 2, 2017.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item Optimized the code that reads reads ClassAds off the wire making the maximum possible update rate
for the Collector about 1.7 times higher than it was before.
\Ticket{6105}
\Ticket{6130}

\item New statistics have been added to the Collector ad to show time spent handling queries.
\Ticket{6123}

\item Changed the formatting of the printing of ClassAd expressions with
parentheses. Now there is no space character after every open parenthesis, or
before every close parenthesis
This looks more natural, is somewhat faster for the condor to parse, and
saves space.  That is, an expression that used to print like

\begin{verbatim}
( ( ( foo ) ) )
\end{verbatim}
now will print like this
\begin{verbatim}
(((foo)))
\end{verbatim}
\Ticket{6082}

\item Technology preview of the HTCondor Annex. The HTCondor Annex allows one
to extend their HTCondor pool into the cloud.
\URL{https://htcondor-wiki.cs.wisc.edu/index.cgi/wiki?p=HowToUseCondorAnnexWithOnDemandInstances}
\Ticket{6121}

\item Added \Opt{-annex} option to \Condor{status} and \Condor{off}.  Requires
an argument; the request is constrained to match machines whose
\Expr{AnnexName} ClassAd attribute matches the argument.
\Ticket{6116}
\Ticket{6117}

\item A refreshed X.509 proxy is now forwarded to the remote cluster
in Bosco.
\Ticket{5841}

\item Added several new statistics to the Negotiator ad, mainly
detailing how time is spent in the negotiation cycle.
\Ticket{6060}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Removed redundant updates to the job queue by the Job Router.
\Ticket{6102}

\end{itemize}

