%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!
%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!
%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!
%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!
%%%      PLEASE RUN A SPELL CHECKER BEFORE COMMITTING YOUR CHANGES!

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Stable Release Series 8.8}\label{sec:History-8-8}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This is the stable release series of HTCondor.
As usual, only bug fixes (and potentially, ports to new platforms)
will be provided in future 8.8.x releases.
New features will be added in the 8.9.x development series.

The details of each version are described below.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-8-3}Version 8.8.3}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.8.3 not yet released.
%\item HTCondor version 8.8.3 released on Month Date, 2019.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item The performance of HTCondor's File Transfer mechanism has improved when
sending multiple files, especially in wide-area network settings.
\Ticket{7000}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug with singularity jobs where TMPDIR was set to the wrong
value.  It is now set the the scratch directory inside the container.
\Ticket{6991}

\item Fixed a bug when pid namespaces where enabled and vanilla checkpointing
was also enabled that caused one copy of the pid namespace wrapper to wrap
the job per each checkpoint restart.
\Ticket{6986}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-8-2}Version 8.8.2}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.8.2 released on April 11, 2019.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item Added a new parameter \Macro{SINGULARITY\_IS\_SETUID}, which defaults
to true.  If false, allows \Condor{ssh\_to\_job} to work when Singularity
is configured to run without the setuid wrapper.
\Ticket{6931}

\item The negotiator parameter \Macro{NEGOTIATOR\_DEPTH\_FIRST}
has been added which, when using partitionable slots, fill each
machine up with jobs before trying to use the next available machine.
\Ticket{5884}

\item The Python bindings \Code{ClassAd} module has
a new \Procedure{printJson} method to serialize a ClassAd
into a string in JSON format.
\Ticket{6950}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Support for the \Condor{ssh\_to\_job} command, when ssh'ing to a 
Singularity job, requires the nsenter command.  Previous versions of HTCondor
relied on features of nsenter not universally available.  8.8.2 now
works with all known versions of nsenter.
\Ticket{6934}

\item Moved the execution of \Macro{USER\_JOB\_WRAPPER} with Singularity jobs
to be executed outside the container, not inside the container.
\Ticket{6904}

\item Fixed a bug where \Condor{ssh\_to\_job} would not work to a Docker 
universe job when file transfer was off.
\Ticket{6945}

\item Included a patch from the development series that fixes problems that
could crash \Condor{annex} to crash.
\Ticket{6980}

\item Fixed a bug that could cause the \File{job\_queue.log} file to
be corrupted when the \Condor{schedd} compacts it.
\Ticket{6929}

\item The \Condor{userprio} command, when given the -negotiator and -l options
used to emit the value of the concurrency limits in the one large ClassAd it
printed.  This was removed in 8.8.0, but has been restored in 8.8.2.
\Ticket{6948}

\item In some situations, the GPU monitoring code could disagree with the
GPU discovery code about the mapping between GPU device indices and actual
devices.  Both now use PCI bus IDs to establish the mapping.  One consequence
of this change is that we now prefer to use NVidia's management library,
rather than the CUDA run-time library, when doing discovery.
\Ticket{6903}
\Ticket{6901}

\item  Corrected documentation of \MacroNI{CHIRP\_DELAYED\_UPDATED\_PREFIX};
it is neither singular nor a prefix.  Also resolved a problem where
administrators had to specify each attribute in that list, rather than via
prefixes or via wildcards.
\Ticket{6958}

\item The Condor{master} now waits until the \Condor{procd} has exited before exiting itself. This change
helps to prevent problems on Windows with using the Service Control Manager to restart the Condor service.
\Ticket{6952}

\item Fixed a bug on Windows that could cause a delay of up to 2 minutes in responding
to \Condor{reconfig}, \Condor{restart} or \Condor{off} commands when using shared port.
\Ticket{6960}

\item Fixed a bug that could cause the \Condor{schedd} on Windows to to restart with the message
"fd\_set is full".  This change reduces that maximum number of active connections that
a \Condor{collector} or \Condor{schedd} on Windows will allow from 1023 to 1014.
\Ticket{6957}

\item Fixed a bug where local universe jobs where unable to run
\Condor{submit} to their local schedd.
\Ticket{6920}

\item Restored the old Python bindings for reading the job event log
(\Code{EventIterator} and \Code{read\_events()}).
These bindings are marked as deprecated, are not available in
Python 3, and will likely be removed permanently in the 8.9 series.
Users should transition to the replacement bindings (\Code{JobEventLog})
\Ticket{6939}

\item Fixed a bug that could cause entries in the job event log to be
written with the wrong job id when a \Condor{shadow} process is used to
run multiple jobs.
\Ticket{6919}

\item In some situations, the bytes sent and bytes received values in
the termination event of the job event log could be reversed.
This has been fixed.
\Ticket{6914}

\item For grid universe jobs of type \Expr{batch}, the job now receives a
signal when the batch system wants it to exit, giving the job a chance to
shut down gracefully.
\Ticket{6915}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-8-1}Version 8.8.1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.8.1 released on February 19, 2019.

\end{itemize}

\noindent Known Issues:

\begin{itemize}

\item GPU resource monitoring is no longer enabled by default after we
received reports indicating excessive CPU usage.  We believe we've fixed
the problem, but would like to get updated reports from users who were
previously affected.  To enable (the patched) GPU resource monitoring,
add `use feature: GPUsMonitor' to the HTCondor configuration.  Thank you.

\Ticket{6857}

\item Discovered a bug in DAGMan where graph metrics reporting could sometimes 
send the \Condor{dagman} process into an infinite loop. We worked around this 
by disabling graph metrics reporting by default, via the new  
\Macro{DAGMAN\_REPORT\_GRAPH\_METRICS} configuration knob.
\Ticket{6896}

\end{itemize}


\noindent New Features:

\begin{itemize}

\item None.

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a bug that caused \Condor{gpu\_discovery} to report the wrong value
for DeviceMemory and possibly other attributes of the GPU when CUDA 10 was
installed as the default run-time.  Also fixed a bug that would sometimes cause
the reported value of DeviceMemory to be limited to 4 Gigabytes.
\Ticket{6883}

\item Fixed bug that prevented HTCondor on Windows from running jobs in the
default configuration when started as a service.
\Ticket{6853}

\item The Job Router no longer sets an incorrect \Attr{User} job
attribute when routing a job between two \Condor{schedd}s with
different values for configuration parameter \MacroNI{UID\_DOMAIN}.
\Ticket{6856}

\item Made Collector.locateAll() method more efficient in the Python
bindings.
\Ticket{6831}

\item Improved efficiency of negotiation code in the \Condor{schedd}.
\Ticket{6834}

\item The new \Expr{minihtcondor} package now starts HTCondor automatically
at after installation.
\Ticket{6888}

\item The \Condor{master} now sends status updates to \Prog{systemd} every 10
seconds.
\Ticket{6888}

\item \Condor{q} -autocluster data is now much more up-to-date.
\Ticket{6833}

\item In order to work better with HTCondor 8.9.1 and later, remove support
for remote submission to \Condor{schedd}s older than version 7.5.0.
\Ticket{6844}

\item Fixed a bug that would cause DAGMan jobs to fail when using Kerberos Authentication on Debian or Ubuntu.
\Ticket{6917}

\item Fixed a bug that caused execute nodes to ignore config knob \Macro{CREDD\_POLLING\_TIMEOUT}.
\Ticket{6887}

\item Python binding API method Schedd.submit() and submitMany() now edits job \Attr{Requirements}
expression to consider the job ad's \Attr{RequestCPUs} and \Attr{RequestGPUs} attributes.
\Ticket{6918}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{\label{sec:New-8-8-0}Version 8.8.0}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Release Notes:

\begin{itemize}

\item HTCondor version 8.8.0 released on January 3, 2019.

\end{itemize}


\noindent New Features:

\begin{itemize}

\item Provides a new package: \Expr{minicondor} on Red Hat based systems and
\Expr{minihtcondor} on Debian and Ubuntu based systems.
This mini-HTCondor package configures HTCondor to work on a single machine.
\Ticket{6823}

\item Made the Python bindings' \PyBindNI{JobEvent} API more Pythonic by
handling optional event attributes as if the \PyBindNI{JobEvent} object
were a dictionary, instead.  See section \ref{Python-JobEventLog} for details.
\Ticket{6820}

\item Added job ad attribute \MacroNI{BlockReadKbytes} and \MacroNI{BlockWriteKybtes}
which describe the number of kbytes read and written by the job to the sandbox
directory.  These are only defined on Linux machines with cgroup support enabled
for vanilla jobs.
\Ticket{6826}

\item The new \Attr{IOWait} attribute gives the I/O Wait time recorded by the
cgroup controller.
\Ticket{6830}

\item \Condor{ssh\_to\_job} is now configured to be more secure. In particular,
it will only use FIPS 140-2 approved algorithms.
\Ticket{6822}

\item Added configuration parameter \MacroNI{CRED\_SUPER\_USERS},
a list of users who are permitted to store credentials for any user
when using the \Condor{store\_credd} command. Normally, users can
only store credentials for themselves.
\Ticket{6346}

\item For packaged HTCondor installations, the package version is now present
in the HTCondor version string.
\Ticket{6828}

\end{itemize}

\noindent Bugs Fixed:

\begin{itemize}

\item Fixed a problem where a daemon would queue updates indefinitely when another
daemon is offline.
This is most noticeable as excess memory utilization when a \Condor{schedd} is
trying to flock to an offline HTCondor pool.
\Ticket{6837}

\item Fixed a bug where invoking the Python bindings as root could change
the effective uid of the calling process.
\Ticket{6817}

\item Jobs in REMOVED status now properly leave the queue when
evaluation of their \Attr{LeaveJobInQueue} attribute changes from
\Expr{True} to \Expr{False}.
\Ticket{6808}

\item Fixed a rarely occurring bug where the \Condor{schedd} would crash when
jobs were submitted with a \Expr{queue} statement with multiple keys.
The bug was introduced in the 8.7.10 release.
\Ticket{6827}

\item Fixed a couple of bugs in the job event log reader code that were made visible by
the new JobEventLog python object. The remote error and job terminated event did not read
all of the available information from the job log correctly. 
\Ticket{6816}
\Ticket{6836}

\item On Debian and Ubuntu systems, the templates for \Condor{ssh\_to\_job} and
interactive submits are no longer installed in \File{/etc/condor}.
\Ticket{6770}

\end{itemize}

