\section{Upgrading from the 8.6 series to the 8.8 series of HTCondor}\label{sec:to-8.8}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\index{upgrading!items to be aware of}
Upgrading from the 8.6 series of HTCondor to the 8.8 series
will bring new features introduced in the 8.7 series of HTCondor.
These new features include the following (note that this list contains
only the most significant changes; a full list of changes can be
found in the version history:~\ref{sec:History-8-7}):

\begin{itemize}

\item \Condor{annex} is tool to help users and administrators use cloud
resources to run HTCondor jobs.
It automates the processes of acquiring those resources, securely configuring
them to safely join the local pool, and ensuring that they shut down when up or
idle for too long.
It presently works only with AWS.

\item The Python bindings now include submit functionality.
\Ticket{6679}
\Ticket{6649}

\item Added a new tool, \Condor{now}, which tries to run the specified job
\emph{now}.  You specify two jobs that you own from the same \Condor{schedd}: the
now-job and the vacate-job.  The latter is immediately vacated; after the
vacated job terminates, if the \Condor{schedd} still has the claim to the vacated job's
slot (and it usually will), the \Condor{schedd} will immediately start the now-job on
that slot.  The now-job must be idle and the vacate-job must be running.  If
you're a queue super-user, the jobs must have the same owner, but that owner
doesn't have to be you.
\Ticket{6659}

\item Provides a new package, \Expr{minicondor} on Red Hat based systems and
\Expr{minihtcondor} on Debian and Ubuntu based systems.
This mini-HTCondor package configures HTCondor to work on a single machine.
\Ticket{6823}

\item HTCondor now tracks and reports GPU Usage and GPU memory usage.
\Ticket{6477}
\Ticket{6544}

\item Several performance enhancements in the collector.

\item The grid universe can now be used to create and manage VM instances
in Microsoft Azure, using the new grid type \SubmitCmdNI{azure}.
\Ticket{6176}

\item Added support for both user and daemon authentication using the MUNGE service.
The MUNGE security method is now supported on all Linux platforms.
\Ticket{6404}

\end{itemize}

Upgrading from the 8.6 series of HTCondor to the 8.8 series will
also introduce changes that administrators and users of sites running
from an older HTCondor version should be aware of when planning an upgrade.
Here is a list of items that administrators should be aware of.

\begin{itemize}

\item In the Job Router, when a candidate job matches multiple routes,
the first route is now always selected.
The old behavior of spreading jobs across all matching routes round-robin
style can be enabled by setting the new configuration parameter
\MacroNI{JOB\_ROUTER\_ROUND\_ROBIN\_SELECTION} to \Expr{True}.
\Ticket{6190}

\item \MacroNI{PREEMPTION\_REQUIREMENTS} in the negotiator no longer has a hard-coded
check that the preempting user has a better fair-share user priority
than the running user.
\Ticket{4699}

Overly-lax expressions (\Expr{True} being the worst) will lead to slots
being preempted every negotiation cycle.
One of the following clauses should be in the expression:

For pools with fair-share only:
\begin{verbatim}
  RemoteUserPrio > TARGET.SubmitterUserPrio * 1.2
\end{verbatim}

For pools with groups and quotas:
\begin{verbatim}
  (SubmitterGroupResourcesInUse < SubmitterGroupQuota) && (RemoteGroupResourcesInUse > RemoteGroupQuota)
\end{verbatim}

\end{itemize}
