%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:contributions}Contributions and Acknowledgments}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\index{HTCondor!contributions}
The quality of the HTCondor project is enhanced by the contributions
of external organizations.
We gratefully acknowledge the following contributions. 

\begin{itemize}

\item{The Globus Alliance} (\URL{http://www.globus.org}), 
for code and assistance in developing HTCondor-G
and the Grid Security Infrastructure (GSI)
for authentication and authorization. 

\item{The GOZAL Project}
from the Computer Science Department
of the Technion Israel Institute of Technology
(\URL{http://www.technion.ac.il/}),
for their enhancements for HTCondor's High Availability.
The \Condor{had} daemon allows one of multiple machines to function
as the central manager for a HTCondor pool.
Therefore, if an acting central manager fails,
another can take its place.

%\item{INFN} (\URL{http://www.infn.it/})
%and EGEE (\URL{http://public.eu-egee.org/}), 
%for for the PBS and LSF GAHP.

\item{Micron Corporation} (\URL{http://www.micron.com/})
for the MSI-based installer for HTCondor on Windows.

\item{Paradyn Project} (\URL{http://www.paradyn.org/})
%and the Universitat Autònoma de Barcelona
and the Universitat Aut\`{o}noma de Barcelona
(\URL{http://www.caos.uab.es/}) for work on the Tool Daemon Protocol (TDP).

\end{itemize}

Our Web Services API acknowledges the use of gSOAP with their
requested wording:

\begin{itemize}
\item
Part of the software embedded in this product is gSOAP software.
Portions created by gSOAP are Copyright (C) 2001-2004 Robert A. van Engelen, Genivia inc. All Rights Reserved.

THE SOFTWARE IN THIS PRODUCT WAS IN PART PROVIDED BY GENIVIA INC AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE AUTHOR BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.

\item
Some distributions of HTCondor include the Google Coredumper library
(\URL{http://goog-coredumper.sourceforge.net/}).  The Google Coredumper
library is released under these terms:

Copyright (c) 2005, Google Inc. \\
All rights reserved.

Redistribution and use in source and binary forms, with or without
modification, are permitted provided that the following conditions are
met:

	\begin{itemize}
    \item Redistributions of source code must retain the above copyright
notice, this list of conditions and the following disclaimer.

    \item Redistributions in binary form must reproduce the above
copyright notice, this list of conditions and the following disclaimer
in the documentation and/or other materials provided with the
distribution.

    \item Neither the name of Google Inc. nor the names of its
contributors may be used to endorse or promote products derived from
this software without specific prior written permission.
	\end{itemize}

THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
"AS IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR
A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT
OWNER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT
LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE,
DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY
THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{HTCondor!acknowledgments}
The HTCondor project wishes to acknowledge the following:

\begin{itemize}

\item This material is based upon work supported by the 
National Science Foundation under Grant Numbers
MCS-8105904, OCI-0437810, and OCI-0850745. 
Any opinions, findings, and conclusions or recommendations expressed 
in this material are those of the author(s) and do not necessarily 
reflect the views of the National Science Foundation.

\end{itemize}
