% include capabilities of:  CondorView  Flocking
%                           MW  DAGMan Glidein
% mention variety of platforms available

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:overview}High-Throughput Computing (HTC) and its Requirements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\index{Condor!overview|(}
\index{overview|(}
For many research and engineering projects, the quality of the research
or the product is heavily dependent upon the quantity of computing
cycles available.
It is not uncommon to find problems that require weeks
or months of computation to solve.
Scientists and engineers engaged in
this sort of work need a computing environment that delivers large
amounts of computational power over a long period of time.
Such an environment is called a High-Throughput Computing (HTC) environment.
\index{High-Throughput Computing (HTC)}
\index{HTC (High-Throughput Computing)}
In contrast, High Performance Computing (HPC)
\index{High-Performance Computing (HPC)}
\index{HPC (High-Performance Computing)}
environments deliver a
tremendous amount of compute power over a short period of time.
HPC environments are often measured in terms of FLoating point Operations
Per Second (FLOPS). 
A growing community is not concerned about operations per second,
but operations per month or per year.
Their problems are of a much larger scale.
They are
more interested in how many jobs they can complete over a long period of
time instead of how fast an individual job can complete.

The key to HTC is to efficiently harness the use of all available
resources. Years ago, the engineering and scientific community relied on
a large, centralized mainframe or a supercomputer to do
computational work. 
A large number of individuals and groups needed
to pool their financial resources to afford such a machine.
Users had to wait for their turn on the mainframe, 
and they had a limited amount of time allocated.
While this environment was inconvenient for users,
the utilization of the mainframe was high;
it was busy nearly all the time.

As computers became smaller, faster, and cheaper, 
users moved away from centralized mainframes and purchased personal desktop
workstations and PCs.
An individual or small group could afford a
computing resource that was available whenever they wanted it.
The personal computer is slower than the large centralized machine,
but it provides exclusive access.
Now, instead of one giant computer for a large institution,
there may be hundreds or thousands of personal computers.
This is an environment of distributed ownership,
\index{distributed ownership!of machines}
where individuals throughout an organization own their own resources.
The total computational power of the institution as a whole may rise
dramatically as the result of such a change,
but because of distributed ownership,
individuals have not been able to capitalize on the institutional growth of
computing power.
And, while distributed ownership is more convenient for the users,
the utilization of the computing power is lower.
Many personal desktop
machines sit idle for very long periods of time while their owners are
busy doing other things (such as being away at lunch, in meetings,
or at home sleeping). 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:what-is-condor}Condor's Power}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Condor is a software system that creates a High-Throughput Computing
(HTC) environment.
It effectively utilizes the computing power of workstations that
communicate over a network.
Condor can manage a dedicated cluster of workstations.
Its power comes from the
ability to effectively harness non-dedicated,
preexisting resources under distributed ownership. 
\index{distributed ownership!of machines}

A user submits the job to Condor.
Condor finds an available machine on the network and begins
running the job on that machine.
Condor has the capability to detect that a machine running a Condor job
is no longer available (perhaps because the owner of the machine
came back from lunch and started typing on the keyboard).
It can checkpoint 
\index{checkpoint}
the job and move (migrate)
\index{migration}
the jobs to a different machine which would otherwise be idle.
Condor continues job on the new machine from
precisely where it left off.

In those cases where Condor can checkpoint and migrate a job,
Condor makes it easy to maximize the number of machines which can run
a job.
In this case, there is no requirement for machines to
share file systems (for example, with NFS or AFS),
so that machines across an entire enterprise can run a job,
including machines in different administrative domains.

Condor can be a real time saver when a job
must be run many (hundreds of) different times,
\index{job!multiple data sets}
perhaps with hundreds of different data sets.
With one command, all of the hundreds of jobs are submitted to Condor.
Depending upon the number of machines in the Condor pool,
dozens or even hundreds of otherwise idle machines
can be running the job at any given moment.

Condor does not require an account (login) on machines where it runs a job.
Condor can do this because of its \Term{remote system call}
\index{remote system call}
technology,
which traps
library calls for such operations as reading or writing from disk
files.
The calls are transmitted over the network to be performed on the machine
where the job was submitted.

\index{Condor!resource management}
\index{resource!management}
Condor provides powerful resource management by
match-making resource
\index{matchmaking}
owners with resource consumers.
This is the cornerstone of a successful HTC environment.
Other compute cluster resource management
systems attach properties to the job queues themselves,
resulting in user confusion over which queue to use as well as administrative
hassle in constantly adding and editing queue properties to satisfy user
demands.
Condor implements 
\Term{ClassAds},
\index{ClassAd}
a clean design that simplifies the user's submission of jobs.

ClassAds work in a fashion similar to the newspaper classified
advertising want-ads. All machines in the Condor pool advertise their
resource properties, both static and dynamic,
such as available RAM memory, CPU type, CPU speed,
virtual memory size, physical location, and current load average,
in a \Term{resource offer} ad.
\index{resource!offer}
A user specifies a \Term{resource request} ad
\index{resource!request}
when submitting a job.
The request defines both the required and a desired set of properties
of the resource to run the job.
Condor acts as a broker by matching and ranking resource
offer ads with resource request ads, making certain that all
requirements in both ads are satisfied.
During this match-making process,
Condor also considers several layers of priority values:
the priority the user assigned to the resource request ad,
the priority of the user which submitted the ad,
and desire of
machines in the pool to accept certain types of ads over others. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Exceptional Features}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
	\item[Checkpoint and Migration.] Where programs can be
linked with Condor libraries, users of Condor may be assured that
their jobs will eventually complete,
even in the ever changing environment that Condor
utilizes.
As a machine running a job submitted to Condor
becomes unavailable,
the job can be check pointed.
\index{checkpoint}
The job may continue after migrating 
\index{migration}
to another machine.
Condor's periodic checkpoint feature 
\index{checkpoint!periodic}
periodically checkpoints a job even in lieu of migration in order to
safeguard the accumulated computation time on a job from being lost in the
event of a system failure such as the machine being shutdown or a crash.
	\item[Remote System Calls.] 
\index{remote system call}
Despite running jobs on remote machines,
the Condor standard universe execution
mode preserves the local execution environment
via remote system calls. Users do not have to worry
about making data files available to remote workstations or even
obtaining a login account on remote workstations before Condor executes
their programs there. The program behaves under Condor as if it were
running as the user that submitted the job on the workstation where it
was originally submitted, no matter on which machine it really ends up
executing on.
	\item[No Changes Necessary to User's Source Code.] No special
programming is required to use Condor.
Condor is able to run non-interactive programs.
The checkpoint and migration of
programs by Condor is transparent and automatic, as is the use of
remote system calls.
If these facilities are desired, the user only
re-links the program.  The code is neither recompiled nor changed.
	\item[Pools of Machines can be Hooked Together.] Flocking is
a feature of Condor that allows jobs submitted within a first pool of
Condor machines to execute on a second pool.
The mechanism is flexible, following requests from the job
submission,
while allowing the second pool, or a subset of machines within
the second pool to set policies over the conditions under
which jobs are executed.
	\item[Jobs can be Ordered.] The ordering of job execution
required by dependencies among jobs in a set is easily handled.
The set of jobs is specified using a directed acyclic graph,
where each job is a node in the graph.
Jobs are submitted to Condor following the dependencies given
by the graph.
	\item[Condor Enables Grid Computing.] As grid computing
becomes a reality, Condor is already there.
The technique of glidein allows jobs submitted to Condor
to be executed on grid machines in various locations worldwide.
As the details of grid computing evolve, so does Condor's
ability, starting with Globus-controlled resources.
	\item[Sensitive to the Desires of Machine Owners.] The
owner of a machine has complete priority over the use
of the machine.
An owner is generally happy to let others compute on
the machine while it is idle, but wants it back
promptly upon returning. The owner does not want to take special
action to regain control. Condor handles this automatically. 
	\item[ClassAds.]The ClassAd mechanism 
\index{ClassAd}
in Condor provides an extremely
flexible, expressive framework for matchmaking
resource requests with resource offers.
Users can easily request both job requirements and job desires.
For example, a user can require that a job run on a machine
with 64 Mbytes of RAM,
but state a preference for 128 Mbytes, if available.
A workstation owner
can state a preference that the workstation runs jobs
from a specified set of users. 
The owner can also require that there be no interactive workstation
activity detectable at certain hours before Condor could
start a job.
Job requirements/preferences and resource availability constraints can be
described in terms of powerful expressions, resulting in
Condor's adaptation to nearly any desired policy. 
\end{description}
\index{Condor!overview|)}
\index{overview|)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:current-limitations}Current Limitations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}

\index{Condor!limitations, under UNIX}
	\item[Limitations on Jobs which can Checkpointed] Although Condor can schedule and
run any type of process, Condor does have some limitations on jobs that it can
transparently checkpoint and migrate:

\input{user-man/limitations.tex}

	Note: these limitations \emph{only} apply to jobs which Condor
has been asked to transparently checkpoint.  If job checkpointing is not
desired, the limitations above do not apply.

	\item[Security Implications.] Condor does a significant amount of
	work to prevent security hazards, but loopholes are known to exist.
	Condor can be instructed to run user programs only as the UNIX
	user nobody, a user login which traditionally has very 
	restricted access.
	But even with access solely as user nobody,
	a sufficiently malicious individual could do such things as fill up
	\File{/tmp} (which is world writable) and/or gain read access to
	world readable files.
	Furthermore, where the security of machines in the pool is a
	high concern, 
	only machines where the UNIX user root on that machine can be
	trusted should be admitted into the pool.
	Condor provides the administrator with extensive security mechanisms 
	to enforce desired policies.

	\item[Jobs Need to be Re-linked to get Checkpointing and Remote System Calls] Although 
typically no source code changes are required,
Condor requires
that the jobs be re-linked with the Condor libraries to take
advantage of checkpointing and remote system calls. This often
precludes commercial software binaries from taking advantage of these services
because commercial packages rarely make their object code
available. 
Condor's other services are still available for these commercial packages.

\end{description}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:Availability}Availability}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{Condor!platforms available}
\index{available platforms}
\index{supported platforms}
\index{platforms supported}
Condor is currently available as a free download from the Internet via the World Wide Web at  
URL \URL{http://www.cs.wisc.edu/condor/downloads}.
Binary distributions of Condor version 6.x are available for the platforms 
detailed in Table~\ref{supported-platforms}.  A platform is an 
architecture/operating system combination.  
Condor binaries are available most major versions of UNIX, as well as
Windows NT.  

\index{clipped platform!definition of}
\index{clipped platform!availability}
In the table, \Term{clipped} means that Condor does not support
checkpointing or remote system calls on the given platform. 
This means that \Term{standard} jobs are not supported, only
\Term{vanilla} jobs.
See section~\ref{sec:Choosing-Universe} on
page~\pageref{sec:Choosing-Universe} for more details on job universes
within Condor and their abilities and limitations.

The Condor source code is no longer available for public download from the Internet.  If you 
desire the Condor source code, please contact the Condor Team in order to discuss it further 
(see Section~\ref{contact-info}, on page~\pageref{contact-info}).

% Karen's table
\begin{center}
\begin{table}[hbt]
\begin{tabular}{|ll|} \hline
\emph{Architecture} & \emph{Operating System} \\ \hline \hline
Hewlett Packard PA-RISC (both PA7000 and PA8000 series) & HPUX 10.20 \\
 & HPUX 11.00 (clipped) \\ \hline
Sun SPARC Sun4m,Sun4c, Sun UltraSPARC & Solaris 8, 9 \\
 & Solaris 10 (clipped), using the Solaris 9 binaries \\ \hline
Silicon Graphics MIPS (R5000, R8000, R10000) & IRIX 6.5 (clipped) \\ \hline
Intel x86 & Red Hat Linux 7.1, 7.2, 7.3, 8.0, 9 \\
 & RedHat Enterprise Linux 3 \\
 & RedHat Enterprise Linux 4 (clipped) \\
% & RedHat Enterprise Linux 4 (clipped), with \File{compat-glibc} and \File{compat-glibc-headers} packages \\
 & Debian Linux 3.1 (sarge) \\
 & Fedora Core 1 \\
 & Fedora Core 2, 3 \\
% & Fedora Core 2, 3, with \File{compat-glibc} and \File{compat-glibc-headers} packages \\
 & Windows 2000 Professional and Server (clipped) \\
 & Windows 2003 Server (Win NT 5.0) (clipped) \\
 & Windows XP Professional (Win NT 5.1) (clipped) \\ \hline
ALPHA & Tru64 5.1 (clipped) \\
 & Red Hat Linux 7.1, 7.2, 7.3 (clipped) \\ \hline
PowerPC & Macintosh OS X (clipped) \\
 & AIX 5.2 (clipped) \\ \hline
Itanium (IA64) & Red Hat Linux 7.1, 7.2, 7.3 (clipped) \\
& SuSE Linux Enterprise Server 8.1 (clipped) \\ \hline
\end{tabular}
\caption{\label{supported-platforms}Condor \VersionNotice\ supported platforms}
\end{table}
\end{center}


\Note Other Linux distributions (Debian, etc.) likely work, but are not tested
or supported.

For more platform-specific information about Condor's support for
various operating systems, see Chapter~\ref{platforms} on
page~\pageref{platforms}. 



Jobs submitted to the standard universe utilize \Condor{compile}
to relink programs with libraries provided by Condor.
Table~\ref{supported-compile} lists supported compilers by
platform.
Other compilers may work, but are not supported.

\index{Condor commands!condor\_compile!list of supported compilers}
\index{condor\_compile command!list of supported compilers}
\index{compilers!supported with condor\_compile}

% condor_compile works on. . .
\begin{center}
\begin{table}[hbt]
\begin{tabular}{|ll|l}
\textbf{Platform} & \textbf{Compiler} & \textbf{Notes}\\ \hline \hline
Solaris (all versions) on SPARC \\ 
& gcc, g++, and g77 & The entire GNU compiler suite must be versions 2.95.3 or 2.95.4. \\ 
& cc, CC & use the standard, native compiler \\ 
& f77, f90 & use the standard, native compiler \\ 
\hline
Red Hat Linux, versions 7.2, and 7.3 on Intel x86 \\ 
& gcc, g++, and g77 & as shipped \\ 
& pgf77 and pgf90, version 5.0 & Portland Group compilers \\ 
& pghpf, version 5.0 & Portland Group high performance Fortran compiler \\ 
& pgcc, version 5.0 \\ 
\hline
Red Hat Linux, version 8 on x86 \\ 
& gcc, g++, and g77 & version 3.2 \\ 
& pgf77 and pgf90, version 5.0 & Portland Group compilers \\ 
& pghpf, version 5.0 & Portland Group high performance Fortran compiler \\ 
& pgcc, version 5.0 \\ 
\hline
Red Hat Linux, version 9 on x86 & gcc, g++, and g77 & as shipped  \\ 
\hline
Red Hat Enterprise Linux 3 on x86 & gcc, g++, and g77 & as shipped  \\ 
\hline
Red Hat Debian Linux 3.1 (sarge) on x86 & gcc up to version 3.4.1 \\ 
\hline
Fedora Core 1 on x86 & gcc, g++, and g77 & as shipped  \\ 
\hline
Fedora Core 2 on x86 & gcc, g++, and g77 & as shipped  \\ 
\hline
Fedora Core 3 on x86 & gcc, g++, and g77 & as shipped  \\ 
\hline
HPUX 10.20 on HP PA-RISC (both PA7000 and PA8000)\\ 
& gcc, g++, and g77; version egcs-1.1.2 \\ 
& cc, CC, aCC & cc and aCC cannot use C++ exceptions \\ 
\hline
% Digitial Unix 4.0 on ALPHA \\ 
% & cc, CC, cxx, and c89 \\ 
% & KCC \\ 
% & gcc, g++, and g77;  version egcs-1.1.2 & We plan to support newer versions of the GNU compiler collection in the near future.\\ 
% & gcc, g++, and g77;  version 2.95.3 \\ 
% \hline
\end{tabular}
\caption{\label{supported-compile}Supported compilers under Condor \VersionNotice\ }
\end{table}
\end{center}

\index{file transfer!large files (>2Gbytes)}
\index{large file transfer support}
The following table, 
Table~\ref{large-file-support},
identifies which platforms support
the transfer of large files (greater than 2 Gbyte in length).
For vanilla universe jobs and those platforms where large file transfer is
supported, the support is automatic.

\begin{center}
\begin{table}[hbt]
\begin{tabular}{|lc|} \hline
\emph{Platform} & \emph{Large File Transfer Supported?} \\ \hline \hline
Hewlett Packard PA-RISC with HPUX 10.20 & Yes \\ \hline
Sun SPARC Sun4m,Sun4c, Sun UltraSPARC with Solaris 8, 9 & Yes \\ \hline
Silicon Graphics MIPS (R5000, R8000, R10000) with IRIX 6.5 &  Yes \\ \hline
Intel x86 with Red Hat Linux 7.1, 7.2, 7,3, 8.0, 9, Enterprise Linux 3, Debian Linux 3.1 (sarge) & Yes \\ 
Intel x86 with Fedora Core 1, 2, 3 & Yes \\
Intel x86 with Windows 2000 Professional and Server, 2003 Server (Win NT 5.0), Windows XP Professional (Win NT 5.1) & Yes \\ \hline
% ALPHA with Digital Unix 4.0 & No \\ \hline
ALPHA with  Tru64 5.1  & No \\ 
ALPHA with Red Hat Linux 7.1, 7.2, 7.3 & Yes \\ \hline
PowerPC with Macintosh OS X  & No \\
PowerPC with AIX 5.2  & Yes \\ \hline
Itanium with Red Hat Linux 7.1, 7.2, 7.3 & Yes \\
Itanium with SuSE Linux Enterprise 8.1 & Yes \\ \hline
\end{tabular}
\caption{\label{large-file-support}Supported platforms for large file transfer of vanilla universe job files}
\end{table}
\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{overview/contributions.tex} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{contact-info}Contact Information}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\index{Condor!contact information}
The latest software releases, publications/papers regarding Condor and other 
High-Throughput Computing
research can be found at the official web site for Condor at  
\URL{http://www.cs.wisc.edu/condor}.

\index{Condor!mailing lists}
\index{mailing lists}
In addition, there is an e-mail list at condor-world@cs.wisc.edu.
The Condor Team uses this e-mail list to announce new releases of
Condor and other major Condor-related news items.
To subscribe or unsubscribe from the the list, follow the instructions at  
\URL{http://www.cs.wisc.edu/condor/mail-lists/}.
Because many of us receive 
too much e-mail as it is, you will be happy to know that the
Condor World e-mail list group is 
moderated, and only major announcements of wide interest are distributed.

Our users support each other by belonging to an unmoderated mailing
list targeted at solving problems with Condor.
Condor team members attempt to monitor traffic to Condor Users,
responding as they can. 
Follow the instructions at
\URL{http://www.cs.wisc.edu/condor/mail-lists/}.

Finally, you can reach the Condor Team directly.
The Condor Team is comprised of the 
developers and administrators of Condor at the University of Wisconsin-Madison.
Condor questions, comments, pleas for help,
and requests for commercial contract consultation or support 
are all welcome;
send Internet e-mail to
\URL{mailto:condor-admin@cs.wisc.edu}.
Please include your name, organization, and telephone number in your message.
If you are having trouble with Condor,
please help us troubleshoot by including as much pertinent information
as you can, including snippets of Condor log files. 

\section{\label{privacy}Privacy Notice}

%
% Note to developers:
% If you change this text, also change
%   http://www.cs.wisc.edu/condor/privacy.html
%

The Condor software periodically sends short messages
to the Condor Project developers at the University of Wisconsin,
reporting totals of machines and jobs in each running Condor system.
An example of such a message is given below.

The Condor Project uses these collected reports to publish
summary figures and tables, such as the total of Condor systems
worldwide, or the geographic distribution of Condor systems.
This information helps the Condor Project to understand
the scale and composition of Condor in the real world
and improve the software accordingly.

The Condor Project will not use these reports to publicly
identify any Condor system or user without permission.
The Condor software does not collect or report any personal
information about individual users.

We hope that you will contribute to the development of Condor
through this reporting feature.
However, you are free to disable it at any time by
changing the configuration variables \Macro{CONDOR\_DEVELOPERS}
and \Macro{CONDOR\_DEVELOPERS\_COLLECTOR},
both described in section \ref{param:CondorDevelopers} of this manual.

Example of data reported:

\begin{verbatim}
This is an automated email from the Condor system
on machine "your.condor.pool.com".  Do not reply.

This Collector has the following IDs:
    CondorVersion: 6.6.0 Nov 12 2003
    CondorPlatform: INTEL-LINUX-GLIBC22

                     Machines Owner Claimed Unclaimed Matched Preempting

         INTEL/LINUX      810    52     716        37       0          5
       INTEL/WINNT50      120     5     115         0       0          0
     SUN4u/SOLARIS28      114    12      92         9       0          1
     SUN4x/SOLARIS28        5     1       0         4       0          0
               Total     1049    70     923        50       0          6

         RunningJobs                IdleJobs
                 920                    3868
\end{verbatim}



